### 2024-08-09 Conformal_manifolds.tex
Notes on conditons to have a flat direction

%!TEX output_directory = aux

\documentclass[11pt]{article}

\usepackage[english]{babel}

% ---- FONT & MICROTYPOGRAPHY ----
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{moresize}

% ---- FORMATTING ----
\usepackage{csquotes,textcase,xspace}

% ---- PAGE LAYOUT ----
\usepackage{geometry}
\geometry{top=2.5cm,bottom=2cm,inner=2cm,outer=2cm,footnotesep=7mm plus 4pt minus 4pt}
\usepackage{setspace}
\setstretch{1.1}

% ---- GRAPHIQUE ----
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[font=small,labelfont=bf,labelsep=space]{caption}
\usepackage{subfigure}
\captionsetup{width=0.9\textwidth,font={small,stretch=1.1}}
\addto\captionsenglish{\renewcommand{\figurename}{Fig.}}
\addto\captionsenglish{\renewcommand{\tablename}{Tab.}}
\definecolor{JoliBleu}{rgb}{0,0.55,0.55}
\definecolor{JoliVert}{rgb}{0.15,0.6,0}
\definecolor{JoliRouge}{rgb}{0.86,0.08,0}
\definecolor{JoliJaune}{rgb}{1,0.75,0}
\definecolor{JoliGris}{rgb}{0.52,0.52,0.51}
\definecolor{myblue}{RGB}{26, 77, 116}
\definecolor{myorange}{RGB}{181, 116, 30}
\definecolor{mydarkorange}{RGB}{166, 88, 0}
\definecolor{mygreen}{RGB}{21, 124, 80}
\definecolor{myblack}{RGB}{43, 65, 82}
\definecolor{myred}{rgb}{0.5, 0.0, 0.13}

% ---- SECTIONING ----
\usepackage{titlesec}
\titleformat{\section}[block]{\Large\boldmath\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\large\boldmath\bfseries}{\thesubsection}{0.5em}{}
\usepackage{appendix}
\renewcommand{\setthesection}{\Alph{section}}
\renewcommand{\restoreapp}{}
\makeatletter
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\@addtoreset{equation}{section}
\makeatother

% ---- FOOTERS HEADERS ----
\usepackage[bottom]{footmisc}
\usepackage{fancyhdr}

% ---- TABLE OF CONTENTS ----
\usepackage{titletoc}
\setcounter{tocdepth}{3}

% ---- BIBLIOGRAPHY ----
\usepackage[nosort]{cite}
\bibliographystyle{JHEP}
\newcommand{\eprint}[1]{{\href{http://arxiv.org/abs/#1}{\texttt{[#1]}}}}
\newcommand{\eprintN}[1]{{\href{http://arxiv.org/abs/#1}{\texttt{#1 [hep-th]}}}}
\newcommand{\doi}[2]{\href{http://dx.doi.org/#2}{#1}}

% ---- HYPER REF ----
\usepackage{hyperref}
\hypersetup{colorlinks=true,
        pdfstartview=FitV,
        linkcolor= mydarkorange,
        citecolor= mydarkorange,
        urlcolor= JoliGris!60!black,
        hypertexnames=false,
        linktoc=page}

% ---- TIKZ ----
\usepackage{tikz}
\usetikzlibrary{calc}

% ---- MATHS ----
\usepackage{amsmath,amssymb,amsfonts,dsfont}
\usepackage{mathrsfs}
\usepackage{physics}
\usepackage{ytableau}
\ytableausetup{boxsize=1.1em,centertableaux}
\usepackage{stmaryrd}
\usepackage{nicefrac}
\allowdisplaybreaks[1]
% \usepackage{bbold}
\usepackage{cases}
\usepackage{bm}
\usepackage{bbm}

% ---- TABLES ----
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{pdflscape}
\usepackage{array}
\usepackage{arydshln}

% ---- ENUMERATION ----
\usepackage[shortlabels]{enumitem}

% ---- MATHS COMMANDS ----
\newcommand{\A}{\ensuremath{\mathcal{A}}\xspace}
\newcommand{\F}{\ensuremath{\mathcal{F}}\xspace}
\renewcommand{\H}{\ensuremath{\mathcal{H}}\xspace}
\newcommand{\M}{\ensuremath{\mathcal{M}}\xspace}
\renewcommand{\P}{\ensuremath{\mathcal{P}}\xspace}
\newcommand{\J}{\ensuremath{\mathcal{J}}\xspace}
\renewcommand{\d}{\ensuremath{\mathrm{d}}\xspace}
\renewcommand{\H}{\ensuremath{\mathcal{H}}\xspace}
\newcommand{\SO}{\ensuremath{\mathrm{SO}}\xspace}
\renewcommand{\O}{\ensuremath{\mathrm{O}}\xspace}
\newcommand{\SL}{\ensuremath{\mathrm{SL}}\xspace}
\newcommand{\Odd}{\ensuremath{\mathrm{O}(d,d)}\xspace}
\newcommand{\odd}{\ensuremath{\mathfrak{o}(d,d)}\xspace}
\renewcommand{\Tr}[1]{\ensuremath{\mathrm{Tr}\left(#1\right)}\xspace}
\newcommand{\vol}{{\,\rm vol}}
\def\sst#1{{\scriptscriptstyle #1}}

\def\0{{\sst{(0)}}}
\def\1{{\sst{(1)}}}
\def\2{{\sst{(2)}}}
\def\3{{\sst{(3)}}}
\def\4{{\sst{(4)}}}
\def\5{{\sst{(5)}}}
\def\6{{\sst{(6)}}}
\def\7{{\sst{(7)}}}
\def\8{{\sst{(8)}}}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}

% ---- COMMENTS ----
\usepackage[subfigure]{tocloft}		
\newcommand{\listnotetitle}{\Large List of Notes}
\newlistof{notes}{nt}{\listnotetitle}
\newcommand{\notelist}[1]{%
	\refstepcounter{notes}
	\addcontentsline{nt}{notes}
	{\protect\numberline{\thenotes}#1}
}

\newcommand{\note}[1]{\notelist{#1}\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries Note: #1}}

% ---- TITLE PAGE ----
\usepackage[affil-it]{authblk}
\def\preprint{}

\makeatletter
\def\@maketitle{%
  \newpage
  \null\hfill\texttt{\preprint}
  \vskip 4em%
  \begin{center}%
  \let \footnote \thanks
    {\LARGE\bfseries \@title \par}%
    \vskip 2.5em%
    {\large
      \lineskip .5em%
      \begin{center}
        \begin{minipage}{0.95\textwidth}
            \begin{tabular}[t]{c}%
            \@author
            \end{tabular}
        \end{minipage}    
      \end{center}\par}%
    \vskip 1em%
    {\large \@date}%
  \end{center}%
  \par
  \vskip 1.5em}
\makeatother

\renewcommand\Authands{ and }

\title{Notes on conformal manifolds}
\author{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\tableofcontents

%%%%%%%%%%%%%%
%%%%%%%%%%%%%%
\section{Comments on Flat Directions and $n$-Hessians} \label{sec: hessians}
%%%%%%%%%%%%%%

Given a real function $V: M \rightarrow \mathbb R$, its critical points are defined as the zeroes of the gradient
%
\begin{equation}
	x^*: H_{m}(x^*)\equiv\partial_mV\big\vert_{x^*}=0\,,
\end{equation}
%
with the $n$-Hessian of $V(x)$ defined as
%
\begin{equation}
	H_{m_1\dots m_n}\equiv\partial_{m_1}\dots\partial_{m_n}V\,.
\end{equation}
%

Flat directions around the critical point $x^*$ are curves $\phi: I\rightarrow M$ such that
%
\begin{equation}	\label{eq: flatdef}
	H_{m}(\phi(t))=0\,,	\qquad\text{with}\quad
	\phi(0)=x^*\,.
\end{equation}
%
Close to $x^*$, the curve can be expanded as
%
\begin{equation}	\label{eq: phiSeries}
	\phi(t)=x^*+\sum_{k=1}^{\infty}\tfrac1{k!}\xi_k\, t^k\,, \qquad\text{with}\quad
	\xi_k=\frac{d^k\phi}{dt^k}\Big\vert_{x^*}\,,
\end{equation}
%
and, accordingly,
%
\begin{equation}
	\begin{aligned}
		H_{m}(\phi(t))&=\sum_{k=1}^{\infty}H_{mn_1\dots n_k}\sum_{a\in\lambda_k}t^{\sum_i^{\vert a\vert}i a_i}\bigg[\prod_{i=1}^{\vert a\vert}\frac1{a_i!}\frac{1}{\big(i!\big)^{a_i}}\xi_i^{\otimes a_i}\bigg]^{n_1\dots n_k}\,,
	\end{aligned}
\end{equation}
%
with all the $n$-Hessians on the right-hand side evaluated at $x^*$. Here, $\lambda_k$ denotes the integer partitions of $k$ (e.g. $\lambda_3=\{(3),(2,1),(1,1,1)\}$), $\vert a\vert$ is the number of elements of a specific partition $a\in\lambda_k$ (e.g. $\vert(2,1)\vert=2$ and $\vert(1,1,1)\vert=3$), and $a_i$ each of its elements. Equation \eqref{eq: flatdef} needs to be satisfied at every order in $t$, and therefore the existence of flat directions amounts to the existence solutions of the system
%
\begin{equation}	\label{eq: flateqnsAll}
	O(t^p):\quad\sum_{\{a_i\}}H_{mn_1\dots n_{k}}\prod_i^{p}\bigg[\frac1{a_i!}\frac1{\big(i!\big)^{a_i}}\xi_i^{\otimes a_i}\bigg]^{n_1\dots n_k}=0\,,
\end{equation}
%
with the set of coefficients $\{a_i\}$ determined as
%
\begin{equation}	\label{eq: as}
	\sum_i^{p}i a_i=p\,, 	\qquad
	a_i\in \mathbb{N}\,,
\end{equation}
%
and $k$ in \eqref{eq: flateqnsAll} a shorthand for $k=\sum_i^p a_i$ for the solutions of \eqref{eq: as}.
For lowest $p$, this is
%
\begin{equation}	\label{eq: flateqns}
	\begin{aligned}
		0&=H_{mn}\xi_1^n\,,		\\[5pt]
		0&=H_{mn}\xi_2^n+H_{mnp}\xi_1^n\xi_1^p\,,	\\[5pt]
		0&=H_{mn}\xi_3^n+3H_{mnp}\xi_2^n\xi_1^p+H_{mnpq}\xi_1^n\xi_1^p\xi_1^q\,,	\\[5pt]
		0&=H_{mn}\xi_4^n+3H_{mnp}\xi_2^n\xi_2^p+4H_{mnp}\xi_3^n\xi_1^p+6H_{mnpq}\xi_2^n\xi_1^p\xi_1^q+H_{mnpqr}\xi_1^n\xi_1^p\xi_1^q\xi_1^r\,,	\\[5pt]
		&\dots
	\end{aligned}
\end{equation}
%

Note that the non-linearity of \eqref{eq: flateqns} in the expansion coefficients of $\phi(t)$ implies that the number of flat directions is not easily related to the dimension of the null space of the 2-Hessian at $x^*$ (i.e. the number of massless scalars if $V$ is the scalar potential). A necessary condition for \eqref{eq: flateqnsAll} to have a solution is
%
\begin{equation}
	\det H_{mn}=0\,,		\\[5pt]
\end{equation}
%
but there can be more flat directions than zero eigenvalues and vice versa. These features will be studied in the following.

%%%%%%%%%%%%%%
\subsection{Flat flat directions} \label{sec: FFC}
%%%%%%%%%%%%%%

When flat directions can be given as straight lines $\phi(t)=x^*+\xi t$ for constant $\xi$, the set of equations \eqref{eq: flateqns} simplifies to the condition $\xi\in K_k$ for all $n\geq1$, with the kernels defined as
%
\begin{equation}	\label{eq: flatness}
	K_k=\{\xi: \xi^{n_1}\dots\xi^{n_{k}}H_{mn_1\dots n_{k}}(x^*)=0\}\,,	\qquad \forall n\geq1\,.
\end{equation}
%
This condition is required for $\partial_mV$ to be constant along the integral curve of $\xi^m$, since
%
\begin{equation}
	\begin{aligned}
		\xi^{n_k}\partial_{n_k}\big(\xi^{n_1}\dots\xi^{n_{k-1}}H_{mn_1\dots n_{k-1}}\big)\big\vert_{x^*}
		=\xi^{n_1}\dots\xi^{n_{k}}H_{mn_1\dots n_{k}}(x^*)
	\end{aligned}
\end{equation}
%
must hold for all $k\geq1$.

Two functions that have flat flat directions and exhibit the subtleties mentioned before are given by
%
\begin{equation}	\label{eq: flatflat}
	V_1(x,y)=x^4(1+y^2)\,,		\qquad\text{and}\qquad
	V_3(x,y)=y^2(x^2-3y^2)\,,
\end{equation}
%
which are plotted in Fig.~\ref{fig: flatflat}.
%
\begin{figure}
	\centering
	\includegraphics[width=0.4\textwidth]{Figures/V1.pdf}
	\qquad
	\includegraphics[width=0.4\textwidth]{Figures/V3.pdf}
	\caption{Contour plots for the potentials $V_1$ (left) and $V_3$ (right) in \eqref{eq: flatflat} with flat directions and $x^*=0$ locus superimposed.}
	\label{fig: flatflat}
\end{figure}
%
In both cases, the 2-Hessian vanishes identically at $x^*=0$, but $V_1$ only has one flat direction given by $(x,y)=(0,\zeta)$, whereas $V_3$ has three independent flat curves:
%
\begin{equation}
	(x,y)=(\zeta_1,\, 0)\,,	\qquad
	(x,y)=(\sqrt3\,\zeta_2,\, \zeta_2)\,,	\qquad
	(x,y)=(-\sqrt3\,\zeta_3,\, \zeta_3)\,.
\end{equation}
%

\note{How is the second compatible with the standard holography lore? Can this type of potentials arise in consistent truncations?}

%%%%%%%%%%%%%%
\subsection{Curved flat directions} \label{sec: FCL}
%%%%%%%%%%%%%%

(alternative name: curved flat curves)

The condition \eqref{eq: flatness} does not capture curves with a non-linear dependence on $t$. For instance,
%
\begin{equation}	\label{eq: Vcurved}
	V(x,y)=x^2(x^2-3y^4)
\end{equation}
%
has flat directions
%
\begin{equation}	\label{eq: curvedcurves}
	(x,y)=(0,\, \zeta_1)\,,	\qquad
	(x,y)=(\sqrt3\,\zeta_2^2,\, \zeta_2)\,,	\qquad
	(x,y)=(-\sqrt3\,\zeta_3^2,\, \zeta_3)\,,
\end{equation}
%
of which only the first is captured by \eqref{eq: flatness}. For the other two, the higher order terms in \eqref{eq: flateqnsAll} also contribute. To gauge-fix the reparameterisation invariance of \eqref{eq: flatdef}, we demand without loss of generality that the lowest non-vanishing term in \eqref{eq: phiSeries} is linear in $t$.  Doing so, \eqref{eq: flateqnsAll} yields \eqref{eq: curvedcurves} unambiguously. We note that for \eqref{eq: Vcurved} the first non-trivial equation arises at order $O(t^5)$, the following at $O(t^{10})$, and from then on we get a condition on every level.

This method has been checked with three other functions with flat directions:
%
\begin{equation}
	\begin{aligned}
		V(x,y)&=(y-\cos x)^2\,,	\\[5pt]
		V(x,y)&=(x^2+y^2-1)^2\,,	\\[5pt]
		V(x,y)&=x^2(x^2+y^2-1)^2\,,
	\end{aligned}
\end{equation}
%
recovering the analytic result in all instances and converging more quickly than for \eqref{eq: Vcurved} (as their series have non-zero contributions at lower orders).

\note{The distinction between the different curves in \eqref{eq: curvedcurves} disappears at linear level, and this is very reminiscent of the TsT vs Wilson loop families in \cite{Eloy:2024lwn}.}

%
\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{Figures/V3curved.pdf}
	\caption{Contour plot for the potential in \eqref{eq: Vcurved} with flat directions in \eqref{eq: curvedcurves} and $x^*=0$ locus superimposed.}
	\label{fig: curvedflat}
\end{figure}
%

%%%%%%%%%%%%%%
\section{SO(8,4) supergravity in $D=3$} \label{sec: 3dSugra}
%%%%%%%%%%%%%%

When apply the above techniques to the potential (2.26) in \cite{Eloy:2021fhc}, we recover the two-parameter family (2.27) in there. I have not managed to get anything else, but that does not mean necessarily that there isn't. It is probably more due to the fact that the system for 13 scalars is very complicated. Using the \texttt{NSolve} routine might be useful to see if there is any solution outside the known class.

\bibliography{references}

\end{document}

### 2024-12-04 Conformal_manifolds.tex

@@
 
+Workflow as of \today:
+\begin{enumerate}
+	\item Generate larger clouds of points for the 7- and 13-param potentials (Gabriel).
+	\item For these two models, get statistics of autoencoders for several attempts per dimension of latent layer (Bastien).
+	\item Go up to full 32-param SO(8,4) potential.
+\end{enumerate}
+
 \tableofcontents
@@
 and $k$ in \eqref{eq: flateqnsAll} a shorthand for $k=\sum_i^p a_i$ for the solutions of \eqref{eq: as}.
-For lowest $p$, this is
+For lowest $p$, this is \note{Can map to CFT $n$-point functions à la Bertolini?}
 %
@@
 	V_1(x,y)=x^4(1+y^2)\,,		\qquad\text{and}\qquad
-	V_3(x,y)=y^2(x^2-3y^2)\,,
+	V_3(x,y)=y^2(x^2-3y^2)^2\,,
 \end{equation}
@@
 \begin{equation}
-	(x,y)=(\zeta_1,\, 0)\,,	\qquad
+	(x,y)=(0,\, \zeta_1)\,,	\qquad
 	(x,y)=(\sqrt3\,\zeta_2,\, \zeta_2)\,,	\qquad
@@
 \note{How is the second compatible with the standard holography lore? Can this type of potentials arise in consistent truncations?}
+
+\note{We should remark that conformal manifolds are not smooth manifolds in general, but algebraic varieties. Apparently, people doing quivers know this [look at papers by Hanany]}
 
@@
 \begin{equation}	\label{eq: Vcurved}
-	V(x,y)=x^2(x^2-3y^4)
+	V(x,y)=x^2(x^2-3y^4)^2
 \end{equation}
@@
 %%%%%%%%%%%%%%
-\section{SO(8,4) supergravity in $D=3$} \label{sec: 3dSugra}
+\section{Machine Learning Approach} \label{sec: MLapproach}
 %%%%%%%%%%%%%%
 
-When apply the above techniques to the potential (2.26) in \cite{Eloy:2021fhc}, we recover the two-parameter family (2.27) in there.
-I have not managed to get anything else, but that does not mean necessarily that there isn't.
-It is probably more due to the fact that the system for 13 scalars is very complicated.
-Using the \texttt{NSolve} routine might be useful to see if there is any solution outside the known class.
+In the following, we obtain and analyse numerically the critical points of different functions $V: \mathbb{R}^n\rightarrow\mathbb{R}$. 
+In this approach, a cloud of points $x_i^m$, $m\in\llbracket1,n\rrbracket$ and $i\in\llbracket1,N\rrbracket$,
+is generated so that the loss function
+%
+\begin{equation}	\label{eq: loss_cloud}
+	L_{V}=\sum_i^N\vert \nabla_m V(x_i)\vert^2
+\end{equation}
+%
+is minimised. 
+For this minimisation, we have employed an protocol based on the \texttt{TensorFlow} Adam optimiser 
+which restarts the optimiser with the initial learning rate after a specified number of epochs until a specified loss value is attained.
+Afterwards and until the pre-determined number of epochs is reached, the learning rate decreases by a factor 10 every few epochs 
+(in the \texttt{grad\_descent\_module.py} package, the original learning rate us used by default for the first 2500 epochs with restarts every 200
+steps, and then updated every 2500 steps. These parameters need to be adapted to the potential under consideration).
 
+The structure of the resulting cloud of points minimising \eqref{eq: loss_cloud} is subseqently learnt using
+autoencoders (AEs), which are non-linear endomorphisms constructed via a neural network with an intermediate layer
+of dimension $\ell < n$, as schematically depicted in figure~\ref{fig: AE_notation}. 
+%
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[scale=3]
+		\def\xlim{.2}
+		\def\ylim{0.5}
+		\def\dist{1.2}	% distance between rectangles from center to center
+
+		% Latent layer
+		\draw[thick,fill=myorange!50] (-\xlim,-0.7*\ylim) -- (\xlim,-0.7*\ylim) -- (\xlim,0.7*\ylim) -- (-\xlim,0.7*\ylim)-- (-\xlim,-0.7*\ylim);
+		\draw (0,0.47*\ylim) circle [radius = 0.4*\xlim] node {\footnotesize{$1$}};
+		\draw (0,-0.47*\ylim) circle [radius = 0.4*\xlim] node {\footnotesize{$\ell$}};
+		\draw[thick, dotted] (0,-0.2*\ylim) -- (0,0.2*\ylim);
+
+		% Hidden layers left
+		\draw[thick,fill=myorange!50] (-1.8*\xlim-\dist,-1.2*\ylim) -- (1.8*\xlim-\dist,-1.2*\ylim) -- (1.8*\xlim-\dist,1.2*\ylim) -- (-1.8*\xlim-\dist,1.2*\ylim)-- (-1.8*\xlim-\dist,-1.2*\ylim);
+
+		\draw (-\dist-1.0*\xlim,0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$1,1$}};
+		\draw (-\dist-1.0*\xlim,-0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$1,q_1$}};
+		\draw (-\dist+1.0*\xlim,0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$p,1$}};
+		\draw (-\dist+1.0*\xlim,-0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$p,q_p$}};
+
+		\draw[thick, dotted] (-\dist+0.6*\xlim,-0.25*\ylim) -- (-\dist+0.6*\xlim,0.25*\ylim);
+		\draw[thick, dotted] (-\dist+0.2*\xlim,-0.25*\ylim) -- (-\dist+0.2*\xlim,0.25*\ylim);
+		\draw[thick, dotted] (-\dist-0.2*\xlim,-0.25*\ylim) -- (-\dist-0.2*\xlim,0.25*\ylim);
+		\draw[thick, dotted] (-\dist-0.6*\xlim,-0.25*\ylim) -- (-\dist-0.6*\xlim,0.25*\ylim);
+
+		\draw[thick, dotted] (-\dist-0.3*\xlim,0.9*\ylim) -- (-\dist+0.3*\xlim,0.9*\ylim);
+		\draw[thick, dotted] (-\dist-0.3*\xlim,-0.9*\ylim) -- (-\dist+0.3*\xlim,-0.9*\ylim);
+
+		% Hidden layers right
+		\draw[thick,fill=myorange!50] (-1.8*\xlim+\dist,-1.2*\ylim) -- (1.8*\xlim+\dist,-1.2*\ylim) -- (1.8*\xlim+\dist,1.2*\ylim) -- (-1.8*\xlim+\dist,1.2*\ylim)-- (-1.8*\xlim+\dist,-1.2*\ylim);
+
+		\draw (\dist-1.0*\xlim,0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$p,1$}};
+		\draw (\dist-1.0*\xlim,-0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$p,q_p$}};
+		\draw (\dist+1.0*\xlim,0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$1,1$}};
+		\draw (\dist+1.0*\xlim,-0.9*\ylim) circle [radius = 0.55*\xlim] node {\tiny{$1,q_1$}};
+
+		\draw[thick, dotted] (\dist+0.6*\xlim,-0.25*\ylim) -- (\dist+0.6*\xlim,0.25*\ylim);
+		\draw[thick, dotted] (\dist+0.2*\xlim,-0.25*\ylim) -- (\dist+0.2*\xlim,0.25*\ylim);
+		\draw[thick, dotted] (\dist-0.2*\xlim,-0.25*\ylim) -- (\dist-0.2*\xlim,0.25*\ylim);
+		\draw[thick, dotted] (\dist-0.6*\xlim,-0.25*\ylim) -- (\dist-0.6*\xlim,0.25*\ylim);
+
+		\draw[thick, dotted] (\dist-0.3*\xlim,0.9*\ylim) -- (\dist+0.3*\xlim,0.9*\ylim);
+		\draw[thick, dotted] (\dist-0.3*\xlim,-0.9*\ylim) -- (\dist+0.3*\xlim,-0.9*\ylim);
+
+		% Input layer
+		\draw[thick,fill=myorange!50] (-2*\dist-\xlim,-\ylim) -- (-2*\dist+\xlim,-\ylim) -- (-2*\dist+\xlim,\ylim) -- (-2*\dist-\xlim,\ylim)-- (-2*\dist-\xlim,-\ylim);
+		\draw (-2*\dist,0.7*\ylim) circle [radius = 0.4*\xlim] node {\footnotesize{$1$}};
+		\draw (-2*\dist,-0.7*\ylim) circle [radius = 0.4*\xlim] node {\footnotesize{$n$}};
+		\draw[thick, dotted] (-2*\dist,-0.25*\ylim) -- (-2*\dist,0.25*\ylim);
+
+		% Output layer
+		\draw[thick,fill=myorange!50] (2*\dist-\xlim,-\ylim) -- (2*\dist+\xlim,-\ylim) -- (2*\dist+\xlim,\ylim) -- (2*\dist-\xlim,\ylim)-- (2*\dist-\xlim,-\ylim);
+		\draw (2*\dist,0.7*\ylim) circle [radius = 0.4*\xlim] node {\footnotesize{$1$}};
+		\draw (2*\dist,-0.7*\ylim) circle [radius = 0.4*\xlim] node {\footnotesize{$n$}};
+		\draw[thick, dotted] (2*\dist,-0.25*\ylim) -- (2*\dist,0.25*\ylim);
+
+		% Trapezoids
+		\draw[fill=JoliGris!20] (-2*\dist+\xlim,-\ylim) -- (-1.8*\xlim-\dist,-1.2*\ylim) -- (-1.8*\xlim-\dist,+1.2*\ylim) -- (-2*\dist+\xlim,\ylim)-- (-2*\dist+\xlim,-\ylim);
+		\draw[fill=JoliGris!20] (1.8*\xlim-\dist,-1.2*\ylim) -- (-\xlim,-0.7*\ylim) -- (-\xlim,+0.7*\ylim) -- (1.8*\xlim-\dist,1.2*\ylim) -- (1.8*\xlim-\dist,-1.2*\ylim);
+		\draw[fill=JoliGris!20] (-1.8*\xlim+\dist,-1.2*\ylim) -- (+\xlim,-0.7*\ylim) -- (+\xlim,+0.7*\ylim) -- (-1.8*\xlim+\dist,1.2*\ylim) -- (-1.8*\xlim+\dist,-1.2*\ylim);
+		\draw[fill=JoliGris!20] (+2*\dist-\xlim,-\ylim) -- (+1.8*\xlim+\dist,-1.2*\ylim) -- (+1.8*\xlim+\dist,+1.2*\ylim) -- (+2*\dist-\xlim,\ylim)-- (+2*\dist-\xlim,-\ylim);
+
+		% Encoder/decoder labels
+		\draw[thick,|-|] (-2*\dist-\xlim,-1.45*\ylim) -- (\xlim,-1.45*\ylim) node [midway, below] {encoder};
+		\draw[thick,|-|] (-\xlim,-1.75*\ylim) -- (2*\dist+\xlim,-1.75*\ylim) node [midway, above] {decoder};
+
+	\end{tikzpicture}
+	\caption{Architecture of a fully-connected symmetric autoencoder with input/output of dimension $n$, a latent layer of dimension $\ell$. 
+	The hidden encoder and decoder subnetworks are arranged specularly, and have $p$ layers of width $q_p$ each.
+	This information will be denoted by a list $[n,q_1,\dots,q_p,\ell]$.}
+	\label{fig: AE_notation}
+\end{figure}
+%
+The loss function for the autoencoder is chosen as
+%
+\begin{equation}	\label{eq: loss_AE}
+	L_{\rm AE}(\ell)=\sum_i^N\big\vert x_i^{\rm (in)}-x_i^{\rm (out)}\big\vert^2
+\end{equation}
+%
+with $x_i^{\rm (out)}$ being the output of the decoder for a given input $x_i^{\rm (in)}$.
+These outputs depend on the value of $\ell$, and the loss function \eqref{eq: loss_AE} displays
+a sharp transition from a steep decline into a plateau when $\ell$ reaches the dimension of the 
+conformal manifold, if the latter does not have separated components. 
+In the latter scenario, a less pronounced transition occurs, and inspection of the values at 
+the latent layer reveals clusters of data associated to the different components.
+
+In the following, we introduce these techniques on a set of toy models of low dimensionality, and then apply these
+tools to the scalar potential (2.26) in \cite{Eloy:2021fhc}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Toy examples}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Higgs potential}
+The potential
+%
+\begin{equation}	\label{eq:toy1_V}
+	V(x^1,x^2,x^3,x^4) = \big[(x^1)^2+(x^2)^2-1\big]^2+(x^3)^2+(x^4)^2\,,
+\end{equation}
+%
+is a mexican-hat potential for the variables $x^1$ and $x^2$, and a harmonic potential for the variables $x^3$ and $x^4$.
+Its vacua are given by two different families of solutions,
+%
+\begin{equation}	\label{eq: toy1_CM}
+	\begin{tabular}{rcllll}
+	family 1	&:& $x^1=0$,	& $x^2=0$,	& $x^3=0$,	& $x^4=0$,	\\[5pt]
+	family 2	&:& $x^1=\cos t$,	& $x^2=\sin t$,	& $x^3=0$,	& $x^4=0$,	\qquad $t\in[0,2\pi)$\,.
+	\end{tabular}
+\end{equation}
+%
+We can capture this structure by performing a gradient descent with loss function \eqref{eq: loss_cloud} 
+for a cloud of $10^5$ randomly generated points in the region $[-0.75,0.75]^4$. 
+See figure~\ref{fig: toy1_cloud} for the attained cloud of points and the corresponding loss function during
+the gradient descent.
+%
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{Figures/loss_cloud_Higgs.png}	\\
+	\includegraphics[width=0.85\textwidth]{Figures/triangle_higgs.png}
+	\caption{Loss function and triangular plot of the numerical vacua of \eqref{eq:toy1_V}.}
+	\label{fig: toy1_cloud}
+\end{figure}
+%
+
+To ascertain the dimension of the geometric structures behind the shapes in figure~\ref{fig: toy1_cloud}, 
+we have employed an AE with the following architectures
+%
+\begin{equation}	\label{eq: AE_architecture_higgs}
+	[n,q_1,q_2,q_3,\ell]=[4,32,16,8,\ell]\,,	\qquad \ell=1,2,3\,,
+\end{equation}
+%
+following the notation of figure~\ref{fig: AE_notation}. For this example, $L_{\rm AE}(\ell)$ in figure~\ref{fig: lossAE_higgs} would naively suggest
+that the underpinning structures are two-dimensional, instead of the zero- and one-dimensional loci in \eqref{eq: toy1_CM}.
+However, close inspection of the output of the encoder half of the autoencoder \eqref{eq: AE_architecture_higgs} for $\ell=2$ reveals
+that the data is cleanly separated into two distinct structures: one point and one (broken) line, as can be observed in 
+figure~\ref{fig: encoded_higgs}. In fact, filtering using the decoder to label the data corresponding to the isolated point in
+figure~\ref{fig: encoded_higgs}, it can be verified that they correspond to solutions in family 1. Filtering out these points,
+the analytical structure of the complementary set can in fact be found to by using the $\ell=1$ decoder as a non-linear function ... 
+\note{how were the details of this procedure?}
+%
+
+%
+\begin{figure}
+	\centering
+	\subfigure[]{
+		\label{fig: lossAE_higgs}	
+		\includegraphics[width=0.48\textwidth]{Figures/lossAE_higgs.png}
+	}
+	%
+	\subfigure[]{
+		\label{fig: encoded_higgs}
+		\includegraphics[width=0.48\textwidth]{Figures/encoded_Higgs_l2.png}
+	}
+	\caption{Loss function encoder output for the autoencoder \eqref{eq: AE_architecture_higgs} and the entire set of data in figure~\ref{fig: toy1_cloud}.}
+	\label{fig: AE_higgs}
+\end{figure}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Scrambled Higgs potential}
+The example above was somewhat trivial given that one could immediately recognise 
+the relevant structure by glancing at figure~\ref{fig: toy1_cloud}, as the variables in which
+the solutions in \eqref{eq: toy1_CM} are most naturally expressed coincide with the variables
+that appear in the potential. In supergravity this will no longer be the case, and to exemplify
+how the autoencoder is useful in this context, let us consider the same potential as above,
+%
+\begin{equation}	\label{eq:toy2_V}
+	V(\tilde{x}^1,\tilde{x}^2,\tilde{x}^3,\tilde{x}^4) = \big[(\tilde{x}^1)^2+(\tilde{x}^2)^2-1\big]^2+(\tilde{x}^3)^2+(\tilde{x}^4)^2\,,
+\end{equation}
+%
+with the variables $\tilde{x}^i$ given by \note{need to decide a non-singular and bijective change of coordinates.}
+%
+\begin{equation}
+	\tilde{x}^1=\dots\,.
+\end{equation}
+%
+Constructing the conformal manifold in terms of $x^i$ results in a could for which the structure of the solutions is
+much less clear, as can be appreciated in figure~\ref{fig: toy2_cloud}. 
+However, the information in an autoencoder given again by \eqref{eq: AE_architecture_higgs} results in
+loss functions and encoded data in precise correspondence with figure~\ref{fig: AE_higgs}.
+
+%%%%%%%%%%%%%%%%
+\subsection{SO(8,4) supergravity}
+
+We have
+
+\begin{enumerate}
+	\item Looked at 3-, 5-, 7- and 13-parameter truncations.
+	\item There was qualitatively different behaviour when using logs vs exps.
+	\item There are spurious structures (forks) that the AE erases (why does it?).
+	\item The spurious structures can be also be broadened using random walks.
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%
 \bibliography{references}

### 2024-12-04 Potential_generator/pot_Higgs_4param.py
Higgs potential in 4d

@@ -1,0 +1,14 @@
+
+import tensorflow as tf
+import numpy as np
+
+dim = 4
+
+def V(x):
+    """
+    V = (-1 + x1 ** 2 + x2 ** 2) ** 2 + x3 ** 2 + x4 ** 2
+    """
+
+    x1, x2, x3, x4 = tf.split(x, 4, axis=1)
+
+    return (-1 + x1 ** 2 + x2 ** 2) ** 2 + x3 ** 2 + x4 ** 2

### 2025-05-13 Draft_MLFlatDirections.tex
Structure for the article.

--- 2024-08-09 Conformal_manifolds.tex
@@
 % ---- COMMENTS ----
-\usepackage[subfigure]{tocloft}		
-\newcommand{\listnotetitle}{\Large List of Notes}
-\newlistof{notes}{nt}{\listnotetitle}
-\newcommand{\notelist}[1]{%
-	\refstepcounter{notes}
-	\addcontentsline{nt}{notes}
-	{\protect\numberline{\thenotes}#1}
-}
-
-\newcommand{\note}[1]{\notelist{#1}\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries Note: #1}}
-
-% ---- TITLE PAGE ----
-\usepackage[affil-it]{authblk}
-\def\preprint{}
-
-\makeatletter
-\def\@maketitle{%
-  \newpage
-  \null\hfill\texttt{\preprint}
-  \vskip 4em%
-  \begin{center}%
-  \let \footnote \thanks
-    {\LARGE\bfseries \@title \par}%
-    \vskip 2.5em%
-    {\large
-      \lineskip .5em%
-      \begin{center}
-        \begin{minipage}{0.95\textwidth}
-            \begin{tabular}[t]{c}%
-            \@author
-            \end{tabular}
-        \end{minipage}    
-      \end{center}\par}%
-    \vskip 1em%
-    {\large \@date}%
-  \end{center}%
-  \par
-  \vskip 1.5em}
-\makeatother
-
-\renewcommand\Authands{ and }
-
-\title{Notes on conformal manifolds}
-\author{}
+\newcommand{\ce}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries (ce: #1)}}
+\newcommand{\gl}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries (gl: #1)}}
 
@@
 
-\maketitle
+\begin{titlepage}
+
+\begin{flushright}
+
+MI-HET-??? \\
+\today
+\end{flushright}
+
+\vspace{25pt}
+
+   \begin{center}
+   \baselineskip=16pt
+
+   \begin{Large}
+
+\mbox{ \bfseries \boldmath  Notes: Machine learning flat directions}
+   \end{Large}
+
+\vspace{25pt}
+
+{\large  Bastien Duboeuf$^{1}$, Camille Eloy$^{1}$ \,and\, Gabriel Larios$^{2}$}
+
+\vspace{25pt}
+
+	\begin{small}
+
+	{\it $^{1}$ ENS de Lyon, Laboratoire de Physique\\
+	 ...}  \\
+
+	\vspace{10pt}
+
+	{\it $^{2}$ Mitchell Institute for Fundamental Physics and Astronomy, \\
+	Texas A\&M University, College Station, TX, 77843, USA}     \\
+
+	\end{small}
+
+\vskip 50pt
+
+\end{center}
+
+\begin{center}
+\textbf{Abstract}
+\end{center}
+
+\begin{quote}
+
+...
+
+\end{quote}
+
+\vfill
+
+\end{titlepage}
 
@@
 
-%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%
-\section{Comments on Flat Directions and $n$-Hessians} \label{sec: hessians}
-%%%%%%%%%%%%%%
+\section{Introduction}
 
-Given a real function $V: M \rightarrow \mathbb R$, its critical points are defined as the zeroes of the gradient
-%
-\begin{equation}
-	x^*: H_{m}(x^*)\equiv\partial_mV\big\vert_{x^*}=0\,,
-\end{equation}
-%
-with the $n$-Hessian of $V(x)$ defined as
-%
-\begin{equation}
-	H_{m_1\dots m_n}\equiv\partial_{m_1}\dots\partial_{m_n}V\,.
-\end{equation}
-%
+\section{Supergravity setup}
+\begin{itemize}[label=\textbullet]
+	\item Context: 6d ${\rm AdS}_{3}\times S^{3}$, truncation to 3d, potential, conformal manifold.
+	\item Choice of truncation from 32 to 13 to 5 variables.
+\end{itemize}
 
-Flat directions around the critical point $x^*$ are curves $\phi: I\rightarrow M$ such that
-%
-\begin{equation}	\label{eq: flatdef}
-	H_{m}(\phi(t))=0\,,	\qquad\text{with}\quad
-	\phi(0)=x^*\,.
-\end{equation}
-%
-Close to $x^*$, the curve can be expanded as
-%
-\begin{equation}	\label{eq: phiSeries}
-	\phi(t)=x^*+\sum_{k=1}^{\infty}\tfrac1{k!}\xi_k\, t^k\,, \qquad\text{with}\quad
-	\xi_k=\frac{d^k\phi}{dt^k}\Big\vert_{x^*}\,,
-\end{equation}
-%
-and, accordingly,
-%
-\begin{equation}
-	\begin{aligned}
-		H_{m}(\phi(t))&=\sum_{k=1}^{\infty}H_{mn_1\dots n_k}\sum_{a\in\lambda_k}t^{\sum_i^{\vert a\vert}i a_i}\bigg[\prod_{i=1}^{\vert a\vert}\frac1{a_i!}\frac{1}{\big(i!\big)^{a_i}}\xi_i^{\otimes a_i}\bigg]^{n_1\dots n_k}\,,
-	\end{aligned}
-\end{equation}
-%
-with all the $n$-Hessians on the right-hand side evaluated at $x^*$.
-Here, $\lambda_k$ denotes the integer partitions of $k$ (e.g.
-$\lambda_3=\{(3),(2,1),(1,1,1)\}$), $\vert a\vert$ is the number of elements of a specific partition $a\in\lambda_k$ (e.g.
-$\vert(2,1)\vert=2$ and $\vert(1,1,1)\vert=3$), and $a_i$ each of its elements.
-Equation \eqref{eq: flatdef} needs to be satisfied at every order in $t$, and therefore the existence of flat directions amounts to the existence solutions of the system
-%
-\begin{equation}	\label{eq: flateqnsAll}
-	O(t^p):\quad\sum_{\{a_i\}}H_{mn_1\dots n_{k}}\prod_i^{p}\bigg[\frac1{a_i!}\frac1{\big(i!\big)^{a_i}}\xi_i^{\otimes a_i}\bigg]^{n_1\dots n_k}=0\,,
-\end{equation}
-%
-with the set of coefficients $\{a_i\}$ determined as
-%
-\begin{equation}	\label{eq: as}
-	\sum_i^{p}i a_i=p\,, 	\qquad
-	a_i\in \mathbb{N}\,,
-\end{equation}
-%
-and $k$ in \eqref{eq: flateqnsAll} a shorthand for $k=\sum_i^p a_i$ for the solutions of \eqref{eq: as}.
-For lowest $p$, this is
-%
-\begin{equation}	\label{eq: flateqns}
-	\begin{aligned}
-		0&=H_{mn}\xi_1^n\,,		\\[5pt]
-		0&=H_{mn}\xi_2^n+H_{mnp}\xi_1^n\xi_1^p\,,	\\[5pt]
-		0&=H_{mn}\xi_3^n+3H_{mnp}\xi_2^n\xi_1^p+H_{mnpq}\xi_1^n\xi_1^p\xi_1^q\,,	\\[5pt]
-		0&=H_{mn}\xi_4^n+3H_{mnp}\xi_2^n\xi_2^p+4H_{mnp}\xi_3^n\xi_1^p+6H_{mnpq}\xi_2^n\xi_1^p\xi_1^q+H_{mnpqr}\xi_1^n\xi_1^p\xi_1^q\xi_1^r\,,	\\[5pt]
-		&\dots
-	\end{aligned}
-\end{equation}
-%
+\section{Numerical analysis}
+	\subsection{Gradient descent and local analysis}
+	\begin{itemize}[label=\textbullet]
+		\item Gradient descent: implementation, sampling, time needed, loss.
+		\item Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least fex points in each direction).
+		\item Clusteting: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space.
+		\item After PCA and clustering we know that the points after the gradient descent sample a three-dimensional manifold.
+	\end{itemize}
 
-Note that the non-linearity of \eqref{eq: flateqns} in the expansion coefficients of $\phi(t)$ implies that the number of flat directions is not easily related to the dimension of the null space of the 2-Hessian at $x^*$ (i.e.
-the number of massless scalars if $V$ is the scalar potential).
-A necessary condition for \eqref{eq: flateqnsAll} to have a solution is
-%
-\begin{equation}
-	\det H_{mn}=0\,,		\\[5pt]
-\end{equation}
-%
-but there can be more flat directions than zero eigenvalues and vice versa. These features will be studied in the following.
+	\subsection{Annealed Importance Sampling for polynomial symbolic regression}
+	\begin{itemize}[label=\textbullet]
+		\item We can convert the potential to a polynomial by converting the variables that appear in exponentials to logs.
+		\item As the potential is a polynomial, the solutions satisfy polynomials equations.
+Discuss that fact that we could get polynomials directly by taking the gradient of the potential, but those will be to complicated to express the vacuum in a usable way.
+We search those using Annealed Importance Sampling.
+		\item Annealed Importance Sampling: first explain general idea (construct density probability, role of temperature, links with Monte-Carlo), discuss $\beta$ to control exploration and exploitation phases.
+		\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
+		\item Discuss the fact that we allow float coefficients even though we know the coefficients will be only integers of square roots of integers?
+		\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
+		\item Results for naive choices of parameters (numbers of itaration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
+Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate.
+Total time needed, without cluster or fancy computers.
+	\end{itemize}
 
-%%%%%%%%%%%%%%
-\subsection{Flat flat directions} \label{sec: FFC}
-%%%%%%%%%%%%%%
+\section{Supergravity solutions}
+\begin{itemize}[label=\textbullet]
+	\item For each couple of candidate polynomials, we get the same expression for the solution, and it indeed defines a unique vacuum of the 3d SUGRA.
+	\item Discussion of the vacuum: gauge group, Zham. metric, change of variables, 3d spectrum (and stability), spin 2 spectrum on $S^{3}$, one parameter seems to be a gauge parameter, uplift?
+\end{itemize}
 
-When flat directions can be given as straight lines $\phi(t)=x^*+\xi t$ for constant $\xi$, the set of equations \eqref{eq: flateqns} simplifies to the condition $\xi\in K_k$ for all $n\geq1$, with the kernels defined as
-%
-\begin{equation}	\label{eq: flatness}
-	K_k=\{\xi: \xi^{n_1}\dots\xi^{n_{k}}H_{mn_1\dots n_{k}}(x^*)=0\}\,,	\qquad \forall n\geq1\,.
-\end{equation}
-%
-This condition is required for $\partial_mV$ to be constant along the integral curve of $\xi^m$, since
-%
-\begin{equation}
-	\begin{aligned}
-		\xi^{n_k}\partial_{n_k}\big(\xi^{n_1}\dots\xi^{n_{k-1}}H_{mn_1\dots n_{k-1}}\big)\big\vert_{x^*}
-		=\xi^{n_1}\dots\xi^{n_{k}}H_{mn_1\dots n_{k}}(x^*)
-	\end{aligned}
-\end{equation}
-%
-must hold for all $k\geq1$.
-
-Two functions that have flat flat directions and exhibit the subtleties mentioned before are given by
-%
-\begin{equation}	\label{eq: flatflat}
-	V_1(x,y)=x^4(1+y^2)\,,		\qquad\text{and}\qquad
-	V_3(x,y)=y^2(x^2-3y^2)\,,
-\end{equation}
-%
-which are plotted in Fig.~\ref{fig: flatflat}.
-%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.4\textwidth]{Figures/V1.pdf}
-	\qquad
-	\includegraphics[width=0.4\textwidth]{Figures/V3.pdf}
-	\caption{Contour plots for the potentials $V_1$ (left) and $V_3$ (right) in \eqref{eq: flatflat} with flat directions and $x^*=0$ locus superimposed.}
-	\label{fig: flatflat}
-\end{figure}
-%
-In both cases, the 2-Hessian vanishes identically at $x^*=0$, but $V_1$ only has one flat direction given by $(x,y)=(0,\zeta)$, whereas $V_3$ has three independent flat curves:
-%
-\begin{equation}
-	(x,y)=(\zeta_1,\, 0)\,,	\qquad
-	(x,y)=(\sqrt3\,\zeta_2,\, \zeta_2)\,,	\qquad
-	(x,y)=(-\sqrt3\,\zeta_3,\, \zeta_3)\,.
-\end{equation}
-%
-
-\note{How is the second compatible with the standard holography lore? Can this type of potentials arise in consistent truncations?}
-
-%%%%%%%%%%%%%%
-\subsection{Curved flat directions} \label{sec: FCL}
-%%%%%%%%%%%%%%
-
-(alternative name: curved flat curves)
-
-The condition \eqref{eq: flatness} does not capture curves with a non-linear dependence on $t$. For instance,
-%
-\begin{equation}	\label{eq: Vcurved}
-	V(x,y)=x^2(x^2-3y^4)
-\end{equation}
-%
-has flat directions
-%
-\begin{equation}	\label{eq: curvedcurves}
-	(x,y)=(0,\, \zeta_1)\,,	\qquad
-	(x,y)=(\sqrt3\,\zeta_2^2,\, \zeta_2)\,,	\qquad
-	(x,y)=(-\sqrt3\,\zeta_3^2,\, \zeta_3)\,,
-\end{equation}
-%
-of which only the first is captured by \eqref{eq: flatness}.
-For the other two, the higher order terms in \eqref{eq: flateqnsAll} also contribute.
-To gauge-fix the reparameterisation invariance of \eqref{eq: flatdef}, we demand without loss of generality that the lowest non-vanishing term in \eqref{eq: phiSeries} is linear in $t$.
-Doing so, \eqref{eq: flateqnsAll} yields \eqref{eq: curvedcurves} unambiguously.
-We note that for \eqref{eq: Vcurved} the first non-trivial equation arises at order $O(t^5)$, the following at $O(t^{10})$, and from then on we get a condition on every level.
-
-This method has been checked with three other functions with flat directions:
-%
-\begin{equation}
-	\begin{aligned}
-		V(x,y)&=(y-\cos x)^2\,,	\\[5pt]
-		V(x,y)&=(x^2+y^2-1)^2\,,	\\[5pt]
-		V(x,y)&=x^2(x^2+y^2-1)^2\,,
-	\end{aligned}
-\end{equation}
-%
-recovering the analytic result in all instances and converging more quickly than for \eqref{eq: Vcurved} (as their series have non-zero contributions at lower orders).
-
-\note{The distinction between the different curves in \eqref{eq: curvedcurves} disappears at linear level, and this is very reminiscent of the TsT vs Wilson loop families in \cite{Eloy:2024lwn}.}
-
-%
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{Figures/V3curved.pdf}
-	\caption{Contour plot for the potential in \eqref{eq: Vcurved} with flat directions in \eqref{eq: curvedcurves} and $x^*=0$ locus superimposed.}
-	\label{fig: curvedflat}
-\end{figure}
-%
-
-%%%%%%%%%%%%%%
-\section{SO(8,4) supergravity in $D=3$} \label{sec: 3dSugra}
-%%%%%%%%%%%%%%
-
-When apply the above techniques to the potential (2.26) in \cite{Eloy:2021fhc}, we recover the two-parameter family (2.27) in there.
-I have not managed to get anything else, but that does not mean necessarily that there isn't.
-It is probably more due to the fact that the system for 13 scalars is very complicated.
-Using the \texttt{NSolve} routine might be useful to see if there is any solution outside the known class.
+\section{Conclusion}
+\begin{itemize}[label=\textbullet]
+	\item Conclusion: good prospects of improvement to be able to access higher dimensional cases. Classify flat directions.
+	\item Appendix with some details on the code?
+\end{itemize}
 

### 2025-05-14 5d_pot_analysis_1_2_4_8_10/autoencoder_analysis_in_py.py
Add the file with the data analaysis on the 5d pot

@@ -1,0 +1,47 @@
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+import tensorflow as tf
+import time
+import keras
+from keras import layers,models,regularizers
+from tensorflow.keras.callbacks import LearningRateScheduler
+from sklearn.model_selection import train_test_split
+import argparse
+
+parser = argparse.ArgumentParser()
+parser.add_argument("-latent_dim", help="", default = 1, type = int)
+parser.add_argument("-input_dim", help="", default = 1, type = int)
+parser.add_argument("-n_epochs", help="", default = 1, type = int)
+parser.add_argument("-batch_size", help="", default = 1, type = int)
+parser.add_argument("-n_neurons", help="", default = 1, type = int)
+parser.add_argument("-path", help="", default = 'None', type = str)
+
+parser.parse_args()
+args = parser.parse_args()
+
+this_latent_dim = args.latent_dim
+input_dim = args.input_dim
+n_neurons = args.n_neurons
+
+x = np.load(args.path)
+x = tf.Variable(x)
+
+set_train, set_test = train_test_split(x.numpy(), test_size=0.1, random_state=1)
+
+inputs = layers.Input(shape=(input_dim,))
+encoded = layers.Dense(n_neurons, activation='sigmoid')(inputs)
+encoded = layers.Dense(n_neurons, activation='sigmoid')(encoded)
+encoded = layers.Dense(this_latent_dim)(encoded)  
+
+decoded = layers.Dense(n_neurons, activation='sigmoid')(encoded)
+decoded = layers.Dense(n_neurons, activation='sigmoid')(decoded)
+decoded = layers.Dense(input_dim)(decoded)  
+
+this_autoencoder = keras.Model(inputs, decoded)
+this_autoencoder.compile(optimizer='adam', loss='mse')
+
+history = this_autoencoder.fit(set_train, set_train, epochs=args.n_epochs, batch_size=args.batch_size, shuffle=True, validation_data=(set_test,set_test))
+    
+np.save(f"History_{input_dim}_{args.n_epochs}_{args.n_neurons}",history)
+this_autoencoder.save(f'ae_{input_dim}_{args.n_epochs}_{args.n_neurons}.keras')

### 2025-05-14 5d_pot_analysis_1_2_4_8_10/grad_descent.py

@@ -1,0 +1,58 @@
+import numpy as np 
+import tensorflow as tf 
+import sys
+import os
+import time 
+#module_path = "/home/bbastien/MLFlatDirections"
+module_path = "/Users/bastienduboeuf/Documents/Recherche/MLForFlatDirections3D/MLFlatDirections"
+sys.path.append(module_path)
+
+import grad_descent_module as gdm 
+import potentials as pot
+import argparse
+
+parser = argparse.ArgumentParser()
+parser.add_argument("-file_of_points", help="File where we should take the points from. If 'None', randomly initialize the points", default = "None", type = str)
+parser.add_argument("-out_file_of_points", help="File where we should save the points.", default = "None", type = str)
+parser.add_argument("-n_points", help="Numbers of point to initialize", default = 10000, type = int)
+parser.add_argument("-update_opt", help="Wether to reinitialize the optimizer", default = False, type = bool)
+parser.add_argument("-n_steps", help="Number of epochs for the gradient descent", default = 1000, type = int)
+parser.add_argument("-n_steps_opt", help="After how many steps should the optimier be reinitialize", default = 200, type = int)
+parser.add_argument("-step_stop_opt", help="After how many steps should the reinitialization be stopped", default = 1500, type = int)
+parser.add_argument("-alpha", help="Learning rate", default = 10**(-2), type = float)
+parser.add_argument("-n_step_print", help="Frequency for printing the output", default = 10, type = int)
+parser.add_argument("-n_var", help="Number of variable", default = 13, type = int)
+#parser.add_argument("-pot", help="Name of the potential", default =, type = int)
+
+parser.parse_args()
+args = parser.parse_args()
+
+n_points = args.n_points
+if args.file_of_points != 'None':
+    x = tf.Variable(np.load(args.file_of_points))
+else: 
+    this_seed = int((time.time()-int(time.time()))*1000)
+    np.random.seed(this_seed)
+    x = tf.Variable(2*np.random.rand(n_points,args.n_var)-1, dtype=tf.float32)
+
+this_history,this_x = gdm.grad_descent_potential(pot.V3d_sugra, 
+                                                 x, 
+                                                 update_opt = args.update_opt, 
+                                                 n_steps = args.n_steps,
+                                                 n_steps_opt = args.n_steps_opt, 
+                                                 step_stop_opt = args.step_stop_opt, 
[…]

### 2025-05-14 Draft_MLFlatDirections.tex

@@
 
-	{\it $^{1}$ ENS de Lyon, Laboratoire de Physique\\
-	 ...}  \\
+	{\it $^{1}$ ENS de Lyon, CNRS, LPENSL, UMR5672,\\ 69342, Lyon cedex 07, France}  \\
 
@@
 
+\paragraph{Potential}
+The 22 scalars of the theory can be parametrised by ($22 = 32 - 10$, with 10 scalars gauge fixed using translations in the gauge group)
+\begin{itemize}[label=\textbullet]
+	\item $m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$,
+	\item $\phi$ a $3\times3$ antisymmetric matrix,
+	\item $\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$,
+	\item a dilaton $\tilde{\varphi}$.
+\end{itemize}
+We can further restrict ourselves to a set of 13 scalars (see ref.~\cite{Eloy:2021fhc}), with
+\begin{equation}
+	\begin{aligned}
+		\xi &= \begin{pmatrix}
+					0 & 0 & 0 & x_{1} \\
+					0 & 0 & 0 & x_{2} \\
+					0 & 0 & 0 & x_{3}
+				\end{pmatrix},
+		\quad
+		\phi = \begin{pmatrix}
+					0 & x_{4} & x_{5} \\
+					-x_{4} & 0 & x_{6} \\
+					-x_{5} & -x_{6} & 0
+				\end{pmatrix},
+		\quad
+		\tilde{\varphi} = x_{13} \\[5pt]
+		\nu &= e^{(6\,x_{7}+3\,x_{8}+\sqrt{3}\,x_{9})/6}
+				\begin{pmatrix}
+					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
+					0 & e^{-x_{8}} & \frac{e^{-x_{8}}\,x_{12}}{\sqrt{2}} \\
+					0 & 0 & e^{-(x_{8}+\sqrt{3}\,x_{9})/2}
+				\end{pmatrix}.
+	\end{aligned}
+\end{equation}
+Scalar potential from ref.~\cite{Eloy:2021fhc}:
+%
+\begin{equation} \label{eq:scalarpotential}
+	\begin{aligned}
+ 		V & = 4\,e^{-4\tilde\varphi}+2\,e^{-2\tilde\varphi}\Big[-\tr\left(m+m^{-1}\right)+\tr\left(\phi m^{-1}\phi\right) -2\,\tr\left(\phi m^{-1}\xi^{2}\right)-2\,\tr\left(\xi^{2}\right)\\
+ 		&\qquad\quad-\tr\left(\xi^{2}m^{-1}\xi^{2}\right)  +\frac{1}{2}\,\det\left(m^{-1}\right)\left(1-\tr\left(\phi^{2}\right)-\tr\left(\xi^{4}\right)+\tr\left(\xi^{2}\right)^{2}\right) \\
+ 		&\qquad\quad +\frac{1}{2}\,{\rm T}\left(m^{-1}(\xi^{2}-\phi),(\xi^{2}+\phi)m^{-1},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2}\right)\\
+ 		&\qquad\quad +\frac{1}{4}\,{\rm T}\left(m^{-1},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2}\right)\Big], 
+ 	\end{aligned}
+\end{equation}
+where ${\rm T}\left(A,B,C\right)=\varepsilon_{mnp}\,\varepsilon_{qrs}\,A^{mq}B^{nr}C^{ps}$.
+
+As a first simplified example we have considered only the parameters $x_{1}, x_{2}, x_{4}, x_{8}$ and $x_{10}$. The potential~\eqref{eq:scalarpotential} becomes
+\begin{equation} \label{eq:scalarpotential124810}
+	\begin{aligned}
+		V &= \frac{1}{8}\, e^{-2\,x_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,x_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
+		  & \quad\qquad\qquad - 4\,e^{3\,x_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
+      			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
+        & \quad\qquad\qquad - 8\,e^{x_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
+      			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
+        & \quad\qquad\qquad + 4\,e^{2\,x_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
+        			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
+        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,x_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
+	\end{aligned}
+\end{equation}
+
 \section{Numerical analysis}
@@
 		\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
-		\item Results for naive choices of parameters (numbers of itaration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
+		\item Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
 Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate.
@@
 	\end{itemize}
+
+	\paragraph{Results}
+	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}. For 100 runs with parameters
+	\begin{equation}
+		\begin{gathered}
+			n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
+			{\rm sample\ size = 10000},\quad p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
+		\end{gathered}
+	\end{equation}
+	the code finds the 7 different following polynomials:
+	\begin{subequations} \label{eq:pols}
+    \begin{align}
+      p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}\tilde{x}_{8} + x_{2}\tilde{x}_{8}x_{10} - \sqrt{2}\,x_{2}x_{4}\tilde{x}_{8},\\
+      p_{2} &= 2\,x_{2} + 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}\tilde{x}_{8}x_{10}^{2},\\
+      p_{3} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\tilde{x}_{8}x_{10} + 2\,x_{1}x_{4}\tilde{x}_{8}
+      		- 2\,x_{2} x_{4}^{2}\tilde{x}_{8},\\
+      p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\,x_{4} + x_{1}\tilde{x}_{8}x_{10}
+      		- x_{2}x_{4}\tilde{x}_{8}x_{10},\\
+      p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10}
+      		+ x_{1}\tilde{x}_{8}x_{10}^{2},\\
+      p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10} 
+      		- \sqrt{2}\,x_{2}\tilde{x}_{8}x_{10} +  x_{1}\tilde{x}_{8}x_{10}^{2},\\
+      p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
+      		- x_{2}^{2}x_{10},
+    \end{align}
+  \end{subequations}
+  where $\tilde{x}_{8} = e^{x_{8}}$, with the distribution:
+  \begin{equation}
+  	\begin{tabular}{l|cccccccc}
+  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
+  		Distribution & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
+  	\end{tabular}
+  \end{equation}
+  The sum of the percentages is higher than 100\% because some runs find more than one polynomials.
+The code fails to find any polynomial in 13\% of the time.
+The averaged time needed for a single run on a PC in $\sim 1400\,{\rm s}$.
 
@@
 \end{itemize}
+
+For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
+\begin{equation}
+	\begin{cases}
+		p_{i} = 0, \\
+		p_{j} = 0,
+	\end{cases}
+\end{equation}
+gives the same solution
+\begin{equation}
+	\begin{cases}
+		\displaystyle x_{1} = \frac{x_{2}}{\sqrt{2}}\,\frac{e^{x_{8}/2}}{e^{x_{8}}-1}\,\Big(-x_{5}\,e^{x_{8}/2} + \sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}\Big),\\[8pt]
+		\displaystyle x_{4} = \frac{e^{-x_{8}/2}}{\sqrt{2}}\,\sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}.
+	\end{cases}
+\end{equation}
+We checked that this defines a 3-parameter solution of three-dimensional half-maximal supergravity. Equivalently:
+\begin{equation}
+	\begin{cases}
+		\displaystyle \tilde{x}_{8} = \frac{x_{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
+		\displaystyle x_{10} = \sqrt{2}\,x_{4}\,\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
+	\end{cases}
+\end{equation}
+The solution preserves a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.
+
+\paragraph{Moduli space}
+The $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
+\begin{equation}
+	x_{1} = r\cos(\theta)\cos(\Phi), \quad x_{2} = r\cos(\theta)\sin(\Phi) \quad {\rm and} \quad x_{4} = r\sin(\theta),
+\end{equation}
+for which the Zamolodchikov metric reads
+\begin{equation}
+	\d^{2}s_{\rm Zam.} = -\,\d r^{2} - r^{2}\,\bigg(\d \theta^{2} - r\cos(\theta)\,\d \theta\d\Phi + \sin(\theta)\,\d r\d\Phi + \frac{1}{2}\,\big(3+r^{2}-\cos(2\theta)\big)\,\d\Phi^{2} \bigg).
+\end{equation}
+\ce{Tests other change of variables? Test choices of variables other than $(x_{1},x_{2},x_{4})$?}
+
+\paragraph{Bosonic spectrum}
+Vector fields:
+\begin{equation}
+ \begin{aligned}	
+	m_{\sst{(1)}}\ell_{\rm AdS}:\quad &
+	0\ [2],	\quad
+	-2\ [5],	\quad
+	2\ [1],	\\[5pt]
+	&	-1\pm\sqrt{\left(1+r^2\right)^2-2\,r^2\,\cos(2\theta)}\ [2+2],	\\[5pt]
+	&	1\pm\sqrt{1+4\,r^2+r^{4}}\ [2+2].
+ \end{aligned}
+\end{equation}
+The integers between square brackets indicate the multiplicity of each eigenvalue.
+The spectrum includes two massless vectors corresponding to the unbroken ${\rm U}(1)\times {\rm U}(1)$ gauge symmetry, although in three dimensions they are non-propagating.
+
+Scalars:
+\begin{equation}
+ \begin{aligned}	
+	\left(m_{\sst{(0)}}\ell_{\rm AdS}\right)^2:\quad&
+	0\ [5],	\quad
+	8\ [1],	\quad
+	r^{2}\,\left(4+r^2\right)\ [8],	\\[5pt]
+	&	2r\,\Big(3\,r+r^{3}\pm(2+r^{2})\,\sqrt{2+r^2-2\,\cos(2\theta)}-r\cos(2\theta)\Big)\ [2+2].
+ \end{aligned}
+\end{equation}
+
+Gravitini:
+\begin{equation}
+	m_{{(\nicefrac32)}}\ell_{\rm AdS}:\quad 
+	\quad \dfrac1{2}\bigg[1\pm\sqrt{4+2\,r^{2}+r^{4}-2r^{2}\cos(2\theta)}\bigg]\ [4+4],
+\end{equation}
+no SUSY enhancements other than $r=0$.
+
+No dependence on $\Phi$.
 

### 2025-05-16 Draft_MLFlatDirections.tex
avec un peu de chance on est bon

@@
 		\item Gradient descent: implementation, sampling, time needed, loss.
+
+		In order to look for flat direction in this potential, we will use numerical tools.
+The path we will follow is the following : first we will sample the underlying manifold, then we will use numerical tools to exctract analytics information on this cloud of points.
+Therefore the first step is to sample the manifold.
+To do so, we choose to do a basic gradient descent.
+We start by randomly uniformy initializing points in an hypercube of length $[-2,2]$.
+This will be important latter to have points which are not only in $[-1,1]$.
+We choose to have $10^5$ points.
+For this example.
+This number is motivated by the dimensionality of our problem.
+If all possible directions are going to be populated, and if wen want $\mathcal{O}(10)$ points in each direction, then we need  $\mathcal{O}(10^5)$ points.
+As the true internal dimension of the manifold is lesser or equal than 5, this number provides an upper bound for the number of points needed to sufficiently sample the manifold.
+We then perfom a gradient descent on the point using the automatic differentiation method of tensorflow.
+For the loss function, we use
+		\begin{equation}
+			\mathcal{L} = \sum_{i = 1}^{n_{points}} |\nabla V(\vec{x}_i)|^2
+		\end{equation}
+		with $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$. We choose to use the Adam optimizer and use a learning rate of $10^{-2}$. We run the gradient descent for $10000$ epochs to make sure of convergence. 
+%		\begin{figure}
+%			\includegraphics[scale = 0.5]{imagefile} % add loss history 
+%		\end{figure}
+		As a first visualisation, we show a triangular plot of the data in Fig.
+\ref{triangular_plot_1_2_4_8_10}.
+This shows all possible $2d$ projections of the data as well as the $1d$ histograms of the data after the gradient descent.
+		\begin{figure}
+			\centering
+			\includegraphics[scale = 0.25]{Figures/triangular_plot_1_2_4_8_10.png} %names need to be changed.
+			\caption{Triangular plot showing $2d$ projections and $1d$ histograms of the data after the gradient descent}
+			\label{triangular_plot_1_2_4_8_10}
+		\end{figure}
+
+		Comments :
+		\begin{enumerate}
+			\item We see some non trivial correlation between the data.
+Note however that some features we see can be caused by the fact that some places may be greater basin of attractions (this is for example what happend in the $x_1/x_2$ plot).
+However, the structure we see in the $x_4/x_8$ or $x_4/x_{10}$ is a remnant of true features of the manifold
+			\item All directions seems to be well populated 
+			\item A great majority of the points fall in the $\vec{0}$ point.
+This is not too surprising.
+This just means that the round sphere solution has a greater basin of attraction.
+Even so, those points are going to be sufficiently good for the rest of the analysis, and we do not try to move the points along flat directions (to depopulate the origin et repopulate the rest).
+		\end{enumerate}
 		\item Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least fex points in each direction).
+
+		Once the gradient descent is done and we sampled the flat direction, it remains to determine what is the underlying manifolds.
+We would like to obtain some analytics expression for this, not only a numerical solution.
+Before proceeding to any sort of symbolic regression and look for such an analytic expression, there is a few things we can do to gain so understanding on the data, such as determining the dimensionality of the manifold, and wheter it a one piece or several pieces manifolds (like 2 intersecting hyperplane or so).
+To do so, we run a local Principal Component Analysis (PCA) algorithm.
+For each point, we select the $k$ nearest neighboors, and we run a PCA analysis on thos points.
+This allows to determine how many directions are needed to explain a given percentage of the spreding of the data, call it $\epsilon$.
+In other words, this allows to determine what is the local dimension around each point.
+We ran such an algorithm for a number of $k$ nearest neighboors equal to $[5,10,20,50,100]$, and for $\epsilon = 0.99$.
+The results are shown in \ref{local_pca}.
+		\begin{figure}
+			\centering
+			\includegraphics[scale=0.5]{Figures/Local_PCA.png}
+			\caption{Results of the local PCA analysis.
+On the $x$-axis is the dimension found by the algorithm, and on the $y$-axis the proportion of points.
+The different curves are for different $k$-nearest neighboors.}
+			\label{local_pca}
+		\end{figure}
+
+		We see that, for every choice of nearest neighboor, a peak at $d=3$, which indicates an underlying dimension of 3 for the manifold.
+We also see that for $k=5$, that a number a point seems to indicate a dimensionality of 2.
+However, if the dimension is indeed 3, then 5 points may not be enough to sufficiently populate the three directions, explaining the failure of the algorithm to find 3.
+We also see that for $k\le20$, that there is more and more points indicating a dimension equals to 4 or 5.
+This can be explained by the fact that we increasing the number of neighboors, we are doing a rougher coarse graining, loosing information on the localilty.
+A too large number of neighboors implies including points which are not really local anymore, artificially increasing the local dimension.
+We conclude that the dimension of the manifold we are looking at is 3.
+
 		\item Clusteting: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space.
-		\item After PCA and clustering we know that the points after the gradient descent sample a three-dimensional manifold.
+
+		Something that might happen, is that we have several manifolds of dimesion 3, and the dimension 4 points we saw above are actually the intersection of those manifolds.
+If we indeed picture the intersection of two lines, then at the intersection point, the local dimension found by the previous algorithm should be 2.
+To exclude such a scenario, we run a clustering algorithm, based on local density.
+For this, we use the HDBSAN algorithm.
+(details on how it works?).
+We choose a minimal cluster size of 10 points.
+Out of the 100000, the algorithm finds 3 cluster : one on dimension 10, one of dimension 91747 and a last one of dimension 6849 (not a total of 100000??).
+The last cluster are just the points that the algorithm did not managed to fit into any cluster.
+For the first one, we interpret it as some fluctuation in our data, making some region of different density as the other, but we do not believe this is some real result, more an artefact.
+Therefore, what the algorithm tells us, is that there seems to be on cluster with more than $90\%$ of the data.
+We show on \ref{3dplots} three-dimensional projections of the data.
+
+		\begin{figure}
+			\centering
+			\includegraphics[scale=0.4]{Figures/3d_plot_x4_x8_x10.png}
+			\includegraphics[scale=0.4]{Figures/3d_plot_x2_x4_x8.png}
+			\caption{3d plot of $x_4$, $x_8$ and $x_{10}$}
+			\label{3dplots}
+		\end{figure}
+		On these scatter plots, the turquoise points are those belonging to the main cluster, and the purple are those for which the algorithm failed to give them a cluster.
+On of the two plot, we can see some few yellow points which correspond to the small cluster with 10 points.
+We can see, from what we can tell with those plots, that all points that could not be assigned to a cluster are on the boarder of the data.
+Therefore, we interpret the fact that those point could not be assigned, not because there are part of another cluster, and a manifold, but because of the lack of points around them due to the fact they are on the boundary of our data.
+We conclude from this analysis, that we possess here a sampling of a unique 3 dimensional manifold.
+
+		%\item After PCA and clustering we know that the points after the gradient descent sample a three-dimensional manifold.
 	\end{itemize}
@@
 We search those using Annealed Importance Sampling.
+
+		Now we have sampled the manifold and exctrated some basic information about it (namely its dimension and the fact that it is made of one block), we would like to see if we can exctract some analytic formula to caracterise it.
+What we have at the moment, are points on a 3-dimensional manifold, which are embedded in a 5-dimensional space.
+Therefore we can conclude that, in order to caracterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
+If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $\tilde{x_{8}} = e^{x_8}$, that this potential is actually a polynomial of the embedding coordinates.
+Therefore, the components of $|\nabla V|$ are also polynomials in those variables.
+We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there are two of those.
+Of course if one takes directly the gradient of \eqref{eq:scalarpotential124810}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
+The problem we are facing here is therefore a problem of symbolic regression : we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
+There are a number of way one can deal with it, using already existing methods such as AI Feynman methods, or ..., or by doing rough gradient descent on the most general polynomial with arbitrary coefficients and trying to minimize its value once evaluated on the data points.
+In the spirit of trying to build a generalisable method, we develop here our own method, which is based on symbolic regression using an Annealing Importance Sampling method.
+
 		\item Annealed Importance Sampling: first explain general idea (construct density probability, role of temperature, links with Monte-Carlo), discuss $\beta$ to control exploration and exploitation phases.
+
+		In the realm of symbolic regression, the objective is to uncover interpretable mathematical expressions that best describe a given dataset.
+In the problem discussed in this paper, we are looking for polynomial expressions such that $p(data) = 0$.
+This task involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods.
+Markov Chain Monte Carlo (MCMC) techniques, while widely used, can struggle with poor mixing and getting trapped in local optima, especially in high-dimensional or multimodal spaces.
+
+		To address these challenges, we employ an Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC) methods.
+AIS constructs a sequence of intermediate distributions that smoothly transition from an initial, tractable distribution (e.g., a prior over symbolic expressions) to the complex target posterior distribution.
+This annealing process is guided by a temperature-like parameter that gradually emphasizes the data likelihood, allowing for more efficient exploration of the probability landscape.
+
+		SMC enhances this procedure by propagating a population of particles—each representing a candidate symbolic expression—through the sequence of distributions.
+At each step, particles are reweighted based on the incremental change in the distribution, resampled to focus computational effort on high-probability regions, and mutated via operations.
+This combination of importance sampling, resampling, and mutation maintains diversity among the particles and prevents premature convergence to suboptimal models.
+
+		These features make AIS-SMC particularly well-suited for symbolic regression tasks, where the search space is not only high-dimensional but also structured and discontinuous.
+
 		\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
+
+		Let us now explain in more details how does this procedure goes.
+The goal is to reconstruct some distribution function $p(z)$, where here $z$ in going to be some polynomial.
+We will try to reconstruct this density function by a serie of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ is going to be the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{dz}$.
+We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N = 1$.
+We then define the unnormalized density at level $n$ in terms of a prior distribution $p_0(z)$ over the hypothesis space and an Loss function $L(z)$
+		\begin{equation}
+			\gamma_n(z) := p_0(z) \: \exp \left( -\beta_n L(z) \right)
+		\end{equation}
+
+		At each step, we have a set of particles $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
+To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and walculate the new unnormalized importance weight $w_n^k$.
+
+		Let us first focus on how we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ given $z_{n-1}^k$. To do so, we choose $q(z_n | z_{n-1})$ to be a Markov kernel
+
 		\item Discuss the fact that we allow float coefficients even though we know the coefficients will be only integers of square roots of integers?

### 2025-05-16 5d_pot_analysis_1_2_4_8_10/autoencoder_analysis_in_py.py

@@ -1,47 +1,0 @@
-import numpy as np
-import os
-import matplotlib.pyplot as plt
-import tensorflow as tf
-import time
-import keras
-from keras import layers,models,regularizers
-from tensorflow.keras.callbacks import LearningRateScheduler
-from sklearn.model_selection import train_test_split
-import argparse
-
-parser = argparse.ArgumentParser()
-parser.add_argument("-latent_dim", help="", default = 1, type = int)
-parser.add_argument("-input_dim", help="", default = 1, type = int)
-parser.add_argument("-n_epochs", help="", default = 1, type = int)
-parser.add_argument("-batch_size", help="", default = 1, type = int)
-parser.add_argument("-n_neurons", help="", default = 1, type = int)
-parser.add_argument("-path", help="", default = 'None', type = str)
-
-parser.parse_args()
-args = parser.parse_args()
-
-this_latent_dim = args.latent_dim
-input_dim = args.input_dim
-n_neurons = args.n_neurons
-
-x = np.load(args.path)
-x = tf.Variable(x)
-
-set_train, set_test = train_test_split(x.numpy(), test_size=0.1, random_state=1)
-
-inputs = layers.Input(shape=(input_dim,))
-encoded = layers.Dense(n_neurons, activation='sigmoid')(inputs)
-encoded = layers.Dense(n_neurons, activation='sigmoid')(encoded)
-encoded = layers.Dense(this_latent_dim)(encoded)  
-
-decoded = layers.Dense(n_neurons, activation='sigmoid')(encoded)
-decoded = layers.Dense(n_neurons, activation='sigmoid')(decoded)
-decoded = layers.Dense(input_dim)(decoded)  
-
-this_autoencoder = keras.Model(inputs, decoded)
-this_autoencoder.compile(optimizer='adam', loss='mse')
-
-history = this_autoencoder.fit(set_train, set_train, epochs=args.n_epochs, batch_size=args.batch_size, shuffle=True, validation_data=(set_test,set_test))
-    
-np.save(f"History_{input_dim}_{args.n_epochs}_{args.n_neurons}",history)
-this_autoencoder.save(f'ae_{input_dim}_{args.n_epochs}_{args.n_neurons}.keras')

### 2025-05-16 5d_pot_analysis_1_2_4_8_10/grad_descent.py

@@ -1,58 +1,0 @@
-import numpy as np 
-import tensorflow as tf 
-import sys
-import os
-import time 
-#module_path = "/home/bbastien/MLFlatDirections"
-module_path = "/Users/bastienduboeuf/Documents/Recherche/MLForFlatDirections3D/MLFlatDirections"
-sys.path.append(module_path)
-
-import grad_descent_module as gdm 
-import potentials as pot
-import argparse
-
-parser = argparse.ArgumentParser()
-parser.add_argument("-file_of_points", help="File where we should take the points from. If 'None', randomly initialize the points", default = "None", type = str)
-parser.add_argument("-out_file_of_points", help="File where we should save the points.", default = "None", type = str)
-parser.add_argument("-n_points", help="Numbers of point to initialize", default = 10000, type = int)
-parser.add_argument("-update_opt", help="Wether to reinitialize the optimizer", default = False, type = bool)
-parser.add_argument("-n_steps", help="Number of epochs for the gradient descent", default = 1000, type = int)
-parser.add_argument("-n_steps_opt", help="After how many steps should the optimier be reinitialize", default = 200, type = int)
-parser.add_argument("-step_stop_opt", help="After how many steps should the reinitialization be stopped", default = 1500, type = int)
-parser.add_argument("-alpha", help="Learning rate", default = 10**(-2), type = float)
-parser.add_argument("-n_step_print", help="Frequency for printing the output", default = 10, type = int)
-parser.add_argument("-n_var", help="Number of variable", default = 13, type = int)
-#parser.add_argument("-pot", help="Name of the potential", default =, type = int)
-
-parser.parse_args()
-args = parser.parse_args()
-
-n_points = args.n_points
-if args.file_of_points != 'None':
-    x = tf.Variable(np.load(args.file_of_points))
-else: 
-    this_seed = int((time.time()-int(time.time()))*1000)
-    np.random.seed(this_seed)
-    x = tf.Variable(2*np.random.rand(n_points,args.n_var)-1, dtype=tf.float32)
-
-this_history,this_x = gdm.grad_descent_potential(pot.V3d_sugra, 
-                                                 x, 
-                                                 update_opt = args.update_opt, 
-                                                 n_steps = args.n_steps,
-                                                 n_steps_opt = args.n_steps_opt, 
-                                                 step_stop_opt = args.step_stop_opt, 
[…]

### 2025-05-16 potentials.py

@@ -1,0 +1,187 @@
+import tensorflow as tf 
+
+def V_5d_1(x):
+    """Constructed by Camille. Should be a line"""
+    x1,x2,x3,x4,x5 = tf.split(x,5,axis=1)
+    return 29 * (x1 ** 2) + 41.66666666666667 * (x1 ** 3) + 81 * (x1 ** 4) -36 * x1 * x2 + 540 * (x1 ** 3) * x2 + 20 * (x2 ** 2) + 1350 * (x1 ** 2) * (x2 ** 2) + 1500 * x1 * (x2 ** 3) + 625 * (x2 ** 4) + 32 * x1 * x3 -50 * (x1 ** 2) * x3 + 324 * (x1 ** 3) * x3 + 1620 * (x1 ** 2) * x2 * x3 + 2700 * x1 * (x2 ** 2) * x3 + 1500 * (x2 ** 3) * x3 + 20 * (x3 ** 2) + 20 * x1 * (x3 ** 2) + 486 * (x1 ** 2) * (x3 ** 2) + 1620 * x1 * x2 * (x3 ** 2) + 1350 * (x2 ** 2) * (x3 ** 2) -2.666666666666667 * (x3 ** 3) + 324 * x1 * (x3 ** 3) + 540 * x2 * (x3 ** 3) + 81 * (x3 ** 4) -4 * x1 * x4 -25 * (x1 ** 2) * x4 -540 * (x1 ** 3) * x4 + 40 * x2 * x4 -2700 * (x1 ** 2) * x2 * x4 -4500 * x1 * (x2 ** 2) * x4 -2500 * (x2 ** 3) * x4 + 40 * x3 * x4 + 20 * x1 * x3 * x4 -1620 * (x1 ** 2) * x3 * x4 -5400 * x1 * x2 * x3 * x4 -4500 * (x2 ** 2) * x3 * x4 -4 * (x3 ** 2) * x4 -1620 * x1 * (x3 ** 2) * x4 -2700 * x2 * (x3 ** 2) * x4 -540 * (x3 ** 3) * x4 + 40 * (x4 ** 2) + 5 * x1 * (x4 ** 2) + 1350 * (x1 ** 2) * (x4 ** 2) + 4500 * x1 * x2 * (x4 ** 2) + 3750 * (x2 ** 2) * (x4 ** 2) -2 * x3 * (x4 ** 2) +
[…]

### 2025-05-16 utils.py

@@ -1,0 +1,271 @@
+import itertools
+import sympy as sp
+from tqdm import tqdm
+import numpy as np 
+import os 
+from matplotlib.colors import LogNorm
+import matplotlib.pyplot as plt
+from matplotlib import colors 
+from matplotlib.ticker import PercentFormatter 
+from sklearn.decomposition import PCA
+
+def triangular_plot(chains,save='None',xlim='None',ylim='None',figsize=(25,25),names=None):
+    data=chains
+    nsteps,ndim=chains.shape
+    fig = plt.figure(figsize=figsize)
+    fig.set(facecolor = "white")
+    for i in range(ndim):
+        ax = fig.add_subplot(ndim,ndim,i*ndim+i+1)
+        ax.hist(data[:,i], 100, color="k", histtype="step")
+        if names == 'None':
+            ax.set_title(f"x{i+1}")
+        else: 
+            ax.set_title(str(names[i]))
+    for i in range(ndim):
+        for j in range(i):
+            plt.subplot(ndim,ndim,ndim*i+j+1)
+            counts,xbins,ybins,image = plt.hist2d(data[:,j],data[:,i],bins=100
+                                      ,norm=LogNorm()
+                                      ,cmap = plt.cm.rainbow)
+            plt.colorbar()
+            plt.contour(counts.transpose(),extent=[xbins[0],xbins[-1],ybins[0],ybins[-1]],
+            linewidths=0.5, cmap = plt.cm.rainbow, levels = [1,100,1000,10000])
+            if not ylim == "None": 
+                plt.ylim(ylim)
+            if not xlim == "None":
+                plt.xlim(xlim)
+    if save != 'None':
+        plt.savefig(save,transparent=False)
+        plt.show()
+    else: 
+        plt.show()
+
+def triangular_plot_slopes(chains,save='None',xlim='None',ylim='None'):
+    data=chains
+    nsteps,ndim=chains.shape
+    fig = plt.figure(figsize=(20,20))
+    fig.set(facecolor = "white")
+    for i in range(ndim):
+        for j in range(i):
+            ax=fig.add_subplot(ndim,ndim,ndim*i+j+1)
+            #those_slope0=np.extract(np.abs(data[:,0])>0.2,data[:,i]/data[:,j])
+            those_slope0=data[:,i]/data[:,j]
+            those_slope=np.extract(np.abs(those_slope0)<10,those_slope0)
+            ax.hist(those_slope,bins=100)
[…]

### 2025-05-16 Draft_MLFlatDirections.tex
Little comments.
Comments during meeting.

@@
 \end{equation}
+\ce{Change notation to keep $x$ for the polynomial variables?}
+
+\ce{Discuss here why we need numerical methods: to complicated for mathematica to simplify the gradient.}
 
@@
 	\subsection{Gradient descent and local analysis}
-	\begin{itemize}[label=\textbullet]
-		\item Gradient descent: implementation, sampling, time needed, loss.
-
+		\paragraph{Gradient descent: implementation, sampling, time needed, loss}
 		In order to look for flat direction in this potential, we will use numerical tools.
@@
 This shows all possible $2d$ projections of the data as well as the $1d$ histograms of the data after the gradient descent.
-		\begin{figure}
+		\begin{figure}[t]
 			\centering
@@
 		\end{enumerate}
-		\item Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least fex points in each direction).
+
+		\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least fex points in each direction)}
 
@@
 
-		\item Clusteting: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space.
-
+		\paragraph{Clusteting: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space}
 		Something that might happen, is that we have several manifolds of dimesion 3, and the dimension 4 points we saw above are actually the intersection of those manifolds.
@@
 We choose a minimal cluster size of 10 points.
-Out of the 100000, the algorithm finds 3 cluster : one on dimension 10, one of dimension 91747 and a last one of dimension 6849 (not a total of 100000??).
+Out of the 100000, the algorithm finds 3 cluster : one on dimension 10, one of dimension 91747 and a last one of dimension 6849 (not a total of 100000??
+Clustering only on the point with 3d neighbourhood to avoid intersections).
 The last cluster are just the points that the algorithm did not managed to fit into any cluster.
@@
 
-		%\item After PCA and clustering we know that the points after the gradient descent sample a three-dimensional manifold.
-	\end{itemize}
+		After PCA and clustering we know that the points after the gradient descent sample a three-dimensional manifold.
 
@@
 	\paragraph{Results}
-	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}. For 100 runs with parameters
+	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}.
+For 100 runs with parameters \ce{\texttt{max degree} is 4, \texttt{max num monomials} is 6.}
 	\begin{equation}
@@
 	\end{equation}
-	the code finds the 7 different following polynomials:
+	the code finds the 7 different following polynomials: \ce{Mention that we ``rounded'' the coefficients to integer and square root of them.}
 	\begin{subequations} \label{eq:pols}
@@
   \end{subequations}
-  where $\tilde{x}_{8} = e^{x_{8}}$, with the distribution:
+  where $\tilde{x}_{8} = e^{x_{8}}$, with the distribution: \ce{It's not a distribution, how to name it? Frequency?}
   \begin{equation}
@@
 The averaged time needed for a single run on a PC in $\sim 1400\,{\rm s}$.
+\ce{This timing is with \texttt{analysis}, it may be less without.}
+
+  \ce{Draw histograms of the polynomials distribution to discuss runs with multiple outputs?}
 
@@
 \end{equation}
-gives the same solution
+gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
 \begin{equation}

### 2025-05-19 Draft_MLFlatDirections.tex
minor changes in the draft, mainly notations
Update the draft with ASMC almost written and improve paragraphs on grad des/PCA/clsutering

@@
 		\paragraph{Gradient descent: implementation, sampling, time needed, loss}
-		In order to look for flat direction in this potential, we will use numerical tools.
-The path we will follow is the following : first we will sample the underlying manifold, then we will use numerical tools to exctract analytics information on this cloud of points.
-Therefore the first step is to sample the manifold.
-To do so, we choose to do a basic gradient descent.
-We start by randomly uniformy initializing points in an hypercube of length $[-2,2]$.
-This will be important latter to have points which are not only in $[-1,1]$.
-We choose to have $10^5$ points.
-For this example.
+
+		To identify the flat directions in the potential, we will use numerical tools.
+The procedure is as follows: first, we sample the underlying manifold, and then we use numerical techniques to extract analytical information from the resulting cloud of points.
+The first step is thus to sample the manifold.
+
+		To do so, we perform a basic gradient descent.
+We begin by randomly and uniformly initializing points within a hypercube of range $[-2,2]$.
+This choice is important to ensure that points are not restricted to the inner range $[-1,1]$.
+For this example, we choose to generate $10^5$ points.
 This number is motivated by the dimensionality of our problem.
-If all possible directions are going to be populated, and if wen want $\mathcal{O}(10)$ points in each direction, then we need  $\mathcal{O}(10^5)$ points.
-As the true internal dimension of the manifold is lesser or equal than 5, this number provides an upper bound for the number of points needed to sufficiently sample the manifold.
-We then perfom a gradient descent on the point using the automatic differentiation method of tensorflow.
-For the loss function, we use
+If we aim to populate all possible directions and want approximately $\mathcal{O}(10)$ points per direction, then we require $\mathcal{O}(10^5)$ points.
+Given that the true intrinsic dimensionality of the manifold is less than or equal to 5, this value serves as a conservative upper bound for the number of points needed to adequately sample the manifold.
+
+		We then perform gradient descent on the points using TensorFlow’s automatic differentiation. The loss function is defined as:
 		\begin{equation}
-			\mathcal{L} = \sum_{i = 1}^{n_{points}} |\nabla V(\vec{x}_i)|^2
+			\mathcal{L} = \sum_{i = 1}^{n_{points}} || \nabla V(\vec{x}^{,i})||^2
 		\end{equation}
-		with $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$. We choose to use the Adam optimizer and use a learning rate of $10^{-2}$. We run the gradient descent for $10000$ epochs to make sure of convergence. 
+		where $\vec{x}^{\,i} = (x^i_1,x^i_2,x^i_4,x^i_8,x^i_{10})$ denotes the data points.
+We use the Adam optimizer with a learning rate of $10^{-2}$ and run the gradient descent for $10,000$ epochs to ensure convergence.
+
 		% \begin{figure}
@@
 			% \end{figure}
-		As a first visualisation, we show a triangular plot of the data in Fig.
+
+		As a first visualization, we present a triangular plot of the data in Fig.
 \ref{triangular_plot_1_2_4_8_10}.
-This shows all possible $2d$ projections of the data as well as the $1d$ histograms of the data after the gradient descent.
+This figure shows all possible 2D projections of the data, along with the 1D histograms of each coordinate after gradient descent.
+
 		\begin{figure}[t]
@@
 
-		Comments :
-		\begin{enumerate}
-			\item We see some non trivial correlation between the data.
-Note however that some features we see can be caused by the fact that some places may be greater basin of attractions (this is for example what happend in the $x_1/x_2$ plot).
-However, the structure we see in the $x_4/x_8$ or $x_4/x_{10}$ is a remnant of true features of the manifold
-			\item All directions seems to be well populated 
-			\item A great majority of the points fall in the $\vec{0}$ point.
-This is not too surprising.
-This just means that the round sphere solution has a greater basin of attraction.
-Even so, those points are going to be sufficiently good for the rest of the analysis, and we do not try to move the points along flat directions (to depopulate the origin et repopulate the rest).
-		\end{enumerate}
+		We can make a few comments on those plots.
+First, we observe non-trivial correlations in the data.
+Some of these may result from larger basins of attraction, such as in the $x_1/x_2$ plot.
+However, the structures seen in the $x_4/x_8$ or $x_4/x_{10}$ plots likely reflect genuine features of the manifold, and will show latter that this is indeed the case.
+We also note that alll directions appear to be well populated.
+Furthermore, we can notice that a large majority of the points converge to the origin $\vec{0}$.
+This is not surprising, as this just mean that the round sphere solution has a larger basin of attraction, which sounds reasonable.
+We do not however attempt to shift the points along flat directions to depopulate the origin or repopulate other regions.
 
@@
 
-		Once the gradient descent is done and we sampled the flat direction, it remains to determine what is the underlying manifolds.
-We would like to obtain some analytics expression for this, not only a numerical solution.
-Before proceeding to any sort of symbolic regression and look for such an analytic expression, there is a few things we can do to gain so understanding on the data, such as determining the dimensionality of the manifold, and wheter it a one piece or several pieces manifolds (like 2 intersecting hyperplane or so).
-To do so, we run a local Principal Component Analysis (PCA) algorithm.
-For each point, we select the $k$ nearest neighboors, and we run a PCA analysis on thos points.
-This allows to determine how many directions are needed to explain a given percentage of the spreding of the data, call it $\epsilon$.
-In other words, this allows to determine what is the local dimension around each point.
-We ran such an algorithm for a number of $k$ nearest neighboors equal to $[5,10,20,50,100]$, and for $\epsilon = 0.99$.
-The results are shown in \ref{local_pca}.
+		Once the gradient descent has been completed and the flat direction sampled, the next step is to identify the structure of the underlying manifold.
+Our goal is to eventually obtain an analytical expression, not just a numerical description.
+Before applying symbolic regression to search for such an expression, we can first perform some exploratory analyses to better understand the data.
+Specifically, we aim to determine the dimensionality of the manifold and whether it consists of a single connected component or multiple disjoint components (e.g., two intersecting hyperplanes).
+
+		To this end, we apply a local Principal Component Analysis (PCA).
+For each point, we identify its $k$ nearest neighbors and perform a PCA on that local neighborhood.
+This procedure allows us to determine how many principal directions are needed to explain a given proportion $\epsilon$ of the data variance.
+In other words, it provides an estimate of the local dimensionality around each point.
+
+		We perform this analysis for several values of $k$, namely $k \in \{5, 10, 20, 50, 100\}$, and we fix $\epsilon = 0.99$. The results are presented in Fig. \ref{local_pca}.
+
 		\begin{figure}
@@
 			\caption{Results of the local PCA analysis.
-On the $x$-axis is the dimension found by the algorithm, and on the $y$-axis the proportion of points.
-The different curves are for different $k$-nearest neighboors.}
+The $x$-axis shows the dimension inferred by the algorithm, and the $y$-axis indicates the proportion of points for which that dimension was found.
+Each curve corresponds to a different value of $k$ in the $k$-nearest neighbors.}
 			\label{local_pca}
@@
 
-		We see that, for every choice of nearest neighboor, a peak at $d=3$, which indicates an underlying dimension of 3 for the manifold.
-We also see that for $k=5$, that a number a point seems to indicate a dimensionality of 2.
-However, if the dimension is indeed 3, then 5 points may not be enough to sufficiently populate the three directions, explaining the failure of the algorithm to find 3.
-We also see that for $k\le20$, that there is more and more points indicating a dimension equals to 4 or 5.
-This can be explained by the fact that we increasing the number of neighboors, we are doing a rougher coarse graining, loosing information on the localilty.
-A too large number of neighboors implies including points which are not really local anymore, artificially increasing the local dimension.
-We conclude that the dimension of the manifold we are looking at is 3.
+		We observe that for every choice of $k$, there is a prominent peak at $d = 3$, suggesting that the underlying manifold is three-dimensional.
+For $k = 5$, a noticeable fraction of points are assigned a dimensionality of 2.
+This can be attributed to the fact that if the true dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality.
+
+		Additionally, for $k \geq 20$, we observe an increasing number of points being assigned dimensionalities of 4 or 5.
+This behavior can be explained by the loss of locality when the number of neighbours becomes too large: increasing $k$ results in a coarser approximation, and the algorithm may then incorporate points that are no longer truly local.
+This artificial enlargement of the neighborhood can cause the estimated local dimensionality to rise.
+
+		We thus conclude that the manifold under investigation has an intrinsic dimension of 3.
 
 		\paragraph{Clusteting: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space}
-		Something that might happen, is that we have several manifolds of dimesion 3, and the dimension 4 points we saw above are actually the intersection of those manifolds.
-If we indeed picture the intersection of two lines, then at the intersection point, the local dimension found by the previous algorithm should be 2.
-To exclude such a scenario, we run a clustering algorithm, based on local density.
-For this, we use the HDBSAN algorithm.
-(details on how it works?).
-We choose a minimal cluster size of 10 points.
-Out of the 100000, the algorithm finds 3 cluster : one on dimension 10, one of dimension 91747 and a last one of dimension 6849 (not a total of 100000??
-Clustering only on the point with 3d neighbourhood to avoid intersections).
-The last cluster are just the points that the algorithm did not managed to fit into any cluster.
-For the first one, we interpret it as some fluctuation in our data, making some region of different density as the other, but we do not believe this is some real result, more an artefact.
-Therefore, what the algorithm tells us, is that there seems to be on cluster with more than $90\%$ of the data.
-We show on \ref{3dplots} three-dimensional projections of the data.
+
+		One possible scenario is that our data actually consists of several distinct three-dimensional manifolds, and the points previously identified with dimension $4$ may lie at the intersections of these manifolds.
+To illustrate, consider the intersection of two lines: at the intersection point, the local dimensionality estimated by the previous PCA algorithm would be 2.
+To rule out this possibility, we apply a clustering algorithm based on local density, where we only select the points of dimension 3.
+This, way, we remove the possible intersection points with dimension 4.
+For the purpose of the clustering, we use the HDBSCAN algorithm\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation.
+Briefly, it is a density-based clustering method that extends DBSCAN by converting it into a hierarchical clustering algorithm and then extracting a flat clustering based on the stability of clusters.}.
+
+		We set the minimum cluster size to 10 points. Out of the 986,060 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.
+
+		The smallest cluster (10 points) is likely an artifact of local fluctuations in the data density and is not interpreted as physically meaningful.
+The last group, comprising 6,849 points, consists of points that the algorithm could not assign to any cluster.
+We interpret these as outliers or edge points rather than representatives of a separate manifold.
+
+		What the algorithm does indicate, however, is that over 90\% of the data belongs to a single dominant cluster. In Fig.~\ref{3dplots}, we show 3D projections of the data to visualize the clustering.
 
@@
 			\includegraphics[scale=0.4]{Figures/3d_plot_x2_x4_x8.png}
-			\caption{3d plot of $x_4$, $x_8$ and $x_{10}$}
+			\caption{3D plots of the data in selected coordinates. Left: $(x_4, x_8, x_{10})$. Right: $(x_2, x_4, x_8)$.}
 			\label{3dplots}
 		\end{figure}
-		On these scatter plots, the turquoise points are those belonging to the main cluster, and the purple are those for which the algorithm failed to give them a cluster.
-On of the two plot, we can see some few yellow points which correspond to the small cluster with 10 points.
-We can see, from what we can tell with those plots, that all points that could not be assigned to a cluster are on the boarder of the data.
-Therefore, we interpret the fact that those point could not be assigned, not because there are part of another cluster, and a manifold, but because of the lack of points around them due to the fact they are on the boundary of our data.
-We conclude from this analysis, that we possess here a sampling of a unique 3 dimensional manifold.
 
-		After PCA and clustering we know that the points after the gradient descent sample a three-dimensional manifold.
+		In these scatter plots, turquoise points belong to the main cluster, while purple points are those that the algorithm failed to assign.
+In one of the plots, a few yellow points can be seen; these correspond to the smallest cluster of 10 points.
+From visual inspection, it appears that the unassigned (purple) points lie mostly on the boundary of the sampled region.
+We therefore interpret their unassigned status not as evidence of belonging to another manifold, but rather as a result of insufficient local density near the edges of the dataset.
+
+		From this analysis, we conclude that the gradient descent procedure has produced a sampling of a single, connected, three-dimensional manifold.
+
+		\vspace{0.5em}
+
+		After performing both PCA and clustering, we thus confirm that the data obtained after gradient descent samples a three-dimensional manifold.
 
@@
 To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and walculate the new unnormalized importance weight $w_n^k$.
+The latter are updated using the formula
+		\begin{equation}
+			w_n^k = w_{n-1}^k \times \alpha_{n}^k
+		\end{equation}
+		where $\alpha_n^k$ is the incremental importance weight. The standard form for $\alpha_n^k$, which requires introducing an auxiliary backward transition kernel $q(z_{n-1} | z_n)$, is:
+		\begin{equation}
+			\alpha_n^k = \frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) } 
+		\end{equation}
+		The weights are finally normalized and we get $w_n^k \rightarrow \frac{w_n^k}{\sum_j w_n^j}$.
 
-		Let us first focus on how we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ given $z_{n-1}^k$. To do so, we choose $q(z_n | z_{n-1})$ to be a Markov kernel
+		Let's us now focus on the forward ($q(z_n^k | z_{n-1}^k)$) and backward propagation kernel ($q(z_{n-1}^k | z_n^k)$).
+The forward propagation kernel defines how we generate the state at time $n$ given the state at time $n-1$.
+It gives the probability to transition from $z_{n-1}$ to $z_n$.
+The backward kernel: It represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
+The purpose of $q$ is to give a proposition for $z_n$ given $z_{n-1}$.
+For the implementation of the two, we decide to implement an AIS-style MCMC code : we make some move in the space of polynomials, and then accept or reject those new polynomials based on an acceptance rate.
+So we first need to choose what are the available moves in the space of polynomials.
+Here are the choices we have made for our symbolic regression task :
+		\begin{itemize}
+			\item Coefficient pertubation.
+Given a polynomial $z_{n-1}$, we choose randomly one of his coefficient and modify it by a random noise from the guassian distribution $\mathcal{N}(0,\sigma^2)$.
+So for eg : $2 x + 3 y^2 \rightarrow  2.1 x + 3 y^2$.
+			\item Variable multiplication.
+Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and multiply it by one of the available variable.
+So for eg : $2 x + 3 y^2 \rightarrow  2 x y + 3 y^2$.
+			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x + 3 y^2 \rightarrow  2 x y + 3 y^2$.
+		\end{itemize}
+		This implementation allows us to straightforwardly calculate the forward and backward propagation kernel.
+For example, the case of the coefficient pertubation is symmetric.
+Therefore $q(z_n^k | z_{n-1}^k) = q(z_{n-1}^k | z_n^k)$, which allows to simplify the calculation of the incremental importance weight.
+
+		The acceptance ration for the MCMC algorithm is given by : 
+		\begin{equation}
+			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)
+		\end{equation}
+		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
+
+		Before closing the section, we need to discuss what is the Loss function we choose.
+It is recquired to compute the unormalized distribution $\gamma_n$.
+Assume that we have $z = \sum_k c_k X_k$, where $c_k$ are the coefficients of the polynomials, and $X_k$ is a short notations for all the possible monomials up to a given degree (so if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_k$ are $1, x, y, x^2, y^2, x y$).
+For the Loss function, we decided to take :
+		\begin{equation}
+			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k c_k}
+		\end{equation}
+		So the first term is just the sum of the squared of the polynomial evaluated on the data.
+We want to make this 0 so we find polynomial that annihilates our data.
+The second part is a regularisation factor : it prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem.
+We typically take $\lambda \sim \mathcal{O}(1000)$.
 
 		\item Discuss the fact that we allow float coefficients even though we know the coefficients will be only integers of square roots of integers?
+
 		\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
+
+		Once the Annealing loop is over, we end up with a total of $n_{sample}$ particles, which in principle should be close to annihilate our data, but whose coefficient may need some more fine tuning.
+To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a pertubation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller.
+This allow to fine-tune the coefficients.
+
 		\item Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
@@
       p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}\tilde{x}_{8} + x_{2}\tilde{x}_{8}x_{10} - \sqrt{2}\,x_{2}x_{4}\tilde{x}_{8},\\
-      p_{2} &= 2\,x_{2} + 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}\tilde{x}_{8}x_{10}^{2},\\
+      p_{2} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}\tilde{x}_{8}x_{10}^{2},\\
       p_{3} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\tilde{x}_{8}x_{10} + 2\,x_{1}x_{4}\tilde{x}_{8}

### 2025-05-19 Draft_MLFlatDirections.tex
Update with more results of AIS.

@@
 	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}.
-For 100 runs with parameters \ce{\texttt{max degree} is 4, \texttt{max num monomials} is 6.}
-	\begin{equation}
-		\begin{gathered}
-			n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
-			{\rm sample\ size = 10000},\quad p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-		\end{gathered}
-	\end{equation}
-	the code finds the 7 different following polynomials: \ce{Mention that we ``rounded'' the coefficients to integer and square root of them.}
+The code finds the 7 different following polynomials: \ce{Mention that we ``rounded'' the coefficients to integer and square root of them.}
 	\begin{subequations} \label{eq:pols}
@@
   \end{subequations}
-  where $\tilde{x}_{8} = e^{x_{8}}$, with the distribution: \ce{It's not a distribution, how to name it? Frequency?}
+  where $\tilde{x}_{8} = e^{x_{8}}$. They are found with different frequencies, depending on the chosen parameters.
+
+  \begin{enumerate}
+  		\item For 100 runs with parameters
+		\begin{equation}
+			\begin{gathered}
+				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
+				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
+				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
+			\end{gathered}
+		\end{equation}
+		the polynomials are found at the following frequencies
 	  \begin{equation}
@@
 	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-  		Distribution & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
+	  		Frequency & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
 	  	\end{tabular}
@@
 The code fails to find any polynomial in 13\% of the time.
-The averaged time needed for a single run on a PC in $\sim 1400\,{\rm s}$.
+The averaged time needed for a single run on a PC in $\sim 700\,{\rm s}$.
 \ce{This timing is with \texttt{analysis}, it may be less without.}
+
+	  Averaged number of particles reproducing a target in a successful run: $931$
+
+	  Mean loss with regularisation for particles reproducing a target: $597.0$
+
+	  Mean loss without regularisation for particles reproducing a target: $345.0$
+  		\item For 100 runs with parameters
+		\begin{equation}
+			\begin{gathered}
+				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
+				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
+				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
+			\end{gathered}
+		\end{equation}
+		the polynomials are found at the following frequencies
+	  \begin{equation}
+	  	\begin{tabular}{l|cccccccc}
+	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
+	  		Frequency & 69\% & 11\% & 7\% & 12\% & 0\% & 4\% & 0\% & 13\%
+	  	\end{tabular}
+	  \end{equation}
+	  Averaged number of particles reproducing a target in a successful run: $960$
+
+	  Mean loss with regularisation for particles reproducing a target: $605.8$
+
+	  Mean loss without regularisation for particles reproducing a target: $358.8$
+	  \item For 100 runs with parameters
+		\begin{equation}
+			\begin{gathered}
+				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
+				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.1, \\
+				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
+			\end{gathered}
+		\end{equation}
+		the polynomials are found at the following frequencies
+	  \begin{equation}
+	  	\begin{tabular}{l|cccccccc}
+	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
+	  		Frequency & 76\% & 18\% & 10\% & 6\% & 4\% & 1\% & 2\% & 6\%
+	  	\end{tabular}
+	  \end{equation}
+	  Averaged number of particles reproducing a target in a successful run: $973$
+
+	  Mean loss with regularisation for particles reproducing a target: $854.2$
+
+	  Mean loss without regularisation for particles reproducing a target: $602.5$
+  \end{enumerate}
 

### 2025-05-20 Draft_MLFlatDirections.tex
Update the results section on AIS and add figures.

@@
   		\item For 100 runs with parameters
-		\begin{equation}
+		\begin{equation} \label{eq:sample10000beta5}
 			\begin{gathered}
@@
 
-	  Averaged number of particles reproducing a target in a successful run: $931$
+	  Averaged number of particles reproducing a target in a successful run: $931 \pm 230$
 
-	  Mean loss with regularisation for particles reproducing a target: $597.0$
+	  Mean loss with regularisation for particles reproducing a target: $285 \pm 108$
 
-	  Mean loss without regularisation for particles reproducing a target: $345.0$
+	  Mean loss without regularisation for particles reproducing a target: $33 \pm 24$
   		\item For 100 runs with parameters
@@
 	  \end{equation}
-	  Averaged number of particles reproducing a target in a successful run: $960$
+	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta5}.
 
-	  Mean loss with regularisation for particles reproducing a target: $605.8$
+	  Averaged number of particles reproducing a target in a successful run: $960 \pm 175$
 
-	  Mean loss without regularisation for particles reproducing a target: $358.8$
+	  Mean loss with regularisation for particles reproducing a target: $282 \pm 91$
+
+	  Mean loss without regularisation for particles reproducing a target: $35 \pm 24$
+
+	  \begin{figure}[h!]
+	  	\centering
+	  	\begin{tikzpicture}
+	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32.pdf}};
+	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32_detailed.pdf}};
+	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+	  	\end{tikzpicture}
+	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta5}.
+(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
+The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
+	  	\label{fig:sample10000beta5}
+	  \end{figure}
+
 	  \item For 100 runs with parameters
-		\begin{equation}
+		\begin{equation} \label{eq:sample10000beta3}
 			\begin{gathered}
@@
 	  \end{equation}
-	  Averaged number of particles reproducing a target in a successful run: $973$
+	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3}.
 
-	  Mean loss with regularisation for particles reproducing a target: $854.2$
+	  Averaged number of particles reproducing a target in a successful run: $973 \pm 103$
 
-	  Mean loss without regularisation for particles reproducing a target: $602.5$
+	  Mean loss with regularisation for particles reproducing a target: $310 \pm 115$
+
+	  Mean loss without regularisation for particles reproducing a target: $58 \pm 40$
+
+	  \begin{figure}[h!]
+	  	\centering
+	  	\begin{tikzpicture}
+	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
+	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
+	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+	  	\end{tikzpicture}
+	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
+(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
+The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
+	  	\label{fig:sample10000beta3}
+	  \end{figure}
+
+	  \item For 100 runs with parameters
+		\begin{equation} \label{eq:sample1000}
+			\begin{gathered}
+				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
+				\texttt{sample size} = 1000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
+				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
+			\end{gathered}
+		\end{equation}
+		the polynomials are found at the following frequencies
+	  \begin{equation}
+	  	\begin{tabular}{l|cccccccc}
+	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
+	  		Frequency & 72\% & 27\% & 3\% & 19\% & 2\% & 0\% & 0\% & 12\%
+	  	\end{tabular}
+	  \end{equation}
+	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample1000}.
+
+	  Averaged number of particles reproducing a target in a successful run: $401 \pm 389$
+
+	  Mean loss with regularisation for particles reproducing a target: $406 \pm 193$ \ce{Needs to be renormalized by the sample size.}
+
+	  Mean loss without regularisation for particles reproducing a target: $272 \pm 192$ \ce{Needs to be renormalized by the sample size.}
+
+	  \begin{figure}[h!]
+	  	\centering
+	  	\begin{tikzpicture}
+	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44.pdf}};
+	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44_detailed.pdf}};
+	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+	  	\end{tikzpicture}
+	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
+(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
+The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
+	  	\label{fig:sample1000}
+	  \end{figure}
   \end{enumerate}

### 2025-05-20 Draft_MLFlatDirections.tex
Corrected small typos, added some comments and a reference.

@@
 
-		\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least fex points in each direction)}
+		\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least few points in each direction)}
 
@@
 		To this end, we apply a local Principal Component Analysis (PCA).
-For each point, we identify its $k$ nearest neighbors and perform a PCA on that local neighborhood.
+For each point, we identify its $k$ nearest neighbours and perform a PCA on that local neighbourhood.
 This procedure allows us to determine how many principal directions are needed to explain a given proportion $\epsilon$ of the data variance.
@@
 The $x$-axis shows the dimension inferred by the algorithm, and the $y$-axis indicates the proportion of points for which that dimension was found.
-Each curve corresponds to a different value of $k$ in the $k$-nearest neighbors.}
+Each curve corresponds to a different value of $k$ in the $k$-nearest neighbours.}
 			\label{local_pca}
@@
 This behavior can be explained by the loss of locality when the number of neighbours becomes too large: increasing $k$ results in a coarser approximation, and the algorithm may then incorporate points that are no longer truly local.
-This artificial enlargement of the neighborhood can cause the estimated local dimensionality to rise.
+This artificial enlargement of the neighbourhood can cause the estimated local dimensionality to rise.
 
@@
 
-		\paragraph{Clusteting: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space}
+		\paragraph{Clustering: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space}
 
@@
 
-		We set the minimum cluster size to 10 points. Out of the 986,060 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.
+		We set the minimum cluster size to 10 points.
+Out of the 986,060 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.
+\ce{Are those numbers right?
+We loose more than 800,000 points?}
 
-		The smallest cluster (10 points) is likely an artifact of local fluctuations in the data density and is not interpreted as physically meaningful.
+		The smallest cluster (10 points) is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
 The last group, comprising 6,849 points, consists of points that the algorithm could not assign to any cluster.
@@
 
-		Now we have sampled the manifold and exctrated some basic information about it (namely its dimension and the fact that it is made of one block), we would like to see if we can exctract some analytic formula to caracterise it.
+		Now we have sampled the manifold and extracted some basic information about it (namely its dimension and the fact that it is made of one block), we would like to see if we can extract some analytic formula to characterise it.
 What we have at the moment, are points on a 3-dimensional manifold, which are embedded in a 5-dimensional space.
-Therefore we can conclude that, in order to caracterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
-If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $\tilde{x_{8}} = e^{x_8}$, that this potential is actually a polynomial of the embedding coordinates.
+Therefore we can conclude that, in order to characterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
+If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $\tilde{x}_{8} = e^{x_8}$, that, up to a global $e^{-2x_8}$ factor, this potential is actually a polynomial of the embedding coordinates.
 Therefore, the components of $|\nabla V|$ are also polynomials in those variables.
@@
 Of course if one takes directly the gradient of \eqref{eq:scalarpotential124810}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
-The problem we are facing here is therefore a problem of symbolic regression : we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
-There are a number of way one can deal with it, using already existing methods such as AI Feynman methods, or ..., or by doing rough gradient descent on the most general polynomial with arbitrary coefficients and trying to minimize its value once evaluated on the data points.
+The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
+There are a number of way one can deal with it, using already existing methods such as AI Feynman methods~\cite{Udrescu:2019mnk}, or ..., or by doing rough gradient descent on the most general polynomial with arbitrary coefficients and trying to minimize its value once evaluated on the data points.
 In the spirit of trying to build a generalisable method, we develop here our own method, which is based on symbolic regression using an Annealing Importance Sampling method.
@@
 
-		In the realm of symbolic regression, the objective is to uncover interpretable mathematical expressions that best describe a given dataset.
+		In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe a given dataset.
 In the problem discussed in this paper, we are looking for polynomial expressions such that $p(data) = 0$.
@@
 The goal is to reconstruct some distribution function $p(z)$, where here $z$ in going to be some polynomial.
-We will try to reconstruct this density function by a serie of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ is going to be the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{dz}$.
+\ce{Notational conflict: $p$ for polynomials and $p$ the distribution.} We will try to reconstruct this density function by series of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ is going to be the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{d}z$.
 We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N = 1$.
-We then define the unnormalized density at level $n$ in terms of a prior distribution $p_0(z)$ over the hypothesis space and an Loss function $L(z)$
+We then define the unnormalized density at level $n$ in terms of a prior distribution $p_0(z)$ over the hypothesis space and a loss function $L(z)$:
 		\begin{equation}
-			\gamma_n(z) := p_0(z) \: \exp \left( -\beta_n L(z) \right)
+			\gamma_n(z) := p_0(z) \: \exp \left( -\beta_n L(z) \right).
 		\end{equation}
@@
 So for eg : $2 x + 3 y^2 \rightarrow  2 x y + 3 y^2$.
-			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x + 3 y^2 \rightarrow  2 x y + 3 y^2$.
+			\item Variable division.
+Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable.
+So for eg : $2 x + 3 y^2 \rightarrow  2 x y + 3 y^2$.
+\ce{Change the example.}
 		\end{itemize}

### 2025-05-21 Draft_MLFlatDirections.tex
Update draft

--- 2025-05-19 Draft_MLFlatDirections.tex
@@
 \newcommand{\gl}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries (gl: #1)}}
+\newcommand{\bd}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries (bd: #1)}}
 
@@
 		where $\vec{x}^{\,i} = (x^i_1,x^i_2,x^i_4,x^i_8,x^i_{10})$ denotes the data points.
-We use the Adam optimizer with a learning rate of $10^{-2}$ and run the gradient descent for $10,000$ epochs to ensure convergence.
+To do the gradient descent, we have noted throught trial en error that reinitializing the optimizer after a periodic amount of steps were significantly speeding up the convergence.
+This is similar to what has been proposed in \cite{loshchilov2017sgdrstochasticgradientdescent} where they do warm restarts.
+However, we have noted that by doing so, the convergence was slower than just reinitializing the optimizer.
+We interpret this by arguying that when we reinitialize the optimizer, it forgets about its passed.
+Therefore, the effective learning rate used by the optimizer is truly the one passed, and not one adjusted by the optimizer.
+The loss function as well as the learning rate history are presented in Fig.
+\ref{label}
+		%We use the Adam optimizer with a learning rate of $10^{-2}$ and run the gradient descent for $10,000$ epochs to ensure convergence.
 
 %		\begin{figure}
-			% \includegraphics[scale = 0.5]{imagefile} % add loss history
+%			\includegraphics[scale = 0.5]{imagefile}
+%			\caption{Loss function for the gradient descent as well as the learning rate schedule, fixed with \texttt{tf.keras.optimizers.schedules.CosineDecayRestarts}, with parameters \texttt{initial_learning_rate = 0.01}, \texttt{first_decay_steps = 400}, \texttt{t_mul = 1.0} , \texttt{m_mul = 1.0}}
 %		\end{figure}
@@
 
-For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
-\begin{equation}
-	\begin{cases}
-		p_{i} = 0, \\
-		p_{j} = 0,
-	\end{cases}
+%For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
+%\begin{equation}
+%	\begin{cases}
+%		p_{i} = 0, \\
+%		p_{j} = 0,
+%	\end{cases}
+%\end{equation}
+%gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
+
+In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in Eq.~\ref{eq:pols}.
+We can now solve the system
+\begin{equation}\label{eq:solvepol}
+	p_i = 0, \quad \forall i \in {1,\dots,7}
 \end{equation}
-gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
+which leads to the following expressions:
 \begin{equation}
@@
 \end{equation}
-We checked that this defines a 3-parameter solution of three-dimensional half-maximal supergravity. Equivalently:
-\begin{equation}
+
+Alternatively, the system can be recast as:
+\begin{equation}\label{eq:rulex8x10}
 	\begin{cases}
-		\displaystyle \tilde{x}_{8} = \frac{x_{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
-		\displaystyle x_{10} = \sqrt{2}\,x_{4}\,\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
+		\displaystyle \tilde{x}{8} = \frac{x{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
+		\displaystyle x_{10} = \sqrt{2},x_{4},\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
 	\end{cases}
 \end{equation}
+
+As anticipated, this defines a three-parameter solution corresponding to a three-dimensional slice of the half-maximal supergravity scalar potential.
+
+Let us make a few remarks at this stage.
+First, it is possible to find solutions to Eq.~\ref{eq:solvepol} which, however, are not solutions of $\nabla V = 0$.
+For instance $x_1 = x_2 = 0$; such cases are excluded, as they do not satisfy the stationarity condition and therefore do not correspond to valid physical solutions.
+
+Secondly, one might argue that only two of the seven polynomials are sufficient to fully characterize the solution.
+That is, choosing any pair $(i,j) \in {1, \dots, 7}$ may suffice to extract a complete description.
+In practice, this is not entirely accurate.
+While such a pair can yield partial constraints—for example, recovering Eq.\ref{eq:rulex8x10}—it may also produce alternative (and potentially less general) parameterizations.
+Upon inspection, all such partial rules are found to be consistent with, and included in, the most general expressions given in Eq.\ref{eq:rulex8x10}.
+
 The solution preserves a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.

### 2025-05-21 Draft_MLFlatDirections.tex
update the draft

@@
 		\end{equation}
-		where $\vec{x}^{\,i} = (x^i_1,x^i_2,x^i_4,x^i_8,x^i_{10})$ denotes the data points.
-To do the gradient descent, we have noted throught trial en error that reinitializing the optimizer after a periodic amount of steps were significantly speeding up the convergence.
-This is similar to what has been proposed in \cite{loshchilov2017sgdrstochasticgradientdescent} where they do warm restarts.
-However, we have noted that by doing so, the convergence was slower than just reinitializing the optimizer.
-We interpret this by arguying that when we reinitialize the optimizer, it forgets about its passed.
-Therefore, the effective learning rate used by the optimizer is truly the one passed, and not one adjusted by the optimizer.
-The loss function as well as the learning rate history are presented in Fig.
-\ref{label}
-		%We use the Adam optimizer with a learning rate of $10^{-2}$ and run the gradient descent for $10,000$ epochs to ensure convergence.
+		where $\vec{x}^{,i} = (x^i_1,x^i_2,x^i_4,x^i_8,x^i_{10})$ denotes the data points.
 
-%		\begin{figure}
-%			\includegraphics[scale = 0.5]{imagefile}
-%			\caption{Loss function for the gradient descent as well as the learning rate schedule, fixed with \texttt{tf.keras.optimizers.schedules.CosineDecayRestarts}, with parameters \texttt{initial_learning_rate = 0.01}, \texttt{first_decay_steps = 400}, \texttt{t_mul = 1.0} , \texttt{m_mul = 1.0}}
-%		\end{figure}
+		Through trial and error, we observed that periodically reinitializing the optimizer significantly improved the convergence rate.
+This technique bears similarity to the concept of warm restarts introduced in \cite{loshchilov2017sgdrstochasticgradientdescent}.
+However, we found that simply scheduling the learning rate without resetting the optimizer yielded slower convergence.
+
+		We interpret this as follows: when the optimizer is reinitialized, it effectively "forgets" its past gradient history.
+As a result, the actual learning rate used corresponds more closely to the specified value, rather than being internally adjusted based on accumulated past gradients.
+This effect seems to contribute to faster convergence in our case.
+
+		The evolution of the loss function, along with the learning rate schedule, is shown in Fig.~\ref{fig:loss_grad_des}.
+As can be seen in this figure, the convergence rate improves significantly each time the optimizer is reinitialized.
+We also observe that, following the last few reinitializations, the loss exhibits a small bump immediately after the restart.
+
+		We interpret this behavior as a consequence of the increased learning rate: some points that previously had low loss values may momentarily worsen before benefiting from faster convergence.
+This effect is likely due to points initially located in regions with weak attractive basins being pushed toward areas where the potential gradient is steeper, thus accelerating their convergence.
+
+		Although this strategy introduces the risk of desampling certain regions in favor of others, we did not observe any such issue in the remainder of our analysis.
+
+		The Adam optimizer was used throughout the gradient descent process.
+We reinitialized it at steps \{250,500,750\}, and fixing the learning rate at $10^{-2}$.
+Then we reinitialized the optimizer at step 1000 but fix the learning rate at $10^{-3}$.
+Finally we reinitialize the optimizer at step 1500 with learning rate $10^{-4}$ and let it run for 1000 more epochs.
+At the end of the run, we found that all points sit close to the value $-4$, and that x\% of the data points are lying at a value with an error of xx.
+Similarly, we found that x\% of the data has a gradient smaller than xx.
+
+		\begin{figure}
+			\centering
+			\includegraphics[scale = 0.5]{Figures/Loss_grad_des.png}
+			\caption{Loss function for the gradient descent as well as the learning rate schedule, both in log scale. The red dashed lines correspond to epochs when the optimizer is reinitialized.}
+			\label{fig:loss_grad_des}
+		\end{figure}
 

### 2025-05-21 Draft_MLFlatDirections.tex
update the draft

@@
 
-		The Adam optimizer was used throughout the gradient descent process.
-We reinitialized it at steps \{250,500,750\}, and fixing the learning rate at $10^{-2}$.
-Then we reinitialized the optimizer at step 1000 but fix the learning rate at $10^{-3}$.
-Finally we reinitialize the optimizer at step 1500 with learning rate $10^{-4}$ and let it run for 1000 more epochs.
-At the end of the run, we found that all points sit close to the value $-4$, and that x\% of the data points are lying at a value with an error of xx.
-Similarly, we found that x\% of the data has a gradient smaller than xx.
+		\begin{figure}
+			\centering
+			\includegraphics[scale=0.35]{Figures/nabla_V_thres.png}
+			\quad
+			\includegraphics[scale=0.35]{Figures/V_values_thres.png}
+			\caption{Left panel: Number of data points with gradient norm smaller than the threshold indicated on the x-axis.
+Right panel: Number of data points whose value deviates from $-4$ by less than the threshold shown on the x-axis.}
+			\label{fig:Analyze_V_points}
+		\end{figure}
+
+		The Adam optimizer was employed throughout the gradient descent procedure.
+It was reinitialized at iterations {250, 500, 750}, with the learning rate fixed at $10^{-2}$.
+At iteration 1000, the optimizer was reinitialized once more, this time with a reduced learning rate of $10^{-3}$.
+A final reinitialization was performed at iteration 1500, setting the learning rate to $10^{-4}$, and the optimization was continued for an additional 1000 epochs.
+
+		Upon completion, it was observed that all data points converged to values close to $-4$.
+Specifically, nearly all data points attained values within an absolute error of $10^{-4}$, with the exception of four points whose deviations were on the order of $10^{-3}$.
+Similarly, 99,739 out of 100,000 data points exhibited gradient norms smaller than $10^{-3}$.
+These results are summarized in Figure~\ref{fig:Analyze_V_points}.
 
@@
 			\includegraphics[scale = 0.5]{Figures/Loss_grad_des.png}
-			\caption{Loss function for the gradient descent as well as the learning rate schedule, both in log scale. The red dashed lines correspond to epochs when the optimizer is reinitialized.}
+			\caption{Evolution of the loss function during gradient descent and corresponding learning rate schedule, both plotted on a logarithmic scale.
+Red dashed lines indicate epochs at which the optimizer was reinitialized.}
 			\label{fig:loss_grad_des}
@@
 We also note that alll directions appear to be well populated.
-Furthermore, we can notice that a large majority of the points converge to the origin $\vec{0}$.
+		%Furthermore, we can notice that a large majority of the points converge to the origin $\vec{0}$.
 This is not surprising, as this just mean that the round sphere solution has a larger basin of attraction, which sounds reasonable.

### 2025-05-21 Draft_MLFlatDirections.tex
Added new run.

--- 2025-05-21 Draft_MLFlatDirections.tex
@@
 \newcommand{\gl}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries (gl: #1)}}
-\newcommand{\bd}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}{\boldmath\bfseries (bd: #1)}}
 
@@
 		where $\vec{x}^{\,i} = (x^i_1,x^i_2,x^i_4,x^i_8,x^i_{10})$ denotes the data points.
-To do the gradient descent, we have noted throught trial en error that reinitializing the optimizer after a periodic amount of steps were significantly speeding up the convergence.
-This is similar to what has been proposed in \cite{loshchilov2017sgdrstochasticgradientdescent} where they do warm restarts.
-However, we have noted that by doing so, the convergence was slower than just reinitializing the optimizer.
-We interpret this by arguying that when we reinitialize the optimizer, it forgets about its passed.
-Therefore, the effective learning rate used by the optimizer is truly the one passed, and not one adjusted by the optimizer.
-The loss function as well as the learning rate history are presented in Fig.
-\ref{label}
-		%We use the Adam optimizer with a learning rate of $10^{-2}$ and run the gradient descent for $10,000$ epochs to ensure convergence.
+We use the Adam optimizer with a learning rate of $10^{-2}$ and run the gradient descent for $10,000$ epochs to ensure convergence.
 
 		% \begin{figure}
-%			\includegraphics[scale = 0.5]{imagefile}
-%			\caption{Loss function for the gradient descent as well as the learning rate schedule, fixed with \texttt{tf.keras.optimizers.schedules.CosineDecayRestarts}, with parameters \texttt{initial_learning_rate = 0.01}, \texttt{first_decay_steps = 400}, \texttt{t_mul = 1.0} , \texttt{m_mul = 1.0}}
+			% \includegraphics[scale = 0.5]{imagefile} % add loss history
 			% \end{figure}
@@
 
-	  Mean loss with regularisation for particles reproducing a target: $285 \pm 108$
+	  Mean loss with regularisation for particles reproducing a target: $597 \pm 264$
 
-	  Mean loss without regularisation for particles reproducing a target: $33 \pm 24$
+	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$
   		\item For 100 runs with parameters
@@
 
-	  Mean loss with regularisation for particles reproducing a target: $282 \pm 91$
+	  Mean loss with regularisation for particles reproducing a target: $606 \pm 257$
 
-	  Mean loss without regularisation for particles reproducing a target: $35 \pm 24$
+	  Mean loss without regularisation for particles reproducing a target: $359 \pm 244$
 
@@
 
-	  Mean loss with regularisation for particles reproducing a target: $310 \pm 115$
+	  Mean loss with regularisation for particles reproducing a target: $854 \pm 427$
 
-	  Mean loss without regularisation for particles reproducing a target: $58 \pm 40$
+	  Mean loss without regularisation for particles reproducing a target: $602 \pm 417$
 
@@
 	  	\end{tikzpicture}
-	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
+	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
 (b) Evolution of the mean numbers of particles reproducing each targets polynomial.
@@
 	  	\label{fig:sample10000beta3}
+	  \end{figure}
+
+	  \item For 100 runs with parameters
+		\begin{equation} \label{eq:sample10000beta3sigmavar}
+			\begin{gathered}
+				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
+				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
+				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
+			\end{gathered}
+		\end{equation}
+		the polynomials are found at the following frequencies
+	  \begin{equation}
+	  	\begin{tabular}{l|cccccccc}
+	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
+	  		Frequency & 68\% & 17\% & 6\% & 9\% & 2\% & 1\% & 1\% & 11\%
+	  	\end{tabular}
+	  \end{equation}
+	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3sigmavar}.
+
+	  Averaged number of particles reproducing a target in a successful run: $966 \pm 115$
+
+	  Mean loss with regularisation for particles reproducing a target: $837 \pm 438$
+
+	  Mean loss without regularisation for particles reproducing a target: $609 \pm 430$
+
+	  \begin{figure}[h!]
+	  	\centering
+	  	\begin{tikzpicture}
+	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46.pdf}};
+	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46_detailed.pdf}};
+	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+	  	\end{tikzpicture}
+	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}.
+(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
+The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
+	  	\label{fig:sample10000beta3sigmavar}
 	  \end{figure}
@@
 	  	\end{tikzpicture}
-	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
+	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
 (b) Evolution of the mean numbers of particles reproducing each targets polynomial.
@@
 
-%For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
-%\begin{equation}
-%	\begin{cases}
-%		p_{i} = 0, \\
-%		p_{j} = 0,
-%	\end{cases}
-%\end{equation}
-%gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
-
-In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in Eq.~\ref{eq:pols}.
-We can now solve the system
-\begin{equation}\label{eq:solvepol}
-	p_i = 0, \quad \forall i \in {1,\dots,7}
+For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
+\begin{equation}
+	\begin{cases}
+		p_{i} = 0, \\
+		p_{j} = 0,
+	\end{cases}
 \end{equation}
-which leads to the following expressions:
+gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
 \begin{equation}
@@
 \end{equation}
-
-Alternatively, the system can be recast as:
-\begin{equation}\label{eq:rulex8x10}
+We checked that this defines a 3-parameter solution of three-dimensional half-maximal supergravity. Equivalently:
+\begin{equation}
 	\begin{cases}
-		\displaystyle \tilde{x}{8} = \frac{x{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
-		\displaystyle x_{10} = \sqrt{2},x_{4},\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
+		\displaystyle \tilde{x}_{8} = \frac{x_{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
+		\displaystyle x_{10} = \sqrt{2}\,x_{4}\,\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
 	\end{cases}
 \end{equation}
-
-As anticipated, this defines a three-parameter solution corresponding to a three-dimensional slice of the half-maximal supergravity scalar potential.
-
-Let us make a few remarks at this stage.
-First, it is possible to find solutions to Eq.~\ref{eq:solvepol} which, however, are not solutions of $\nabla V = 0$.
-For instance $x_1 = x_2 = 0$; such cases are excluded, as they do not satisfy the stationarity condition and therefore do not correspond to valid physical solutions.
-
-Secondly, one might argue that only two of the seven polynomials are sufficient to fully characterize the solution.
-That is, choosing any pair $(i,j) \in {1, \dots, 7}$ may suffice to extract a complete description.
-In practice, this is not entirely accurate.
-While such a pair can yield partial constraints—for example, recovering Eq.\ref{eq:rulex8x10}—it may also produce alternative (and potentially less general) parameterizations.
-Upon inspection, all such partial rules are found to be consistent with, and included in, the most general expressions given in Eq.\ref{eq:rulex8x10}.
-
 The solution preserves a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.

### 2025-05-22 Draft_MLFlatDirections.tex
Update of the results section.

@@
   \begin{enumerate}
-  		\item For 100 runs with parameters
-		\begin{equation} \label{eq:sample10000beta5}
+  		\item {\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}
+
+	  For 100 runs with parameters
+		\begin{equation} \label{eq:sample10000beta3}
 			\begin{gathered}
 				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
+				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.1, \\
 				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
@@
 	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
+	  		Frequency & 76\% & 18\% & 10\% & 6\% & 4\% & 1\% & 2\% & 6\%
 	  	\end{tabular}
 	  \end{equation}
-	  The sum of the percentages is higher than 100\% because some runs find more than one polynomials.
-The code fails to find any polynomial in 13\% of the time.
-The averaged time needed for a single run on a PC in $\sim 700\,{\rm s}$.
-\ce{This timing is with \texttt{analysis}, it may be less without.}
+	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3}.
 
-	  Averaged number of particles reproducing a target in a successful run: $931 \pm 230$
+	  Averaged number of particles reproducing a target in a successful run: $973 \pm 103$
 
-	  Mean loss with regularisation for particles reproducing a target: $597 \pm 264$
+	  Mean loss with regularisation for particles reproducing a target: $854 \pm 427$
 
-	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$
-  		\item For 100 runs with parameters
+	  Mean loss without regularisation for particles reproducing a target: $602 \pm 417$
+
+	  \begin{figure}[h!]
+	  	\centering
+	  	\begin{tikzpicture}
+	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
+	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
+	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+	  	\end{tikzpicture}
+	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
+(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
+The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
+	  	\label{fig:sample10000beta3}
+	  \end{figure}
+
+	  After the AIS, we performed an exploitation phase to fine tune the coefficients.
+The distributions of the particles with respect to their loss (without regularisation), is plotted in fig.~\ref{fig:distlocalsearch}.
+The fine tuning (with \texttt{local\_search}) is made using the loss with regularisation.
+
+	  \begin{figure}[h!]
+	  	\centering
+	  	\includegraphics[scale=0.75]{Figures/Local_search_2025_05_19_at_06_01_21.pdf}
+	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} Distributions of all the 100,000 particles with respect to their loss (without regularisation) (a) directly after AIS with parameters~\eqref{eq:sample10000beta3} and (b) after 200 steps of \texttt{local\_search}.
+The fine tuning (with \texttt{local\_search}) is made using the loss with regularisation.}
+	  	\label{fig:distlocalsearch}
+	  \end{figure}
+
+	  We list below, for each polynomials in eq.~\eqref{eq:pols}, one example of representing particles directly after AIS and after the fine tuning, and the associated losses (without regularisation):
+	  \begin{align}
+	  	p_{1}:&\quad
+	  	\begin{aligned}
+	  		&-1.939\,x_{1} + 2.120\,x_{1}\tilde{x}_{8} + x_{10}x_{2}\tilde{x}_{8} - 2.266\, x_{2}x_{4}\tilde{x}_{8} + 0.029\,x_{2}^{2}x_{4},\quad L^{(\lambda = 0)} \simeq 754, \\
+			&-1.416\,x_{1} + 1.414\, x_{1}\tilde{x}_{8} + x_{10}x_{2}\tilde{x}_{8} - 1.414\,x_{2}x_{4}\tilde{x}_{8} + 0.00001\,x_{2}^{2}x_{4},\quad L^{(\lambda = 0)} \simeq 0.0040,
+	  	\end{aligned} \\[7pt]
+	  	p_{2}:&\quad
+	  	\begin{aligned}
+	  		&2.213\,x_{2} - 2.075\,x_{2}\tilde{x}_{8} + 1.674\,x_{1}x_{10} + 2.015\,x_{1}x_{4} - x_{10}^{2}x_{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 244, \\
+			&2.002\,x_{2} - 2.002\,x_{2}\tilde{x}_{8} + 1.417\,x_{1}x_{10} + 2.001\,x_{1}x_{4} - x_{10}^{2}x_{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.015,
+	  	\end{aligned} \\[7pt]
+	  	p_{3}:&\quad
+	  	\begin{aligned}
+	  		&2\,x_{2} - 1.808\,x_{2}\tilde{x}_{8} + 1.168\,x_{1}\tilde{x}_{8}x_{10} + 1.828\,x_{1}x_{4}\tilde{x}_{8} - 1.864\,x_{2}x_{4}^{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 180, \\
+			&2\,x_{2} - 1.998\,x_{2}\tilde{x}_{8} + 1.412\,x_{1}\tilde{x}_{8}x_{10} + 1.998\,x_{1}x_{4}\tilde{x}_{8} - 1.998\,x_{2}x_{4}^{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.016,
+	  	\end{aligned} \\[7pt]
+	  	p_{4}:&\quad
+	  	\begin{aligned}
+	  		&1.458\,x_{2} - 1.341\,x_{2}\tilde{x}_{8} + 1.497\,x_{1}x_{4} + x_{1}\tilde{x}_{8}x_{10} - 1.008\,x_{2}x_{4}\tilde{x}_{8}x_{10} + 0.020 x_{2}^{2}x_{4}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 218, \\
+			&1.419\,x_{2} - 1.418\,x_{2}\tilde{x}_{8} + 1.416\,x_{1}x_{4} + x_{1}\tilde{x}_{8}x_{10} - 1.001\,x_{2}x_{4}\tilde{x}_{8}x_{10} - 0.0003\,x_{2}^{2}x_{4}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.074,
+	  	\end{aligned} \\[7pt]
+	  	p_{5}:&\quad
+	  	\begin{aligned}
+	  		&-2.179\,x_{1} - 1.571\,x_{2}x_{4} - 1.953\,x_{1}x_{4}^{2} + 1.983\,x_{1}\tilde{x}_{8} + 1.530\,x_{2}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2},\quad L^{(\lambda = 0)} \simeq 210, \\
+			&-2.008\,x_{1} - 2.001\,x_{2}x_{4} - 1.999\,x_{1}x_{4}^{2} + 1.995\,x_{1}\tilde{x}_{8} + 1.412\,x_{2}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2},\quad L^{(\lambda = 0)} \simeq 0.228,
+	  	\end{aligned} \\[7pt]
+	  	p_{6}:&\quad
+	  	\begin{aligned}
+	  		&- 2.856\,x_{2}x_{4} - 2.499\,x_{1}x_{4}^{2} + 2.721\,x_{2}x_{4}\tilde{x}_{8} + 1.677\,x_{2}x_{10} - 1.187\,x_{2}\tilde{x}_{8}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2} ,\quad L^{(\lambda = 0)} \simeq 202, \\
+			&- 2.043\,x_{2}x_{4} - 2.005\,x_{1}x_{4}^{2} + 2.030\,x_{2}x_{4} \tilde{x}_{8} + 1.393\,x_{2}x_{10} - 1.401\,x_{2}\tilde{x}_{8}x_{10} + x_{1}\tilde{x}_{8}x_{10}^2 ,\quad L^{(\lambda = 0)} \simeq 1.28,
+	  	\end{aligned} \\[7pt]
+	  	p_{7}:&\quad
+	  	\begin{aligned}
+	  		&- 1.354\,x_{1}^{2}x_{4} + 1.243\,x_{2}^{2}x_{4} + 1.304\,x_{1}x_{2}x_{4}^{2} - 1.053\,x_{1}^{2}x_{10} - x_{2}^{2}x_{10} + 0.052\,x_{2}x_{4}^{2}x_{10} ,\quad L^{(\lambda = 0)} \simeq 373, \\
+			&- 1.413\,x_{1}^{2}x_{4} + 1.415\,x_{2}^{2}x_{4} + 1.413\,x_{1}x_{2}x_{4}^{2} - 0.997\,x_{1}^{2}x_{10} - x_{2}^{2}x_{10} + 0.0003\,x_{2}x_{4}^{2}x_{10} ,\quad L^{(\lambda = 0)} \simeq 0.038.
+	  	\end{aligned}
+	  \end{align}
+
+	  \item {\bfseries \boldmath $\beta$ in power $4$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}
+
+	  For 100 runs with parameters
+		\begin{equation} \label{eq:sample10000beta4}
+			\begin{gathered}
+				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
+				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{4}, \quad \sigma = 0.1, \\
+				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
+			\end{gathered}
+		\end{equation}
+		the polynomials are found at the following frequencies
+	  \begin{equation}
+	  	\begin{tabular}{l|cccccccc}
+	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
+	  		Frequency & 74\% & 17\% & 7\% & 8\% & 2\% & 0\% & 2\% & 6\%
+	  	\end{tabular}
+	  \end{equation}
+	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta4}.
+
+	  Averaged number of particles reproducing a target in a successful run: $951 \pm 200$
+
+	  Mean loss with regularisation for particles reproducing a target: $709 \pm 320$
+
+	  Mean loss without regularisation for particles reproducing a target: $452 \pm 309$
+
+	  \begin{figure}[h!]
+	  	\centering
+	  	\begin{tikzpicture}
+	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_22_at_08_48_38.pdf}};
+	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_22_at_08_48_38_detailed.pdf}};
+	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+	  	\end{tikzpicture}
+	  	\caption{{\bfseries \boldmath $\beta$ in power $4$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta4}.
+(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
+The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
+	  	\label{fig:sample10000beta4}
+	  \end{figure}
+
+	  \item {\bfseries \boldmath $\beta$ in power $5$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}
+
+  		For 100 runs with parameters
 		\begin{equation}
@@
 	  	\end{tikzpicture}
-	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta5}.
+	  	\caption{{\bfseries \boldmath $\beta$ in power $5$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta5}.
 (b) Evolution of the mean numbers of particles reproducing each targets polynomial.
@@
 
-	  \item For 100 runs with parameters
-		\begin{equation} \label{eq:sample10000beta3}
+  		\item {\bfseries \boldmath $\beta$ in power $5$, $\sigma$ varying, $\texttt{sample size} = 10000$}
+
+  		For 100 runs with parameters
+		\begin{equation} \label{eq:sample10000beta5}
 			\begin{gathered}
 				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.1, \\
+				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
 				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
@@
 	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 76\% & 18\% & 10\% & 6\% & 4\% & 1\% & 2\% & 6\%
+	  		Frequency & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
 	  	\end{tabular}
 	  \end{equation}
-	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3}.
+	  The sum of the percentages is higher than 100\% because some runs find more than one polynomials.
+The code fails to find any polynomial in 13\% of the time.
+The averaged time needed for a single run on a PC in $\sim 700\,{\rm s}$.
+\ce{This timing is with \texttt{analysis}, it may be less without.}
 
-	  Averaged number of particles reproducing a target in a successful run: $973 \pm 103$
+	  Averaged number of particles reproducing a target in a successful run: $931 \pm 230$
 
-	  Mean loss with regularisation for particles reproducing a target: $854 \pm 427$
+	  Mean loss with regularisation for particles reproducing a target: $597 \pm 264$
 
-	  Mean loss without regularisation for particles reproducing a target: $602 \pm 417$
+	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$
 
-	  \begin{figure}[h!]
-	  	\centering
-	  	\begin{tikzpicture}
-	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
-	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
-	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-	  	\end{tikzpicture}
-	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
-(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
-The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
-	  	\label{fig:sample10000beta3}
-	  \end{figure}
+	  \item {\bfseries \boldmath $\beta$ in power $3$, $\sigma$ varying, $\texttt{sample size} = 10000$}
 
-	  \item For 100 runs with parameters
+	  For 100 runs with parameters
 		\begin{equation} \label{eq:sample10000beta3sigmavar}
@@
 	  	\end{tikzpicture}
-	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}.
+	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma$ varying, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}.
 (b) Evolution of the mean numbers of particles reproducing each targets polynomial.
@@
 
-	  \item For 100 runs with parameters
+	  \item {\bfseries \boldmath $\beta$ in power $5$, $\sigma=0.1$, $\texttt{sample size} = 1000$}
+
+	  For 100 runs with parameters
 		\begin{equation} \label{eq:sample1000}
@@
 	  	\end{tikzpicture}
-	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
+	  	\caption{{\bfseries \boldmath $\beta$ in power $5$, $\sigma=0.1$, $\texttt{sample size} = 1000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
 (b) Evolution of the mean numbers of particles reproducing each targets polynomial.

### 2025-05-22 Draft_MLFlatDirections.tex
update the draft

--- 2025-05-21 Draft_MLFlatDirections.tex
@@
 		\tilde{\varphi} = x_{13} \\[5pt]
-		\nu &= e^{(6\,x_{7}+3\,x_{8}+\sqrt{3}\,x_{9})/6}
+		\nu &= e^{(6\,x_{7}+3\,\tilde{x}_{8}+\sqrt{3}\,x_{9})/6}
 				\begin{pmatrix}
 					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
-					0 & e^{-x_{8}} & \frac{e^{-x_{8}}\,x_{12}}{\sqrt{2}} \\
-					0 & 0 & e^{-(x_{8}+\sqrt{3}\,x_{9})/2}
+					0 & e^{-\tilde{x}_{8}} & \frac{e^{-\tilde{x}_{8}}\,x_{12}}{\sqrt{2}} \\
+					0 & 0 & e^{-(\tilde{x}_{8}+\sqrt{3}\,x_{9})/2}
 				\end{pmatrix}.
@@
 
-As a first simplified example we have considered only the parameters $x_{1}, x_{2}, x_{4}, x_{8}$ and $x_{10}$. The potential~\eqref{eq:scalarpotential} becomes
+As a first simplified example we have considered only the parameters $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$ and $x_{10}$. The potential~\eqref{eq:scalarpotential} becomes
 \begin{equation} \label{eq:scalarpotential124810}
 	\begin{aligned}
-		V &= \frac{1}{8}\, e^{-2\,x_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,x_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
-		  & \quad\qquad\qquad - 4\,e^{3\,x_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
+		V &= \frac{1}{8}\, e^{-2\,\tilde{x}_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,\tilde{x}_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
+		  & \quad\qquad\qquad - 4\,e^{3\,\tilde{x}_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
       			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
-        & \quad\qquad\qquad - 8\,e^{x_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
+        & \quad\qquad\qquad - 8\,e^{\tilde{x}_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
       			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
-        & \quad\qquad\qquad + 4\,e^{2\,x_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
+        & \quad\qquad\qquad + 4\,e^{2\,\tilde{x}_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
         			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
-        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,x_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
+        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,\tilde{x}_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
 	\end{aligned}
@@
 		\end{equation}
-		where $\vec{x}^{,i} = (x^i_1,x^i_2,x^i_4,x^i_8,x^i_{10})$ denotes the data points.
+		where $\vec{x}^{\,i} = (x^i_1,x^i_2,x^i_4,\tilde{x}^i_8,x^i_{10})$ denotes the data points.
 
@@
 			\centering
-			\includegraphics[scale = 0.25]{Figures/triangular_plot_1_2_4_8_10.png} %names need to be changed.
+			\includegraphics[scale = 0.3]{Figures/triangular_plot_1_2_4_8_10_new.png} %names need to be changed.
 			\caption{Triangular plot showing $2d$ projections and $1d$ histograms of the data after the gradient descent}
@@
 Some of these may result from larger basins of attraction, such as in the $x_1/x_2$ plot.
-However, the structures seen in the $x_4/x_8$ or $x_4/x_{10}$ plots likely reflect genuine features of the manifold, and will show latter that this is indeed the case.
+However, the structures seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots likely reflect genuine features of the manifold, and will show latter that this is indeed the case.
 We also note that alll directions appear to be well populated.
@@
 
-		We set the minimum cluster size to 10 points.
-Out of the 986,060 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.
-\ce{Are those numbers right?
-We loose more than 800,000 points?}
+		We set the minimum cluster size to 10 points. Out of the 98,606 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.
 
@@
 What we have at the moment, are points on a 3-dimensional manifold, which are embedded in a 5-dimensional space.
-Therefore we can conclude that, in order to characterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
-If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $\tilde{x}_{8} = e^{x_8}$, that, up to a global $e^{-2x_8}$ factor, this potential is actually a polynomial of the embedding coordinates.
+Therefore we can conclude that, in order to characterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
+If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to a global $e^{-2\tilde{x}_8}$ factor, this potential is actually a polynomial of the embedding coordinates.
 Therefore, the components of $|\nabla V|$ are also polynomials in those variables.
-We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there are two of those.
+We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those.
+Note that we are now taking $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
 Of course if one takes directly the gradient of \eqref{eq:scalarpotential124810}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
@@
   \end{subequations}
-  where $\tilde{x}_{8} = e^{x_{8}}$. They are found with different frequencies, depending on the chosen parameters.
+  where $x_{8} = e^{\tilde{x}_{8}}$. They are found with different frequencies, depending on the chosen parameters.
 
@@
 
-	  Mean loss with regularisation for particles reproducing a target: $597 \pm 264$
+	  Mean loss with regularisation for particles reproducing a target: $285 \pm 108$
 
-	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$
+	  Mean loss without regularisation for particles reproducing a target: $33 \pm 24$
   		\item For 100 runs with parameters
@@
 
-	  Mean loss with regularisation for particles reproducing a target: $606 \pm 257$
+	  Mean loss with regularisation for particles reproducing a target: $282 \pm 91$
 
-	  Mean loss without regularisation for particles reproducing a target: $359 \pm 244$
+	  Mean loss without regularisation for particles reproducing a target: $35 \pm 24$
 
@@
 
-	  Mean loss with regularisation for particles reproducing a target: $854 \pm 427$
+	  Mean loss with regularisation for particles reproducing a target: $310 \pm 115$
 
-	  Mean loss without regularisation for particles reproducing a target: $602 \pm 417$
+	  Mean loss without regularisation for particles reproducing a target: $58 \pm 40$
 
@@
 	  	\end{tikzpicture}
-	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
+	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
 (b) Evolution of the mean numbers of particles reproducing each targets polynomial.
@@
 	  	\label{fig:sample10000beta3}
-	  \end{figure}
-
-	  \item For 100 runs with parameters
-		\begin{equation} \label{eq:sample10000beta3sigmavar}
-			\begin{gathered}
-				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
-				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-			\end{gathered}
-		\end{equation}
-		the polynomials are found at the following frequencies
-	  \begin{equation}
-	  	\begin{tabular}{l|cccccccc}
-	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 68\% & 17\% & 6\% & 9\% & 2\% & 1\% & 1\% & 11\%
-	  	\end{tabular}
-	  \end{equation}
-	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3sigmavar}.
-
-	  Averaged number of particles reproducing a target in a successful run: $966 \pm 115$
-
-	  Mean loss with regularisation for particles reproducing a target: $837 \pm 438$
-
-	  Mean loss without regularisation for particles reproducing a target: $609 \pm 430$
-
-	  \begin{figure}[h!]
-	  	\centering
-	  	\begin{tikzpicture}
-	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46.pdf}};
-	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46_detailed.pdf}};
-	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-	  	\end{tikzpicture}
-	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}.
-(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
-The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
-	  	\label{fig:sample10000beta3sigmavar}
 	  \end{figure}
@@
 	  	\end{tikzpicture}
-	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
+	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
 (b) Evolution of the mean numbers of particles reproducing each targets polynomial.

### 2025-05-26 Draft_MLFlatDirections.tex
update the draft which now looks almost like a v0 of the paper. Removed the itemize, add an intro and a conclusion. Write a sugra setup section

@@
 
+\def\bbar#1{\bar{\bar{#1}}}
+
+\newcommand{\cN}{{\cal N}}
+\newcommand{\cA}{{\cal A}}
+%\newcommand{\Tr}{\mbox{Tr}}
+%\newcommand{\tr}{\mbox{tr}}
+\newcommand{\cZ}{{\cal Z}}
+
+\newcommand{\bK}{{\bar{K}}}
+\newcommand{\bL}{{\bar{L}}}
+\newcommand{\bM}{{\bar{M}}}
+\newcommand{\bN}{{\bar{N}}}
+\newcommand{\bP}{{\bar{P}}}
+\newcommand{\bQ}{{\bar{Q}}}
+\newcommand{\bR}{{\bar{R}}}
+\newcommand{\bS}{{\bar{S}}}
+\newcommand{\bk}{{\bar{k}}}
+\newcommand{\bl}{{\bar{l}}}
+\newcommand{\bzero}{{\bar{0}}}
+\newcommand{\balpha}{{\bar{\alpha}}}
+\newcommand{\bbeta}{{\bar{\beta}}}
+
+\def\dA{{\dot{A}}}
+\def\dB{{\dot{B}}}
+\def\dC{{\dot{C}}}
+\def\dD{{\dot{D}}}
+
+\def\ft#1#2{{\textstyle{{\scriptstyle #1}\over {\scriptstyle #2}}}}
+\def\fft#1#2{{#1 \over #2}}
+\def\del{\partial}
+\def\vp{\varphi}
+\def\sst#1{{\scriptscriptstyle #1}}
+\def\oneone{\rlap 1\mkern4mu{\rm l}}
+\def\td{\tilde}
+\def\wtd{\widetilde}
+
 \def\0{{\sst{(0)}}}
@@
 
+The AdS/CFT correspondence stands as one of the most profound dualities in theoretical physics, establishing a remarkable equivalence between gravitational theories in Anti-de Sitter (AdS) spacetimes and conformal field theories (CFTs) living on their boundaries.
+This correspondence has revolutionized our understanding of both quantum gravity and strongly coupled field theories, providing unprecedented insights into the holographic nature of gravity.
+
+Within this holographic framework, supergravity theories in AdS backgrounds serve as the low-energy effective descriptions of string theory compactifications, making them natural laboratories for exploring the gravitational side of the duality.
+On the CFT side, the dual conformal field theories often exhibit rich structures of exactly marginal operators whose coupling constants parametrize conformal manifolds—moduli spaces where the theory remains conformal but with varying coupling strengths.
+The AdS/CFT correspondence maps these conformal manifolds to flat directions in the supergravity scalar potential, where the cosmological constant remains fixed while scalar field configurations vary continuously.
+
+Understanding these flat directions is therefore of great importance for several interconnected reasons.
+First, they encode the conformal manifolds of the dual CFTs, providing direct access to the space of exactly marginal deformations and their associated beta functions.
+Second, they reveal the vacuum structure of supergravity theories, determining which background configurations preserve supersymmetry and their associated stability properties.
+
+However, the explicit characterization of these flat directions presents formidable technical challenges.
+Supergravity scalar potentials, even in truncated models, typically involve dozens of scalar fields with intricate non-linear interactions.
+The resulting expressions for critical points—where all first derivatives vanish—quickly become too complex for traditional symbolic manipulation, rendering analytical approaches computationally intractable.
+This complexity paradox is particularly frustrating given that physically meaningful solutions often admit relatively simple parametric descriptions once discovered.
+
+The emergence of machine learning techniques in theoretical physics offers new avenues for tackling such problems.
+Rather than attempting to solve the full symbolic system directly, we can leverage numerical methods to sample the solution space and then employ symbolic regression to extract analytical patterns from the resulting data.
+This hybrid approach potentially circumvents the computational bottlenecks that plague purely symbolic methods while maintaining the goal of obtaining exact analytical expressions.
+
+In this work, we demonstrate the viability of this machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of three-dimensional chiral $\mathcal{N} = (2,0)$ supergravity arising from $AdS_3 \times S^3$ compactification from 6d supergravity, or from the compactification of type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
+Our methodology combines gradient descent sampling of the flat direction manifold with a novel annealed importance sampling algorithm for polynomial symbolic regression.
+We show that this approach successfully identifies the underlying three-dimensional conformal manifold and automatically discovers the polynomial constraints that characterize it analytically.
+
+The paper is organized as follows.
+Section 2 establishes the supergravity setup, presenting the scalar potential in its full complexity and motivating the truncation to five fields.
+Section 3 details our numerical methodology, covering both the gradient descent sampling procedure and the annealed importance sampling approach to symbolic regression.
+Section 4 analyzes the discovered supergravity solutions, including their geometric interpretation and spectrum analysis.
+Finally, Section 5 concludes with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
+
 \section{Supergravity setup}
-\begin{itemize}[label=\textbullet]
-	\item Context: 6d ${\rm AdS}_{3}\times S^{3}$, truncation to 3d, potential, conformal manifold.
-	\item Choice of truncation from 32 to 13 to 5 variables.
-\end{itemize}
-
-\paragraph{Potential}
-The 22 scalars of the theory can be parametrised by ($22 = 32 - 10$, with 10 scalars gauge fixed using translations in the gauge group)
-\begin{itemize}[label=\textbullet]
-	\item $m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$,
-	\item $\phi$ a $3\times3$ antisymmetric matrix,
-	\item $\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$,
-	\item a dilaton $\tilde{\varphi}$.
-\end{itemize}
-We can further restrict ourselves to a set of 13 scalars (see ref.~\cite{Eloy:2021fhc}), with
-\begin{equation}
-	\begin{aligned}
-		\xi &= \begin{pmatrix}
-					0 & 0 & 0 & x_{1} \\
-					0 & 0 & 0 & x_{2} \\
-					0 & 0 & 0 & x_{3}
-				\end{pmatrix},
-		\quad
-		\phi = \begin{pmatrix}
-					0 & x_{4} & x_{5} \\
-					-x_{4} & 0 & x_{6} \\
-					-x_{5} & -x_{6} & 0
-				\end{pmatrix},
-		\quad
-		\tilde{\varphi} = x_{13} \\[5pt]
-		\nu &= e^{(6\,x_{7}+3\,\tilde{x}_{8}+\sqrt{3}\,x_{9})/6}
+%\begin{itemize}[label=\textbullet]
+%	\item Context: 6d ${\rm AdS}_{3}\times S^{3}$, truncation to 3d, potential, conformal manifold.
+
+Three-dimensional $\mathcal{N}=8$ (half-maximal) gauged supergravity is governed by the Lagrangian
+%
+\begin{equation}	\label{eq: lagrangian_rephrased} 
+	e^{-1}\mathcal{L}=R+\frac1{8}g^{\mu\nu}D_\mu M^{\bM\bN}D_\nu M_{\bM\bN}+e^{-1}\mathcal{L}_{\text{CS}}-V\,,
+\end{equation}
+%
+which comprises the Einstein-Hilbert term $R$, the kinetic term for scalar fields parametrized by the matrix $M_{\bM\bN}$, a Chern-Simons contribution $\mathcal{L}_{\text{CS}}$, and a scalar potential $V$.
+
+The gauging structure is encoded in an embedding tensor that takes the general form
+%
+\begin{equation}	\label{eq: embtensor_rephrased}
+	\Theta_{\bK\bL\vert\bM\bN}=\theta_{\bK\bL\bM\bN}+\frac12\Big(\eta_{\bM[\bK}\theta_{\bL]\bN}-\eta_{\bN[\bK}\theta_{\bL]\bM}\Big)+\theta\,\eta_{\bM[\bK}\eta_{\bL]\bN}\,.
+\end{equation}
+%
+where we have a fully antisymmetric component $\theta_{\bK\bL\bM\bN}=\theta_{[\bK\bL\bM\bN]}$, a symmetric traceless part $\theta_{\bL\bK}=\theta_{(\bL\bK)}$, and a constant parameter $\theta$.
+The metric $\eta_{\bK\bL}$ is the SO(8,4)-invariant bilinear form used for index contractions.
+
+The scalar degrees of freedom parametrize the coset space
+%
+\begin{equation}	\label{eq: scalarcoset_rephrased}
+	\frac{\text{SO}(8,4)}{\text{SO}(8)\times\text{SO}(4)}\,,
+\end{equation}
+%
+through the symmetric matrix $M_{\bK\bL}=\mathcal{V}_{\bK}{}^{\bM}\mathcal{V}_{\bL}{}^{\bN}\delta_{\bM\bN}$, where $\mathcal{V}_{\bK}{}^{\bM}$ represents the coset representative.
+
+The gauge covariant derivatives are constructed using the embedding tensor according to
+%
+\begin{equation}
+	D_\mu =\partial_\mu + A_\mu{}^{\bM\bN}\,\Theta_{\bM\bN\vert\bP\bQ}\, T^{\bP\bQ}\,,
+\end{equation}
+%
+where $A_\mu{}^{\bM\bN}$ are the gauge fields and $T^{\bP\bQ}$ are the generators of the SO(8,4) algebra satisfying
+%
+\begin{equation} \label{eq:so84gen_rephrased}
+	\big(T^{\bar M\bar N}\big){}_{\bar P}{}^{\bar Q} = 2\,\delta_{\bar P}{}^{[\bar M}\,\eta^{\bar N]\bar Q}\,.
+\end{equation}
+%
+The covariant derivative acting on the scalar matrix becomes
+%
+\begin{equation}
+	D_\mu M_{\bM\bN}=\partial_\mu M_{\bM\bN}+4\,A_\mu{}^{\bP\bQ}\,\Theta_{\bP\bQ\vert(\bM}{}^{\bK}\, M_{\bN)\bK}\,,
+\end{equation}
+%
+ensuring gauge invariance of the scalar kinetic terms.
+
+The Chern-Simons contribution is given by
+%
+\begin{equation}
+	{\cal L}_{\rm CS}= -\varepsilon^{\,\mu\nu\rho}\,\Theta_{\bar M\bar N|\bar P\bar Q}\,A_{\mu}{}^{\bar M\bar N}\left(\partial_{\nu}\,A_{\rho}{}^{\bar P\bar Q}  + \frac{1}{3}\, \Theta_{\bar R\bar S|\bar U\bar V}\,f^{\bar P\bar Q,\bar R\bar S}{}_{\bar X\bar Y}\, A_{\nu}{}^{\bar U\bar V} A_{\rho}{}^{\bar X\bar Y} \right)\,,
+\end{equation}
+%
+where $f^{\bar M\bar N,\bar P\bar Q}{}_{\bar K\bar L} = 4\,\delta_{[\bar K}{}^{[\bar M}\eta^{\bar N][\bar P}\delta_{\bar L]}{}^{\bar Q]}$ are the structure constants of the SO(8,4) Lie algebra, and $\varepsilon^{\mu\nu\rho}$ is the three-dimensional Levi-Civita tensor.
+
+The scalar potential can be expressed in terms of the embedding tensor components as
+%
+{\setlength\arraycolsep{1.2pt}
+	\begin{equation}	\label{eq: scalarpot_rephrased}
+		\begin{aligned}
+			V	&=	\frac1{12}\,\theta_{\bK\bL\bM\bN}\theta_{\bP\bQ\bR\bS}\Big(M^{\bK\bP}M^{\bL\bQ}M^{\bM\bR}M^{\bN\bS}-6\,M^{\bK\bP}M^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}\\
+			&\qquad\qquad\qquad\qquad\quad+8\,M^{\bK\bP}\eta^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}-3\,\eta^{\bK\bP}\eta^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}\Big)\\
+			&\quad +\frac1{8}\,\theta_{\bK\bL}\theta_{\bP\bQ}\Big(2\,M^{\bK\bP}M^{\bL\bQ}-2\,\eta^{\bK\bP}\eta^{\bL\bQ}-M^{\bK\bL}M^{\bP\bQ}\Big)+4\,\theta\theta_{\bK\bL}M^{\bK\bL}-32\,\theta^2\,.
+		\end{aligned}
+	\end{equation}
+}
+In order to describe the $\mathcal{N} = (2,0)$ theory, it is useful to break the SO(8,4) group as
+
+\begin{equation}	\label{eq: gl3gradingbar}
+	\begin{aligned}
+		\text{SO}(8,4)	&\longrightarrow	\enspace \text{GL}(3,\mathbb{R})\times\text{SO}(1,1)\times\text{SO}(4)_{\rm global}\,,	\\
+		X^{\bM}		&\longrightarrow	\quad \{X^{\bar m},\; X_{\bar m},\; X^\bzero,\; X_\bzero,\; X^\balpha\}\,,
+	\end{aligned}
+\end{equation}
+where $\bar m\in\llbracket1,3\rrbracket$ and $\balpha\in\llbracket9,12\rrbracket$ label the SL(3, $\mathbb{R}$) and SO(4)$_{\rm global}$ vector representations, respectively.
+In this basis, the SO(8,4)-invariant tensor reads
+%
+\begin{equation}	\label{eq: Paulieta}
+	\eta_{\bM\bN}=
 	\begin{pmatrix}
-					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
-					0 & e^{-\tilde{x}_{8}} & \frac{e^{-\tilde{x}_{8}}\,x_{12}}{\sqrt{2}} \\
-					0 & 0 & e^{-(\tilde{x}_{8}+\sqrt{3}\,x_{9})/2}
-				\end{pmatrix}.
-	\end{aligned}
-\end{equation}
-Scalar potential from ref.~\cite{Eloy:2021fhc}:
-%
+		0 & \delta_{\bar m}{}^{\bar n} & 0 & 0 &0\\
+		\delta^{\bar m}{}_{\bar n} & 0 & 0 & 0 &0\\
+		0 & 0 & 0 & 1 & 0\\
+		0 & 0 & 1 & 0 & 0\\
+		0 & 0 & 0 & 0 & -\delta_{\balpha\bbeta}
+	\end{pmatrix}\,.
+\end{equation}
+The embedding tensor have the the following expression
+\begin{equation}{\label{eq:SO84embeddings}}
+		\theta_{\bar m \bar n \bar p\,\bzero}=-2\,\lambda\,\varepsilon_{\bar m \bar n \bar p}\,,		\qquad	\theta_{\bar m \bar n \bar p}{}^{\bzero}=\varepsilon_{\bar m \bar n \bar p}\,, \qquad	\theta_{\bar m \bar n}{}^{\bar p}{}_{\bzero}=\varepsilon_{\bar m \bar n \bar p}\,,
+\end{equation}
+or equivalently
+
+\begin{equation}
+	X_{\bar m\bar n \bar p} = \varepsilon_{\bar m \bar n \bar p}\,,		\qquad
+	X_{\bar m}{}^{\bar n \bar p} = \varepsilon_{\bar m \bar n \bar p}\,,	\qquad
+	X^{\bar m}{}_{\bar n}{}^{\bar p} = \varepsilon_{\bar m \bar n \bar p}\,,	\qquad
+	X^{\bar m\bar n}{}_{\bar p} = \varepsilon_{\bar m \bar n \bar p}\,,
+\end{equation}
+	%item Choice of truncation from 32 to 13 to 5 variables.
+%\end{itemize}
+Parametrizing the scalar matrix following \cite{Eloy:2021fhc}, we have for the scalar matrix 
+\begin{equation}	\label{eq: scalarmatrix}
+	M_{\bM\bN}
+	=
+	\begin{pmatrix}
+		m+(\xi^2+\phi)m^{-1}(\xi^2-\phi)+2\xi^2	& 	(\xi^2+\phi)m^{-1}		&	0	&  0  &	-\sqrt2\,[1+(\xi^2+\phi)m^{-1}]\xi	\\
+		m^{-1}(\xi^2-\phi)	& 	m^{-1}	&	0  	&  0  &	-\sqrt2\,m^{-1}\xi	\\
+		0		&	0		&	e^{2\tilde\varphi}	&	0				&	0		\\
+		0		&	0		&	0				&	e^{-2\tilde\varphi}	&	0		\\
+		-\sqrt2\,\xi^T[1+m^{-1}(\xi^2-\phi)]	&	-\sqrt2\,\xi^Tm^{-1}	&	0	&	0	&	1+2\,\xi^Tm^{-1}\xi	\\
+	\end{pmatrix}\,,
+\end{equation}
+which encodes 22 scalars of the theory ($22 = 32 - 10$, with 10 scalars gauge fixed using translations in the gauge group), which have been parametrized by 
+$m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$, $\phi$ a $3\times3$ antisymmetric matrix,$\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$, a dilaton $\tilde{\varphi}$.
+With this parametrization, the potential takes the from ref.~\cite{Eloy:2021fhc}:
 \begin{equation} \label{eq:scalarpotential}
@@
 \end{equation}
-where ${\rm T}\left(A,B,C\right)=\varepsilon_{mnp}\,\varepsilon_{qrs}\,A^{mq}B^{nr}C^{ps}$.
-
-As a first simplified example we have considered only the parameters $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$ and $x_{10}$. The potential~\eqref{eq:scalarpotential} becomes
+where ${\rm T}\left(A,B,C\right)=\varepsilon_{mnp}\,\varepsilon_{qrs}\,A^{mq}B^{nr}C^{ps}$. We can further restrict ourselves to a set of 13 scalars which is still a consistent truncation, with 
+\begin{equation}
+	\begin{aligned}
+		\xi &= \begin{pmatrix}
+					0 & 0 & 0 & x_{1} \\
+					0 & 0 & 0 & x_{2} \\
+					0 & 0 & 0 & x_{3}
+				\end{pmatrix}, \\[5pt]
+		\phi &= \begin{pmatrix}
+					0 & x_{4} & x_{5} \\
+					-x_{4} & 0 & x_{6} \\
+					-x_{5} & -x_{6} & 0
+				\end{pmatrix}, \\[5pt]
+		\tilde{\varphi} &= \tilde{x}_{13}, \\[5pt]
+		\nu &= e^{(6\,\tilde{x}_{7}+3\,\tilde{x}_{8}+\sqrt{3}\,\tilde{x}_{9})/6}
+				\begin{pmatrix}
+					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
+					0 & e^{-\tilde{x}_{8}} & \frac{e^{-\tilde{x}_{8}}\,x_{12}}{\sqrt{2}} \\
+					0 & 0 & e^{-(\tilde{x}_{8}+\sqrt{3}\,\tilde{x}_{9})/2}
+				\end{pmatrix}.
+	\end{aligned}
+\end{equation}
+
+As an initial simplification, we restrict our analysis to the scalar fields $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
+This choice is made to facilitate a more tractable starting point for the investigation, and corresponds to a randomly selected subset of the original set of thirteen scalar fields.
+It is important to note that this subset no longer defines a consistent truncation of the full theory.
+Nevertheless, despite the fact that the effective theory defined by these five scalars may be formally ill-defined—due to potential higher-order interactions that could source the remaining scalar fields—the solutions we obtain remain valid solutions of the complete theory.
+This is because we compute the critical points of the scalar potential by first evaluating $\nabla V = 0$, and only then setting the remaining scalar fields to zero.
+By adopting this procedure—taking the gradient of the potential prior to truncation—we ensure that the resulting configurations satisfy the equations of motion and are thus genuine solutions of the full theory.
+Under this truncation, the scalar potential~\eqref{eq:scalarpotential} reduces to:
 \begin{equation} \label{eq:scalarpotential124810}
@@
 \end{equation}
-\ce{Change notation to keep $x$ for the polynomial variables?}
-
-\ce{Discuss here why we need numerical methods: to complicated for mathematica to simplify the gradient.}
+
+Let us make a comment at this point.
+Looking at the potential given in Eq.~\ref{eq:scalarpotential124810} and since we have an explicit formula, one might argue that the problem of identifying flat directions could be addressed by directly computing the gradient of the expression and subsequently simplifying the resulting equations.
+However, attempting to carry out this procedure using a symbolic solver such as Mathematica quickly reveals its limitations: the resulting expressions are too complex to be simplified into a manageable form, and do not yield usable relationships that express some variables in terms of others.
+This complexity does not, however, rule out the possibility that simpler solutions satisfying the condition of vanishing gradient may exist.
+In this work, we aim to identify such solutions, which we seek using numerical methods.
+
+An additional advantage of this approach is its broader applicability.
+In scenarios where an explicit analytic expression for the potential is inaccessible—yet numerical evaluation remains feasible—our method retains its validity.
+Hence, the numerical strategy adopted here may prove effective even in cases where an exact analytic expression for the potential is out of reach.
 
@@
 	\subsection{Gradient descent and local analysis}
-		\paragraph{Gradient descent: implementation, sampling, time needed, loss}
+		%\paragraph{Gradient descent: implementation, sampling, time needed, loss}
 
@@
 			\centering
-			\includegraphics[scale=0.35]{Figures/nabla_V_thres.png}
+			\includegraphics[scale=0.35]{Figures/log_grad_V_hist.png}
 			\quad
-			\includegraphics[scale=0.35]{Figures/V_values_thres.png}
-			\caption{Left panel: Number of data points with gradient norm smaller than the threshold indicated on the x-axis.
-Right panel: Number of data points whose value deviates from $-4$ by less than the threshold shown on the x-axis.}
+			\includegraphics[scale=0.35]{Figures/log_Vp4_hist.png}
+			\caption{Left panel: Histogram of the logarithm of the norm of the gradient for each point. Right panel: Histogram of the distance of the value of the potential for each point.}
 			\label{fig:Analyze_V_points}
@@
 			\caption{Evolution of the loss function during gradient descent and corresponding learning rate schedule, both plotted on a logarithmic scale.
-Red dashed lines indicate epochs at which the optimizer was reinitialized.}
+Dashed lines indicate epochs at which the optimizer was reinitialized.}
 			\label{fig:loss_grad_des}
@@
 However, the structures seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots likely reflect genuine features of the manifold, and will show latter that this is indeed the case.
-We also note that alll directions appear to be well populated.
+We also note that all directions appear to be well populated.
 		%Furthermore, we can notice that a large majority of the points converge to the origin $\vec{0}$.
@@
 
-		\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least few points in each direction)}
+		%\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least few points in each direction)}
 
@@
 Before applying symbolic regression to search for such an expression, we can first perform some exploratory analyses to better understand the data.
-Specifically, we aim to determine the dimensionality of the manifold and whether it consists of a single connected component or multiple disjoint components (e.g., two intersecting hyperplanes).
+Specifically, we aim to determine the dimensionality of the manifold and wether it consists of a single connected component or multiple disjoint components (e.g., two intersecting hyperplanes).
 
@@
 
-		\begin{figure}
+		\begin{figure}[h!]
 			\centering
-			\includegraphics[scale=0.5]{Figures/Local_PCA.png}
+			\includegraphics[scale=0.4]{Figures/Local_PCA.png}
 			\caption{Results of the local PCA analysis.
@@
 For $k = 5$, a noticeable fraction of points are assigned a dimensionality of 2.
-This can be attributed to the fact that if the true dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality.
+This can be attributed to the fact that if the true dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality for a fraction of the points.
 
@@
 
-		\paragraph{Clustering: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space}
+		%\paragraph{Clustering: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space}
 
@@
 
-		\begin{figure}
+		\begin{figure}[h!]
 			\centering
-			\includegraphics[scale=0.4]{Figures/3d_plot_x4_x8_x10.png}
-			\includegraphics[scale=0.4]{Figures/3d_plot_x2_x4_x8.png}
+			\hspace{-2cm}
+			\includegraphics[scale=0.5]{Figures/3d_plot_x4_x8_x10.png}
+			\includegraphics[scale=0.5]{Figures/3d_plot_x2_x4_x8.png}
 			\caption{3D plots of the data in selected coordinates. Left: $(x_4, x_8, x_{10})$. Right: $(x_2, x_4, x_8)$.}
@@
 	\subsection{Annealed Importance Sampling for polynomial symbolic regression}
-	\begin{itemize}[label=\textbullet]
-		\item We can convert the potential to a polynomial by converting the variables that appear in exponentials to logs.
-		\item As the potential is a polynomial, the solutions satisfy polynomials equations.
+	%\begin{itemize}[label=\textbullet]
+		%\item We can convert the potential to a polynomial by converting the variables that appear in exponentials to logs.
+	%\item As the potential is a polynomial, the solutions satisfy polynomials equations.
 Discuss that fact that we could get polynomials directly by taking the gradient of the potential, but those will be to complicated to express the vacuum in a usable way.
@@
 What we have at the moment, are points on a 3-dimensional manifold, which are embedded in a 5-dimensional space.
-Therefore we can conclude that, in order to characterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
+Therefore we can conclude that, in order to characterise the manifold, we need two independent constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
 If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to a global $e^{-2\tilde{x}_8}$ factor, this potential is actually a polynomial of the embedding coordinates.
@@
 The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
-There are a number of way one can deal with it, using already existing methods such as AI Feynman methods~\cite{Udrescu:2019mnk}, or ..., or by doing rough gradient descent on the most general polynomial with arbitrary coefficients and trying to minimize its value once evaluated on the data points.
+There are a number of way one can deal with it, using already existing methods such as AI Feynman methods~\cite{Udrescu:2019mnk}, or ...
+\bd{litterature review}.
 In the spirit of trying to build a generalisable method, we develop here our own method, which is based on symbolic regression using an Annealing Importance Sampling method.
 
-		\item Annealed Importance Sampling: first explain general idea (construct density probability, role of temperature, links with Monte-Carlo), discuss $\beta$ to control exploration and exploitation phases.
+		%\item Annealed Importance Sampling: first explain general idea (construct density probability, role of temperature, links with Monte-Carlo), discuss $\beta$ to control exploration and exploitation phases.
 
 		In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe a given dataset.
-In the problem discussed in this paper, we are looking for polynomial expressions such that $p(data) = 0$.
+In the problem discussed in this paper, we are looking for polynomial expressions such that $p(\vec{x}^i) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
 This task involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods.
@@
 
-		\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
+		%\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
 
 		Let us now explain in more details how does this procedure goes.
-The goal is to reconstruct some distribution function $p(z)$, where here $z$ in going to be some polynomial.
-\ce{Notational conflict: $p$ for polynomials and $p$ the distribution.} We will try to reconstruct this density function by series of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ is going to be the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{d}z$.
+The goal is to reconstruct some distribution function $d(z)$, where here $z$ in going to be some polynomial.
+We will try to reconstruct this density function by series of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ is going to be the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{d}z$.
 We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N = 1$.
@@
 		\begin{equation}
-			\gamma_n(z) := p_0(z) \: \exp \left( -\beta_n L(z) \right).
-		\end{equation}
-
-		At each step, we have a set of particles $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
-To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and walculate the new unnormalized importance weight $w_n^k$.
+			\gamma_n(z) := d_0(z) \: \exp \left( -\beta_n L(z) \right).
+		\end{equation}
+
+		At each step, we have a set of particles and weights $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
+To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and calculate the new unnormalized importance weight $w_n^k$.
 The latter are updated using the formula
@@
 
-		Let's us now focus on the forward ($q(z_n^k | z_{n-1}^k)$) and backward propagation kernel ($q(z_{n-1}^k | z_n^k)$).
+		Let's us now focus on the forward $q(z_n^k | z_{n-1}^k)$ and backward propagation kernel $q(z_{n-1}^k | z_n^k)$ for now.
 The forward propagation kernel defines how we generate the state at time $n$ given the state at time $n-1$.
 It gives the probability to transition from $z_{n-1}$ to $z_n$.
-The backward kernel: It represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
+The backward kerne represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
 The purpose of $q$ is to give a proposition for $z_n$ given $z_{n-1}$.
@@
 Given a polynomial $z_{n-1}$, we choose randomly one of his coefficient and modify it by a random noise from the guassian distribution $\mathcal{N}(0,\sigma^2)$.
-So for eg : $2 x + 3 y^2 \rightarrow  2.1 x + 3 y^2$.
+So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2.1 x_1 + 3 x_2^2$.
 			\item Variable multiplication.
 Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and multiply it by one of the available variable.
-So for eg : $2 x + 3 y^2 \rightarrow  2 x y + 3 y^2$.
-			\item Variable division.
-Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable.
-So for eg : $2 x + 3 y^2 \rightarrow  2 x y + 3 y^2$.
-\ce{Change the example.}
+So for eg : $2 ^x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$.
+			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$. 
 		\end{itemize}
-		This implementation allows us to straightforwardly calculate the forward and backward propagation kernel.
-For example, the case of the coefficient pertubation is symmetric.
-Therefore $q(z_n^k | z_{n-1}^k) = q(z_{n-1}^k | z_n^k)$, which allows to simplify the calculation of the incremental importance weight.
-
-		The acceptance ration for the MCMC algorithm is given by : 
+		This implementation enables a direct computation of both the forward and backward propagation kernels. In particular, for the case of coefficient perturbations, the transition is symmetric. That is,
+		\begin{equation}
+			q(z_n^k \mid z_{n-1}^k) = q(z_{n-1}^k \mid z_n^k),
+		\end{equation}
+		which significantly simplifies the computation of the incremental importance weight.
+
+		However, this symmetry does not hold in general.
+For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
+In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
+
+		The acceptance ratio for the MCMC algorithm is given by : 
 		\begin{equation}
@@
 		Before closing the section, we need to discuss what is the Loss function we choose.
-It is recquired to compute the unormalized distribution $\gamma_n$.
+It is required to compute the unormalized distribution $\gamma_n$.
 Assume that we have $z = \sum_k c_k X_k$, where $c_k$ are the coefficients of the polynomials, and $X_k$ is a short notations for all the possible monomials up to a given degree (so if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_k$ are $1, x, y, x^2, y^2, x y$).
@@
 
-		\item Discuss the fact that we allow float coefficients even though we know the coefficients will be only integers of square roots of integers?
-
-		\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
+		%\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
 
@@
 
-		\item Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
+		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
 Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate.
-Total time needed, without cluster or fancy computers.
-	\end{itemize}
+Total time needed, without cluster or fancy computers.}
+	%\end{itemize}
 
@@
 	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}.
-The code finds the 7 different following polynomials: \ce{Mention that we ``rounded'' the coefficients to integer and square root of them.}
+The code finds the 7 different following polynomials:
 	\begin{subequations} \label{eq:pols}
     \begin{align}
-      p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}\tilde{x}_{8} + x_{2}\tilde{x}_{8}x_{10} - \sqrt{2}\,x_{2}x_{4}\tilde{x}_{8},\\
-      p_{2} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}\tilde{x}_{8}x_{10}^{2},\\
-      p_{3} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\tilde{x}_{8}x_{10} + 2\,x_{1}x_{4}\tilde{x}_{8}
-      		- 2\,x_{2} x_{4}^{2}\tilde{x}_{8},\\
-      p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\,x_{4} + x_{1}\tilde{x}_{8}x_{10}
-      		- x_{2}x_{4}\tilde{x}_{8}x_{10},\\
-      p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10}
-      		+ x_{1}\tilde{x}_{8}x_{10}^{2},\\
-      p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10} 
-      		- \sqrt{2}\,x_{2}\tilde{x}_{8}x_{10} +  x_{1}\tilde{x}_{8}x_{10}^{2},\\
+      p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\
+      p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
+      p_{3} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
+      		- 2\,x_{2} x_{4}^{2}x_8,\\
+      p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
+      		- x_{2}x_{4}x_8x_{10},\\
+      p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
+      		+ x_{1}x_8x_{10}^{2},\\
+      p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
+      		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},\\
       p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
@@
 
+  	Let us clarify a point regarding the expected structure of the solutions to the system defined by the critical points of the scalar potential, i.e., the variety defined by the vanishing of the gradient $\nabla V$.
+
+  In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field.
+In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$.
+That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.
+
+  The conformal manifold (or the moduli space of solutions) is then a subvariety of this ambient space, defined as the common zero locus of the polynomials in $\nabla V$.
+From the perspective of algebraic geometry, this variety is cut out by an ideal in the polynomial ring with coefficients in the aforementioned field extension of $\mathbb{Q}$.
+Since the defining equations have coefficients in this field, the variety itself is defined over that same field.
+
+  Now, consider the numerical solutions obtained via methods such as annealed importance sampling.
+If these numerical procedures converge to points on the same variety, and assuming that the variety is irreducible over the given field, then any point (i.e., any solution) on the variety must lie in the same field extension over which the variety is defined.
+This follows from basic principles in algebraic geometry: the set of algebraic points on a variety defined over a field $K$ are themselves algebraic over $K$, and the field of definition of these points must be a (possibly finite) extension of $K$.
+
+  Therefore, even if the numerical solver does not explicitly reveal this, one should expect that the coordinates of the solutions (i.e., the values of the scalar fields at critical points) lie in the same field extension of $\mathbb{Q}$ as the coefficients of the original system of polynomials $\nabla V$.
+That is, they should belong to $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$ or a finite extension thereof.
+
+  This argument justifies the expectation that if the scalar potential $V$ and its gradient $\nabla V$ involve only rational numbers and square roots, then the solutions to $\nabla V = 0$—regardless of how they are found—should also lie within the same field extension.
+
+  This is this argument that allowed us to round the coefficients of the polynomials given by the annealed importance sampling algorithm, and found the polynomials in \ref{eq:pols}.
+
   \begin{enumerate}
-  		\item {\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}
+  		\item {\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample\_size} = 10000$}
 
@@
 \section{Supergravity solutions}
-\begin{itemize}[label=\textbullet]
-	\item For each couple of candidate polynomials, we get the same expression for the solution, and it indeed defines a unique vacuum of the 3d SUGRA.
-	\item Discussion of the vacuum: gauge group, Zham. metric, change of variables, 3d spectrum (and stability), spin 2 spectrum on $S^{3}$, one parameter seems to be a gauge parameter, uplift?
-\end{itemize}
+%\begin{itemize}[label=\textbullet]
+%	\item For each couple of candidate polynomials, we get the same expression for the solution, and it indeed defines a unique vacuum of the 3d SUGRA.
+%	\item Discussion of the vacuum: gauge group, Zham. metric, change of variables, 3d spectrum (and stability), spin 2 spectrum on $S^{3}$, one parameter seems to be a gauge parameter, uplift?
+%\end{itemize}
 
@@
 	\begin{cases}
-		\displaystyle \tilde{x}{8} = \frac{x{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
+		\displaystyle \tilde{x}_{8} = \frac{x{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
 		\displaystyle x_{10} = \sqrt{2},x_{4},\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
@@
 
-\paragraph{Moduli space}
+%\paragraph{Moduli space}
 The $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
@@
 	\item Appendix with some details on the code?
+
 \end{itemize}
 
+In this work, we have presented a novel machine learning approach to systematically identify and characterize flat directions in supergravity scalar potentials.
+Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (2,0) supergravity derived from
+$AdS_3 \times S^3 \times T^4$ compactifications of IIB supergravity.
+
+We developed a robust pipeline that transitions from numerical exploration to analytical understanding.
+The gradient descent procedure successfully samples the flat direction manifold, while local PCA analysis reveals its intrinsic dimensionality.
+Most notably, our annealed importance sampling approach to symbolic regression automatically discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
+
+Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold, with one direction potentially gauge-fixable.
+The discovered solution preserves $U(1) \times U(1)$ gauged symmetry and exhibits a rich spectrum structure.
+The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold.
+
+The method demonstrates remarkable efficiency and reliability.
+Across different parameter choices, we achieve success rates of 69-76\% for the most common polynomial constraint, with computation times of approximately 700 seconds per run on standard hardware.
+The algorithm discovers seven distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
+
+This approach opens several promising avenues for advancement.
+The scalability to higher-dimensional cases represents the most immediate challenge and opportunity.
+By increasing the number of particles, refining the annealing schedule, and optimizing polynomial search strategies, we anticipate extending this methodology to the full 13-scalar theory and potentially to other supergravity models.
+
+Beyond technical improvements, this work suggests a broader paradigm for studying conformal manifolds in string theory and supergravity.
+The ability to automatically extract analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
+
+The marriage of machine learning techniques with traditional supergravity analysis represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
+As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
+
+While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
+
 \bibliography{references}

### 2025-05-27 Draft_MLFlatDirections.tex
update figures

@@
 
-In this work, we demonstrate the viability of this machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of three-dimensional chiral $\mathcal{N} = (2,0)$ supergravity arising from $AdS_3 \times S^3$ compactification from 6d supergravity, or from the compactification of type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
+In this work, we demonstrate the viability of this machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of three-dimensional chiral $\mathcal{N} = (1,1)$ supergravity arising from $AdS_3 \times S^3$ compactification from 6d supergravity, or from the compactification of type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
 Our methodology combines gradient descent sampling of the flat direction manifold with a novel annealed importance sampling algorithm for polynomial symbolic regression.
@@
 }
-In order to describe the $\mathcal{N} = (2,0)$ theory, it is useful to break the SO(8,4) group as
-
-\begin{equation}	\label{eq: gl3gradingbar}
-	\begin{aligned}
-		\text{SO}(8,4)	&\longrightarrow	\enspace \text{GL}(3,\mathbb{R})\times\text{SO}(1,1)\times\text{SO}(4)_{\rm global}\,,	\\
-		X^{\bM}		&\longrightarrow	\quad \{X^{\bar m},\; X_{\bar m},\; X^\bzero,\; X_\bzero,\; X^\balpha\}\,,
-	\end{aligned}
-\end{equation}
-where $\bar m\in\llbracket1,3\rrbracket$ and $\balpha\in\llbracket9,12\rrbracket$ label the SL(3, $\mathbb{R}$) and SO(4)$_{\rm global}$ vector representations, respectively.
-In this basis, the SO(8,4)-invariant tensor reads
-%
-\begin{equation}	\label{eq: Paulieta}
-	\eta_{\bM\bN}=
-	\begin{pmatrix}
-		0 & \delta_{\bar m}{}^{\bar n} & 0 & 0 &0\\
-		\delta^{\bar m}{}_{\bar n} & 0 & 0 & 0 &0\\
-		0 & 0 & 0 & 1 & 0\\
-		0 & 0 & 1 & 0 & 0\\
-		0 & 0 & 0 & 0 & -\delta_{\balpha\bbeta}
-	\end{pmatrix}\,.
-\end{equation}
-The embedding tensor have the the following expression
-\begin{equation}{\label{eq:SO84embeddings}}
-		\theta_{\bar m \bar n \bar p\,\bzero}=-2\,\lambda\,\varepsilon_{\bar m \bar n \bar p}\,,		\qquad	\theta_{\bar m \bar n \bar p}{}^{\bzero}=\varepsilon_{\bar m \bar n \bar p}\,, \qquad	\theta_{\bar m \bar n}{}^{\bar p}{}_{\bzero}=\varepsilon_{\bar m \bar n \bar p}\,,
-\end{equation}
-or equivalently
-
-\begin{equation}
-	X_{\bar m\bar n \bar p} = \varepsilon_{\bar m \bar n \bar p}\,,		\qquad
-	X_{\bar m}{}^{\bar n \bar p} = \varepsilon_{\bar m \bar n \bar p}\,,	\qquad
-	X^{\bar m}{}_{\bar n}{}^{\bar p} = \varepsilon_{\bar m \bar n \bar p}\,,	\qquad
-	X^{\bar m\bar n}{}_{\bar p} = \varepsilon_{\bar m \bar n \bar p}\,,
-\end{equation}
-	%item Choice of truncation from 32 to 13 to 5 variables.
-%\end{itemize}
+\bd{redo}
 Parametrizing the scalar matrix following \cite{Eloy:2021fhc}, we have for the scalar matrix 
@@
 
+We note here that all dilaton fields are denoted with a tilde.
+This convention is adopted in anticipation of a later redefinition of the form \( x_i = e^{\tilde{x}_i} \) for these fields.
+By reserving the notation without tildes for the exponentiated variables, we maintain a clear and consistent distinction for use in subsequent expressions.
+
 As an initial simplification, we restrict our analysis to the scalar fields $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
@@
 			\includegraphics[scale = 0.5]{Figures/Loss_grad_des.png}
-			\caption{Evolution of the loss function during gradient descent and corresponding learning rate schedule, both plotted on a logarithmic scale.
+			\caption{Evolution of the loss function during gradient descent and corresponding learning rate schedule, noted $\alpha$ on the left y-axis, both plotted on a logarithmic scale.
 Dashed lines indicate epochs at which the optimizer was reinitialized.}
@@
 			\centering
-			\includegraphics[scale = 0.3]{Figures/triangular_plot_1_2_4_8_10_new.png} %names need to be changed.
+			\includegraphics[scale = 0.3]{Figures/triangular_plot_1_2_4_8_10.png} %names need to be changed.
 			\caption{Triangular plot showing $2d$ projections and $1d$ histograms of the data after the gradient descent}

### 2025-06-11 Notes_MKFLatDirection.tex
Update the draft and create the notes for us

--- 2025-05-27 Draft_MLFlatDirections.tex
@@
 Within this holographic framework, supergravity theories in AdS backgrounds serve as the low-energy effective descriptions of string theory compactifications, making them natural laboratories for exploring the gravitational side of the duality.
-On the CFT side, the dual conformal field theories often exhibit rich structures of exactly marginal operators whose coupling constants parametrize conformal manifolds—moduli spaces where the theory remains conformal but with varying coupling strengths.
-The AdS/CFT correspondence maps these conformal manifolds to flat directions in the supergravity scalar potential, where the cosmological constant remains fixed while scalar field configurations vary continuously.
-
-Understanding these flat directions is therefore of great importance for several interconnected reasons.
-First, they encode the conformal manifolds of the dual CFTs, providing direct access to the space of exactly marginal deformations and their associated beta functions.
-Second, they reveal the vacuum structure of supergravity theories, determining which background configurations preserve supersymmetry and their associated stability properties.
+Studying the CFT side is very interesting : CFT play a crucial role in statistical physics where they describe some phase transition ; they are also fixed point of Renormalisation Group flow.
+An interesting question is to know wether those CFT are isolated fixed points, or belong to a continous family of CFT's.
+The space of deformations that takes from one CFT to another is called the conformal manifild.
+They are parametrized by exactely marginal operator, or in other words operators whose $\beta$ functions exactly vanish.
+From this perspective, the AdS/CFT correspondence maps these conformal manifolds to flat directions in the supergravity scalar potential, where the cosmological constant remains fixed while scalar field configurations vary continuously.
+Studying these flat directions is therefore of great importance.
 
@@
 }
-\bd{redo}
+
+Decomposing SO(8,4) according to 
+%
+\begin{equation}	\label{eq: gl3gradingbar}
+	\begin{aligned}
+		\text{SO}(8,4)	&\longrightarrow	\enspace \text{GL}(3,\mathbb{R})\times\text{SO}(1,1)\times\text{SO}(4)_{\rm global}\,,	\\
+		X^{\bM}		&\longrightarrow	\quad \{X^{\bar m},\; X_{\bar m},\; X^\bzero,\; X_\bzero,\; X^\balpha\}\,,
+	\end{aligned}
+\end{equation}
+where $\bar m\in\llbracket1,3\rrbracket$ and $\balpha\in\llbracket9,12\rrbracket$ label the SL(3, $\mathbb{R}$) and SO(4)$_{\rm global}$ vector representations, respectively.
+In this basis, the SO(8,4)-invariant tensor reads
+%
+\begin{equation}	\label{eq: Paulieta}
+	\eta_{\bM\bN}=
+	\begin{pmatrix}
+		0 & \delta_{\bar m}{}^{\bar n} & 0 & 0 &0\\
+		\delta^{\bar m}{}_{\bar n} & 0 & 0 & 0 &0\\
+		0 & 0 & 0 & 1 & 0\\
+		0 & 0 & 1 & 0 & 0\\
+		0 & 0 & 0 & 0 & -\delta_{\balpha\bbeta}
+	\end{pmatrix}\,.
+\end{equation}
+
 Parametrizing the scalar matrix following \cite{Eloy:2021fhc}, we have for the scalar matrix 
@@
 which encodes 22 scalars of the theory ($22 = 32 - 10$, with 10 scalars gauge fixed using translations in the gauge group), which have been parametrized by 
-$m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$, $\phi$ a $3\times3$ antisymmetric matrix,$\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$, a dilaton $\tilde{\varphi}$.
+$m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$, $\phi$ a $3\times3$ antisymmetric matrix, $\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$, a dilaton $\tilde{\varphi}$.
 With this parametrization, the potential takes the from ref.~\cite{Eloy:2021fhc}:
@@
 Nevertheless, despite the fact that the effective theory defined by these five scalars may be formally ill-defined—due to potential higher-order interactions that could source the remaining scalar fields—the solutions we obtain remain valid solutions of the complete theory.
-This is because we compute the critical points of the scalar potential by first evaluating $\nabla V = 0$, and only then setting the remaining scalar fields to zero.
+This is because we compute the critical points of the scalar potential by first evaluating $\nabla V = 0$ keeping all the fields alive, and only then setting the remaining scalar fields to zero.
 By adopting this procedure—taking the gradient of the potential prior to truncation—we ensure that the resulting configurations satisfy the equations of motion and are thus genuine solutions of the full theory.
@@
 Let us make a comment at this point.
-Looking at the potential given in Eq.~\ref{eq:scalarpotential124810} and since we have an explicit formula, one might argue that the problem of identifying flat directions could be addressed by directly computing the gradient of the expression and subsequently simplifying the resulting equations.
+Since we have an explicit parametrisation of the potential with Eq.
+\ref{eq:scalarpotential}, one might argue that the problem of identifying flat directions could be addressed by directly computing the gradient of the expression, setting the appropriate scalar fields to zero and subsequently simplifying the resulting equations.
 However, attempting to carry out this procedure using a symbolic solver such as Mathematica quickly reveals its limitations: the resulting expressions are too complex to be simplified into a manageable form, and do not yield usable relationships that express some variables in terms of others.
@@
 Hence, the numerical strategy adopted here may prove effective even in cases where an exact analytic expression for the potential is out of reach.
+\bd{other motivation?
+Example of this ?
+}
 
@@
 	\paragraph{Results}
-	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}.
-The code finds the 7 different following polynomials:
+	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential}.
+The code finds the 8 different following polynomials:
 	\begin{subequations} \label{eq:pols}
@@
       p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
-      		- x_{2}^{2}x_{10},
+      		- x_{2}^{2}x_{10}, \\
+      p_{8} &= -2 + 4 x_{8} - 2 x_8^2 + 2 x_{4}^2 x_8 - x_8^2 x_{10}^2
     \end{align}

### 2025-06-13 Draft_MLFlatDirections.tex
update the draft

@@
 \usepackage{graphicx}
+\usepackage{adjustbox} 
 \usepackage{xcolor}
@@
 
-   \begin{Large}
-
-\mbox{ \bfseries \boldmath  Notes: Machine learning flat directions}
-   \end{Large}
+\title Machine learning to study marginal deformation of 2d conformal field theories
 
@@
 
-The AdS/CFT correspondence stands as one of the most profound dualities in theoretical physics, establishing a remarkable equivalence between gravitational theories in Anti-de Sitter (AdS) spacetimes and conformal field theories (CFTs) living on their boundaries.
+The AdS/CFT correspondence \cite{Maldacena:1997re} stands as one of the most profound dualities in theoretical physics, establishing a remarkable equivalence between gravitational theories in Anti-de Sitter (AdS) spacetimes and conformal field theories (CFTs) living on their boundaries.
 This correspondence has revolutionized our understanding of both quantum gravity and strongly coupled field theories, providing unprecedented insights into the holographic nature of gravity.
@@
 Within this holographic framework, supergravity theories in AdS backgrounds serve as the low-energy effective descriptions of string theory compactifications, making them natural laboratories for exploring the gravitational side of the duality.
-On the CFT side, the dual conformal field theories often exhibit rich structures of exactly marginal operators whose coupling constants parametrize conformal manifolds—moduli spaces where the theory remains conformal but with varying coupling strengths.
-The AdS/CFT correspondence maps these conformal manifolds to flat directions in the supergravity scalar potential, where the cosmological constant remains fixed while scalar field configurations vary continuously.
-
-Understanding these flat directions is therefore of great importance for several interconnected reasons.
-First, they encode the conformal manifolds of the dual CFTs, providing direct access to the space of exactly marginal deformations and their associated beta functions.
-Second, they reveal the vacuum structure of supergravity theories, determining which background configurations preserve supersymmetry and their associated stability properties.
-
+Studying the CFT side is very interesting : CFT play a crucial role in statistical physics where they are known to describe phase transitions ; they are also fixed point of Renormalisation Group flow and this is this latter point that is our interest in this paper.
+An interesting question is indeed to know wether those CFT are isolated fixed points of RG flows, or belong to a continous family of CFT's.
+If this is the case, the space of deformations that takes from one CFT to another is called the conformal manifold.
+They are parametrized by exactely marginal operator, or in other words operators whose $\beta$ functions exactly vanish.
+
+From this perspective, the AdS/CFT correspondence relates conformal manifolds on the boundary theory to flat directions in the scalar potential of the dual supergravity theory.
+Along these directions, the scalar field configurations vary continuously while the cosmological constant remains fixed.
+In general, supersymmetry is believed to be necessary for the existence of holographic conformal manifolds, as non-supersymmetric AdS solutions are typically considered unstable \cite{Ooguri:2016pdq,Palti:2019pca}.
+However, recent investigations \cite{Giambrone:2021wsm} have identified AdS$_4$ configurations that appear to evade this requirement, with no evidence of standard decay channels—neither perturbative nor non-perturbative—being present.
+In the context of AdS$_3$/CFT$_2$, the situation may be even richer.
+A well-known counterexample has existed for some time \cite{Aharony:2001dp,Dong:2014tsa}, which is well understood from both the field theory and gravitational perspectives.
+More generally, within the supergravity approximation, continuous deformations correspond to classically marginal operators.
+These operators become exactly marginal only if their marginality persists at finite values of both the rank N and the CFT coupling.
+Recent work \cite{Eloy:2024lwn} has demonstrated the existence of families of marginal deformations that are perturbatively stable, using the framework of Exceptional Field Theory (ExFT).
+
+In this work, we propose a novel approach, where we study directly the scalar potential of supergravity.
+As already mentionned, the marginal deformation of CFT's in the large N limit, are in correspondance with the flat directions in the potential, i.e.
+when there is a continuous set a scalar fields such that $\nabla V = 0$.
 However, the explicit characterization of these flat directions presents formidable technical challenges.
@@
 
-The emergence of machine learning techniques in theoretical physics offers new avenues for tackling such problems.
-Rather than attempting to solve the full symbolic system directly, we can leverage numerical methods to sample the solution space and then employ symbolic regression to extract analytical patterns from the resulting data.
-This hybrid approach potentially circumvents the computational bottlenecks that plague purely symbolic methods while maintaining the goal of obtaining exact analytical expressions.
-
-In this work, we demonstrate the viability of this machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of three-dimensional chiral $\mathcal{N} = (1,1)$ supergravity arising from $AdS_3 \times S^3$ compactification from 6d supergravity, or from the compactification of type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
-Our methodology combines gradient descent sampling of the flat direction manifold with a novel annealed importance sampling algorithm for polynomial symbolic regression.
-We show that this approach successfully identifies the underlying three-dimensional conformal manifold and automatically discovers the polynomial constraints that characterize it analytically.
+The emergence of machine learning techniques in theoretical physics opens new avenues for addressing such complex problems.
+Instead of solving the full symbolic system analytically from the outset, one can employ numerical methods to sample the solution space and subsequently apply symbolic regression to extract analytical patterns from the data.
+This hybrid approach has the potential to bypass the computational bottlenecks inherent in purely symbolic methods, while still aiming to uncover exact analytical expressions.
+
+Similar strategies have previously been applied to identify new isolated vacua in $\mathrm{SO}(8)$ supergravity \cite{Comsa:2019rcz,Berman:2022jqn}.
+More broadly, there has been increasing interest in applying machine learning and numerical techniques across various domains of high-energy physics.
+This includes, for instance, the characterization of Calabi–Yau metrics and hypersurfaces \cite{Ashmore:2019wzb,Berman:2021mcw,Larfors:2022nep,Berglund:2022gvm,Jejjala:2020wcc,Douglas:2006rr,Larfors:2021pbb,He:2018jtw}, as well as broader efforts to explore the string theory landscape using machine learning techniques \cite{He:2017aed,Carifio:2017bov,Ruehle:2017mzq}.
+Additional applications include studies in CFT \cite{Chen:2020dxg}, investigations of the supergravity landscape \cite{Brady:2025zzi,Krishnan:2020sfg}, and explorations of the AdS/CFT correspondence \cite{Hashimoto:2018ftp}.
+More generally, machine learning has found utility in the study of string theory, geometry, and fundamental physics \cite{Ruehle:2020jrk,He:2023csq,Bao:2021auj}.
+
+In this work, we demonstrate the viability of the aformentionned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of three-dimensional chiral $\mathcal{N} = (1,1)$  supergravity arising from $AdS_3 \times S^3$ compactification from 6d supergravity, or from the compactification of type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
+Our methodology combines gradient descent sampling of the flat direction manifold with some symbolic regression technique.
+There exist a large litterature on symbolic regression, using methods from genetic programming \cite{koza1994genetic,randall2022bingo,burlacu2019parsimony}, to deep machine learning \cite{petersen2019deep,kamienny2022end}, generative modelling \cite{valipour2021symbolicgpt} and diffusion models \cite{bastiani2025diffusion}.
+However, in the spirit of trying to build a generalisable method, we develop here our own algorithm, which is based on symbolic regression using an Annealing Importance Sampling method (AIS) \cite{neal1998annealedimportancesampling}.
+In this paper, we will study a 5 parameter truncation, which is itself coming from a 13 parameter consistent truncation of $\mathcal{N} = (1,1)$ 6-dimensional supergravity.
+
+The study of this 5 dimensional parameter potentiel is separated into several parts.
+We first use the gradient descent to efficiently sample the underlying conformal manifold.
+Combined with numerical analysis, such as principal component analysis and clustering, we can identify the existence of a 3-dimensional continuous family.
+We then use an AIS technique combined with a sequential Monte Carlo approach (SMC) \cite{del2006sequential} in order to do symbolic regression.
+As we will indeed demonstrate in the paper, there exist polynomial constraints on the 5 parameters, viewed as embedding coordinates, that projects them on the 3 dimensional manifolds.
+We manage to identify 8 of those constraints on the data, not all independent, which once solved gives that two of the embedding coordinates can be expressed in terms of the others.
+This provides an explicit family of 3 dimensional parameters family
 
@@
 
-As an initial simplification, we restrict our analysis to the scalar fields $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
-This choice is made to facilitate a more tractable starting point for the investigation, and corresponds to a randomly selected subset of the original set of thirteen scalar fields.
-It is important to note that this subset no longer defines a consistent truncation of the full theory.
-Nevertheless, despite the fact that the effective theory defined by these five scalars may be formally ill-defined—due to potential higher-order interactions that could source the remaining scalar fields—the solutions we obtain remain valid solutions of the complete theory.
-This is because we compute the critical points of the scalar potential by first evaluating $\nabla V = 0$, and only then setting the remaining scalar fields to zero.
-By adopting this procedure—taking the gradient of the potential prior to truncation—we ensure that the resulting configurations satisfy the equations of motion and are thus genuine solutions of the full theory.
-Under this truncation, the scalar potential~\eqref{eq:scalarpotential} reduces to:
-\begin{equation} \label{eq:scalarpotential124810}
-	\begin{aligned}
-		V &= \frac{1}{8}\, e^{-2\,\tilde{x}_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,\tilde{x}_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
-		  & \quad\qquad\qquad - 4\,e^{3\,\tilde{x}_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
-      			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
-        & \quad\qquad\qquad - 8\,e^{\tilde{x}_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
-      			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
-        & \quad\qquad\qquad + 4\,e^{2\,\tilde{x}_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
-        			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
-        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,\tilde{x}_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
-	\end{aligned}
-\end{equation}
+As an initial simplification, we restrict our analysis to the scalar fields $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x{10}$.
+This subset, selected at random from the original set of thirteen scalar fields, serves to render the problem more tractable at the outset.
+It is important to emphasize, however, that this subset does not constitute a consistent truncation of the full theory.
+Consequently, the effective theory defined by these five scalars may be formally ill-defined, as higher-order interactions could, in principle, source the remaining fields.
+
+Nevertheless, the solutions we obtain remain valid solutions of the complete theory.
+This is because we identify the critical points of the scalar potential by first computing $\nabla V = 0$ with all scalar fields included, and only then setting the remaining fields to zero.
+By performing the differentiation before the truncation, we ensure that the resulting configurations satisfy the full equations of motion and are therefore legitimate solutions of the complete theory.
+
+To compute the gradient, we exploit the fact that we possess an analytic expression for the scalar potential \eqref{eq:scalarpotential}, which we implement in Mathematica for numerical analysis.
+Note however that it could have been fully done using a numerical approach, automatic differenciations methods (that we will use later to do the gradient descent for the loss function).
+%Under this truncation, the scalar potential~\eqref{eq:scalarpotential} reduces to:
+%\begin{equation} \label{eq:scalarpotential124810}
+%	\begin{aligned}
+%		V &= \frac{1}{8}\, e^{-2\,\tilde{x}_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,\tilde{x}_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
+%		  & \quad\qquad\qquad - 4\,e^{3\,\tilde{x}_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
+%      			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
+%        & \quad\qquad\qquad - 8\,e^{\tilde{x}_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
+%      			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
+%        & \quad\qquad\qquad + 4\,e^{2\,\tilde{x}_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
+%        			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
+%        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,\tilde{x}_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
+%	\end{aligned}
+%\end{equation}
 
 Let us make a comment at this point.
-Looking at the potential given in Eq.~\ref{eq:scalarpotential124810} and since we have an explicit formula, one might argue that the problem of identifying flat directions could be addressed by directly computing the gradient of the expression and subsequently simplifying the resulting equations.
+Since we have an explicit parametrisation of the potential with \eqref{eq:scalarpotential}, one might argue that the problem of identifying flat directions could be addressed by directly computing the gradient of the expression, setting the appropriate scalar fields to zero and subsequently simplifying the resulting equations.
 However, attempting to carry out this procedure using a symbolic solver such as Mathematica quickly reveals its limitations: the resulting expressions are too complex to be simplified into a manageable form, and do not yield usable relationships that express some variables in terms of others.
@@
 An additional advantage of this approach is its broader applicability.
-In scenarios where an explicit analytic expression for the potential is inaccessible—yet numerical evaluation remains feasible—our method retains its validity.
+In scenarios where an explicit analytic expression for the potential and its gradient is inaccessible—yet numerical evaluation remains feasible—our method retains its validity.
 Hence, the numerical strategy adopted here may prove effective even in cases where an exact analytic expression for the potential is out of reach.
+\bd{other motivation?
+Example of this ?
+}
 
@@
 This choice is important to ensure that points are not restricted to the inner range $[-1,1]$.
+This will be important later, when performing the symbolic regression.
 For this example, we choose to generate $10^5$ points.
@@
 		\begin{equation}
-			\mathcal{L} = \sum_{i = 1}^{n_{points}} || \nabla V(\vec{x}^{,i})||^2
-		\end{equation}
-		where $\vec{x}^{\,i} = (x^i_1,x^i_2,x^i_4,\tilde{x}^i_8,x^i_{10})$ denotes the data points.
+			\mathcal{L} = \sum_{i = 1}^{n_{points}} ||\left.\nabla V(\vec{X}^{\,i})\,\right|_{\vec{y}=0}||^2
+		\end{equation}
+		where $\vec{X}^{\,i} = (x^i_1,\dots,x^i_6,\tilde{x}^i_7,\tilde{x}^i_8,\tilde{x}^i_9,x^i_{10},\dots,x^i_{12},\tilde{x}^i_{13})$ and $\vec{y}^{\,i} = (x^i_3,x^i_5,x^i_6,\tilde{x}^i_7,\tilde{x}^i_9,x^i_{11},x^i_{12},\tilde{x}^i_{11})$ denotes the data points.
+As already mentionned above, we use the analytic formula for $\nabla V$, but we could have perform the gradient descent by fully using automatic differentiation.
 
@@
 However, we found that simply scheduling the learning rate without resetting the optimizer yielded slower convergence.
-
 We interpret this as follows: when the optimizer is reinitialized, it effectively "forgets" its past gradient history.
@@
 This effect seems to contribute to faster convergence in our case.
-
-		The evolution of the loss function, along with the learning rate schedule, is shown in Fig.~\ref{fig:loss_grad_des}.
+The evolution of the loss function, along with the learning rate schedule, is shown in Fig.~\eqref{fig:loss_grad_des}.
 As can be seen in this figure, the convergence rate improves significantly each time the optimizer is reinitialized.
 We also observe that, following the last few reinitializations, the loss exhibits a small bump immediately after the restart.
-
 We interpret this behavior as a consequence of the increased learning rate: some points that previously had low loss values may momentarily worsen before benefiting from faster convergence.
 This effect is likely due to points initially located in regions with weak attractive basins being pushed toward areas where the potential gradient is steeper, thus accelerating their convergence.
-
-		Although this strategy introduces the risk of desampling certain regions in favor of others, we did not observe any such issue in the remainder of our analysis.
+Although this strategy introduces the risk of desampling certain regions in favor of others, they correspond to low convergence regions.
+As we are anyway not interested in those places, but rather real flat directions, this is not a problem for us.
 
@@
 At iteration 1000, the optimizer was reinitialized once more, this time with a reduced learning rate of $10^{-3}$.
-A final reinitialization was performed at iteration 1500, setting the learning rate to $10^{-4}$, and the optimization was continued for an additional 1000 epochs.
+A final reinitialization was performed at iteration 1500, setting the learning rate to $10^{-4}$, and the optimization was continued for an additional 500 epochs.
 
 		Upon completion, it was observed that all data points converged to values close to $-4$.
-Specifically, nearly all data points attained values within an absolute error of $10^{-4}$, with the exception of four points whose deviations were on the order of $10^{-3}$.
+Specifically, nearly all data points attained values within an absolute error of at least $10^{-4}$, with the exception of four points whose deviations were on the order of $10^{-3}$.
 Similarly, 99,739 out of 100,000 data points exhibited gradient norms smaller than $10^{-3}$.
@@
 
-		\begin{figure}
+		\begin{figure}[h!]
 			\centering
-			\includegraphics[scale = 0.5]{Figures/Loss_grad_des.png}
+			\includegraphics[scale = 0.5]{Figures/Loss_grad_des_1.png}
 			\caption{Evolution of the loss function during gradient descent and corresponding learning rate schedule, noted $\alpha$ on the left y-axis, both plotted on a logarithmic scale.
@@
 This figure shows all possible 2D projections of the data, along with the 1D histograms of each coordinate after gradient descent.
-
-		\begin{figure}[t]
+		\begin{figure}[h!]
 			\centering
@@
 		\end{figure}
-
 		We can make a few comments on those plots.
@@
 We do not however attempt to shift the points along flat directions to depopulate the origin or repopulate other regions.
-
 		%\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least few points in each direction)}
-
 		Once the gradient descent has been completed and the flat direction sampled, the next step is to identify the structure of the underlying manifold.
@@
 Specifically, we aim to determine the dimensionality of the manifold and wether it consists of a single connected component or multiple disjoint components (e.g., two intersecting hyperplanes).
-
 		To this end, we apply a local Principal Component Analysis (PCA).
@@
 In other words, it provides an estimate of the local dimensionality around each point.
-
 		We perform this analysis for several values of $k$, namely $k \in \{5, 10, 20, 50, 100\}$, and we fix $\epsilon = 0.99$. The results are presented in Fig. \ref{local_pca}.
@@
 This can be attributed to the fact that if the true dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality for a fraction of the points.
-
 		Additionally, for $k \geq 20$, we observe an increasing number of points being assigned dimensionalities of 4 or 5.
@@
 This artificial enlargement of the neighbourhood can cause the estimated local dimensionality to rise.
-
 		We thus conclude that the manifold under investigation has an intrinsic dimension of 3.
@@
 To rule out this possibility, we apply a clustering algorithm based on local density, where we only select the points of dimension 3.
-This, way, we remove the possible intersection points with dimension 4.
+This, way, we remove the possible intersection points with dimension 4 or 5.
 For the purpose of the clustering, we use the HDBSCAN algorithm\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation.
 Briefly, it is a density-based clustering method that extends DBSCAN by converting it into a hierarchical clustering algorithm and then extracting a flat clustering based on the stability of clusters.}.
-
 		We set the minimum cluster size to 10 points. Out of the 98,606 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849. 
-
 		The smallest cluster (10 points) is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
@@
 We interpret these as outliers or edge points rather than representatives of a separate manifold.
-
 		What the algorithm does indicate, however, is that over 90\% of the data belongs to a single dominant cluster. In Fig.~\ref{3dplots}, we show 3D projections of the data to visualize the clustering. 
-
 		\begin{figure}[h!]
@@
 		\end{figure}
-
 		In these scatter plots, turquoise points belong to the main cluster, while purple points are those that the algorithm failed to assign.
@@
 Therefore we can conclude that, in order to characterise the manifold, we need two independent constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
-If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to a global $e^{-2\tilde{x}_8}$ factor, this potential is actually a polynomial of the embedding coordinates.
+If we have a look at the form of the potential, we can observe that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to some potential global factor of the dilaton of the form $e^{\tilde{x}_8}$, this potential is actually a polynomial of the embedding coordinates.
 Therefore, the components of $|\nabla V|$ are also polynomials in those variables.
 We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those.
-Note that we are now taking $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
-Of course if one takes directly the gradient of \eqref{eq:scalarpotential124810}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
+Note that we are now taking $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
+Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
 The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
-There are a number of way one can deal with it, using already existing methods such as AI Feynman methods~\cite{Udrescu:2019mnk}, or ...
-\bd{litterature review}.
-In the spirit of trying to build a generalisable method, we develop here our own method, which is based on symbolic regression using an Annealing Importance Sampling method.
 
@@
 We then define the unnormalized density at level $n$ in terms of a prior distribution $p_0(z)$ over the hypothesis space and a loss function $L(z)$:
-		\begin{equation}
+		\begin{equation}\label{eq:gamman}
 			\gamma_n(z) := d_0(z) \: \exp \left( -\beta_n L(z) \right).
@@
 It gives the probability to transition from $z_{n-1}$ to $z_n$.
-The backward kerne represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
+The backward kernel represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
 The purpose of $q$ is to give a proposition for $z_n$ given $z_{n-1}$.
@@
 			\item Coefficient pertubation.
-Given a polynomial $z_{n-1}$, we choose randomly one of his coefficient and modify it by a random noise from the guassian distribution $\mathcal{N}(0,\sigma^2)$.
+Given a polynomial $z_{n-1}$, we choose randomly one of its coefficient and modify it by a random noise from the guassian distribution $\mathcal{N}(0,\sigma^2)$.
 So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2.1 x_1 + 3 x_2^2$.
@@
 Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and multiply it by one of the available variable.
-So for eg : $2 ^x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$.
+So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$.
 			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$. 
@@
 
-		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
+%		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
 Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate.
@@
 
-	\paragraph{Results}
-	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}.
-The code finds the 7 different following polynomials:
+	The results of this mlethod are as follow. The code finds 8 different following polynomials: 
 	\begin{subequations} \label{eq:pols}
@@
       p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
-      		- x_{2}^{2}x_{10},
+      		- x_{2}^{2}x_{10}, \\
+      p_{8} &= -2 + 4 x_{8} - 2 x_8^2 + 2 x_{4}^2 x_8 - x_8^2 x_{10}^2
     \end{align}
   \end{subequations}
-  where $x_{8} = e^{\tilde{x}_{8}}$. They are found with different frequencies, depending on the chosen parameters.
+  where $x_{8} = e^{\tilde{x}_{8}}$. They are found with different frequencies with some polynomials occuring more often than others. The results are presented in \eqref{table:results}.
 
@@
 
-  This is this argument that allowed us to round the coefficients of the polynomials given by the annealed importance sampling algorithm, and found the polynomials in \ref{eq:pols}.
-
-  \begin{enumerate}
-  		\item {\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample\_size} = 10000$}
-
-	  For 100 runs with parameters
-		\begin{equation} \label{eq:sample10000beta3}
-			\begin{gathered}
-				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.1, \\
-				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-			\end{gathered}
-		\end{equation}
-		the polynomials are found at the following frequencies
-	  \begin{equation}
-	  	\begin{tabular}{l|cccccccc}
-	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 76\% & 18\% & 10\% & 6\% & 4\% & 1\% & 2\% & 6\%
+ This is this argument that allowed us to round the coefficients of the polynomials given by the annealed importance sampling algorithm, and found the polynomials in Eq. \eqref{eq:pols}.
+
+We now provide further details about the implementation of our code.
+To recover the polynomials presented in Eq.~\eqref{eq:pols}, we performed 1000 independent runs, each involving 1000 particles.
+As can be seen in \eqref{eq:gamman}, we see that what matters the most in the the inverse temperature, but rather the inverse temperature multiplied by the loss function.
+Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed ans adaptive temperature approach, as previously described.
+The acceptance ratio was controlled by the following schedule:
+\begin{equation}
+	\texttt{acceptance\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
+\end{equation}
+which encourages exploration during the early stages of training and gradually transitions to a more selective regime. We initialized the algorithm with 
+\begin{equation}\label{eq:sample10000adaptativetemp}
+	\begin{aligned}
+		&\beta = 10^{-6}\,, \\
+		&\texttt{p\_{modify} = 0.5},\\
+		&\texttt{p\_{multiply} = 0.25},\\
+		&\texttt{p\_{divide} = 0.25}. 
+	\end{aligned}
+\end{equation}
+This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
+For the representation of polynomials, we adopt a vectorial approach.
+Specifically, each polynomial is represented as an array of its coefficients $\{c_k\}$, where $k \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of authorized monomials, determined by the chosen maximum degree.
+We also impose a constraint on the maximum number of terms within a single polynomial to promote sparsity.
+An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.
+For the simulations we have done, we chose :
+\begin{equation}
+	\begin{aligned}
+	&\texttt{max\_degree} = 4,\\
+	&\texttt{max\_num\_monomials} = 6.
+\end{aligned}
+\end{equation}
+The main results are presented in Fig.\eqref{fig:evolutionoftargetreproduction} and the losses of the run are shown in Fig. \ref{fig:losses_ASMC}. 
+%\begin{figure}
+%	\centering
+%	\includegraphics[scale=0.35]{Figures/Loss_all_ASMC.png}
+%	\caption{Losses of all the 1000 runs in shaded blue and the average loss over all run in brown.}
+%	\label{fig:losses_ASMC}
+%\end{figure}
+The frequencies with which each of the polynomials in Eq.~\eqref{eq:pols} was recovered are reported in the table below:
+  \begin{equation}
+  	\label{table:results}
+	\begin{tabular}{l|ccccccccc}
+		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $p_{8}$ &  $\varnothing$  \\\hline\hline
+		Frequency & 92.6\% & 75.0\% & 1.7\% & 51.9\% & 0.7\% & 0.1\% & 0.2\% & 0.7\% & 0.3\%
 	\end{tabular}
 \end{equation}
-	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3}.
-
-	  Averaged number of particles reproducing a target in a successful run: $973 \pm 103$
-
-	  Mean loss with regularisation for particles reproducing a target: $854 \pm 427$
-
-	  Mean loss without regularisation for particles reproducing a target: $602 \pm 417$
+
+With this approach, the average number of particles reproducing one of the target polynomials at the end of a run is 882, with a standard deviation of 200.
+Moreover, the algorithm typically identifies an average of 2.24 distinct polynomials per run, demonstrating its capacity to uncover multiple solutions simultaneously.
+Finally the algorithm failed at finding a solution in only 3 runs, demonstrating the robustness of the technique.
 
@@
 	\centering
-	  	\begin{tikzpicture}
-	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
-	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
-	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-	  	\end{tikzpicture}
-	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}.
-(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
-The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
-	  	\label{fig:sample10000beta3}
+	\begin{adjustbox}{width=20cm,center}
+		\begin{minipage}[t]{0.31\paperwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figures/Count_beta_adaptative_temp_indiv}
+			\caption*{(a)}
+		\end{minipage}%
+		\hfill
+		\begin{minipage}[t]{0.31\paperwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figures/Count_good_pol_all}
+			\caption*{(b)}
+		\end{minipage}%
+		\hfill
+		\begin{minipage}[t]{0.31\paperwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figures/Loss_all_ASMC.png}
+			\caption*{(c)}
+		\end{minipage}
+	\end{adjustbox}
+	\caption{{\bfseries \boldmath \texttt{acceptance\_ratio} = 0.8 - 0.5 $\times$ (\texttt{epoch}/\texttt{n\_epochs})} (a) Evolution of the mean number of particles reproducing each target polynomial (log scale).
+(b) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp}.}
+	\label{fig:evolutionoftargetreproduction}
 \end{figure}
 
-	  After the AIS, we performed an exploitation phase to fine tune the coefficients.
-The distributions of the particles with respect to their loss (without regularisation), is plotted in fig.~\ref{fig:distlocalsearch}.
-The fine tuning (with \texttt{local\_search}) is made using the loss with regularisation.
-
-	  \begin{figure}[h!]
-	  	\centering
-	  	\includegraphics[scale=0.75]{Figures/Local_search_2025_05_19_at_06_01_21.pdf}
-	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} Distributions of all the 100,000 particles with respect to their loss (without regularisation) (a) directly after AIS with parameters~\eqref{eq:sample10000beta3} and (b) after 200 steps of \texttt{local\_search}.
-The fine tuning (with \texttt{local\_search}) is made using the loss with regularisation.}
-	  	\label{fig:distlocalsearch}
-	  \end{figure}
-
-	  We list below, for each polynomials in eq.~\eqref{eq:pols}, one example of representing particles directly after AIS and after the fine tuning, and the associated losses (without regularisation):
-	  \begin{align}
-	  	p_{1}:&\quad
-	  	\begin{aligned}
-	  		&-1.939\,x_{1} + 2.120\,x_{1}\tilde{x}_{8} + x_{10}x_{2}\tilde{x}_{8} - 2.266\, x_{2}x_{4}\tilde{x}_{8} + 0.029\,x_{2}^{2}x_{4},\quad L^{(\lambda = 0)} \simeq 754, \\
-			&-1.416\,x_{1} + 1.414\, x_{1}\tilde{x}_{8} + x_{10}x_{2}\tilde{x}_{8} - 1.414\,x_{2}x_{4}\tilde{x}_{8} + 0.00001\,x_{2}^{2}x_{4},\quad L^{(\lambda = 0)} \simeq 0.0040,
-	  	\end{aligned} \\[7pt]
-	  	p_{2}:&\quad
-	  	\begin{aligned}
-	  		&2.213\,x_{2} - 2.075\,x_{2}\tilde{x}_{8} + 1.674\,x_{1}x_{10} + 2.015\,x_{1}x_{4} - x_{10}^{2}x_{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 244, \\
-			&2.002\,x_{2} - 2.002\,x_{2}\tilde{x}_{8} + 1.417\,x_{1}x_{10} + 2.001\,x_{1}x_{4} - x_{10}^{2}x_{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.015,
-	  	\end{aligned} \\[7pt]
-	  	p_{3}:&\quad
-	  	\begin{aligned}
-	  		&2\,x_{2} - 1.808\,x_{2}\tilde{x}_{8} + 1.168\,x_{1}\tilde{x}_{8}x_{10} + 1.828\,x_{1}x_{4}\tilde{x}_{8} - 1.864\,x_{2}x_{4}^{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 180, \\
-			&2\,x_{2} - 1.998\,x_{2}\tilde{x}_{8} + 1.412\,x_{1}\tilde{x}_{8}x_{10} + 1.998\,x_{1}x_{4}\tilde{x}_{8} - 1.998\,x_{2}x_{4}^{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.016,
-	  	\end{aligned} \\[7pt]
-	  	p_{4}:&\quad
-	  	\begin{aligned}
-	  		&1.458\,x_{2} - 1.341\,x_{2}\tilde{x}_{8} + 1.497\,x_{1}x_{4} + x_{1}\tilde{x}_{8}x_{10} - 1.008\,x_{2}x_{4}\tilde{x}_{8}x_{10} + 0.020 x_{2}^{2}x_{4}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 218, \\
-			&1.419\,x_{2} - 1.418\,x_{2}\tilde{x}_{8} + 1.416\,x_{1}x_{4} + x_{1}\tilde{x}_{8}x_{10} - 1.001\,x_{2}x_{4}\tilde{x}_{8}x_{10} - 0.0003\,x_{2}^{2}x_{4}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.074,
-	  	\end{aligned} \\[7pt]
-	  	p_{5}:&\quad
-	  	\begin{aligned}
-	  		&-2.179\,x_{1} - 1.571\,x_{2}x_{4} - 1.953\,x_{1}x_{4}^{2} + 1.983\,x_{1}\tilde{x}_{8} + 1.530\,x_{2}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2},\quad L^{(\lambda = 0)} \simeq 210, \\
-			&-2.008\,x_{1} - 2.001\,x_{2}x_{4} - 1.999\,x_{1}x_{4}^{2} + 1.995\,x_{1}\tilde{x}_{8} + 1.412\,x_{2}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2},\quad L^{(\lambda = 0)} \simeq 0.228,
-	  	\end{aligned} \\[7pt]
-	  	p_{6}:&\quad
-	  	\begin{aligned}
-	  		&- 2.856\,x_{2}x_{4} - 2.499\,x_{1}x_{4}^{2} + 2.721\,x_{2}x_{4}\tilde{x}_{8} + 1.677\,x_{2}x_{10} - 1.187\,x_{2}\tilde{x}_{8}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2} ,\quad L^{(\lambda = 0)} \simeq 202, \\
-			&- 2.043\,x_{2}x_{4} - 2.005\,x_{1}x_{4}^{2} + 2.030\,x_{2}x_{4} \tilde{x}_{8} + 1.393\,x_{2}x_{10} - 1.401\,x_{2}\tilde{x}_{8}x_{10} + x_{1}\tilde{x}_{8}x_{10}^2 ,\quad L^{(\lambda = 0)} \simeq 1.28,
-	  	\end{aligned} \\[7pt]
-	  	p_{7}:&\quad
-	  	\begin{aligned}
-	  		&- 1.354\,x_{1}^{2}x_{4} + 1.243\,x_{2}^{2}x_{4} + 1.304\,x_{1}x_{2}x_{4}^{2} - 1.053\,x_{1}^{2}x_{10} - x_{2}^{2}x_{10} + 0.052\,x_{2}x_{4}^{2}x_{10} ,\quad L^{(\lambda = 0)} \simeq 373, \\
-			&- 1.413\,x_{1}^{2}x_{4} + 1.415\,x_{2}^{2}x_{4} + 1.413\,x_{1}x_{2}x_{4}^{2} - 0.997\,x_{1}^{2}x_{10} - x_{2}^{2}x_{10} + 0.0003\,x_{2}x_{4}^{2}x_{10} ,\quad L^{(\lambda = 0)} \simeq 0.038.
-	  	\end{aligned}
-	  \end{align}
-
-	  \item {\bfseries \boldmath $\beta$ in power $4$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}
-
-	  For 100 runs with parameters
-		\begin{equation} \label{eq:sample10000beta4}
-			\begin{gathered}
-				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{4}, \quad \sigma = 0.1, \\
-				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-			\end{gathered}
-		\end{equation}
-		the polynomials are found at the following frequencies
-	  \begin{equation}
-	  	\begin{tabular}{l|cccccccc}
-	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 74\% & 17\% & 7\% & 8\% & 2\% & 0\% & 2\% & 6\%
-	  	\end{tabular}
-	  \end{equation}
-	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta4}.
-
-	  Averaged number of particles reproducing a target in a successful run: $951 \pm 200$
-
-	  Mean loss with regularisation for particles reproducing a target: $709 \pm 320$
-
-	  Mean loss without regularisation for particles reproducing a target: $452 \pm 309$
-
-	  \begin{figure}[h!]
-	  	\centering
-	  	\begin{tikzpicture}
-	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_22_at_08_48_38.pdf}};
-	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_22_at_08_48_38_detailed.pdf}};
-	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-	  	\end{tikzpicture}
-	  	\caption{{\bfseries \boldmath $\beta$ in power $4$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta4}.
-(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
-The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
-	  	\label{fig:sample10000beta4}
-	  \end{figure}
-
-	  \item {\bfseries \boldmath $\beta$ in power $5$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}
-
-  		For 100 runs with parameters
-		\begin{equation}
-			\begin{gathered}
-				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
-				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-			\end{gathered}
-		\end{equation}
-		the polynomials are found at the following frequencies
-	  \begin{equation}
-	  	\begin{tabular}{l|cccccccc}
-	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 69\% & 11\% & 7\% & 12\% & 0\% & 4\% & 0\% & 13\%
-	  	\end{tabular}
-	  \end{equation}
-	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta5}.
-
-	  Averaged number of particles reproducing a target in a successful run: $960 \pm 175$
-
-	  Mean loss with regularisation for particles reproducing a target: $606 \pm 257$
-
-	  Mean loss without regularisation for particles reproducing a target: $359 \pm 244$
-
-	  \begin{figure}[h!]
-	  	\centering
-	  	\begin{tikzpicture}
-	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32.pdf}};
-	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32_detailed.pdf}};
-	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-	  	\end{tikzpicture}
-	  	\caption{{\bfseries \boldmath $\beta$ in power $5$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta5}.
-(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
-The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
-	  	\label{fig:sample10000beta5}
-	  \end{figure}
-
-  		\item {\bfseries \boldmath $\beta$ in power $5$, $\sigma$ varying, $\texttt{sample size} = 10000$}
-
-  		For 100 runs with parameters
-		\begin{equation} \label{eq:sample10000beta5}
-			\begin{gathered}
-				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
-				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-			\end{gathered}
-		\end{equation}
-		the polynomials are found at the following frequencies
-	  \begin{equation}
-	  	\begin{tabular}{l|cccccccc}
-	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
-	  	\end{tabular}
-	  \end{equation}
-	  The sum of the percentages is higher than 100\% because some runs find more than one polynomials.
-The code fails to find any polynomial in 13\% of the time.
-The averaged time needed for a single run on a PC in $\sim 700\,{\rm s}$.
-\ce{This timing is with \texttt{analysis}, it may be less without.}
-
-	  Averaged number of particles reproducing a target in a successful run: $931 \pm 230$
-
-	  Mean loss with regularisation for particles reproducing a target: $597 \pm 264$
-
-	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$
-
-	  \item {\bfseries \boldmath $\beta$ in power $3$, $\sigma$ varying, $\texttt{sample size} = 10000$}
-
-	  For 100 runs with parameters
-		\begin{equation} \label{eq:sample10000beta3sigmavar}
-			\begin{gathered}
-				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
-				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-			\end{gathered}
-		\end{equation}
-		the polynomials are found at the following frequencies
-	  \begin{equation}
-	  	\begin{tabular}{l|cccccccc}
-	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 68\% & 17\% & 6\% & 9\% & 2\% & 1\% & 1\% & 11\%
-	  	\end{tabular}
-	  \end{equation}
-	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3sigmavar}.
-
-	  Averaged number of particles reproducing a target in a successful run: $966 \pm 115$
-
-	  Mean loss with regularisation for particles reproducing a target: $837 \pm 438$
-
-	  Mean loss without regularisation for particles reproducing a target: $609 \pm 430$
-
-	  \begin{figure}[h!]
-	  	\centering
-	  	\begin{tikzpicture}
-	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46.pdf}};
-	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46_detailed.pdf}};
-	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-	  	\end{tikzpicture}
-	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma$ varying, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}.
-(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
-The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
-	  	\label{fig:sample10000beta3sigmavar}
-	  \end{figure}
-
-	  \item {\bfseries \boldmath $\beta$ in power $5$, $\sigma=0.1$, $\texttt{sample size} = 1000$}
-
-	  For 100 runs with parameters
-		\begin{equation} \label{eq:sample1000}
-			\begin{gathered}
-				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
-				\texttt{sample size} = 1000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
-				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
-			\end{gathered}
-		\end{equation}
-		the polynomials are found at the following frequencies
-	  \begin{equation}
-	  	\begin{tabular}{l|cccccccc}
-	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
-	  		Frequency & 72\% & 27\% & 3\% & 19\% & 2\% & 0\% & 0\% & 12\%
-	  	\end{tabular}
-	  \end{equation}
-	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample1000}.
-
-	  Averaged number of particles reproducing a target in a successful run: $401 \pm 389$
-
-	  Mean loss with regularisation for particles reproducing a target: $406 \pm 193$ \ce{Needs to be renormalized by the sample size.}
-
-	  Mean loss without regularisation for particles reproducing a target: $272 \pm 192$ \ce{Needs to be renormalized by the sample size.}
-
-	  \begin{figure}[h!]
-	  	\centering
-	  	\begin{tikzpicture}
-	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44.pdf}};
-	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44_detailed.pdf}};
-	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-	  	\end{tikzpicture}
-	  	\caption{{\bfseries \boldmath $\beta$ in power $5$, $\sigma=0.1$, $\texttt{sample size} = 1000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}.
-(b) Evolution of the mean numbers of particles reproducing each targets polynomial.
-The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
-	  	\label{fig:sample1000}
-	  \end{figure}
-  \end{enumerate}
-
-  \ce{Draw histograms of the polynomials distribution to discuss runs with multiple outputs?}
-
+\section{Conclusion}
+
+In this work, we have presented a novel machine learning approach to systematically identify and characterize flat directions in supergravity scalar potentials.
+Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (2,0) supergravity derived from
+$AdS_3 \times S^3 \times T^4$ compactifications of IIB supergravity.
+
+We developed a robust pipeline that transitions from numerical exploration to analytical understanding.
+The gradient descent procedure successfully samples the flat direction manifold, while local PCA analysis reveals its intrinsic dimensionality.
+Most notably, our annealed importance sampling approach to symbolic regression automatically discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
+
+Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold, with one direction potentially gauge-fixable.
+The discovered solution preserves $U(1) \times U(1)$ gauged symmetry and exhibits a rich spectrum structure.
+The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold.
+
+The method demonstrates remarkable efficiency and reliability.
+The algorithm discovers eight distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
+Futhermore, upon 1000 the algorithm failed at finding any solution in only 3 cases, demonstrating the robustness of the method.
+
+This approach opens several promising avenues for advancement.
+The scalability to higher-dimensional cases represents the most immediate challenge and opportunity.
+By increasing the number of particles, refining the annealing schedule, and optimizing polynomial search strategies, we anticipate extending this methodology to the full 13-scalar theory and potentially to other supergravity models.
+
+Beyond technical improvements, this work suggests a broader paradigm for studying conformal manifolds in string theory and supergravity.
+The ability to automatically extract analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
+
+The marriage of machine learning techniques with traditional supergravity analysis represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
+As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
+
+While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
+
+\appendix
 \section{Supergravity solutions}
@@
 
-\section{Conclusion}
-\begin{itemize}[label=\textbullet]
-	\item Conclusion: good prospects of improvement to be able to access higher dimensional cases. Classify flat directions.
-	\item Appendix with some details on the code?
-
-\end{itemize}
-
-In this work, we have presented a novel machine learning approach to systematically identify and characterize flat directions in supergravity scalar potentials.
-Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (2,0) supergravity derived from
-$AdS_3 \times S^3 \times T^4$ compactifications of IIB supergravity.
-
-We developed a robust pipeline that transitions from numerical exploration to analytical understanding.
-The gradient descent procedure successfully samples the flat direction manifold, while local PCA analysis reveals its intrinsic dimensionality.
-Most notably, our annealed importance sampling approach to symbolic regression automatically discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
-
-Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold, with one direction potentially gauge-fixable.
-The discovered solution preserves $U(1) \times U(1)$ gauged symmetry and exhibits a rich spectrum structure.
-The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold.
-
-The method demonstrates remarkable efficiency and reliability.
-Across different parameter choices, we achieve success rates of 69-76\% for the most common polynomial constraint, with computation times of approximately 700 seconds per run on standard hardware.
-The algorithm discovers seven distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
-
-This approach opens several promising avenues for advancement.
-The scalability to higher-dimensional cases represents the most immediate challenge and opportunity.
-By increasing the number of particles, refining the annealing schedule, and optimizing polynomial search strategies, we anticipate extending this methodology to the full 13-scalar theory and potentially to other supergravity models.
-
-Beyond technical improvements, this work suggests a broader paradigm for studying conformal manifolds in string theory and supergravity.
-The ability to automatically extract analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
-
-The marriage of machine learning techniques with traditional supergravity analysis represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
-As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
-
-While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
-
 \bibliography{references}

### 2025-06-13 potentials.py
add the potentials.py with the analytic gradient for the 5d trunc implemented

@@ -185,3 +185,80 @@ x10 * x2 * (x3 ** 2) -((x2 ** 2) * (1 + x3 ** 2)) + x4 ** 2 + (x1 ** \
 + x3 * x5)) + 2 * (tf.sqrt(2.)) * x10 * ((x1 ** 3) * x2 + (x1 ** 2) * \
 x4 -(x2 * (x2 * x4 + x3 * x5)) + x1 * (x2 ** 3 + 2 * x2 * (x3 ** 2) \
 -(x2 * (x4 ** 2)) -(x3 * x4 * x5)))
+
+def grad_V_1_2_4_8_10(x):
+    x1,x2,x4,x8,x10=tf.split(x,5,axis=1)
+    n_sample = x.shape[0]
+    f1 = 4 * (tf.exp(-2 * x8)) * (x1 ** 3) -((tf.exp(x8)) * (2 + \
+x10 ** 2) * ((tf.sqrt(2.)) * x10 * (x2 ** 3) + 2 * x1 * (-1 + x2 ** 2) \
++ 2 * x2 * x4)) + 2 * (2 * (x1 ** 3) + 3 * (tf.sqrt(2.)) * (x1 ** 2) * \
+x10 * x2 + (tf.sqrt(2.)) * x10 * x2 * (x2 -x4) * (x2 + x4) + x1 * (-4 \
++ (4 + 3 * (x10 ** 2)) * (x2 ** 2) + 2 * (tf.sqrt(2.)) * x10 * x4)) + \
+(tf.exp(-x8)) * (-8 * (x1 ** 3) -6 * (tf.sqrt(2.)) * (x1 ** 2) * x10 * \
+x2 + 4 * x2 * x4 + 4 * x1 * (1 -(x2 ** 2) + x4 ** 2)) 
+    f2 = -3 * \
+(tf.sqrt(2.)) * x1 * x10 * (-2 + (tf.exp(x8)) * (2 + x10 ** 2)) * (x2 ** \
+2) + ((-2 + (tf.exp(x8)) * (2 + x10 ** 2)) ** 2) * (x2 ** 3) + 2 * x2 \
+* (-4 -2 * (tf.exp(-x8)) * (-1 + x1 ** 2) + (x1 ** 2) * (4 + 3 * (x10 \
+** 2)) -2 * (tf.sqrt(2.)) * x10 * x4 -((tf.exp(x8)) * (2 + x10 ** 2) * \
[…]

### 2025-06-17 Draft_MLFlatDirections.tex
correct typos and add flowchart for ASMC

@@
 \usepackage[english]{babel}
+
+\usepackage[most]{tcolorbox}
 
@@
 \usetikzlibrary{calc}
+\usetikzlibrary{shapes.geometric, arrows.meta, positioning}
+
+\tikzstyle{startstop} = [ellipse, minimum width=3.5cm, minimum height=1.cm, text centered, draw=black, fill=gray!20]
+\tikzstyle{process} = [rectangle, minimum width=6cm, minimum height=1.2cm, text centered, draw=black, fill=myblue!75]
+\tikzstyle{decision} = [rectangle, minimum width=5cm, minimum height=1.2cm, text centered, draw=black, fill=myorange!100, aspect=2]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 In this work, we propose a novel approach, where we study directly the scalar potential of supergravity.
-As already mentionned, the marginal deformation of CFT's in the large N limit, are in correspondance with the flat directions in the potential, i.e.
+As already mentionned, the marginal deformations of CFT's in the large N limit, are in correspondance with the flat directions in the potential, i.e.
 when there is a continuous set a scalar fields such that $\nabla V = 0$.
@@
 The emergence of machine learning techniques in theoretical physics opens new avenues for addressing such complex problems.
-Instead of solving the full symbolic system analytically from the outset, one can employ numerical methods to sample the solution space and subsequently apply symbolic regression to extract analytical patterns from the data.
+Instead of solving the full symbolic system analytically from the outset, one can employ numerical methods to sample the solution space and subsequently apply symbolic regression techniques to extract analytical patterns from the data.
 This hybrid approach has the potential to bypass the computational bottlenecks inherent in purely symbolic methods, while still aiming to uncover exact analytical expressions.
@@
 
-As an initial simplification, we restrict our analysis to the scalar fields $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x{10}$.
+As an initial simplification, we restrict our analysis to the scalar fields $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
 This subset, selected at random from the original set of thirteen scalar fields, serves to render the problem more tractable at the outset.
@@
 In scenarios where an explicit analytic expression for the potential and its gradient is inaccessible—yet numerical evaluation remains feasible—our method retains its validity.
+In particular, one could replace the analytic gradient by automatic differenciation methods if one can only evaluate the potential.
 Hence, the numerical strategy adopted here may prove effective even in cases where an exact analytic expression for the potential is out of reach.
@@
 	\subsection{Gradient descent and local analysis}
-		%\paragraph{Gradient descent: implementation, sampling, time needed, loss}
-
 		To identify the flat directions in the potential, we will use numerical tools.
@@
 The first step is thus to sample the manifold.
+			\subsubsection{Sampling the manifold}
+		%\paragraph{Gradient descent: implementation, sampling, time needed, loss}
 
@@
 
-		We then perform gradient descent on the points using TensorFlow’s automatic differentiation. The loss function is defined as:
+		We then perform gradient descent on the points using TensorFlow’s automatic differentiation \cite{tensorflow2015-whitepaper}. The loss function is defined as:
 		\begin{equation}
@@
 		where $\vec{X}^{\,i} = (x^i_1,\dots,x^i_6,\tilde{x}^i_7,\tilde{x}^i_8,\tilde{x}^i_9,x^i_{10},\dots,x^i_{12},\tilde{x}^i_{13})$ and $\vec{y}^{\,i} = (x^i_3,x^i_5,x^i_6,\tilde{x}^i_7,\tilde{x}^i_9,x^i_{11},x^i_{12},\tilde{x}^i_{11})$ denotes the data points.
+This way we only keep $(x^i_1,x^i_2,x^i_4,\tilde{x}^i_8,x^i_{10})$ alive after we have taken the derivative.
 As already mentionned above, we use the analytic formula for $\nabla V$, but we could have perform the gradient descent by fully using automatic differentiation.
@@
 		%\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least few points in each direction)}
+		\subsubsection{Determining the dimension}
 		Once the gradient descent has been completed and the flat direction sampled, the next step is to identify the structure of the underlying manifold.
@@
 		In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe a given dataset.
-In the problem discussed in this paper, we are looking for polynomial expressions such that $p(\vec{x}^i) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
+In the problem discussed in this paper, we are looking for polynomial expressions such that $p(\vec{x}^{\,i}) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
 This task involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods.
@@
 
+		\subsubsection{Annealed Sequential Monte Carlo principle}
 		To address these challenges, we employ an Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC) methods.
@@
 This allow to fine-tune the coefficients.
-
+\hspace{-2cm}
+\begin{center}
+	\begin{minipage}{18cm}
+		\begin{tcolorbox}[colback=myblue!5,
+			colframe=myblue,
+			title=Algorithm flowchart for ASMC algorithm,
+			halign title=flush center,
+			sharp corners
+			]
+%	\scalebox{0.5}{
+\begin{tikzpicture}[node distance=1.8cm and .5cm]
+
+	% Nodes
+	\node (start) [startstop] {Start};
+
+	\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
+	\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
+	\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
+	\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};
+
+	\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
+	\node (resample) [process, right=4.25cm of ess_check] {Resample particles};
+
+	\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
+	\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};
+
+	\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};
+
+	\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
+	\node (output) [process, below of=exploit] {Return best coefficients and logs};
+	\node (stop) [startstop, below of=output] {Stop};
+
+	% Arrows
+	\draw [arrow] (start) -- (init_particles);
+	\draw [arrow] (init_particles) -- (set_weights);
+	\draw [arrow] (set_weights) -- (compute_beta);
+	\draw [arrow] (compute_beta) -- (weight_update);
+	\draw [arrow] (weight_update) -- (ess_check);
+
+	\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
+	\draw [arrow] (resample) |- (mutation);
+
+	\draw [arrow] (ess_check) -- node[left] {No} (mutation);
+	\draw [arrow] (mutation) -- (acceptance);
+	\draw [arrow] (acceptance) -- (end_iter);
+
+	\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
+	\node [pos=10, below=430pt, xshift=-100pt] {No};
+	\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);
+
+	\draw [arrow] (exploit) -- (output);
+	\draw [arrow] (output) -- (stop);
+		\end{tikzpicture}
+		\end{tcolorbox}
+\end{minipage}
+\end{center}
 %		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
@@
 
-	The results of this mlethod are as follow. The code finds 8 different following polynomials: 
+	\subsubsection{Results}
+
+	The results of this method are as follow. The code finds 8 different following polynomials: 
 	\begin{subequations} \label{eq:pols}
@@
  This is this argument that allowed us to round the coefficients of the polynomials given by the annealed importance sampling algorithm, and found the polynomials in Eq. \eqref{eq:pols}.
+
+ \subsubsection{Setup of ASMC}
 

### 2025-06-17 Draft_MLFlatDirections.tex
replace flowchart

@@
 This allow to fine-tune the coefficients.
-\hspace{-2cm}
-\begin{center}
-	\begin{minipage}{18cm}
-		\begin{tcolorbox}[colback=myblue!5,
-			colframe=myblue,
-			title=Algorithm flowchart for ASMC algorithm,
-			halign title=flush center,
-			sharp corners
-			]
-%	\scalebox{0.5}{
-\begin{tikzpicture}[node distance=1.8cm and .5cm]
-
-	% Nodes
-	\node (start) [startstop] {Start};
-
-	\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
-	\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
-	\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
-	\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};
-
-	\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
-	\node (resample) [process, right=4.25cm of ess_check] {Resample particles};
-
-	\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
-	\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};
-
-	\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};
-
-	\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
-	\node (output) [process, below of=exploit] {Return best coefficients and logs};
-	\node (stop) [startstop, below of=output] {Stop};
-
-	% Arrows
-	\draw [arrow] (start) -- (init_particles);
-	\draw [arrow] (init_particles) -- (set_weights);
-	\draw [arrow] (set_weights) -- (compute_beta);
-	\draw [arrow] (compute_beta) -- (weight_update);
-	\draw [arrow] (weight_update) -- (ess_check);
-
-	\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
-	\draw [arrow] (resample) |- (mutation);
-
-	\draw [arrow] (ess_check) -- node[left] {No} (mutation);
-	\draw [arrow] (mutation) -- (acceptance);
-	\draw [arrow] (acceptance) -- (end_iter);
-
-	\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
-	\node [pos=10, below=430pt, xshift=-100pt] {No};
-	\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);
-
-	\draw [arrow] (exploit) -- (output);
-	\draw [arrow] (output) -- (stop);
-		\end{tikzpicture}
-		\end{tcolorbox}
-\end{minipage}
-\end{center}
+
 %		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
@@
   In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field.
-In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$.
+In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with
+  \begin{center}
+  	\begin{minipage}{18cm}
+  		\begin{tcolorbox}[colback=myblue!5,
+  			colframe=myblue,
+  			title=Algorithm flowchart for ASMC algorithm,
+  			halign title=flush center,
+  			sharp corners
+  			]
+  			%	\scalebox{0.5}{
+  				\begin{tikzpicture}[node distance=1.8cm and .5cm]
+
+  					% Nodes
+  					\node (start) [startstop] {Start};
+
+  					\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
+  					\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
+  					\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
+  					\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};
+
+  					\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
+  					\node (resample) [process, right=4.25cm of ess_check] {Resample particles};
+
+  					\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
+  					\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};
+
+  					\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};
+
+  					\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
+  					\node (output) [process, below of=exploit] {Return best coefficients and logs};
+  					\node (stop) [startstop, below of=output] {Stop};
+
+  					% Arrows
+  					\draw [arrow] (start) -- (init_particles);
+  					\draw [arrow] (init_particles) -- (set_weights);
+  					\draw [arrow] (set_weights) -- (compute_beta);
+  					\draw [arrow] (compute_beta) -- (weight_update);
+  					\draw [arrow] (weight_update) -- (ess_check);
+
+  					\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
+  					\draw [arrow] (resample) |- (mutation);
+
+  					\draw [arrow] (ess_check) -- node[left] {No} (mutation);
+  					\draw [arrow] (mutation) -- (acceptance);
+  					\draw [arrow] (acceptance) -- (end_iter);
+
+  					\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
+  					\node [pos=10, below=430pt, xshift=-100pt] {No};
+  					\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);
+
+  					\draw [arrow] (exploit) -- (output);
+  					\draw [arrow] (output) -- (stop);
+  				\end{tikzpicture}
+  			\end{tcolorbox}
+  		\end{minipage}
+  	\end{center}
+  	coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$.
 That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.

### 2025-06-17 Draft_MLFlatDirections.tex
replace flowchart

@@
 \usepackage{tikz}
+\usepackage{tcolorbox}
 \usetikzlibrary{calc}
@@
 
-\tikzstyle{startstop} = [ellipse, minimum width=3.5cm, minimum height=1.cm, text centered, draw=black, fill=gray!20]
-\tikzstyle{process} = [rectangle, minimum width=6cm, minimum height=1.2cm, text centered, draw=black, fill=myblue!75]
-\tikzstyle{decision} = [rectangle, minimum width=5cm, minimum height=1.2cm, text centered, draw=black, fill=myorange!100, aspect=2]
-\tikzstyle{arrow} = [thick,->,>=stealth]
+% Définition des couleurs modernes
+\definecolor{deepblue}{RGB}{41, 128, 185}
+\definecolor{lightblue}{RGB}{174, 214, 241}
+\definecolor{emerald}{RGB}{46, 204, 113}
+\definecolor{lightemerald}{RGB}{212, 245, 227}
+\definecolor{coral}{RGB}{231, 76, 60}
+\definecolor{lightcoral}{RGB}{250, 215, 212}
+\definecolor{charcoal}{RGB}{52, 73, 94}
+\definecolor{lightgray}{RGB}{150, 150, 150}
+
+% Styles épurés et modernes
+\tikzstyle{startstop} = [
+ellipse, 
+minimum width=3cm, 
+minimum height=1cm, 
+text centered, 
+draw=charcoal, 
+fill=lightgray,
+line width=1.2pt,
+font=\sffamily\small\bfseries
+]
+
+\tikzstyle{process} = [
+rectangle, 
+minimum width=5.5cm, 
+minimum height=1.1cm, 
+text centered,
+draw=myblue, 
+fill=lightblue,
+line width=1pt,
+rounded corners=2pt,
+font=\sffamily\small
+]
+
+\tikzstyle{decision} = [
+rectangle, 
+minimum width=3.2cm, 
+minimum height=1.cm, 
+text centered, 
+draw=coral, 
+fill=lightcoral,
+line width=1pt,
+font=\sffamily\small\bfseries,
+aspect=1.3
+]
+
+\tikzstyle{arrow} = [
+thick,
+->,
+>=Stealth,
+color=charcoal,
+line width=1.5pt
+]
+
+\tikzstyle{arrow_label} = [
+font=\sffamily\small\bfseries,
+color=charcoal
+]
 
@@
 \begin{center}
-  	\begin{minipage}{18cm}
-  		\begin{tcolorbox}[colback=myblue!5,
+	\begin{minipage}{16cm}
+		\begin{tcolorbox}[
+			colback=white,
 			colframe=myblue,
-  			title=Algorithm flowchart for ASMC algorithm,
+			title=\textbf{Algorithme ASMC - Diagramme de flux},
+			fonttitle=\sffamily\large,
 			halign title=flush center,
-  			sharp corners
+			boxrule=2pt,
+			left=6pt,
+			right=6pt,
+			top=8pt,
+			bottom=8pt
 			]
-  			%	\scalebox{0.5}{
-  				\begin{tikzpicture}[node distance=1.8cm and .5cm]
-
-  					% Nodes
+			\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]
+
+				% Nœuds
 				\node (start) [startstop] {Start};
 
-  					\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
-  					\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
-  					\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
-  					\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};
-
-  					\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
-  					\node (resample) [process, right=4.25cm of ess_check] {Resample particles};
-
-  					\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
-  					\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};
-
-  					\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};
-
-  					\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
-  					\node (output) [process, below of=exploit] {Return best coefficients and logs};
-  					\node (stop) [startstop, below of=output] {Stop};
-
-  					% Arrows
+				\node (init_particles) [process, below of=start] {Initialize particles et weights};
+
+				\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};
+
+				\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};
+
+				\node (ess_check) [decision, below of=weight_update] {ESS $<$ Threshold ?};
+
+				\node (resample) [process, right=3.8cm of ess_check] {Resampling particles};
+
+				\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with Metropolis Hasting proposal};
+
+				\node (acceptance) [process, below of=mutation] {Accept/Reject particles};
+
+				\node (end_iter) [decision, below of=acceptance] {Last step ?};
+
+				\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};
+
+				\node (output) [process, below of=exploit] {Return current particles};
+
+				\node (stop) [startstop, below of=output] {End};
+
+				% Flèches avec étiquettes améliorées
 				\draw [arrow] (start) -- (init_particles);
-  					\draw [arrow] (init_particles) -- (set_weights);
-  					\draw [arrow] (set_weights) -- (compute_beta);
+				\draw [arrow] (init_particles) -- (compute_beta);
 				\draw [arrow] (compute_beta) -- (weight_update);
@@
 
-  					\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
+				\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
 				\draw [arrow] (resample) |- (mutation);
 
-  					\draw [arrow] (ess_check) -- node[left] {No} (mutation);
+				\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
 				\draw [arrow] (mutation) -- (acceptance);
@@
 
-  					\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
-  					\node [pos=10, below=430pt, xshift=-100pt] {No};
-  					\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);
-
+				% Boucle de retour améliorée
+				\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {Non} ++(-4.5,0) |- (compute_beta);
+
+				\draw [arrow] (end_iter) -- node[right, arrow_label] {No} (exploit);
 				\draw [arrow] (exploit) -- (output);
 				\draw [arrow] (output) -- (stop);
+
 			\end{tikzpicture}
@@
 \end{center}
+%  \begin{center}
+%  	\begin{minipage}{18cm}
+%  		\begin{tcolorbox}[colback=myblue!5,
+%  			colframe=myblue,
+%  			title=Algorithm flowchart for ASMC algorithm,
+%  			halign title=flush center,
+%  			sharp corners
+%  			]
+%  			%	\scalebox{0.5}{
+%  				\begin{tikzpicture}[node distance=1.8cm and .5cm]
+%  					
+%  					% Nodes
+%  					\node (start) [startstop] {Start};
+%  					
+%  					\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
+%  					\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
+%  					\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
+%  					\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};
+%  					
+%  					\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
+%  					\node (resample) [process, right=4.25cm of ess_check] {Resample particles};
+%  					
+%  					\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
+%  					\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};
+%  					
+%  					\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};
+%  					
+%  					\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
+%  					\node (output) [process, below of=exploit] {Return best coefficients and logs};
+%  					\node (stop) [startstop, below of=output] {Stop};
+%  					
+%  					% Arrows
+%  					\draw [arrow] (start) -- (init_particles);
+%  					\draw [arrow] (init_particles) -- (set_weights);
+%  					\draw [arrow] (set_weights) -- (compute_beta);
+%  					\draw [arrow] (compute_beta) -- (weight_update);
+%  					\draw [arrow] (weight_update) -- (ess_check);
+%  					
+%  					\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
+%  					\draw [arrow] (resample) |- (mutation);
+%  					
+%  					\draw [arrow] (ess_check) -- node[left] {No} (mutation);
+%  					\draw [arrow] (mutation) -- (acceptance);
+%  					\draw [arrow] (acceptance) -- (end_iter);
+%  					
+%  					\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
+%  					\node [pos=10, below=430pt, xshift=-100pt] {No};
+%  					\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);
+%  					
+%  					\draw [arrow] (exploit) -- (output);
+%  					\draw [arrow] (output) -- (stop);
+%  				\end{tikzpicture}
+%  			\end{tcolorbox}
+%  		\end{minipage}
+%  	\end{center}
   	coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$.

### 2025-06-23 Draft_MLFlatDirections.tex
Add and correct the pseudo code in Appendix

@@
 \usepackage[most]{tcolorbox}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 Our methodology combines gradient descent sampling of the flat direction manifold with some symbolic regression technique.
-There exist a large litterature on symbolic regression, using methods from genetic programming \cite{koza1994genetic,randall2022bingo,burlacu2019parsimony}, to deep machine learning \cite{petersen2019deep,kamienny2022end}, generative modelling \cite{valipour2021symbolicgpt} and diffusion models \cite{bastiani2025diffusion}.
+There exist a large litterature on symbolic regression, using methods from genetic programming \cite{koza1994genetic} such as \cite{virgolin2021improving,randall2022bingo,burlacu2019parsimony}, to deep machine learning \cite{petersen2019deep,kamienny2022end}, generative modelling \cite{valipour2021symbolicgpt}, diffusion models \cite{bastiani2025diffusion}, and equation learner with the nodes being symbolic operations \cite{2018arXiv180607259S}.
+Another state-of-the art algorithm is the AIFeynman methods \cite{Udrescu:2019mnk}.
+They use neural network to identify structure in the dataset (such as translational symmetries, multiplicative separability, compositionality, \dots) to recursively define simpler problems on which they can fit the solutions with polynomials.
 However, in the spirit of trying to build a generalisable method, we develop here our own algorithm, which is based on symbolic regression using an Annealing Importance Sampling method (AIS) \cite{neal1998annealedimportancesampling}.
@@
 
-	The results of this method are as follow. The code finds 8 different following polynomials: 
+	The results of this method are as follow. The code finds the 8 different following polynomials: 
 	\begin{subequations} \label{eq:pols}
@@
   In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field.
-In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with
-\begin{center}
-	\begin{minipage}{16cm}
+In our case, the potential $V$ and its gradient $\nabla V$ are polynomial  functions with coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$.
+That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.
+\begin{figure}[h!]
+	\centering
+	\begin{minipage}{14cm}
 		\begin{tcolorbox}[
@@
 			colframe=myblue,
-			title=\textbf{Algorithme ASMC - Diagramme de flux},
+			title=\textbf{ASMC Algorithm},
 			fonttitle=\sffamily\large,
@@
 	\end{minipage}
-\end{center}
-%  \begin{center}
-%  	\begin{minipage}{18cm}
-%  		\begin{tcolorbox}[colback=myblue!5,
-%  			colframe=myblue,
-%  			title=Algorithm flowchart for ASMC algorithm,
-%  			halign title=flush center,
-%  			sharp corners
-%  			]
-%  			%	\scalebox{0.5}{
-%  				\begin{tikzpicture}[node distance=1.8cm and .5cm]
-%  					
-%  					% Nodes
-%  					\node (start) [startstop] {Start};
-%  					
-%  					\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
-%  					\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
-%  					\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
-%  					\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};
-%  					
-%  					\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
-%  					\node (resample) [process, right=4.25cm of ess_check] {Resample particles};
-%  					
-%  					\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
-%  					\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};
-%  					
-%  					\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};
-%  					
-%  					\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
-%  					\node (output) [process, below of=exploit] {Return best coefficients and logs};
-%  					\node (stop) [startstop, below of=output] {Stop};
-%  					
-%  					% Arrows
-%  					\draw [arrow] (start) -- (init_particles);
-%  					\draw [arrow] (init_particles) -- (set_weights);
-%  					\draw [arrow] (set_weights) -- (compute_beta);
-%  					\draw [arrow] (compute_beta) -- (weight_update);
-%  					\draw [arrow] (weight_update) -- (ess_check);
-%  					
-%  					\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
-%  					\draw [arrow] (resample) |- (mutation);
-%  					
-%  					\draw [arrow] (ess_check) -- node[left] {No} (mutation);
-%  					\draw [arrow] (mutation) -- (acceptance);
-%  					\draw [arrow] (acceptance) -- (end_iter);
-%  					
-%  					\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
-%  					\node [pos=10, below=430pt, xshift=-100pt] {No};
-%  					\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);
-%  					
-%  					\draw [arrow] (exploit) -- (output);
-%  					\draw [arrow] (output) -- (stop);
-%  				\end{tikzpicture}
-%  			\end{tcolorbox}
-%  		\end{minipage}
-%  	\end{center}
-  	coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$.
-That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.
+	\caption{The flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
+	\label{ASMCflowchart}
+\end{figure}
 
@@
 \end{equation}
-The main results are presented in Fig.\eqref{fig:evolutionoftargetreproduction} and the losses of the run are shown in Fig. \ref{fig:losses_ASMC}. 
+The main results are summarized in Fig. \ref{fig:evolutionoftargetreproduction} (a) and (b) and the losses of the run are shown in Fig. \ref{fig:evolutionoftargetreproduction} (c). 
 %\begin{figure}
@@
 In this work, we have presented a novel machine learning approach to systematically identify and characterize flat directions in supergravity scalar potentials.
-Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (2,0) supergravity derived from
+Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (1,1) supergravity derived from
 $AdS_3 \times S^3 \times T^4$ compactifications of IIB supergravity.
@@
 While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
+
+\bibliography{references}
 
@@
 
-\bibliography{references}
+\newpage
+\section{Details on the algorithm}
+
+\begin{algorithm}
+	\caption{Local Dimension Estimation using PCA}
+	\label{alg:local-dim}
+	\begin{algorithmic}[1]
+
+		\State \textbf{Function} \textsc{LocalDim1Point}($\texttt{x}$, $\texttt{var\_thres}$)
+		\State \hspace{0.5cm} Apply PCA to data matrix $\texttt{x}$
+		\State \hspace{0.5cm} Compute explained variance ratios: $\texttt{lambda\_1, lambda\_2,} \ldots, \texttt{lambda\_d}$
+		\State \hspace{0.5cm} Compute cumulative variance: $\texttt{cumvar\_k} = \sum_{\texttt{i=1}}^\texttt{k} \texttt{lambda\_i}$ for $\texttt{k = 1, }\ldots\texttt{, d}$
+		\State \hspace{0.5cm} Find $\texttt{dim = min\{k : cumvar\_k} \geq \texttt{var\_thres\}}$
+		\State \hspace{0.5cm} \textbf{return} $\texttt{dim}$
+		\State
+
+%		\State \textbf{Function} \textsc{ComputeLocalDim}(\texttt{i, data, neighbors\_idx, var\_thres})
+%		\State \hspace{0.5cm} Extract local neighbors : \texttt{local\_neighbors} $\leftarrow$ \texttt{data[neighbors\_idx[i]]}
+%		\State \hspace{0.5cm} \texttt{dim} $\leftarrow$ \textsc{LocalDim1Point}(\texttt{local\_neighbors, var\_thres})
+%		\State \hspace{0.5cm} \textbf{return} \texttt{[dim, i]}
+%		\State
+
+%		\Require \texttt{data} (input data matrix of size \texttt{n $\times$ d}), \texttt{n\_neig} (number of neighbors), \texttt{var\_thres} (variance threshold)
+%		\Ensure Local dimensions for all points
+
+		\State \textbf{Function} \textsc{LocalDimNPoints}(\texttt{data, n\_neig, var\_thres})
+		\State \hspace{0.5cm} \texttt{n\_points} $\leftarrow$ number of rows in \texttt{data}
+		\State \hspace{0.5cm} Initialize \texttt{results} $\leftarrow \emptyset$
+%		\State \hspace{0.5cm} Fit KD-Tree on \texttt{data} with \texttt{n\_neig} neighbors \Comment{Find k-nearest neighbors using KD-Tree}
+		\State \hspace{0.5cm} Compute \texttt{neighbors\_idx} for all points in \texttt{data}
+		\For{\texttt{i = 1} to \texttt{n\_points}} \Comment{Compute local dimensions for all points}
+		\State \texttt{result\_i} $\leftarrow$ \textsc{ComputeLocalDim}(\texttt{i, data, neighbors\_idx, var\_thres})
+		\State Append \texttt{result\_i} to \texttt{results}
+		\EndFor
+
+		\Return \texttt{results}
+	\end{algorithmic}
+\end{algorithm}
+
+In this appendix, we detail the different algorithm that we used. We first here provide a pseudo-code for the AIS-SMC algorithm :
+
+%\begin{algorithm}
+%	\caption{Annealing Importance Sampling for Polynomial Discovery}
+%	\label{alg:annealing-is}
+%	\begin{algorithmic}[1]
+%		\Require $n\_iter$ (number of iterations), $n\_particles$ (number of particles), $target\_acc\_rate(\cdot,\cdot)$ (target acceptance rate), $adaptation\_strength$ (temperature adaptation parameter)
+%		
+%		\State Initialize particles $\{z_0^{(k)}\}_{k=1}^{n\_particles}$ with sparse polynomials
+%		\State Set $w_0^{(k)} = 1/n\_particles$ and $\tilde{w}_0^{(k)} = 1$ for all $k$ \Comment{normalized and unnormalized weights}
+%
+%		\State $z_{prev} \leftarrow z_0$, $best\_loss \leftarrow \infty$, $acceptance\_history \leftarrow \emptyset$, $q_{ratio}^{(k)}=1$ for all $k$ \Comment{q is the proposal ratio}, $\beta_0 \leftarrow 10^{-8}$
+%		
+%		\For{$i = 1$ to $n\_iter$} \Comment{Temperature adaptation}
+%
+%		\State $\beta_{prev} \leftarrow \beta_{current}$, $avg\_acc \leftarrow$ mean$(acceptance\_history)$ \Comment{only of the last 5 epochs}
+%		\If{$avg\_acc < target\_acc\_rate(i, n\_iter) - 0.05$}
+%		\State $\beta_{current} \leftarrow \beta_{current} \times (1 - adaptation\_strength)$
+%		\ElsIf{$avg\_acc > target\_acc\_rate(i, n\_iter) + 0.05$}
+%		\State $\beta_{current} \leftarrow \beta_{current} \times (1 + adaptation\_strength)$
+%		\EndIf
+%
+%		
+%		\For{$k = 1$ to $n\_particles$} \Comment{Reweighting step}
+%		\State Compute $\log \gamma_i(z_i^{(k)}) = -\beta_{current} \times loss(z_i^{(k)}) $
+%		\State Compute $\log \gamma_{i-1}(z_{i-1}^{(k)}) = -\beta_{prev} \times loss(z_{prev}^{(k)})$
+%		\State $\Delta \log w_i^{(k)} \leftarrow \log \gamma_i(z_i^{(k)}) - \log \gamma_{i-1}(z_{i-1}^{(k)}) + \log q_{ratio}^{(k)}$
+%		\EndFor
+%		
+%		\State Update unnormalized weights: $\tilde{w}_i^{(k)} \leftarrow \tilde{w}_{i-1}^{(k)} \times \exp(\Delta \log w_i^{(k)})$
+%		\State Normalize weights: $w_i^{(k)} \leftarrow \tilde{w}_i^{(k)} / \sum_{j=1}^{n\_particles} \tilde{w}_i^{(j)}$
+%		\State Compute ESS: $ESS = 1 / \sum_{k=1}^{n\_particles} (w_i^{(k)})^2$
+%		
+%		\If{$ESS < n\_particles / 2$} \Comment{Resampling}
+%		\State Resample particles: $\{z_i^{(k)}\}_{k=1}^{n\_particles} \sim Multinomial(n\_particles, \{w_i^{(k)}\}_{k=1}^{n\_particles})$
+%		\State Reset weights: $w_i^{(k)} = 1/n\_particles$, $\tilde{w}_i^{(k)} = 1$ for all $k$
+%		\State Update $z_{prev}$ accordingly
+%		\EndIf
+%		
+%		\State $z_{before\_mutation} \leftarrow z_i$ (save current particles)
+%
+%		\For{$k = 1$ to $n\_particles$} \Comment{Mutating with Metropolis-Hasting}
+%		\State Propose $z'^{(k)} \sim q(z'^{(k)} | z_i^{(k)})$ using specialized MH proposal
+%		\State Compute $\log p_{current}^{(k)} = -\beta_{current} \times loss(z_i^{(k)}) + sparsity\_prior(z_i^{(k)})$
+%		\State Compute $\log p_{proposed}^{(k)} = -\beta_{current} \times loss(z'^{(k)}) + sparsity\_prior(z'^{(k)})$
+%		\State $\log \alpha^{(k)} \leftarrow \log p_{proposed}^{(k)} - \log p_{current}^{(k)} + \log q_{ratio}^{(k)}$
+%		\State Generate $u^{(k)} \sim \mathcal{U}(0,1)$
+%		\If{$\log u^{(k)} < \log \alpha^{(k)}$}
+%		\State $z_i^{(k)} \leftarrow z'^{(k)}$ (accept proposal)
+%		\EndIf
+%		\EndFor
+%		
+%		\State $acceptance\_rate \leftarrow$ fraction of accepted proposals
+%		\State Add $acceptance\_rate$ to $acceptance\_history$
+%		\State $z_{prev} \leftarrow z_{before\_mutation}$ (update for next iteration)
+%		
+%		\EndFor
+%
+%		
+%		\Return final particles, final losses, final weights
+%	\end{algorithmic}
+%\end{algorithm}
+
+\begin{algorithm}
+	\caption{Annealing Importance Sampling for Polynomial Discovery}
+	\label{alg:annealing-is}
+	\begin{algorithmic}[1]
+		\Require \texttt{n\_iter} (number of iterations), \texttt{n\_particles} (number of particles), \texttt{target\_acc\_rate}$(\cdot,\cdot)$ (target acceptance rate), \texttt{adaptation\_strength} (temperature adaptation parameter)
+
+		\State Initialize particles $\{\texttt{z\_0}^{(k)}\}_{k=1}^{\texttt{n\_particles}}$ with sparse polynomials
+		\State Set $\texttt{w\_0}^{\texttt{(k)}} = 1/\texttt{n\_particles}$ and $\texttt{w\_unorm\_0}^{\texttt{(k)}} = 1$ for all $\texttt k$ \Comment{normalized and unnormalized weights}
+		\State $\texttt{z\_prev} \leftarrow \texttt{z\_0}$, $\texttt{best\_loss} \leftarrow \infty$, $\texttt{acceptance\_history} \leftarrow \emptyset$, $\texttt{q\_ratio}^{\texttt{(k)}}=1$ for all $k$, $\texttt{beta\_0} \leftarrow \texttt{init\_beta}$ \Comment{q is the proposal ratio}
+
+		\For{$\texttt{i = 1}$ to \texttt{n\_iter}} \Comment{Temperature adaptation}
+		\State $\texttt{beta\_{prev}} \leftarrow \texttt{beta\_current}$
+		\State $\texttt{avg\_acc} \leftarrow$ mean$(\texttt{acceptance\_history})$ \Comment{only of the last 5 epochs}
+		\If{$\texttt{avg\_acc < target\_acc\_rate(i, n\_iter) - 0.05}$}
+		\State $\texttt{beta\_current} \leftarrow \texttt{beta\_current} \times \texttt{(1 - adaptation\_strength)}$
+		\ElsIf{$\texttt{avg\_acc > target\_acc\_rate(i, n\_iter) + 0.05}$}
+		\State $\texttt{beta\_current} \leftarrow \texttt{beta\_current} \times \texttt{(1 + adaptation\_strength)}$
+		\EndIf
+
+		\For{$\texttt{k = 1}$ to \texttt{n\_particles}} \Comment{Reweighting step}
+		\State Compute $\texttt{log(gamma\_i(z\_i}^{\texttt{(k)}} \texttt{)) = - beta\_current} \times \texttt{loss}(\texttt{z\_i}^{\texttt{(k)}}) $
+		\State Compute $\texttt{log(gamma\_(i-1)}(\texttt{z\_(i-1)}^{\texttt{(k)}}\texttt{)) = - beta\_prev} \times \texttt{loss}(\texttt{z\_prev}^{\texttt{(k)}})$
+		\State $\Delta \log \texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{log(gamma\_i(\texttt{z\_i}}^{\texttt{(k)}}  \texttt{) - log(gamma\_(i-1)(z\_(i-1)}^{\texttt{(k)}} \texttt{) + log(q\_ratio}^{\texttt{(k)}}\texttt)$
+		\EndFor
+
+		\State Update unnormalized weights: $\texttt{w\_unorm\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_(i-1)}^{\texttt{(k)}} \times \texttt{exp(}\Delta \texttt{log w\_i}^{\texttt{(k)}}\texttt)$
+		\State Normalize weights: $\texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt/ \sum_{\texttt{j=1}}^{\texttt{n\_particles}} \texttt{w\_unorm\_i}^{\texttt{(j)}}$
+		\State Compute ESS: $\texttt{ESS = 1 /} \sum_{\texttt{k=1}}^{\texttt{n\_particles}} \texttt{(w\_i}^{\texttt{(k)}})^\texttt2$
+
+		\If{$\texttt{ESS < n\_particles / 2}$} \Comment{Resampling}
+		\State Resample particles: $\{\texttt{z\_i}^{\texttt{(k)}}\}_{\texttt{k=1}}^{\texttt{n\_particles}} \sim \texttt{Multinomial}(\texttt{n\_particles}, \{\texttt{w\_i}^{\texttt{(k)}}\}_{\texttt{k=1}}^{\texttt{n\_particles}})$
+		\State Reset weights: $\texttt{w\_i}^{\texttt{(k)}} = \texttt{1/n\_particles}$, $\texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt{= 1}$ for all $\texttt k$
+		\State Update $\texttt{z\_prev}$ accordingly
+		\EndIf
+
+		\State $\texttt{z\_before\_mutation} \leftarrow \texttt{z\_i}$ (save current particles)
+		\For{$\texttt{k = 1}$ to \texttt{n\_particles}} \Comment{Mutating with Metropolis-Hasting}
+		\State Propose $\texttt{z}'^{\texttt{(k)}} \sim \texttt{q}(\texttt{z}'^{\texttt{(k)}} | \texttt{z\_i}^{\texttt{(k)}})$ using specialized MH proposal
+		\State Compute $ \texttt{log(p\_current}^{\texttt{(k)}} \texttt{) = - beta\_current} \times \texttt{loss}(\texttt{z\_i}^{\texttt{(k)}}) + \texttt{sparsity\_prior}(\texttt{z\_i}^{\texttt{(k)}})$
+		\State Compute $\texttt{log(p\_proposed}^{\texttt{(k)}} \texttt{) = - beta\_current} \times \texttt{loss}(\texttt{z}'^{\texttt{(k)}}) + \texttt{sparsity\_prior}(\texttt{z}'^{\texttt{(k)}})$
+		\State $\texttt{log(alpha}^{\texttt{(k)}} \texttt) \leftarrow  \texttt{log(p\_proposed}^{\texttt{(k)}}  \texttt{) -  log(p\_current}^{\texttt{(k)}}  \texttt{) + log(q\_ratio}^{\texttt{(k)}}\texttt)$
+		\State Generate $\texttt{u}^{\texttt{(k)}} \sim \mathcal{U}\texttt{(0,1)}$
+		\If{$\texttt{u}^{\texttt{(k)}} \texttt{ < alpha}^{\texttt{(k)}}$}
+		\State $\texttt{z\_i}^{\texttt{(k)}} \leftarrow \texttt{z}'^{\texttt{(k)}}$ (accept proposal)
+		\EndIf
+		\EndFor
+
+		\State $\texttt{acceptance\_rate} \leftarrow$ fraction of accepted proposals
+		\State Add $\texttt{acceptance\_rate}$ to $\texttt{acceptance\_history}$
+		\State $\texttt{z\_prev} \leftarrow \texttt{z\_before\_mutation}$ (update for next iteration)
+
+		\EndFor
+
+		\Return \texttt{final particles, final losses, final weights}
+	\end{algorithmic}
+\end{algorithm}
+
+This pseudo code sketch how does our annealing loops work.
+Here is the pseudo-code for the initialization of each individual polynomial.
+We chose to generate more terms with a high number of monomials, because in principle there are more possibilities of polynomials with larger number of monomials.
+This does not prevent the code from finding polynomials with lower number of monomials as we can see on the results.
+The polynomial that the code find the most often is the polynomial $p_1$ which only has 4 terms instead of 5 or 6 for all others polynomials.
+The code can find such polynomials by putting gradually one or several of the coefficients to zero.
+Note also that we could include the possibility in the MH process too add/remove monomials.
+However, in the spirit of making "small" steps in the search space, we decided not to for now.
+\begin{algorithm}
+	\caption{Initialize Sparse Polynomials}
+	\label{alg:initialize-sparse}
+	\begin{algorithmic}[1]
+		\Require $\texttt{n\_particles}$ (number of particles), $\texttt{max\_degree}$ (maximum polynomial degree), $\texttt{num\_vars}$ (number of variables), $\texttt{max\_num\_monomials}$ (maximum number of monomials per polynomial), $\texttt{num\_terms}$ (total number of possible terms)
+
+		\State $\texttt{particles} \leftarrow \mathbf{0}_{\texttt{n\_particles} \times \texttt{num\_terms}}$
+		\State $\texttt{max\_monomials} \leftarrow \texttt{max\_num\_monomials}$
+
+		\State $\texttt{n\_mon\_to\_max\_order} \leftarrow \binom{\texttt{max\_degree + num\_vars}}{\texttt{max\_degree}}$ \Comment{Compute total number of possible monomials up to max degree}
+
+		\State $\texttt{n\_mon\_all\_coeff} \leftarrow \emptyset$
+		\State $\texttt{n\_tot\_pol} \leftarrow \texttt{0}$ 
+		\For{$\texttt{i = 1}$ to $\texttt{max\_num\_monomials}$} \Comment{Compute probability distribution over number of monomials}
+		\State $\texttt{n\_mon\_i\_coeff} \leftarrow \binom{\texttt{n\_mon\_to\_max\_order}}{i}$ \Comment{Number of polynomials with exactly $i$ monomials}
+		\State $\texttt{n\_tot\_pol} \leftarrow \texttt{n\_tot\_pol + n\_mon\_i\_coeff}$
+		\State Append $\texttt{n\_mon\_i\_coeff}$ to $\texttt{n\_mon\_all\_coeff}$
+		\EndFor
+
+		\State $\texttt{proba} \leftarrow \texttt{n\_mon\_all\_coeff / n\_tot\_pol}$ \Comment{Normalize to get probabilities}
+
+		\For{$\texttt{i = 1}$ to $\texttt{n\_particles}$} \Comment{Generate particles}
+
+		\State $\texttt{num\_monomials} \sim \texttt{Categorical(\{1, 2, \ldots, max\_monomials\}, proba)}$ \Comment{Sample number of monomials according to computed distribution}
+
+		\State $\texttt{nonzero\_indices}\leftarrow$ sample $\texttt{num\_monomials}$ indices from $\{\texttt{1, 2, }\ldots, \texttt{num\_terms}\}$ without replacement \Comment{Randomly select which monomials will be non-zero}
+
+		\For{\texttt{j} $ \in \texttt{nonzero\_indices}$} \Comment{Generate random coefficients}
+		\State $\texttt{particles[i, j] }\leftarrow \mathcal{U}(-2,2)$ 
+		\Comment{Uniform in $[-2, 2]$}
+		\EndFor
+		\EndFor
+
+		\Return $\texttt{particles}$
+	\end{algorithmic}
+\end{algorithm}
 

### 2025-06-30 Draft_MLFlatDirections.tex
Update the draft

@@
 
-\title Machine learning to study marginal deformation of 2d conformal field theories
+{\Large Machine learning the Conformal Manifold of Holographic CFT2’s}
 
@@
 Along these directions, the scalar field configurations vary continuously while the cosmological constant remains fixed.
-In general, supersymmetry is believed to be necessary for the existence of holographic conformal manifolds, as non-supersymmetric AdS solutions are typically considered unstable \cite{Ooguri:2016pdq,Palti:2019pca}.
+In general, supersymmetry is believed to be necessary for the existence of holographic conformal manifolds, as non-supersymmetric AdS solutions are typically expected to be unstable \cite{Ooguri:2016pdq,Palti:2019pca}.
 However, recent investigations \cite{Giambrone:2021wsm} have identified AdS$_4$ configurations that appear to evade this requirement, with no evidence of standard decay channels—neither perturbative nor non-perturbative—being present.
@@
 More generally, within the supergravity approximation, continuous deformations correspond to classically marginal operators.
-These operators become exactly marginal only if their marginality persists at finite values of both the rank N and the CFT coupling.
+These operators become exactly marginal only if their marginality persists at finite values of both the rank $N$ and the CFT coupling.
 Recent work \cite{Eloy:2024lwn} has demonstrated the existence of families of marginal deformations that are perturbatively stable, using the framework of Exceptional Field Theory (ExFT).
@@
 In this work, we propose a novel approach, where we study directly the scalar potential of supergravity.
-As already mentionned, the marginal deformations of CFT's in the large N limit, are in correspondance with the flat directions in the potential, i.e.
+As already mentionned, the classical marginal deformations of CFT's in the large $N$ limit, are in correspondance with the flat directions in the potential, i.e.
 when there is a continuous set a scalar fields such that $\nabla V = 0$.
@@
 The resulting expressions for critical points—where all first derivatives vanish—quickly become too complex for traditional symbolic manipulation, rendering analytical approaches computationally intractable.
-This complexity paradox is particularly frustrating given that physically meaningful solutions often admit relatively simple parametric descriptions once discovered.
 
@@
 Instead of solving the full symbolic system analytically from the outset, one can employ numerical methods to sample the solution space and subsequently apply symbolic regression techniques to extract analytical patterns from the data.
-This hybrid approach has the potential to bypass the computational bottlenecks inherent in purely symbolic methods, while still aiming to uncover exact analytical expressions.
-
-Similar strategies have previously been applied to identify new isolated vacua in $\mathrm{SO}(8)$ supergravity \cite{Comsa:2019rcz,Berman:2022jqn}.
+This hybrid approach has the potential to bypass the computational bottlenecks inherent in purely symbolic methods, while still having the potential to uncover exact analytical expressions.
+
+Machine learning strategies have previously been applied to identify new isolated vacua in $\mathrm{SO}(8)$ supergravity \cite{Comsa:2019rcz,Berman:2022jqn}.
 More broadly, there has been increasing interest in applying machine learning and numerical techniques across various domains of high-energy physics.
@@
 
-In this work, we demonstrate the viability of the aformentionned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of three-dimensional chiral $\mathcal{N} = (1,1)$  supergravity arising from $AdS_3 \times S^3$ compactification from 6d supergravity, or from the compactification of type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
+In this work, we demonstrate the viability of the aformentionned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of six-dimensional non-chiral $\mathcal{N} = (1,1)$ supergravity on $AdS_3 \times S^3$, or to type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
 Our methodology combines gradient descent sampling of the flat direction manifold with some symbolic regression technique.
@@
 We manage to identify 8 of those constraints on the data, not all independent, which once solved gives that two of the embedding coordinates can be expressed in terms of the others.
-This provides an explicit family of 3 dimensional parameters family
+This provides an explicit 3 dimensional parameters family
 
@@
 Section 3 details our numerical methodology, covering both the gradient descent sampling procedure and the annealed importance sampling approach to symbolic regression.
-Section 4 analyzes the discovered supergravity solutions, including their geometric interpretation and spectrum analysis.
-Finally, Section 5 concludes with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
+Finally, Section 4 concludes with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
 
@@
 %
-where $f^{\bar M\bar N,\bar P\bar Q}{}_{\bar K\bar L} = 4\,\delta_{[\bar K}{}^{[\bar M}\eta^{\bar N][\bar P}\delta_{\bar L]}{}^{\bar Q]}$ are the structure constants of the SO(8,4) Lie algebra, and $\varepsilon^{\mu\nu\rho}$ is the three-dimensional Levi-Civita tensor.
+where $f^{\bar M\bar N,\bar P\bar Q}{}_{\bar K\bar L} = 4\,\delta_{[\bar K}{}^{[\bar M}\eta^{\bar N][\bar P}\delta_{\bar L]}{}^{\bar Q]}$ are the structure constants of the SO(8,4) Lie algebra, and $\varepsilon^{\mu\nu\rho}$ is the three-dimensional Levi-Civita symbol.
 
@@
 
-As an initial simplification, we restrict our analysis to the scalar fields $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
+A first numerical exploration suggests that attention can be focused on the five scalars $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
 This subset, selected at random from the original set of thirteen scalar fields, serves to render the problem more tractable at the outset.
 It is important to emphasize, however, that this subset does not constitute a consistent truncation of the full theory.
-Consequently, the effective theory defined by these five scalars may be formally ill-defined, as higher-order interactions could, in principle, source the remaining fields.
+Consequently, the truncated theory involving only five scalar fields may not constitute a formally consistent truncation of the full 13-scalar theory, as higher-order interactions could, in principle, source the remaining scalar modes.
+As a result, the interpretation of the five-scalar theory as a consistent subsector of the original theory may no longer hold.
+Nonetheless, the five-scalar model remains a self-consistent theory in its own right and can be used independently.
+This distinction does not affect our numerical approach.
 
@@
 This choice is important to ensure that points are not restricted to the inner range $[-1,1]$.
-This will be important later, when performing the symbolic regression.
+This will be important later, when performing the symbolic regression \footnote{The rationale is that symbolic regression (SR) evaluates the data points ${\vec{x}^i}$ using a candidate polynomial function $p$.
+The loss function—used later to assess the quality of a given polynomial—is defined as $\sum_i p(\vec{x}^i)$.
+When all data points lie within the interval $[-1, 1]$, the SR algorithm tends to favor high-degree polynomials, as these often yield smaller values over this range, thereby artificially lowering the loss.
+Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of overly complex polynomials that exploit this effect.}.
 For this example, we choose to generate $10^5$ points.
@@
 This effect is likely due to points initially located in regions with weak attractive basins being pushed toward areas where the potential gradient is steeper, thus accelerating their convergence.
-Although this strategy introduces the risk of desampling certain regions in favor of others, they correspond to low convergence regions.
-As we are anyway not interested in those places, but rather real flat directions, this is not a problem for us.
+This strategy introduces the risk of desampling certain regions in favor of others, introducing the risk to hide some flat directions in the potential.
+However, we believe that with enough points, it is very unlikely for a flat direction to be completely hidden from us and desampled.
 
@@
 		\subsubsection{Determining the dimension}
-		Once the gradient descent has been completed and the flat direction sampled, the next step is to identify the structure of the underlying manifold.
+		Once the gradient descent has been completed and the flat directions sampled, the next step is to identify the structure of the underlying manifold.
 Our goal is to eventually obtain an analytical expression, not just a numerical description.
@@
 This artificial enlargement of the neighbourhood can cause the estimated local dimensionality to rise.
-		We thus conclude that the manifold under investigation has an intrinsic dimension of 3.
+		We thus assume that the manifold under investigation has an intrinsic dimension of 3.
 
@@
 This, way, we remove the possible intersection points with dimension 4 or 5.
-For the purpose of the clustering, we use the HDBSCAN algorithm\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation.
+For the purpose of the clustering, we use the HDBSCAN algorithm\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation \cite{10.1007/978-3-642-37456-2_14}.
 Briefly, it is a density-based clustering method that extends DBSCAN by converting it into a hierarchical clustering algorithm and then extracting a flat clustering based on the stability of clusters.}.
@@
 
-		After performing both PCA and clustering, we thus confirm that the data obtained after gradient descent samples a three-dimensional manifold.
+		After performing both PCA and clustering, we thus find that the data obtained after gradient descent samples a three-dimensional manifold.
 
@@
 		\subsubsection{Annealed Sequential Monte Carlo principle}
+
+		\begin{figure}[h!]
+			\centering
+			\begin{minipage}{15cm}
+				\begin{tcolorbox}[
+					colback=white,
+					colframe=myblue,
+					title=\textbf{ASMC Algorithm},
+					fonttitle=\sffamily\large,
+					halign title=flush center,
+					boxrule=2pt,
+					left=6pt,
+					right=6pt,
+					top=8pt,
+					bottom=8pt
+					]
+					\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]
+
+						% Nœuds
+						\node (start) [startstop] {Start};
+
+						\node (init_particles) [process, below of=start] {Initialize particles et weights};
+
+						\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};
+
+						\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};
+
+						\node (ess_check) [decision, below of=weight_update] {Effective Sample Size $<$ Threshold ?};
+
+						\node (resample) [process, right=3.8cm of ess_check] {Resampling particles};
+
+						\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with MCMC kernel};
+
+						\node (acceptance) [process, below of=mutation] {Accept/Reject particles};
+
+						\node (end_iter) [decision, below of=acceptance] {Last step ?};
+
+						\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};
+
+						\node (output) [process, below of=exploit] {Return particles};
+
+						\node (stop) [startstop, below of=output] {End};
+
+						% Flèches avec étiquettes améliorées
+						\draw [arrow] (start) -- (init_particles);
+						\draw [arrow] (init_particles) -- (compute_beta);
+						\draw [arrow] (compute_beta) -- (weight_update);
+						\draw [arrow] (weight_update) -- (ess_check);
+
+						\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
+						\draw [arrow] (resample) |- (mutation);
+
+						\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
+						\draw [arrow] (mutation) -- (acceptance);
+						\draw [arrow] (acceptance) -- (end_iter);
+
+						% Boucle de retour améliorée
+						\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {No} ++(-4.5,0) |- (compute_beta);
+
+						\draw [arrow] (end_iter) -- node[right, arrow_label] {No} (exploit);
+						\draw [arrow] (exploit) -- (output);
+						\draw [arrow] (output) -- (stop);
+
+					\end{tikzpicture}
+				\end{tcolorbox}
+			\end{minipage}
+			\caption{The flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
+			\label{ASMCflowchart}
+		\end{figure}
+
 		To address these challenges, we employ an Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC) methods.
@@
 So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$.
-			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$. 
+			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x_1 x_2 + 3 x_2^2 \rightarrow  2 x_1 + 3 x_2^2$. 
 		\end{itemize}
@@
 		\begin{equation}
-			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k c_k}
+			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k |c_k|}
 		\end{equation}
@@
       		- x_{2}^{2}x_{10}, \\
-      p_{8} &= -2 + 4 x_{8} - 2 x_8^2 + 2 x_{4}^2 x_8 - x_8^2 x_{10}^2
+      p_{8} &= -2 + 4 x_{8} - 2 x_8^2 + 2 x_{4}^2 x_8 - x_8^2 x_{10}^2,
     \end{align}
@@
 That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.
-\begin{figure}[h!]
-	\centering
-	\begin{minipage}{14cm}
-		\begin{tcolorbox}[
-			colback=white,
-			colframe=myblue,
-			title=\textbf{ASMC Algorithm},
-			fonttitle=\sffamily\large,
-			halign title=flush center,
-			boxrule=2pt,
-			left=6pt,
-			right=6pt,
-			top=8pt,
-			bottom=8pt
-			]
-			\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]
-
-				% Nœuds
-				\node (start) [startstop] {Start};
-
-				\node (init_particles) [process, below of=start] {Initialize particles et weights};
-
-				\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};
-
-				\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};
-
-				\node (ess_check) [decision, below of=weight_update] {ESS $<$ Threshold ?};
-
-				\node (resample) [process, right=3.8cm of ess_check] {Resampling particles};
-
-				\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with Metropolis Hasting proposal};
-
-				\node (acceptance) [process, below of=mutation] {Accept/Reject particles};
-
-				\node (end_iter) [decision, below of=acceptance] {Last step ?};
-
-				\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};
-
-				\node (output) [process, below of=exploit] {Return current particles};
-
-				\node (stop) [startstop, below of=output] {End};
-
-				% Flèches avec étiquettes améliorées
-				\draw [arrow] (start) -- (init_particles);
-				\draw [arrow] (init_particles) -- (compute_beta);
-				\draw [arrow] (compute_beta) -- (weight_update);
-				\draw [arrow] (weight_update) -- (ess_check);
-
-				\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
-				\draw [arrow] (resample) |- (mutation);
-
-				\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
-				\draw [arrow] (mutation) -- (acceptance);
-				\draw [arrow] (acceptance) -- (end_iter);
-
-				% Boucle de retour améliorée
-				\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {Non} ++(-4.5,0) |- (compute_beta);
-
-				\draw [arrow] (end_iter) -- node[right, arrow_label] {No} (exploit);
-				\draw [arrow] (exploit) -- (output);
-				\draw [arrow] (output) -- (stop);
-
-			\end{tikzpicture}
-		\end{tcolorbox}
-	\end{minipage}
-	\caption{The flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
-	\label{ASMCflowchart}
-\end{figure}
 
@@
 We now provide further details about the implementation of our code.
-To recover the polynomials presented in Eq.~\eqref{eq:pols}, we performed 1000 independent runs, each involving 1000 particles.
+To recover the polynomials presented in Eq.~\eqref{eq:pols}, we performed 1000 independent runs on a cluster, each involving 1000 particles.
 As can be seen in \eqref{eq:gamman}, we see that what matters the most in the the inverse temperature, but rather the inverse temperature multiplied by the loss function.
@@
 	\begin{aligned}
-		&\beta = 10^{-6}\,, \\
+		&\texttt{n\_epochs = 1000}\,,\\
+		&\texttt{beta = 1e{-6}}\,, \\
 		&\texttt{p\_{modify} = 0.5},\\
@@
 \end{equation}
+
 This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
@@
 \end{equation}
-The main results are summarized in Fig. \ref{fig:evolutionoftargetreproduction} (a) and (b) and the losses of the run are shown in Fig. \ref{fig:evolutionoftargetreproduction} (c). 
+The time it takes to do a single run in approximately 600s on a regular computer.
+The main results are summarized in Fig.
+\ref{fig:evolutionoftargetreproduction} (a) and (b) and the losses of the run are shown in Fig.
+\ref{fig:evolutionoftargetreproduction} (c).
 %\begin{figure}
@@
   	\label{table:results}
-	\begin{tabular}{l|ccccccccc}
+	\begin{tabular}{c|ccccccccc}
 		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $p_{8}$ &  $\varnothing$  \\\hline\hline
-		Frequency & 92.6\% & 75.0\% & 1.7\% & 51.9\% & 0.7\% & 0.1\% & 0.2\% & 0.7\% & 0.3\%
+		Frequency & 92.6\% & 75.0\% & 1.7\% & 51.9\% & 0.7\% & 0.1\% & 0.2\% & 0.7\% & 0.3\% \\\hline\hline
+		Maximum \# of Representant & 1000 & 1000 & 869 & 991 & 710 & 18 & 879 & 207 & $\varnothing$
+
 	\end{tabular}
@@
 With this approach, the average number of particles reproducing one of the target polynomials at the end of a run is 882, with a standard deviation of 200.
-Moreover, the algorithm typically identifies an average of 2.24 distinct polynomials per run, demonstrating its capacity to uncover multiple solutions simultaneously.
-Finally the algorithm failed at finding a solution in only 3 runs, demonstrating the robustness of the technique.
+Moreover, the algorithm typically identifies an average of 2.24 distinct polynomials per run, with a maximum number of 4, demonstrating its capacity to uncover multiple solutions simultaneously.
+Finally the algorithm failed at finding a solution in only 3 runs.
+This is sumed up in Fig.
+\ref{fig:piechart}.
+We see that for $77.4\%$ on the time that the algorithm finds more than a single solution, demonstrating the robustness of the technique.
 
@@
 
+In comparaison with state of the art technique, we have used the AIFeynman algorithm on our data set, with again $x_8 = \exp(\tilde{x}_8)$, such that we again look for polynomial expressions.
+We have run it with the following configuration
+\begin{equation}
+	\begin{aligned}
+		&\texttt{BF\_try\_time} = 300, \\
+		&\texttt{polyfit\_deg} = 6, \\
+		&\texttt{NN\_epochs} = 5000.\\
+	\end{aligned}
+\end{equation}
+The first parameter fixes the time limit in seconds for each brute force call, \texttt{polyfit\_deg} gives the maximum degree of the polynomial tried by the polynomial fit routine and \texttt{NN\_epochs} is the number of training epoch for the internal neural network.
+The function used for the brut force tests are
+\begin{equation}
+\texttt{+*-/><} \sim \texttt{\textbackslash R1}
+\end{equation}
+The binary operations are addition, multiplication, substraction and division.
+The unary ones are inverse, increment, decrement, negation and square root.
+Finally there is a nonary one, the unity.
+For more details we refer to \cite{Udrescu:2019mnk}.
+
+In this algorithm, one tries to fit one of the variables in term of the others. Here, we used it to fit $x_{10}$ in terms of the others. The AIFeynman algorithm finds a solution in TIME : 
+\begin{equation}
+	\texttt{x\_10 = 1.414213551821*(x\_4-((x\_1/x\_2)-((x\_1/x\_2)/x\_8))}
+\end{equation}
+which after identifying the numerical factor with $\sqrt 2$ and inverting the relation gives 
+\begin{equation}
+	- \sqrt 2 x_1 + \sqrt 2 x_1 x_8 + x_2 x_8  x_{10} -\sqrt 2 x_2 x_4 x_8 = 0
+\end{equation}
+which corresponds to $p_1$ of Eq.
+\eqref{eq:pols}.
+While the AIFeynman code is able to recover one of the constraints, it exhibits several drawbacks compared to our method.
+First, it is significantly slower: it required TIME (to be specified) compared to approximately 600 seconds for a single run of our ASMC algorithm.
+Moreover, the AIFeynman framework is based on expressing one variable as a function of the others, which assumes the invertibility of the underlying relation.
+In general, this is not guaranteed for the class of polynomials in Eq.
+\eqref{eq:pols}, and obtaining a closed-form inverse can be nontrivial or even impossible for higher-degree expressions.
+In our case, each polynomial involves at most quadratic terms in any single variable, ensuring invertibility, but this property would not hold for more complex models.
+In addition, AIFeynman is limited to recovering one constraint per run, whereas our ASMC method can discover multiple constraints simultaneously.
+This is reflected in our results, where each run identified an average of 2.15 polynomials, with up to 4 found in the best case.
+Finally, the brute-force regression strategy used by AIFeynman makes it less effective for identifying higher-degree polynomials, whose complexity increases the search difficulty.
+In contrast, our method treats all polynomials as equally probable, regardless of their degree, enabling it to uncover more intricate structures more efficiently \footnote{Note that we do not claim that we have used the AIFeynman in the most optimal way.}.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=0.5]{Figures/piechart_results_n_pol_each_run.png}
+	\caption{Pie chart showing the repartition of the number of distinct polynomials found in the runs. Note that there is also the failure case, which corresponds 3 different runs.}
+	\label{fig:piechart}
+\end{figure}
+
 \section{Conclusion}
@@
 
-Beyond technical improvements, this work suggests a broader paradigm for studying conformal manifolds in string theory and supergravity.
-The ability to automatically extract analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
+Beyond technical improvements, this work suggests a broader paradigm for exctrating conformal manifolds in string theory and supergravity.
+This analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
 
@@
 While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
-
-\bibliography{references}
 
@@
 However, in the spirit of making "small" steps in the search space, we decided not to for now.
+
 \begin{algorithm}
@@
 
+\bibliography{references}
+
 \end{document}

### 2025-07-11 Draft_MLFlatDirections.tex
First update of the results section.

@@
 
-		At each step, we have a set of particles and weights $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
+		At each epoch, we have a set of particles and weights $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
 To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and calculate the new unnormalized importance weight $w_n^k$.
@@
 		\end{itemize}
-		This implementation enables a direct computation of both the forward and backward propagation kernels. In particular, for the case of coefficient perturbations, the transition is symmetric. That is,
+		The polynomials get mutated at each epoch.
+The mutation is chosen randomly, assigning probabilities \texttt{p\_{modify}} , \texttt{p\_{multiply}} and \texttt{p\_{divide}} to each possibility.
+This implementation enables a direct computation of both the forward and backward propagation kernels.
+In particular, for the case of coefficient perturbations, the transition is symmetric.
+That is,
 		\begin{equation}
@@
 		The acceptance ratio for the MCMC algorithm is given by : 
-		\begin{equation}
+		\begin{equation}\label{eq:acceptanceratio}
 			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)
@@
 		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
+
+		We have adapted the classic approach outilned above.
+As can be seen in \eqref{eq:gamman}, what matters the most to determine $\gamma_{n}$ is not the inverse temperature, but rather the product of the inverse temperature and the loss function.
+Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach.
+The acceptance ratio is controlled by the following schedule as function of the \texttt{epoch}:
+		\begin{equation} \label{eq:acceptanceratioschedule}
+			\texttt{acceptance\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
+		\end{equation}
+		where \texttt{n\_epochs} is the total number of epochs.
+This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
+\ce{So we don't use eq.~\eqref{eq:acceptanceratio} at all?
+This is not clear to me.}
 
@@
 For the Loss function, we decided to take :
-		\begin{equation}
+		\begin{equation} \label{eq:lossreg}
 			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k |c_k|}
@@
 
-		Once the Annealing loop is over, we end up with a total of $n_{sample}$ particles, which in principle should be close to annihilate our data, but whose coefficient may need some more fine tuning.
+		Once the Annealing loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some more fine tuning.
 To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a pertubation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller.
 This allow to fine-tune the coefficients.
+\ce{Mention threshold?
+And number of iterations?}
 
@@
 
+\section{Results}
+\paragraph{Initialisation}
+We initialized the algorithm with 
+\begin{equation}	\label{eq:sample10000adaptativetemp}
+	\begin{aligned}
+		&\texttt{n\_epochs} = 1000,\\
+		&\texttt{beta}  = 10^{-6}, \\
+		&\texttt{p\_{modify}} = 0.5,\\
+		&\texttt{p\_{multiply}} = 0.25,\\
+		&\texttt{p\_{divide}} = 0.25. 
+	\end{aligned}
+\end{equation}
+This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
+For the representation of polynomials, we adopt a vectorial approach: each polynomial is represented as an array of its coefficients $\{c_k\}$, where $k \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of available monomials, determined by the chosen maximum degree \texttt{max\_degree}.
+We also impose a constraint on the maximum number of terms within a single polynomial to promote sparsity.
+An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.
+For the simulations we have done, we chose :
+\begin{equation} \label{eq:parampol}
+	\begin{aligned}
+		&\texttt{max\_degree} = 4,\\
+		&\texttt{max\_num\_monomials} = 6.
+	\end{aligned}
+\end{equation}
+
+\paragraph{Typical run}
+After a run, the 1000 particles are typically distributed into less than 10 different type of polynomials.
+\ce{Check the exact number.} Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
+We select the representant of each type that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{lossreg}).
+Here is an example of ouput for a given run: \ce{Here $\texttt{threshold} = 0.1$ and $\texttt{steps} = 1000$ for the local search.}
+\begin{subequations}
+    \begin{align}
+		1.999\,x_{2} - 1.999\,x_{2}x_{8} + 1.414\,x_{1}x_{10} + 1.999\,x_{1}x_{4} - x_{10}^{2}x_{2}x_{8},\quad &L^{(\lambda = 0)} \simeq 2 \times 10^{-4},  \label{eq:expol1}\\
+		2\,x_{2} - 1.999\,x_{2}x_{8} + 1.415\,x_{1}x_{8}x_{10} + 2.001\,x_{1}x_{4}x_{8} - 2.002\,x_{2}x_{4}^{2}x_{8},\quad &L^{(\lambda = 0)} \simeq 3 \times 10^{-3}, \label{eq:expol2}\\
+		x_{1}x_{8}x_{10} + 1.416\,x_{1}x_{4}x_{8} - 1.516\,x_{2}x_{4}^{2}x_{8},\quad &L^{(\lambda = 0)} \simeq 3 \times 10^{2}, \label{eq:expol3}\\
+		2\,x_{2} - 1.972\,x_{2}x_{8} + 0.816\,x_{1}x_{10} + 1.369\,x_{1}x_{4} - 0.442\,x_{10}^{2}x_{2},\quad &L^{(\lambda = 0)} \simeq 3 \times 10^{2}, \label{eq:expol4}
+	\end{align}
+\end{subequations}
+where we normalised the coefficients be setting one of them to $1$ or $2$.
+Then, we filter out the polynomials with loss higher than $1$, as the polynomials~\eqref{eq:expol3} and~\eqref{eq:expol4}, which do not annihilate the data.
+As discussed in sec.
+??
+\ce{to do}, the coefficients must be combinations of rational numbers or square roots thereof.
+We then deduce from eq.~\eqref{eq:expol1} and~\eqref{eq:expol2} the candidate annihilator polynomials for the above example:
+\begin{equation}
+	\begin{gathered}
+		2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
+      2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
+      		- 2\,x_{2} x_{4}^{2}x_8.
+	\end{gathered}
+\end{equation}
+
+\paragraph{Statistics}
+We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
+It takes approximately 600\,s to do a single run on a regular computer.
+\ce{That's without local search, right?} The code finds the 8 different following polynomials:
+\begin{subequations} \label{eq:pols}
+ \begin{align}
+   p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\
+   p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
+   p_{3} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
+   		- 2\,x_{2} x_{4}^{2}x_8,\\
+   p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
+   		- x_{2}x_{4}x_8x_{10},\\
+   p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
+   		+ x_{1}x_8x_{10}^{2},\\
+   p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
+   		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},\\
+   p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
+   		- x_{2}^{2}x_{10}, \\
+   p_{8} &= -2 + 4 x_{8} - 2 x_8^2 + 2 x_{4}^2 x_8 - x_8^2 x_{10}^2,
+ \end{align}
+\end{subequations}
+where $x_{8} = e^{\tilde{x}_{8}}$.
+They are found with different frequencies with some polynomials occurring more often than others, as reported in tab.~\ref{table:results}.
+The average number of particles reproducing one of the annihilator polynomials at the end of a run is 882, with a standard deviation of 200.
+Moreover, the algorithm typically identifies an average of $2.24$ distinct polynomials per run, with a maximum number of $4$, demonstrating its capacity to uncover multiple solutions simultaneously.
+Finally, the algorithm failed at finding a solution in only 3 runs.
+This is summed up in fig.~\ref{fig:piechart}.
+We see that for $77.4\%$ on the time that the algorithm finds more than a single solution, demonstrating the robustness of the method.
+
+\begin{figure}
+	\centering
+	\input{Figures/Piechart_n_pols.pgf}
+	\caption{Pie chart of the repartition of the number of distinct polynomials found in a run.}
+	\label{fig:piechart}
+\end{figure}
+
+\begin{table}
+	\centering
+	\renewcommand{\arraystretch}{1.3}
+	\begin{tabular}{c|ccccccccc}
+		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $p_{8}$ &  $\varnothing$  \\\hline\hline
+		Frequency & 92.6\% & 75.0\% & 1.7\% & 51.9\% & 0.7\% & 0.1\% & 0.2\% & 0.7\% & 0.3\% \\
+		Maximum \# of representatives & 1000 & 1000 & 869 & 991 & 710 & 18 & 879 & 207 & --
+	\end{tabular}
+	\caption{Statistics of the ability of the ASMC algorithm to produce the polynomials~\eqref{eq:pols} on 1000 runs with parameters~\eqref{eq:sample10000adaptativetemp} and~\eqref{eq:parampol}.
+The frequencies represent the percentage of runs featuring a given polynomial in its outputs, and the maximum number of representatives gives the maximum number of particles representing the polynomial in a given run.
+The column $\varnothing$ counts the runs that failed to produce an annihilator polynomial.}
+	\label{table:results}
+\end{table}
+
+The dynamics of appearance of each annihilator polynomial is plotted in fig.~\ref{fig:evolutionoftargetreproduction}(a), together with the evolution of the inverse temperature $\beta$, averaged on the 1000 runs.
+Note that the dynamics depend strongly on the polynomial, some of the appearing after only few dozens of epochs, and others just before the end of the runs.
+The evolution of the inverse temperature, imposed by eq.~\eqref{eq:acceptanceratioschedule}, is polynomial.
+\ce{Do a fit.}.
+The losses of the runs are shown in fig.~\ref{fig:evolutionoftargetreproduction}(c).
+\ce{Describe more the loss?
+Is it summed on all particles?}.
+
+\ce{Keep fig.~\ref{fig:evolutionoftargetreproduction}(b)?}
+
+\begin{figure}[h!]
+	\centering
+	\begin{adjustbox}{width=20cm,center}
+		\begin{minipage}[t]{0.31\paperwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figures/Count_beta_adaptative_temp_indiv}
+			\caption*{(a)}
+		\end{minipage}%
+		\hfill
+		\begin{minipage}[t]{0.31\paperwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figures/Count_good_pol_all}
+			\caption*{(b)}
+		\end{minipage}%
+		\hfill
+		\begin{minipage}[t]{0.31\paperwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figures/Loss_all_ASMC.png}
+			\caption*{(c)}
+		\end{minipage}
+	\end{adjustbox}
+	\caption{(a) Dynamics of the mean number of particles reproducing each polynomial in eq.~\eqref{eq:pols} (left scale) and evolution of the inverse temperature $\beta$ and its $1\sigma$ deviation (right scale).
+(b) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp}.
+(c) Evolution of the losses during the runs (in blue) and their average (in yellow).}
+	\label{fig:evolutionoftargetreproduction}
+\end{figure}
+
+\ce{Tests sur le gradient analytique pour voir si c'est un polynome annulateur.}
+
+\paragraph{Comparison with AIFeynman}
+In comparaison with state of the art technique, we have used the AIFeynman algorithm on our data set, with again $x_8 = \exp(\tilde{x}_8)$, such that we again look for polynomial expressions.
+We have run it with the following configuration
+\begin{equation}
+	\begin{aligned}
+		&\texttt{BF\_try\_time} = 300, \\
+		&\texttt{polyfit\_deg} = 6, \\
+		&\texttt{NN\_epochs} = 5000.\\
+	\end{aligned}
+\end{equation}
+The first parameter fixes the time limit in seconds for each brute force call, \texttt{polyfit\_deg} gives the maximum degree of the polynomial tried by the polynomial fit routine and \texttt{NN\_epochs} is the number of training epoch for the internal neural network.
+The function used for the brut force tests are
+\begin{equation}
+\texttt{+*-/><} \sim \texttt{\textbackslash R1}
+\end{equation}
+The binary operations are addition, multiplication, substraction and division.
+The unary ones are inverse, increment, decrement, negation and square root.
+Finally there is a nonary one, the unity.
+For more details we refer to \cite{Udrescu:2019mnk}.
+
+In this algorithm, one tries to fit one of the variables in term of the others. Here, we used it to fit $x_{10}$ in terms of the others. The AIFeynman algorithm finds a solution in TIME : 
+\begin{equation}
+	\texttt{x\_10 = 1.414213551821*(x\_4-((x\_1/x\_2)-((x\_1/x\_2)/x\_8))}
+\end{equation}
+which after identifying the numerical factor with $\sqrt 2$ and inverting the relation gives 
+\begin{equation}
+	- \sqrt 2 x_1 + \sqrt 2 x_1 x_8 + x_2 x_8  x_{10} -\sqrt 2 x_2 x_4 x_8 = 0
+\end{equation}
+which corresponds to $p_1$ of Eq.
+\eqref{eq:pols}.
+While the AIFeynman code is able to recover one of the constraints, it exhibits several drawbacks compared to our method.
+First, it is significantly slower: it required TIME (to be specified) compared to approximately 600 seconds for a single run of our ASMC algorithm.
+Moreover, the AIFeynman framework is based on expressing one variable as a function of the others, which assumes the invertibility of the underlying relation.
+In general, this is not guaranteed for the class of polynomials in Eq.
+\eqref{eq:pols}, and obtaining a closed-form inverse can be nontrivial or even impossible for higher-degree expressions.
+In our case, each polynomial involves at most quadratic terms in any single variable, ensuring invertibility, but this property would not hold for more complex models.
+In addition, AIFeynman is limited to recovering one constraint per run, whereas our ASMC method can discover multiple constraints simultaneously.
+This is reflected in our results, where each run identified an average of 2.15 polynomials, with up to 4 found in the best case.
+Finally, the brute-force regression strategy used by AIFeynman makes it less effective for identifying higher-degree polynomials, whose complexity increases the search difficulty.
+In contrast, our method treats all polynomials as equally probable, regardless of their degree, enabling it to uncover more intricate structures more efficiently \footnote{Note that we do not claim that we have used the AIFeynman in the most optimal way.}.
+
+\paragraph{Supergravity}
+%\begin{itemize}[label=\textbullet]
+%	\item For each couple of candidate polynomials, we get the same expression for the solution, and it indeed defines a unique vacuum of the 3d SUGRA.
+%	\item Discussion of the vacuum: gauge group, Zham. metric, change of variables, 3d spectrum (and stability), spin 2 spectrum on $S^{3}$, one parameter seems to be a gauge parameter, uplift?
+%\end{itemize}
+
+%For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
+%\begin{equation}
+%	\begin{cases}
+	%		p_{i} = 0, \\
+	%		p_{j} = 0,
+	%	\end{cases}
+%\end{equation}
+%gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
+
+In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in Eq.~\ref{eq:pols}.
+We can now solve the system
+\begin{equation}\label{eq:solvepol}
+	p_i = 0, \quad \forall i \in {1,\dots,7}
+\end{equation}
+which leads to the following expressions:
+\begin{equation}
+	\begin{cases}
+		\displaystyle x_{1} = \frac{x_{2}}{\sqrt{2}}\,\frac{e^{x_{8}/2}}{e^{x_{8}}-1}\,\Big(-x_{5}\,e^{x_{8}/2} + \sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}\Big),\\[8pt]
+		\displaystyle x_{4} = \frac{e^{-x_{8}/2}}{\sqrt{2}}\,\sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}.
+	\end{cases}
+\end{equation}
+
+Alternatively, the system can be recast as:
+\begin{equation}\label{eq:rulex8x10}
+	\begin{cases}
+		\displaystyle \tilde{x}_{8} = \frac{x{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
+		\displaystyle x_{10} = \sqrt{2},x_{4},\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
+	\end{cases}
+\end{equation}
+
+As anticipated, this defines a three-parameter solution corresponding to a three-dimensional slice of the half-maximal supergravity scalar potential.
+
+Let us make a few remarks at this stage.
+First, it is possible to find solutions to Eq.~\ref{eq:solvepol} which, however, are not solutions of $\nabla V = 0$.
+For instance $x_1 = x_2 = 0$; such cases are excluded, as they do not satisfy the stationarity condition and therefore do not correspond to valid physical solutions.
+
+Secondly, one might argue that only two of the seven polynomials are sufficient to fully characterize the solution.
+That is, choosing any pair $(i,j) \in {1, \dots, 7}$ may suffice to extract a complete description.
+In practice, this is not entirely accurate.
+While such a pair can yield partial constraints—for example, recovering Eq.\ref{eq:rulex8x10}—it may also produce alternative (and potentially less general) parameterizations.
+Upon inspection, all such partial rules are found to be consistent with, and included in, the most general expressions given in Eq.\ref{eq:rulex8x10}.
+
+The solution preserves a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.
+
+%\paragraph{Moduli space}
+The $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
+\begin{equation}
+	x_{1} = r\cos(\theta)\cos(\Phi), \quad x_{2} = r\cos(\theta)\sin(\Phi) \quad {\rm and} \quad x_{4} = r\sin(\theta),
+\end{equation}
+for which the Zamolodchikov metric reads
+\begin{equation}
+	\d^{2}s_{\rm Zam.} = -\,\d r^{2} - r^{2}\,\bigg(\d \theta^{2} - r\cos(\theta)\,\d \theta\d\Phi + \sin(\theta)\,\d r\d\Phi + \frac{1}{2}\,\big(3+r^{2}-\cos(2\theta)\big)\,\d\Phi^{2} \bigg).
+\end{equation}
+\ce{Tests other change of variables? Test choices of variables other than $(x_{1},x_{2},x_{4})$?}
+
+\paragraph{Bosonic spectrum}
+Vector fields:
+\begin{equation}
+	\begin{aligned}	
+		m_{\sst{(1)}}\ell_{\rm AdS}:\quad &
+		0\ [2],	\quad
+		-2\ [5],	\quad
+		2\ [1],	\\[5pt]
+		&	-1\pm\sqrt{\left(1+r^2\right)^2-2\,r^2\,\cos(2\theta)}\ [2+2],	\\[5pt]
+		&	1\pm\sqrt{1+4\,r^2+r^{4}}\ [2+2].
+	\end{aligned}
+\end{equation}
+The integers between square brackets indicate the multiplicity of each eigenvalue.
+The spectrum includes two massless vectors corresponding to the unbroken ${\rm U}(1)\times {\rm U}(1)$ gauge symmetry, although in three dimensions they are non-propagating.
+
+Scalars:
+\begin{equation}
+	\begin{aligned}	
+		\left(m_{\sst{(0)}}\ell_{\rm AdS}\right)^2:\quad&
+		0\ [5],	\quad
+		8\ [1],	\quad
+		r^{2}\,\left(4+r^2\right)\ [8],	\\[5pt]
+		&	2r\,\Big(3\,r+r^{3}\pm(2+r^{2})\,\sqrt{2+r^2-2\,\cos(2\theta)}-r\cos(2\theta)\Big)\ [2+2].
+	\end{aligned}
+\end{equation}
+
+Gravitini:
+\begin{equation}
+	m_{{(\nicefrac32)}}\ell_{\rm AdS}:\quad 
+	\quad \dfrac1{2}\bigg[1\pm\sqrt{4+2\,r^{2}+r^{4}-2r^{2}\cos(2\theta)}\bigg]\ [4+4],
+\end{equation}
+no SUSY enhancements other than $r=0$.
+
+No dependence on $\Phi$.
+
 \section{Conclusion}

### 2025-07-15 Draft_MLFlatDirections.tex
Update réunion Bastien.

@@
 Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach.
-The acceptance ratio is controlled by the following schedule as function of the \texttt{epoch}:
+The number of particles accepted at each run is monitored.
+We aim at following the following schedule as function of the \texttt{epoch}:
 		\begin{equation} \label{eq:acceptanceratioschedule}
@@
 		where \texttt{n\_epochs} is the total number of epochs.
+If we accept more particle (in the 5 last epochs), we decrease the temperature by 5\%, if we accept less we increase it by 5\%.
 This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
@@
 	\begin{aligned}
-		&\texttt{n\_epochs} = 1000,\\
-		&\texttt{beta}  = 10^{-6}, \\
-		&\texttt{p\_{modify}} = 0.5,\\
-		&\texttt{p\_{multiply}} = 0.25,\\
-		&\texttt{p\_{divide}} = 0.25. 
+		&\texttt{n\_epochs = 1000},\\
+		&\texttt{beta  = 1e-6}, \\
+		&\texttt{p\_{modify} = 0.5},\\
+		&\texttt{p\_{multiply} = 0.25},\\
+		&\texttt{p\_{divide} = 0.25}. 
 	\end{aligned}
@@
 	\begin{aligned}
-		&\texttt{max\_degree} = 4,\\
-		&\texttt{max\_num\_monomials} = 6.
+		&\texttt{max\_degree = 4},\\
+		&\texttt{max\_num\_monomials = 6.}
 	\end{aligned}
 \end{equation}
+\ce{Give details on the basis of polynomials. 126.}
 
@@
 \ce{Check the exact number.} Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
-We select the representant of each type that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{lossreg}).
-Here is an example of ouput for a given run: \ce{Here $\texttt{threshold} = 0.1$ and $\texttt{steps} = 1000$ for the local search.}
+We select the representant of each type that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}).
+Here is an example of output for a given run: \ce{Here $\texttt{threshold} = 0.1$ and $\texttt{steps} = 1000$ for the local search.}
 \begin{subequations}
@@
 Note that the dynamics depend strongly on the polynomial, some of the appearing after only few dozens of epochs, and others just before the end of the runs.
-The evolution of the inverse temperature, imposed by eq.~\eqref{eq:acceptanceratioschedule}, is polynomial.
+\ce{The polynomials are organize in three classes, the first ones appear after typically a dozen of iteration, the second one after 100 and the last one are very difficult to find and rare.
+The code favors the polynomials with lowest loss through resampling.
+Du fait de la structure, quand un polynome est trouvé il est favorisé au détriment des autres (resampling).
+Faire une figure ?} The evolution of the inverse temperature, imposed by eq.~\eqref{eq:acceptanceratioschedule}, is polynomial.
 \ce{Do a fit.}.
-The losses of the runs are shown in fig.~\ref{fig:evolutionoftargetreproduction}(c).
+\ce{At the end beta is not 1.
+This allows to find more than one candidate polynomials, favors the diversity.
+This is linked to the choice of the acceptance ration at the end.
+The lower the acceptance ration, the higher beta.
+If ratio too low, no diversoty.
+If ratio too high, shitty polynomials.} The losses of the runs are shown in fig.~\ref{fig:evolutionoftargetreproduction}(c).
 \ce{Describe more the loss?
-Is it summed on all particles?}.
+It is the best loss at each step.
+Use the loss to show that we indeed converged}.
 

### 2025-07-16 Draft_MLFlatDirections.tex
Update of the figures.

@@
 
-\documentclass[11pt]{article}
+\documentclass[11pt,a4paper]{article}
 
@@
 text centered, 
-draw=coral, 
-fill=lightcoral,
+draw=myorange, 
+fill=myorange!20,
 line width=1pt,
@@
 		We then perform gradient descent on the points using TensorFlow’s automatic differentiation \cite{tensorflow2015-whitepaper}. The loss function is defined as:
-		\begin{equation}
+		\begin{equation} \label{eq:lossgraddes}
 			\mathcal{L} = \sum_{i = 1}^{n_{points}} ||\left.\nabla V(\vec{X}^{\,i})\,\right|_{\vec{y}=0}||^2
@@
 			\centering
-			\includegraphics[scale=0.35]{Figures/log_grad_V_hist.png}
-			\quad
-			\includegraphics[scale=0.35]{Figures/log_Vp4_hist.png}
-			\caption{Left panel: Histogram of the logarithm of the norm of the gradient for each point. Right panel: Histogram of the distance of the value of the potential for each point.}
+			\subfigure{ \label{fig:log_grad_V}
+				\begin{tikzpicture}
+			  		\draw (0,0) node (fig1) {\includegraphics[scale=0.7]{Figures/log_grad_V_hist_21_05_2025.pdf}};
+			  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+			  		\draw (9,0) node (fig2) {\includegraphics[scale=0.7]{Figures/log_Vp4_hist_21_05_2025.pdf}};
+			  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+			  	\end{tikzpicture}
+			}
+			\subfigure{\label{fig:log_Vp4}}
+			\vspace{-1cm}
+			\caption{(a) Histogram of the the norm of the gradient for each point ($x$ axis is in $\log$ scale).
+(b) Histogram of the distance of the value of the potential to $V(0)$ for each point ($x$ axis is in $\log$ scale).}
 			\label{fig:Analyze_V_points}
@@
 			\centering
-			\includegraphics[scale = 0.5]{Figures/Loss_grad_des_1.png}
-			\caption{Evolution of the loss function during gradient descent and corresponding learning rate schedule, noted $\alpha$ on the left y-axis, both plotted on a logarithmic scale.
+			\includegraphics[scale = 0.75]{Figures/Loss_grad_des_21_05_2025.pdf}
+			\caption{Evolution of the loss function~\eqref{eq:lossgraddes} during gradient descent and corresponding learning rate schedule, noted $\alpha$ on the left y-axis, both plotted on a logarithmic scale.
 Dashed lines indicate epochs at which the optimizer was reinitialized.}
@@
 			\centering
-			\includegraphics[scale = 0.3]{Figures/triangular_plot_1_2_4_8_10.png} %names need to be changed.
+			\makebox[\textwidth][c]{\includegraphics[scale = 0.7]{Figures/Triangular_plot_1_2_4_8_10_21_05_2025.pdf}}
 			\caption{Triangular plot showing $2d$ projections and $1d$ histograms of the data after the gradient descent}
@@
 In other words, it provides an estimate of the local dimensionality around each point.
-		We perform this analysis for several values of $k$, namely $k \in \{5, 10, 20, 50, 100\}$, and we fix $\epsilon = 0.99$. The results are presented in Fig. \ref{local_pca}.
+		We perform this analysis for several values of $k$, namely $k \in \{5, 10, 20, 50, 100\}$, and we fix $\epsilon = 0.99$. The results are presented in fig.~\ref{local_pca}.
 
@@
 			\centering
-			\includegraphics[scale=0.4]{Figures/Local_PCA.png}
+			\includegraphics[scale=0.75]{Figures/Local_PCA_21_05_2025.pdf}
 			\caption{Results of the local PCA analysis.
@@
 
-						\draw [arrow] (end_iter) -- node[right, arrow_label] {No} (exploit);
+						\draw [arrow] (end_iter) -- node[right, arrow_label] {Yes} (exploit);
 						\draw [arrow] (exploit) -- (output);
@@
 
-\ce{Keep fig.~\ref{fig:evolutionoftargetreproduction}(b)?}
+\begin{figure}
+	\centering
+	\subfigure{ \label{fig:count_pol_all_beta}
+		\begin{tikzpicture}
+	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.7]{Figures/Count_pol_all_beta_1000runs_13.pdf}};
+	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+	  		\draw (8.25,0) node (fig2) {\includegraphics[scale=0.7]{Figures/Count_pol_indiv_1000runs_13.pdf.pdf}};
+	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+	  	\end{tikzpicture}
+	}
+	\subfigure{\label{fig:count_pol_indiv}}
+	\vspace{-1cm}
+	\caption{(a) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp} (left scale) and evolution of the inverse temperature $\beta$ and its $1\sigma$ deviation (right scale).
+(b) Dynamics of the mean number of particles reproducing each polynomial in eq.~\eqref{eq:pols} (the scale of the $y$ axis is logarithmic).}
+	\label{fig:evolutionoftargetreproduction}
+\end{figure}
 
@@
 	\centering
-	\begin{adjustbox}{width=20cm,center}
-		\begin{minipage}[t]{0.31\paperwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figures/Count_beta_adaptative_temp_indiv}
-			\caption*{(a)}
-		\end{minipage}%
-		\hfill
-		\begin{minipage}[t]{0.31\paperwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figures/Count_good_pol_all}
-			\caption*{(b)}
-		\end{minipage}%
-		\hfill
-		\begin{minipage}[t]{0.31\paperwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figures/Loss_all_ASMC.png}
-			\caption*{(c)}
-		\end{minipage}
-	\end{adjustbox}
-	\caption{(a) Dynamics of the mean number of particles reproducing each polynomial in eq.~\eqref{eq:pols} (left scale) and evolution of the inverse temperature $\beta$ and its $1\sigma$ deviation (right scale).
-(b) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp}.
-(c) Evolution of the losses during the runs (in blue) and their average (in yellow).}
-	\label{fig:evolutionoftargetreproduction}
+	\includegraphics[scale=0.75]{Figures/Loss_all_ASMC_1000runs_13.pdf}
+	\caption{Evolution of the losses during the runs (in blue) and their average (in yellow).}
+	\label{fig:lossallASMC}
 \end{figure}
 
-\ce{Tests sur le gradient analytique pour voir si c'est un polynome annulateur.}
+\ce{Tests sur le gradient analytique pour voir si c'est un polynome annulateur. {\bfseries Say more. Add legend?}}
 

### 2025-07-16 potentials.py
add some potentials and gradients to the potentials.py file

@@ -188,77 +188,529 @@ x4 -(x2 * (x2 * x4 + x3 * x5)) + x1 * (x2 ** 3 + 2 * x2 * (x3 ** 2) \
 
 def grad_V_1_2_4_8_10(x):
     x1,x2,x4,x8,x10=tf.split(x,5,axis=1)
-    n_sample = x.shape[0]
+    n_sample = x.shape[0] 
+
     f1 = 4 * (tf.exp(-2 * x8)) * (x1 ** 3) -((tf.exp(x8)) * (2 + \
-x10 ** 2) * ((tf.sqrt(2.)) * x10 * (x2 ** 3) + 2 * x1 * (-1 + x2 ** 2) \
-+ 2 * x2 * x4)) + 2 * (2 * (x1 ** 3) + 3 * (tf.sqrt(2.)) * (x1 ** 2) * \
-x10 * x2 + (tf.sqrt(2.)) * x10 * x2 * (x2 -x4) * (x2 + x4) + x1 * (-4 \
-+ (4 + 3 * (x10 ** 2)) * (x2 ** 2) + 2 * (tf.sqrt(2.)) * x10 * x4)) + \
-(tf.exp(-x8)) * (-8 * (x1 ** 3) -6 * (tf.sqrt(2.)) * (x1 ** 2) * x10 * \
-x2 + 4 * x2 * x4 + 4 * x1 * (1 -(x2 ** 2) + x4 ** 2)) 
+x10 ** 2) * ((tf.sqrt(2)) * x10 * (x2 ** 3) + 2 * x1 * (-1 + x2 ** 2) \
++ 2 * x2 * x4)) + 2 * (2 * (x1 ** 3) + 3 * (tf.sqrt(2)) * (x1 ** 2) * \
+x10 * x2 + (tf.sqrt(2)) * x10 * x2 * (x2 -x4) * (x2 + x4) + x1 * (-4 \
++ (4 + 3 * (x10 ** 2)) * (x2 ** 2) + 2 * (tf.sqrt(2)) * x10 * x4)) + \
+(tf.exp(-x8)) * (-8 * (x1 ** 3) -6 * (tf.sqrt(2)) * (x1 ** 2) * x10 * \
+x2 + 4 * x2 * x4 + 4 * x1 * (1 -(x2 ** 2) + x4 ** 2))
+    
     f2 = -3 * \
[…]

### 2025-07-23 Draft_MLFlatDirections.tex

@@
 
-\section{Supergravity setup}
-%\begin{itemize}[label=\textbullet]
-%	\item Context: 6d ${\rm AdS}_{3}\times S^{3}$, truncation to 3d, potential, conformal manifold.
-
+\section{Supergravity setup} \label{sec:sugra}
 Three-dimensional $\mathcal{N}=8$ (half-maximal) gauged supergravity is governed by the Lagrangian
@@
 \end{equation}
-
-We note here that all dilaton fields are denoted with a tilde.
+For later convenience, we define a thirteen-dimensional vector
+\begin{equation} \label{eq:defvecX}
+	% \vec{X} = (x_1,\dots,x_6,\tilde{x}_7,\tilde{x}_8,\tilde{x}_9,x_{10},\dots,x_{12},\tilde{x}_{13})
+	\vec{X} = (x_1, x_{2}, x_{3}, x_{4}, x_{5}, x_6, \tilde{x}_7, \tilde{x}_8, \tilde{x}_9,x_{10}, x_{11}, x_{12}, \tilde{x}_{13})
+\end{equation}
+encompassing all parameters.
+Note here that all dilaton fields are denoted with a tilde.
 This convention is adopted in anticipation of a later redefinition of the form \( x_i = e^{\tilde{x}_i} \) for these fields.
-By reserving the notation without tildes for the exponentiated variables, we maintain a clear and consistent distinction for use in subsequent expressions.
+%By reserving the notation without tildes for the exponentiated variables, we maintain a clear and consistent distinction for use in subsequent expressions.
 
@@
 It is important to emphasize, however, that this subset does not constitute a consistent truncation of the full theory.
-Consequently, the truncated theory involving only five scalar fields may not constitute a formally consistent truncation of the full 13-scalar theory, as higher-order interactions could, in principle, source the remaining scalar modes.
+Consequently, the truncated theory involving only five scalar fields may not constitute a formally consistent truncation of the full thirteen-scalar theory, as higher-order interactions could, in principle, source the remaining scalar modes.
 As a result, the interpretation of the five-scalar theory as a consistent subsector of the original theory may no longer hold.
 Nonetheless, the five-scalar model remains a self-consistent theory in its own right and can be used independently.
-This distinction does not affect our numerical approach.
-
-Nevertheless, the solutions we obtain remain valid solutions of the complete theory.
-This is because we identify the critical points of the scalar potential by first computing $\nabla V = 0$ with all scalar fields included, and only then setting the remaining fields to zero.
+This distinction does not affect our numerical approach: the solutions we obtain remain valid solutions of the complete theory.
+This is because we identify the critical points of the scalar potential by first computing $\nabla V = 0$ with all scalar fields included, and only then setting the remaining fields
+\begin{equation} \label{eq:defvecy}
+	\vec{y} = (x_3,x_5,x_6,\tilde{x}_7,\tilde{x}_9,x_{11},x_{12},\tilde{x}_{11})
+\end{equation}
+to zero, as detailed in sec.~\ref{sec:graddes}.
 By performing the differentiation before the truncation, we ensure that the resulting configurations satisfy the full equations of motion and are therefore legitimate solutions of the complete theory.
 
-To compute the gradient, we exploit the fact that we possess an analytic expression for the scalar potential \eqref{eq:scalarpotential}, which we implement in Mathematica for numerical analysis.
-Note however that it could have been fully done using a numerical approach, automatic differenciations methods (that we will use later to do the gradient descent for the loss function).
+To compute the gradient, we exploit the fact that we possess an analytic expression for the scalar potential~\eqref{eq:scalarpotential}, which we implement in Mathematica for numerical analysis.
+Note however that it could have been fully done using a numerical approach, automatic differentiations methods (that we will use later to do the gradient descent for the loss function).
 %Under this truncation, the scalar potential~\eqref{eq:scalarpotential} reduces to:
@@
 In scenarios where an explicit analytic expression for the potential and its gradient is inaccessible—yet numerical evaluation remains feasible—our method retains its validity.
-In particular, one could replace the analytic gradient by automatic differenciation methods if one can only evaluate the potential.
+In particular, one could replace the analytic gradient by automatic differentiation methods if one can only evaluate the potential.
 Hence, the numerical strategy adopted here may prove effective even in cases where an exact analytic expression for the potential is out of reach.
@@
 \section{Numerical analysis}
-	\subsection{Gradient descent and local analysis}
 To identify the flat directions in the potential, we will use numerical tools.
 The procedure is as follows: first, we sample the underlying manifold, and then we use numerical techniques to extract analytical information from the resulting cloud of points.
-The first step is thus to sample the manifold.
-			\subsubsection{Sampling the manifold}
-		%\paragraph{Gradient descent: implementation, sampling, time needed, loss}
-
-		To do so, we perform a basic gradient descent.
-We begin by randomly and uniformly initializing points within a hypercube of range $[-2,2]$.
-This choice is important to ensure that points are not restricted to the inner range $[-1,1]$.
-This will be important later, when performing the symbolic regression \footnote{The rationale is that symbolic regression (SR) evaluates the data points ${\vec{x}^i}$ using a candidate polynomial function $p$.
-The loss function—used later to assess the quality of a given polynomial—is defined as $\sum_i p(\vec{x}^i)$.
+The sampling of the manifold is done through a gradient descent.
+We then analyse its dimension and structure using a local Principal Component Analysis~(PCA) and clustering algorithms, and finally extract analytical constraints defining the manifold thanks to Symbolic Regression methods.
+We detail these different procedures in the following.
+
+	\subsection{Sampling the manifold: gradient descent} \label{sec:graddes}
+	To perform the gradient descent, we initialise randomly and uniformly points within a hypercube of range $[-2,2]$.
+This choice is important to ensure that points are not restricted to the inner range~$[-1,1]$, which will be crucial for the Symbolic Regression.\footnote{The rationale is that symbolic regression (SR) evaluates the data points $\vec{x}^{(i)}$ using a candidate polynomial function $p$.
+The loss function—used later to assess the quality of a given polynomial—is defined as $\sum_i p(\vec{x}^{(i)}$.
 When all data points lie within the interval $[-1, 1]$, the SR algorithm tends to favor high-degree polynomials, as these often yield smaller values over this range, thereby artificially lowering the loss.
-Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of overly complex polynomials that exploit this effect.}.
-For this example, we choose to generate $10^5$ points.
-This number is motivated by the dimensionality of our problem.
-If we aim to populate all possible directions and want approximately $\mathcal{O}(10)$ points per direction, then we require $\mathcal{O}(10^5)$ points.
-Given that the true intrinsic dimensionality of the manifold is less than or equal to 5, this value serves as a conservative upper bound for the number of points needed to adequately sample the manifold.
-
-		We then perform gradient descent on the points using TensorFlow’s automatic differentiation \cite{tensorflow2015-whitepaper}. The loss function is defined as:
+Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of overly complex polynomials that exploit this effect.} \ce{Put the footnote later in the SR section?} As the example we're focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points: we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
+As the solutions manifold lie within the five dimensional space, its intrinsic dimension is less than or equal to 5.
+The value $10^5$ then serves as a conservative upper bound for the number of points needed to adequately sample the manifold.
+
+	We then perform a gradient descent on the points using TensorFlow’s automatic differentiation \cite{tensorflow2015-whitepaper}. The loss function is defined as
 	\begin{equation} \label{eq:lossgraddes}
-			\mathcal{L} = \sum_{i = 1}^{n_{points}} ||\left.\nabla V(\vec{X}^{\,i})\,\right|_{\vec{y}=0}||^2
-		\end{equation}
-		where $\vec{X}^{\,i} = (x^i_1,\dots,x^i_6,\tilde{x}^i_7,\tilde{x}^i_8,\tilde{x}^i_9,x^i_{10},\dots,x^i_{12},\tilde{x}^i_{13})$ and $\vec{y}^{\,i} = (x^i_3,x^i_5,x^i_6,\tilde{x}^i_7,\tilde{x}^i_9,x^i_{11},x^i_{12},\tilde{x}^i_{11})$ denotes the data points.
-This way we only keep $(x^i_1,x^i_2,x^i_4,\tilde{x}^i_8,x^i_{10})$ alive after we have taken the derivative.
-As already mentionned above, we use the analytic formula for $\nabla V$, but we could have perform the gradient descent by fully using automatic differentiation.
-
-		Through trial and error, we observed that periodically reinitializing the optimizer significantly improved the convergence rate.
-This technique bears similarity to the concept of warm restarts introduced in \cite{loshchilov2017sgdrstochasticgradientdescent}.
+		\mathcal{L} = \sum_{i = 1}^{n_{\rm points}} \left|\left|\left.\nabla V(\vec{X}^{(i)})\,\right|_{\vec{y}^{\,(i)}=0}\right|\right|^2,
+	\end{equation}
+	% where $\vec{X}^{(i)} = (x^{(i)}_1,\dots,x^{(i)}_6,\tilde{x}^{(i)}_7,\tilde{x}^{(i)}_8,\tilde{x}^{(i)}_9,x^{(i)}_{10},\dots,x^{(i)}_{12},\tilde{x}^{(i)}_{13})$ and $\vec{y}^{\,(i)} = (x^{(i)}_3,x^{(i)}_5,x^{(i)}_6,\tilde{x}^{(i)}_7,\tilde{x}^{(i)}_9,x^{(i)}_{11},x^{(i)}_{12},\tilde{x}^{(i)}_{11})$
+	see eq.~\eqref{eq:defvecX} and~\eqref{eq:defvecy} for the definitions of the vectors $\vec{X}$ and $\vec{y}$.
+The exponents $(i)$ denote the data points, with $i\in\llbracket1,n_{\rm points}\rrbracket$.
+This way we only keep $(x^{(i)}_1,x^{(i)}_2,x^{(i)}_4,\tilde{x}^{(i)}_8,x^{(i)}_{10})$ alive after we have taken the derivative.
+As already mentioned above, we use the analytic formula for $\nabla V$, but we could have performed the gradient descent by fully using automatic differentiation.
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale = 0.75]{Figures/Loss_grad_des_21_05_2025.pdf}
+		\caption{Evolution of the loss function~\eqref{eq:lossgraddes} during gradient descent (right $y$-axis, in blue) and corresponding learning rate schedule $\alpha$ (left $y$-axis in orange), both plotted on a logarithmic scale.
+Dashed lines indicate epochs at which the optimizer was reinitialized.}
+		\label{fig:loss_grad_des}
+	\end{figure}
+
+	The Adam optimizer was employed throughout the gradient descent procedure~\cite{kingma2017adammethodstochasticoptimization}.
+Through trial and error, we observed that periodically reinitialising the optimizer significantly improved the convergence rate.
+It was reinitialised at iterations {250, 500, 750}, with the learning rate $\alpha$ fixed at $10^{-2}$.
+At iteration 1000, the optimizer was reinitialised once more, this time with a reduced learning rate of $10^{-3}$.
+A final reinitialisation was performed at iteration 1500, setting the learning rate to $10^{-4}$, and the optimization was continued for an additional 500 epochs.
+The evolution of the loss function~\eqref{eq:lossgraddes}, along with the learning rate schedule, is shown in fig.~\ref{fig:loss_grad_des}.
+As can be seen in this figure, the convergence rate improves significantly each time the optimizer is reinitialised.
+We also observe that, following the last few reinitialisations, the loss exhibits a small bump immediately after the restart.
+We interpret this behaviour as follows: the learning rate gets internally adjusted by the Adam optimizer during the descent, and may well be smaller than the instructions when the reset occurs.
+The learning rate then gets suddenly increased, and some points that previously had low loss values may momentarily worsen before benefiting from faster convergence.
+This effect is likely due to points initially located in regions with weak attractive basins being pushed toward areas where the potential gradient is steeper, thus accelerating their convergence.
+This strategy introduces the risk of desampling certain regions in favour of others, introducing the risk to hide some flat directions in the potential.
+However, we believe that with enough points, it is very unlikely for a flat direction to be completely hidden from us and desampled.
+This method bears similarity to the concept of warm restarts introduced in ref.~\cite{loshchilov2017sgdrstochasticgradientdescent}, where the authors reset the learning rate to some value at each reset, without reinitialising the whole optimizer.
 However, we found that simply scheduling the learning rate without resetting the optimizer yielded slower convergence.
-We interpret this as follows: when the optimizer is reinitialized, it effectively "forgets" its past gradient history.
+We interpret this as follows: when the optimizer is reinitialised, it effectively "forgets" its past gradient history.
 As a result, the actual learning rate used corresponds more closely to the specified value, rather than being internally adjusted based on accumulated past gradients.
 This effect seems to contribute to faster convergence in our case.
-The evolution of the loss function, along with the learning rate schedule, is shown in Fig.~\eqref{fig:loss_grad_des}.
-As can be seen in this figure, the convergence rate improves significantly each time the optimizer is reinitialized.
-We also observe that, following the last few reinitializations, the loss exhibits a small bump immediately after the restart.
-We interpret this behavior as a consequence of the increased learning rate: some points that previously had low loss values may momentarily worsen before benefiting from faster convergence.
-This effect is likely due to points initially located in regions with weak attractive basins being pushed toward areas where the potential gradient is steeper, thus accelerating their convergence.
-This strategy introduces the risk of desampling certain regions in favor of others, introducing the risk to hide some flat directions in the potential.
-However, we believe that with enough points, it is very unlikely for a flat direction to be completely hidden from us and desampled.
 
@@
 		\vspace{-1cm}
-			\caption{(a) Histogram of the the norm of the gradient for each point ($x$ axis is in $\log$ scale).
-(b) Histogram of the distance of the value of the potential to $V(0)$ for each point ($x$ axis is in $\log$ scale).}
+		\caption{(a) Histogram of the the norm of the gradient for each point ($x$-axis is in $\log$ scale).
+(b)~Histogram of the distance of the value of the potential to $V(0)$ for each point ($x$-axis is in $\log$ scale).
+Note that four points have deviations of the order of $10^{-3}$ and are not visible on the figure.}
 		\label{fig:Analyze_V_points}
@@
 
-		The Adam optimizer was employed throughout the gradient descent procedure.
-It was reinitialized at iterations {250, 500, 750}, with the learning rate fixed at $10^{-2}$.
-At iteration 1000, the optimizer was reinitialized once more, this time with a reduced learning rate of $10^{-3}$.
-A final reinitialization was performed at iteration 1500, setting the learning rate to $10^{-4}$, and the optimization was continued for an additional 500 epochs.
-
-		Upon completion, it was observed that all data points converged to values close to $-4$.
-Specifically, nearly all data points attained values within an absolute error of at least $10^{-4}$, with the exception of four points whose deviations were on the order of $10^{-3}$.
-Similarly, 99,739 out of 100,000 data points exhibited gradient norms smaller than $10^{-3}$.
-These results are summarized in Figure~\ref{fig:Analyze_V_points}.
-
-		\begin{figure}[h!]
-			\centering
-			\includegraphics[scale = 0.75]{Figures/Loss_grad_des_21_05_2025.pdf}
-			\caption{Evolution of the loss function~\eqref{eq:lossgraddes} during gradient descent and corresponding learning rate schedule, noted $\alpha$ on the left y-axis, both plotted on a logarithmic scale.
-Dashed lines indicate epochs at which the optimizer was reinitialized.}
-			\label{fig:loss_grad_des}
-		\end{figure}
-
-		As a first visualization, we present a triangular plot of the data in Fig.
-\ref{triangular_plot_1_2_4_8_10}.
-This figure shows all possible 2D projections of the data, along with the 1D histograms of each coordinate after gradient descent.
-		\begin{figure}[h!]
+	Upon completion, the loss function converges around $0.002$.
+The distribution of the values of the gradient at each of the data points is plotted in fig.~\ref{fig:log_grad_V}.
+More than $93\%$ of the points converged to values of $\vert\nabla V\vert$ lower than $10^{-4}$, and more than $99\%$ of them exhibited gradient norms smaller than $10^{-3}$, yielding a satisfying sampling of the flat directions.
+As can be observed in fig.~\ref{fig:log_Vp4}, all data points converged to values close to $V(0)=-4$.
+Specifically, nearly all points attained $V(0)$ within an absolute error of at least $10^{-4}$, with the exception of four points whose deviations were of the order of $10^{-3}$ (not visible on the graph).
+As the origin $\vec{X}=0$ of the parameter space corresponds to the three-dimensional truncation of the round ${\rm AdS}_{3}\times S^{3}$ solution of half-maximal supergravity in six dimensions, this confirms that the data points lie within flat directions of the potential.
+
+	\begin{figure}
 		\centering
 		\makebox[\textwidth][c]{\includegraphics[scale = 0.7]{Figures/Triangular_plot_1_2_4_8_10_21_05_2025.pdf}}
-			\caption{Triangular plot showing $2d$ projections and $1d$ histograms of the data after the gradient descent}
+		\caption{Triangular plot showing all $2d$ projections and $1d$ histograms of the data after the gradient descent.}
 		\label{triangular_plot_1_2_4_8_10}
 	\end{figure}
-		We can make a few comments on those plots.
-First, we observe non-trivial correlations in the data.
-Some of these may result from larger basins of attraction, such as in the $x_1/x_2$ plot.
-However, the structures seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots likely reflect genuine features of the manifold, and will show latter that this is indeed the case.
-We also note that all directions appear to be well populated.
-		%Furthermore, we can notice that a large majority of the points converge to the origin $\vec{0}$.
-This is not surprising, as this just mean that the round sphere solution has a larger basin of attraction, which sounds reasonable.
-We do not however attempt to shift the points along flat directions to depopulate the origin or repopulate other regions.
-		%\paragraph{Local PCA: graphs of number of patches with given local dimension, and with varying size of local patch, discuss optimal patch size (we want at least few points in each direction)}
-		\subsubsection{Determining the dimension}
+
+	As a first visualisation, we present a triangular plot of the data in fig.~\ref{triangular_plot_1_2_4_8_10}.
+\ce{Sure of the use of ``triangular''?} This figure shows all possible 2d projections of the data, along with the 1d histograms of each coordinate after gradient descent.
+Note that all directions appear to be well populated.
+There also seems to be non-trivial correlations in the data, see for example the $x_1/x_2$, $x_4/\tilde{x}_8$ or $x_4/x_{10}$ graphs.
+They could be genuine correlations, or may result from larger basins of attraction.
+Thanks to the analysis of sec.~\ref{sec:results}, we will conclude that the structures in the $x_1/x_2$ plot are artefacts of the gradient descent, whereas the ones seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots reflect genuine features of the manifold.
+
+	\subsection{Local analysis: extracting the dimension}
 	Once the gradient descent has been completed and the flat directions sampled, the next step is to identify the structure of the underlying manifold.
 Our goal is to eventually obtain an analytical expression, not just a numerical description.
-Before applying symbolic regression to search for such an expression, we can first perform some exploratory analyses to better understand the data.
-Specifically, we aim to determine the dimensionality of the manifold and wether it consists of a single connected component or multiple disjoint components (e.g., two intersecting hyperplanes).
-		To this end, we apply a local Principal Component Analysis (PCA).
+Before applying symbolic regression to search for such an expression, we first perform some exploratory analyses to better understand the data.
+Specifically, we aim at determining the dimension of the manifold and whether it consists of a single connected component or multiple disjoint components (\textit{e.g.} two intersecting hyperplanes).
+To this end, we apply a local Principal Component Analysis (PCA, see for example ref.~\cite{scikit-learn}).
 For each point, we identify its $k$ nearest neighbours and perform a PCA on that local neighbourhood.
 This procedure allows us to determine how many principal directions are needed to explain a given proportion $\epsilon$ of the data variance.
-In other words, it provides an estimate of the local dimensionality around each point.
-		We perform this analysis for several values of $k$, namely $k \in \{5, 10, 20, 50, 100\}$, and we fix $\epsilon = 0.99$. The results are presented in fig.~\ref{local_pca}.
-
-		\begin{figure}[h!]
+In other words, it provides an estimate of the local dimensionality around each point, \textit{i.e.} the dimension of its local tangent space.
+We perform this analysis for several values of $k$, namely $k \in \{5, 10, 20, 50, 100\}$, and we fix $\epsilon = 0.99$.
+The results are presented in fig.~\ref{fig:local_pca}.
+We observe that for every choice of $k$, there is a prominent peak at $d = 3$, suggesting that the underlying manifold is three-dimensional.
+For $k = 5$, a noticeable fraction of points are assigned dimension 2.
+This can be attributed to the fact that if the true dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality for a fraction of the points.
+Additionally, for $k \geq 20$, we observe an increasing number of points being assigned dimensions 4 or 5.
+This behaviour can be explained by the loss of locality when the number of neighbours becomes too large: increasing $k$ results in a coarser approximation, and the algorithm may then incorporate points that are no longer truly local.
+This artificial enlargement of the neighbourhood can cause the estimated local dimensionality to rise.
+We thus conclude that the manifold under investigation has an intrinsic dimension of 3.
+
+	\begin{figure}
 		\centering
@@
 Each curve corresponds to a different value of $k$ in the $k$-nearest neighbours.}
-			\label{local_pca}
+		\label{fig:local_pca}
 	\end{figure}
 
-		We observe that for every choice of $k$, there is a prominent peak at $d = 3$, suggesting that the underlying manifold is three-dimensional.
-For $k = 5$, a noticeable fraction of points are assigned a dimensionality of 2.
-This can be attributed to the fact that if the true dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality for a fraction of the points.
-		Additionally, for $k \geq 20$, we observe an increasing number of points being assigned dimensionalities of 4 or 5.
-This behavior can be explained by the loss of locality when the number of neighbours becomes too large: increasing $k$ results in a coarser approximation, and the algorithm may then incorporate points that are no longer truly local.
-This artificial enlargement of the neighbourhood can cause the estimated local dimensionality to rise.
-		We thus assume that the manifold under investigation has an intrinsic dimension of 3.
-
-		%\paragraph{Clustering: HDBScan (only parameter: minimal number of points in a cluster), and graphs of 3d slices of the 5d space}
-
-		One possible scenario is that our data actually consists of several distinct three-dimensional manifolds, and the points previously identified with dimension $4$ may lie at the intersections of these manifolds.
-To illustrate, consider the intersection of two lines: at the intersection point, the local dimensionality estimated by the previous PCA algorithm would be 2.
-To rule out this possibility, we apply a clustering algorithm based on local density, where we only select the points of dimension 3.
-This, way, we remove the possible intersection points with dimension 4 or 5.
-For the purpose of the clustering, we use the HDBSCAN algorithm\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation \cite{10.1007/978-3-642-37456-2_14}.
+	One possible scenario is that our data actually consists of several distinct three-dimensional manifolds, intersecting at least at the origin $\vec{X}=0$, and the points previously identified with dimension $4$ may lie at the intersections of these manifolds.
+Consider for example the intersection of two lines: at the intersection point, the local dimension estimated by the previous PCA algorithm would be 2.
+To rule out this possibility, we apply a clustering algorithm, based on local density, on the points with tangent spaces of dimension 3 only.
+This, way, we remove the possible intersection points with local dimension 4 or 5.
+For the purpose of the clustering, we used the HDBSCAN algorithm\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation~\cite{10.1007/978-3-642-37456-2_14}.
 Briefly, it is a density-based clustering method that extends DBSCAN by converting it into a hierarchical clustering algorithm and then extracting a flat clustering based on the stability of clusters.}.
-		We set the minimum cluster size to 10 points. Out of the 98,606 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849. 
+
+	We set the minimum cluster size to 10 points.
+\ce{Redo explanations here, with the new data.
+Explain results with the fact that the algo is density based?
+Try to depopulate a bit the center?
+By randomly removing points?} \ce{Give the choice for $k$: $20$.} Out of the 98,606 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.
+
 	The smallest cluster (10 points) is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
@@
 
+	\ce{ICI}
+
 	\subsection{Annealed Importance Sampling for polynomial symbolic regression}
@@
 
-						\node (ess_check) [decision, below of=weight_update] {Effective Sample Size $<$ Threshold ?};
+						\node (ess_check) [decision, below of=weight_update] {Effective Sample Size $<$ Threshold?};
 
@@
 
-						\node (end_iter) [decision, below of=acceptance] {Last step ?};
+						\node (end_iter) [decision, below of=acceptance] {Last step?};
 
@@
 We want to make this 0 so we find polynomial that annihilates our data.
-The second part is a regularisation factor : it prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem.
+The second part is a regularisation factor: it prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem.
 We typically take $\lambda \sim \mathcal{O}(1000)$.
@@
 
-	\subsubsection{Results}
-
-	The results of this method are as follow. The code finds the 8 different following polynomials: 
-	\begin{subequations} \label{eq:pols}
-    \begin{align}
-      p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\
-      p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
-      p_{3} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
-      		- 2\,x_{2} x_{4}^{2}x_8,\\
-      p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
-      		- x_{2}x_{4}x_8x_{10},\\
-      p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
-      		+ x_{1}x_8x_{10}^{2},\\
-      p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
-      		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},\\
-      p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
-      		- x_{2}^{2}x_{10}, \\
-      p_{8} &= -2 + 4 x_{8} - 2 x_8^2 + 2 x_{4}^2 x_8 - x_8^2 x_{10}^2,
-    \end{align}
-  \end{subequations}
-  where $x_{8} = e^{\tilde{x}_{8}}$. They are found with different frequencies with some polynomials occuring more often than others. The results are presented in \eqref{table:results}.
-
-  	Let us clarify a point regarding the expected structure of the solutions to the system defined by the critical points of the scalar potential, i.e., the variety defined by the vanishing of the gradient $\nabla V$.
-
-  In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field.
-In our case, the potential $V$ and its gradient $\nabla V$ are polynomial  functions with coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$.
-That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.
-
-  The conformal manifold (or the moduli space of solutions) is then a subvariety of this ambient space, defined as the common zero locus of the polynomials in $\nabla V$.
-From the perspective of algebraic geometry, this variety is cut out by an ideal in the polynomial ring with coefficients in the aforementioned field extension of $\mathbb{Q}$.
-Since the defining equations have coefficients in this field, the variety itself is defined over that same field.
-
-  Now, consider the numerical solutions obtained via methods such as annealed importance sampling.
-If these numerical procedures converge to points on the same variety, and assuming that the variety is irreducible over the given field, then any point (i.e., any solution) on the variety must lie in the same field extension over which the variety is defined.
-This follows from basic principles in algebraic geometry: the set of algebraic points on a variety defined over a field $K$ are themselves algebraic over $K$, and the field of definition of these points must be a (possibly finite) extension of $K$.
-
-  Therefore, even if the numerical solver does not explicitly reveal this, one should expect that the coordinates of the solutions (i.e., the values of the scalar fields at critical points) lie in the same field extension of $\mathbb{Q}$ as the coefficients of the original system of polynomials $\nabla V$.
-That is, they should belong to $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$ or a finite extension thereof.
-
-  This argument justifies the expectation that if the scalar potential $V$ and its gradient $\nabla V$ involve only rational numbers and square roots, then the solutions to $\nabla V = 0$—regardless of how they are found—should also lie within the same field extension.
-
- This is this argument that allowed us to round the coefficients of the polynomials given by the annealed importance sampling algorithm, and found the polynomials in Eq. \eqref{eq:pols}.
-
- \subsubsection{Setup of ASMC}
-
-We now provide further details about the implementation of our code.
-To recover the polynomials presented in Eq.~\eqref{eq:pols}, we performed 1000 independent runs on a cluster, each involving 1000 particles.
-As can be seen in \eqref{eq:gamman}, we see that what matters the most in the the inverse temperature, but rather the inverse temperature multiplied by the loss function.
-Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed ans adaptive temperature approach, as previously described.
-The acceptance ratio was controlled by the following schedule:
-\begin{equation}
-	\texttt{acceptance\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
-\end{equation}
-which encourages exploration during the early stages of training and gradually transitions to a more selective regime. We initialized the algorithm with 
-\begin{equation}\label{eq:sample10000adaptativetemp}
-	\begin{aligned}
-		&\texttt{n\_epochs = 1000}\,,\\
-		&\texttt{beta = 1e{-6}}\,, \\
-		&\texttt{p\_{modify} = 0.5},\\
-		&\texttt{p\_{multiply} = 0.25},\\
-		&\texttt{p\_{divide} = 0.25}. 
-	\end{aligned}
-\end{equation}
-
-This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
-For the representation of polynomials, we adopt a vectorial approach.
-Specifically, each polynomial is represented as an array of its coefficients $\{c_k\}$, where $k \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of authorized monomials, determined by the chosen maximum degree.
-We also impose a constraint on the maximum number of terms within a single polynomial to promote sparsity.
-An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.
-For the simulations we have done, we chose :
-\begin{equation}
-	\begin{aligned}
-	&\texttt{max\_degree} = 4,\\
-	&\texttt{max\_num\_monomials} = 6.
-\end{aligned}
-\end{equation}
-The time it takes to do a single run in approximately 600s on a regular computer.
-The main results are summarized in Fig.
-\ref{fig:evolutionoftargetreproduction} (a) and (b) and the losses of the run are shown in Fig.
-\ref{fig:evolutionoftargetreproduction} (c).
-%\begin{figure}
-%	\centering
-%	\includegraphics[scale=0.35]{Figures/Loss_all_ASMC.png}
-%	\caption{Losses of all the 1000 runs in shaded blue and the average loss over all run in brown.}
-%	\label{fig:losses_ASMC}
-%\end{figure}
-The frequencies with which each of the polynomials in Eq.~\eqref{eq:pols} was recovered are reported in the table below:
-  \begin{equation}
-  	\label{table:results}
-	\begin{tabular}{c|ccccccccc}
-		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $p_{8}$ &  $\varnothing$  \\\hline\hline
-		Frequency & 92.6\% & 75.0\% & 1.7\% & 51.9\% & 0.7\% & 0.1\% & 0.2\% & 0.7\% & 0.3\% \\\hline\hline
-		Maximum \# of Representant & 1000 & 1000 & 869 & 991 & 710 & 18 & 879 & 207 & $\varnothing$
-
-	\end{tabular}
-\end{equation}
-
-With this approach, the average number of particles reproducing one of the target polynomials at the end of a run is 882, with a standard deviation of 200.
-Moreover, the algorithm typically identifies an average of 2.24 distinct polynomials per run, with a maximum number of 4, demonstrating its capacity to uncover multiple solutions simultaneously.
-Finally the algorithm failed at finding a solution in only 3 runs.
-This is sumed up in Fig.
-\ref{fig:piechart}.
-We see that for $77.4\%$ on the time that the algorithm finds more than a single solution, demonstrating the robustness of the technique.
-
-\begin{figure}[h!]
-	\centering
-	\begin{adjustbox}{width=20cm,center}
-		\begin{minipage}[t]{0.31\paperwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figures/Count_beta_adaptative_temp_indiv}
-			\caption*{(a)}
-		\end{minipage}%
-		\hfill
-		\begin{minipage}[t]{0.31\paperwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figures/Count_good_pol_all}
-			\caption*{(b)}
-		\end{minipage}%
-		\hfill
-		\begin{minipage}[t]{0.31\paperwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figures/Loss_all_ASMC.png}
-			\caption*{(c)}
-		\end{minipage}
-	\end{adjustbox}
-	\caption{{\bfseries \boldmath \texttt{acceptance\_ratio} = 0.8 - 0.5 $\times$ (\texttt{epoch}/\texttt{n\_epochs})} (a) Evolution of the mean number of particles reproducing each target polynomial (log scale).
-(b) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp}.}
-	\label{fig:evolutionoftargetreproduction}
-\end{figure}
-
-In comparaison with state of the art technique, we have used the AIFeynman algorithm on our data set, with again $x_8 = \exp(\tilde{x}_8)$, such that we again look for polynomial expressions.
-We have run it with the following configuration
-\begin{equation}
-	\begin{aligned}
-		&\texttt{BF\_try\_time} = 300, \\
-		&\texttt{polyfit\_deg} = 6, \\
-		&\texttt{NN\_epochs} = 5000.\\
-	\end{aligned}
-\end{equation}
-The first parameter fixes the time limit in seconds for each brute force call, \texttt{polyfit\_deg} gives the maximum degree of the polynomial tried by the polynomial fit routine and \texttt{NN\_epochs} is the number of training epoch for the internal neural network.
-The function used for the brut force tests are
-\begin{equation}
-\texttt{+*-/><} \sim \texttt{\textbackslash R1}
-\end{equation}
-The binary operations are addition, multiplication, substraction and division.
-The unary ones are inverse, increment, decrement, negation and square root.
-Finally there is a nonary one, the unity.
-For more details we refer to \cite{Udrescu:2019mnk}.
-
-In this algorithm, one tries to fit one of the variables in term of the others. Here, we used it to fit $x_{10}$ in terms of the others. The AIFeynman algorithm finds a solution in TIME : 
-\begin{equation}
-	\texttt{x\_10 = 1.414213551821*(x\_4-((x\_1/x\_2)-((x\_1/x\_2)/x\_8))}
-\end{equation}
-which after identifying the numerical factor with $\sqrt 2$ and inverting the relation gives 
-\begin{equation}
-	- \sqrt 2 x_1 + \sqrt 2 x_1 x_8 + x_2 x_8  x_{10} -\sqrt 2 x_2 x_4 x_8 = 0
-\end{equation}
-which corresponds to $p_1$ of Eq.
-\eqref{eq:pols}.
-While the AIFeynman code is able to recover one of the constraints, it exhibits several drawbacks compared to our method.
-First, it is significantly slower: it required TIME (to be specified) compared to approximately 600 seconds for a single run of our ASMC algorithm.
-Moreover, the AIFeynman framework is based on expressing one variable as a function of the others, which assumes the invertibility of the underlying relation.
-In general, this is not guaranteed for the class of polynomials in Eq.
-\eqref{eq:pols}, and obtaining a closed-form inverse can be nontrivial or even impossible for higher-degree expressions.
-In our case, each polynomial involves at most quadratic terms in any single variable, ensuring invertibility, but this property would not hold for more complex models.
-In addition, AIFeynman is limited to recovering one constraint per run, whereas our ASMC method can discover multiple constraints simultaneously.
-This is reflected in our results, where each run identified an average of 2.15 polynomials, with up to 4 found in the best case.
-Finally, the brute-force regression strategy used by AIFeynman makes it less effective for identifying higher-degree polynomials, whose complexity increases the search difficulty.
-In contrast, our method treats all polynomials as equally probable, regardless of their degree, enabling it to uncover more intricate structures more efficiently \footnote{Note that we do not claim that we have used the AIFeynman in the most optimal way.}.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=0.5]{Figures/piechart_results_n_pol_each_run.png}
-	\caption{Pie chart showing the repartition of the number of distinct polynomials found in the runs. Note that there is also the failure case, which corresponds 3 different runs.}
-	\label{fig:piechart}
-\end{figure}
-
-\section{Results}
-\paragraph{Initialisation}
-We initialized the algorithm with 
+\section{Results} \label{sec:results}
+	\subsection{Initialisation of the algorithm}
+	We initialized the algorithm with \ce{Give $\lambda$? Do we have all parameters here?}
 	\begin{equation}	\label{eq:sample10000adaptativetemp}
@@
 	This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
-For the representation of polynomials, we adopt a vectorial approach: each polynomial is represented as an array of its coefficients $\{c_k\}$, where $k \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of available monomials, determined by the chosen maximum degree \texttt{max\_degree}.
-We also impose a constraint on the maximum number of terms within a single polynomial to promote sparsity.
+For the representation of polynomials, we adopt a vectorial approach: each polynomial is represented as an array of its coefficients $\{c_k\}$, where $k \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of available monomials, determined by the chosen maximum degree \texttt{max\_degree} and the number of variables.
+We also impose a constraint on the maximum number of terms within a single polynomial \texttt{max\_num\_monomials} to promote sparsity.
 An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.
@@
 	\end{equation}
-\ce{Give details on the basis of polynomials. 126.}
-
-\paragraph{Typical run}
+	With these parameters and given that we are dealing with $5$ variables, $n_{\text{mon}} = 126$.
+
+	\subsection{Analysis of a typical run}
 	After a run, the 1000 particles are typically distributed into less than 10 different type of polynomials.
-\ce{Check the exact number.} Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
-We select the representant of each type that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}).
+\ce{Check the exact number.
+Update with a new run.} Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
+We select the representative of each type that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}).
 Here is an example of output for a given run: \ce{Here $\texttt{threshold} = 0.1$ and $\texttt{steps} = 1000$ for the local search.}
@@
 	\end{subequations}
-where we normalised the coefficients be setting one of them to $1$ or $2$.
+	where we normalised the coefficients by setting one of them to $1$ or $2$.
 Then, we filter out the polynomials with loss higher than $1$, as the polynomials~\eqref{eq:expol3} and~\eqref{eq:expol4}, which do not annihilate the data.
-As discussed in sec.
-??
-\ce{to do}, the coefficients must be combinations of rational numbers or square roots thereof.
+Given that the coefficients of the gradient $\nabla V$ are only integers and square roots of integers, the coefficients of the polynomials annihilating $\nabla V$ must be combinations of rational numbers or square roots thereof.
 We then deduce from eq.~\eqref{eq:expol1} and~\eqref{eq:expol2} the candidate annihilator polynomials for the above example:
@@
 
-\paragraph{Statistics}
+	\ce{Change of philosophy here: after SR, we select the best particle, and perform local search.
+If loss get very low and coefficient not zero, considered as annihilator polynomial.
+Then filter out the particles containing this polynomial, and repeat on the best particles of the remaining set.
+Keep it concise.
+Maybe plot of the loss for the best particle during local search.}
+
+	\subsection{Statistics}
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
-It takes approximately 600\,s to do a single run on a regular computer.
-\ce{That's without local search, right?} The code finds the 8 different following polynomials:
+It takes approximately 600\,s to do a single run without local search on a regular computer.
+The code finds the 8 different following polynomials: \ce{Sort polynomials in accordance with their frequency.}
 	\begin{subequations} \label{eq:pols}
@@
 	   p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
+	   p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
+	   		- x_{2}x_{4}x_8x_{10},\\
 	   p_{3} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
 	   		- 2\,x_{2} x_{4}^{2}x_8,\\
-   p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
-   		- x_{2}x_{4}x_8x_{10},\\
+	   p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
+	   		- x_{2}^{2}x_{10}, \\
 	   p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
 	   		+ x_{1}x_8x_{10}^{2},\\
+	   p_{8} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\
 	   p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
-   		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},\\
-   p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
-   		- x_{2}^{2}x_{10}, \\
-   p_{8} &= -2 + 4 x_{8} - 2 x_8^2 + 2 x_{4}^2 x_8 - x_8^2 x_{10}^2,
+	   		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},
 	 \end{align}
@@
 	where $x_{8} = e^{\tilde{x}_{8}}$.
-They are found with different frequencies with some polynomials occurring more often than others, as reported in tab.~\ref{table:results}.
-The average number of particles reproducing one of the annihilator polynomials at the end of a run is 882, with a standard deviation of 200.
-Moreover, the algorithm typically identifies an average of $2.24$ distinct polynomials per run, with a maximum number of $4$, demonstrating its capacity to uncover multiple solutions simultaneously.
-Finally, the algorithm failed at finding a solution in only 3 runs.
+They are found with different frequencies, with some polynomials occurring more often than others, as reported in tab.~\ref{table:results}.
+The algorithm typically identifies an average of $2.2$ distinct polynomials per run, with a maximum number of $4$, demonstrating its capacity to uncover multiple solutions simultaneously.
+The algorithm failed at finding a solution in only 3 runs.
 This is summed up in fig.~\ref{fig:piechart}.
-We see that for $77.4\%$ on the time that the algorithm finds more than a single solution, demonstrating the robustness of the method.
-
-\begin{figure}
-	\centering
-	\input{Figures/Piechart_n_pols.pgf}
-	\caption{Pie chart of the repartition of the number of distinct polynomials found in a run.}
-	\label{fig:piechart}
-\end{figure}
+Note that in $77\%$ of the time the algorithm finds more than a single solution, demonstrating the robustness of the method.
 
@@
 		\begin{tabular}{c|ccccccccc}
-		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $p_{8}$ &  $\varnothing$  \\\hline\hline
-		Frequency & 92.6\% & 75.0\% & 1.7\% & 51.9\% & 0.7\% & 0.1\% & 0.2\% & 0.7\% & 0.3\% \\
-		Maximum \# of representatives & 1000 & 1000 & 869 & 991 & 710 & 18 & 879 & 207 & --
+			& $p_{1}$ & $p_{2}$ & $p_{4}$ & $p_{3}$ & $p_{7}$ & $p_{5}$ & $p_{8}$  & $p_{6}$&  $\varnothing$  \\\hline\hline
+			Frequency & 92.6\% & 75.0\% & 51.9\% & 1.7\% & 0.2\% & 0.7\% & 0.7\% & 0.3\% & 0.1\% \\
+			Maximum \# of representatives & 1000 & 1000 & 991 & 869 & 879 & 710 & 207 & 18 & --
 		\end{tabular}
@@
 
-The dynamics of appearance of each annihilator polynomial is plotted in fig.~\ref{fig:evolutionoftargetreproduction}(a), together with the evolution of the inverse temperature $\beta$, averaged on the 1000 runs.
-Note that the dynamics depend strongly on the polynomial, some of the appearing after only few dozens of epochs, and others just before the end of the runs.
-\ce{The polynomials are organize in three classes, the first ones appear after typically a dozen of iteration, the second one after 100 and the last one are very difficult to find and rare.
-The code favors the polynomials with lowest loss through resampling.
-Du fait de la structure, quand un polynome est trouvé il est favorisé au détriment des autres (resampling).
-Faire une figure ?} The evolution of the inverse temperature, imposed by eq.~\eqref{eq:acceptanceratioschedule}, is polynomial.
-\ce{Do a fit.}.
-\ce{At the end beta is not 1.
-This allows to find more than one candidate polynomials, favors the diversity.
-This is linked to the choice of the acceptance ration at the end.
-The lower the acceptance ration, the higher beta.
-If ratio too low, no diversoty.
-If ratio too high, shitty polynomials.} The losses of the runs are shown in fig.~\ref{fig:evolutionoftargetreproduction}(c).
-\ce{Describe more the loss?
-It is the best loss at each step.
-Use the loss to show that we indeed converged}.
+	\begin{figure}
+		\centering
+		\input{Figures/Piechart_n_pols.pgf}
+		\caption{Pie chart of the repartition of the number of distinct polynomials found in a single run.}
+		\label{fig:piechart}
+	\end{figure}
+
+	We have tracked the appearance of the polynomials~\eqref{eq:pols} during each of the 1000 runs.
+To do so, we have counted at each epoch the number of particles including the same monomials as the annihilator polynomials.\footnote{Thus, a particle featuring the same monomials as one of the polynomials~\eqref{eq:pols} will be counted, even if the coefficients do not match, and if there are additional monomials.} The total number of particles reproducing at least one of the annihilator polynomials listed in eq.~\eqref{eq:pols} is plotted in fig.~\ref{fig:count_pol_all_beta}, together with the evolution of the inverse temperature $\beta$, both averaged on the 1000 runs.
+The proportion of annihilator polynomials among the particles start to be significant after approximately 700 epochs.
+It then increases quickly and, towards the end of each run, an average of $88\%$ of the particles do reproduce one of the annihilator polynomials, with a standard deviation of $20\%$.
+The evolution of this proportion is explained by the structure of the method: the code favours the particles with highest weights, and thus those that cause a significant improvement to the loss function, at each resampling.
+Once an annihilator polynomials is reached, it colonises larger and larger proportions of the particles at each resampling.
+
+	The evolution of the inverse temperature is dictated by eq.~\eqref{eq:acceptanceratioschedule}.
+Note that $\beta$ is equal to $0.02$ in average at the end of the runs.
+The temperature is thus still quite high, which favours diversity.
+This is a key ingredient to get more than one candidate polynomials per run.
+The end value of $\beta$ is intimately linked to the choice of target acceptance ratio in eq.~\eqref{eq:acceptanceratioschedule}: the lower the acceptance ratio, the higher the inverse temperature $\beta$.
+On the one hand, if the ratio is too low, very few particles get mutated and it's difficult to explore the space of polynomials and to have diverse outputs.
+On the other hand, if the ratio is too high, there are too many mutations: the output features a large number of polynomials, but lots of them do not converge to an annihilator polynomials because the algorithm is not selective enough.
+It is a matter of balance between exploration and exploitation.
+
+	The dynamics of appearance of each annihilator polynomial is plotted in fig.~\ref{fig:count_pol_indiv}, averaged on the 1000 runs.
+The dynamics depend strongly on the polynomial and we observe three different classes.
+In the first case, for $p_{1}, p_{2}$ and $p_{4}$, the first occurrences appear typically after only few dozen of epochs; and in the the second one, constituted of $p_{3}, p_{5}, p_{7}$ and $p_{8}$, after few hundreds of epochs.
+The last class has $p_{6}$ as its only representative.
+This polynomial is very difficult to produce, and when it appears it is only towards the end of the runs.
+The stair-step patterns, with sudden jumps in the population of the polynomials alternating with phases of stagnation, are due to the use of resampling in the algorithm.
+When a particle get close enough to an annihilating polynomials, its loss gets lowered significantly faster than the one of the other particles.
+This induces an increase of its weight and it will populate a large part of the sample at the next resampling.
+The coefficients get improved during the stagnation phases, inducing an increase of the polynomials weights, and thus even larger colonizations during the following resamplings.
+This also induces a competition between the annihilator polynomials, the ones that get bettered the more easily (typically those with fewest terms) are favoured.
+This mechanism explains the decrease in the averaged population of the polynomial $p_{8}$ observed after 800 epochs in fig.~\ref{fig:count_pol_indiv}.
+
+	The best loss for each of the 1000 runs is shown in fig.~\ref{fig:lossallASMC} in blue, together with their mean value in yellow, with a logarithmic $y$-axis.
+The losses here do include the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}.
+For a given run, we are plotting the best loss at each epoch, the curves thus do not follow single particles.
+On average the loss get bettered by two orders of magnitude during a run, illustrating the convergence of the algorithm.
+\ce{Discuss the fact that it's still high.
+Also linked to the low $\beta$.
+Sufficient to distinguish good polynomials using local search.}
 
@@
 		\caption{(a) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp} (left scale) and evolution of the inverse temperature $\beta$ and its $1\sigma$ deviation (right scale).
-(b) Dynamics of the mean number of particles reproducing each polynomial in eq.~\eqref{eq:pols} (the scale of the $y$ axis is logarithmic).}
+(b) Dynamics of the mean number of particles reproducing each polynomial in eq.~\eqref{eq:pols} (the scale of the $y$-axis is logarithmic).}
 		\label{fig:evolutionoftargetreproduction}
@@
 		\includegraphics[scale=0.75]{Figures/Loss_all_ASMC_1000runs_13.pdf}
-	\caption{Evolution of the losses during the runs (in blue) and their average (in yellow).}
+		\caption{Evolution of the lowest loss during each of the 1000 runs (in blue) and their average (in yellow).
+The losses are computed with the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}.}
 		\label{fig:lossallASMC}
@@
 
-\ce{Tests sur le gradient analytique pour voir si c'est un polynome annulateur. {\bfseries Say more. Add legend?}}
-
-\paragraph{Comparison with AIFeynman}
+	\subsection{Supergravity solution}
+	In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in eq.~\eqref{eq:pols}.
+We know from sec.~\ref{sec:gadientlocalanalysis} that the manifold we are aiming at parametrising is three-dimensional.
+As the parameter space is of dimension $5$, we only need two constraints to define the solutions, and the eight polynomials of eq.~\eqref{eq:pols} are not independent.
+We are however only interested in finding an analytic parametrisation of the solutions manifold, and the easiest to find it is to solve the system
+	\begin{equation}\label{eq:solvepol}
+		p_i = 0, \quad \forall i \in {1,\dots,8}.
+	\end{equation}
+	This leads to the following rules between the parameters:
+	\begin{equation}\label{eq:rulex8x10}
+		\begin{cases}
+			\displaystyle e^{\tilde{x}_{8}} = \frac{x_{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
+			\displaystyle x_{10} = \sqrt{2}\,x_{4}\,\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
+		\end{cases}
+	\end{equation}
+	Alternatively, the system can be recast as:
+	\begin{equation}
+		\begin{cases}
+			\displaystyle x_{1} = \frac{x_{2}}{e^{\tilde{x}_{8}}-1}\,\Big(x_{4}\,e^{\tilde{x}_{8}} \pm \sqrt{-1+\big(2+x_{4}^{2}\big)\,e^{x_{8}}-e^{2\tilde{x}_{8}}}\Big),\\[8pt]
+			\displaystyle x_{10} = \mp\,e^{-\tilde{x}_{8}}\,\sqrt{-2+2\,\big(2+x_{4}^{2}\big)\,e^{\tilde{x}_{8}}-2\,e^{2\tilde{x}_{8}}},
+		\end{cases}
+	\end{equation}
+	or
+	\begin{equation}
+		\begin{cases}
+			\displaystyle x_{1} = \frac{x_{2}}{\sqrt{2}}\,\frac{e^{\tilde{x}_{8}/2}}{e^{\tilde{x}_{8}}-1}\,\Big(-x_{10}\,e^{\tilde{x}_{8}/2} \pm \sqrt{2-4\,e^{\tilde{x}_{8}}+e^{2\tilde{x}_{8}}\big(2+x_{10}^{2}\big)}\Big),\\[8pt]
+			\displaystyle x_{4} = \pm \frac{e^{-x_{8}/2}}{\sqrt{2}}\,\sqrt{2-4\,e^{\tilde{x}_{8}}+e^{2\tilde{x}_{8}}\big(2+x_{10}^{2}\big)}.
+		\end{cases}
+	\end{equation}
+	As anticipated, this defines a three-parameter manifold.
+We tested analytically that $\nabla V = 0$ for any of these rules.
+The three-parameter manifold then corresponds defines a three-dimensional space of flat directions of the half-maximal supergravity scalar potential.\footnote{One might argue that only two of the eight polynomials are sufficient to fully characterize the solution.
+That is, choosing any pair $(i,j) \in {1, \dots, 8}$ may suffice to extract a complete description.
+In practice, this is not entirely accurate.
+While such a pair can yield partial constraints -- for example, recovering eq.~\eqref{eq:rulex8x10} -- it may also produce alternative (and potentially less general) parameterisations.
+Upon inspection, all such partial rules are found to be consistent with, and included in, the most general expressions given in eq.~\eqref{eq:rulex8x10}.}
+
+	The supergravity solution can be shown to preserve a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.
+Using the parametrisation~\eqref{eq:rulex8x10}, the $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
+	\begin{equation}
+		x_{1} = r\cos(\theta)\cos(\Phi), \quad x_{2} = r\cos(\theta)\sin(\Phi) \quad {\rm and} \quad x_{4} = r\sin(\theta),
+	\end{equation}
+	for which the Zamolodchikov metric reads
+	\begin{equation}
+		\d^{2}s_{\rm Zam.} = -\,\d r^{2} - r^{2}\,\bigg(\d \theta^{2} - r\cos(\theta)\,\d \theta\d\Phi + \sin(\theta)\,\d r\d\Phi + \frac{1}{2}\,\big(3+r^{2}-\cos(2\theta)\big)\,\d\Phi^{2} \bigg).
+	\end{equation}
+
+\section{Conclusion}
+
+In this work, we have presented a novel machine learning approach to systematically identify and characterize flat directions in supergravity scalar potentials.
+Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (1,1) supergravity derived from
+$AdS_3 \times S^3 \times T^4$ compactifications of IIB supergravity.
+
+We developed a robust pipeline that transitions from numerical exploration to analytical understanding.
+The gradient descent procedure successfully samples the flat direction manifold, while local PCA analysis reveals its intrinsic dimensionality.
+Most notably, our annealed importance sampling approach to symbolic regression automatically discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
+
+Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold, with one direction potentially gauge-fixable.
+The discovered solution preserves $U(1) \times U(1)$ gauged symmetry and exhibits a rich spectrum structure.
+The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold.
+
+The method demonstrates remarkable efficiency and reliability.
+The algorithm discovers eight distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
+Futhermore, upon 1000 the algorithm failed at finding any solution in only 3 cases, demonstrating the robustness of the method.
+
+This approach opens several promising avenues for advancement.
+The scalability to higher-dimensional cases represents the most immediate challenge and opportunity.
+By increasing the number of particles, refining the annealing schedule, and optimizing polynomial search strategies, we anticipate extending this methodology to the full 13-scalar theory and potentially to other supergravity models.
+
+Beyond technical improvements, this work suggests a broader paradigm for exctrating conformal manifolds in string theory and supergravity.
+This analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
+
+The marriage of machine learning techniques with traditional supergravity analysis represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
+As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
+
+While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
+
+\appendix
+\section{Comparison with AIFeynman} \ce{Appendix?}
 In comparaison with state of the art technique, we have used the AIFeynman algorithm on our data set, with again $x_8 = \exp(\tilde{x}_8)$, such that we again look for polynomial expressions.
@@
 In contrast, our method treats all polynomials as equally probable, regardless of their degree, enabling it to uncover more intricate structures more efficiently \footnote{Note that we do not claim that we have used the AIFeynman in the most optimal way.}.
-
-\paragraph{Supergravity}
-%\begin{itemize}[label=\textbullet]
-%	\item For each couple of candidate polynomials, we get the same expression for the solution, and it indeed defines a unique vacuum of the 3d SUGRA.
-%	\item Discussion of the vacuum: gauge group, Zham. metric, change of variables, 3d spectrum (and stability), spin 2 spectrum on $S^{3}$, one parameter seems to be a gauge parameter, uplift?
-%\end{itemize}
-
-%For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
-%\begin{equation}
-%	\begin{cases}
-	%		p_{i} = 0, \\
-	%		p_{j} = 0,
-	%	\end{cases}
-%\end{equation}
-%gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
-
-In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in Eq.~\ref{eq:pols}.
-We can now solve the system
-\begin{equation}\label{eq:solvepol}
-	p_i = 0, \quad \forall i \in {1,\dots,7}
-\end{equation}
-which leads to the following expressions:
-\begin{equation}
-	\begin{cases}
-		\displaystyle x_{1} = \frac{x_{2}}{\sqrt{2}}\,\frac{e^{x_{8}/2}}{e^{x_{8}}-1}\,\Big(-x_{5}\,e^{x_{8}/2} + \sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}\Big),\\[8pt]
-		\displaystyle x_{4} = \frac{e^{-x_{8}/2}}{\sqrt{2}}\,\sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}.
-	\end{cases}
-\end{equation}
-
-Alternatively, the system can be recast as:
-\begin{equation}\label{eq:rulex8x10}
-	\begin{cases}
-		\displaystyle \tilde{x}_{8} = \frac{x{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
-		\displaystyle x_{10} = \sqrt{2},x_{4},\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
-	\end{cases}
-\end{equation}
-
-As anticipated, this defines a three-parameter solution corresponding to a three-dimensional slice of the half-maximal supergravity scalar potential.
-
-Let us make a few remarks at this stage.
-First, it is possible to find solutions to Eq.~\ref{eq:solvepol} which, however, are not solutions of $\nabla V = 0$.
-For instance $x_1 = x_2 = 0$; such cases are excluded, as they do not satisfy the stationarity condition and therefore do not correspond to valid physical solutions.
-
-Secondly, one might argue that only two of the seven polynomials are sufficient to fully characterize the solution.
-That is, choosing any pair $(i,j) \in {1, \dots, 7}$ may suffice to extract a complete description.
-In practice, this is not entirely accurate.
-While such a pair can yield partial constraints—for example, recovering Eq.\ref{eq:rulex8x10}—it may also produce alternative (and potentially less general) parameterizations.
-Upon inspection, all such partial rules are found to be consistent with, and included in, the most general expressions given in Eq.\ref{eq:rulex8x10}.
-
-The solution preserves a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.
-
-%\paragraph{Moduli space}
-The $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
-\begin{equation}
-	x_{1} = r\cos(\theta)\cos(\Phi), \quad x_{2} = r\cos(\theta)\sin(\Phi) \quad {\rm and} \quad x_{4} = r\sin(\theta),
-\end{equation}
-for which the Zamolodchikov metric reads
-\begin{equation}
-	\d^{2}s_{\rm Zam.} = -\,\d r^{2} - r^{2}\,\bigg(\d \theta^{2} - r\cos(\theta)\,\d \theta\d\Phi + \sin(\theta)\,\d r\d\Phi + \frac{1}{2}\,\big(3+r^{2}-\cos(2\theta)\big)\,\d\Phi^{2} \bigg).
-\end{equation}
-\ce{Tests other change of variables? Test choices of variables other than $(x_{1},x_{2},x_{4})$?}
-
-\paragraph{Bosonic spectrum}
-Vector fields:
-\begin{equation}
-	\begin{aligned}	
-		m_{\sst{(1)}}\ell_{\rm AdS}:\quad &
-		0\ [2],	\quad
-		-2\ [5],	\quad
-		2\ [1],	\\[5pt]
-		&	-1\pm\sqrt{\left(1+r^2\right)^2-2\,r^2\,\cos(2\theta)}\ [2+2],	\\[5pt]
-		&	1\pm\sqrt{1+4\,r^2+r^{4}}\ [2+2].
-	\end{aligned}
-\end{equation}
-The integers between square brackets indicate the multiplicity of each eigenvalue.
-The spectrum includes two massless vectors corresponding to the unbroken ${\rm U}(1)\times {\rm U}(1)$ gauge symmetry, although in three dimensions they are non-propagating.
-
-Scalars:
-\begin{equation}
-	\begin{aligned}	
-		\left(m_{\sst{(0)}}\ell_{\rm AdS}\right)^2:\quad&
-		0\ [5],	\quad
-		8\ [1],	\quad
-		r^{2}\,\left(4+r^2\right)\ [8],	\\[5pt]
-		&	2r\,\Big(3\,r+r^{3}\pm(2+r^{2})\,\sqrt{2+r^2-2\,\cos(2\theta)}-r\cos(2\theta)\Big)\ [2+2].
-	\end{aligned}
-\end{equation}
-
-Gravitini:
-\begin{equation}
-	m_{{(\nicefrac32)}}\ell_{\rm AdS}:\quad 
-	\quad \dfrac1{2}\bigg[1\pm\sqrt{4+2\,r^{2}+r^{4}-2r^{2}\cos(2\theta)}\bigg]\ [4+4],
-\end{equation}
-no SUSY enhancements other than $r=0$.
-
-No dependence on $\Phi$.
-
-\section{Conclusion}
-
-In this work, we have presented a novel machine learning approach to systematically identify and characterize flat directions in supergravity scalar potentials.
-Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (1,1) supergravity derived from
-$AdS_3 \times S^3 \times T^4$ compactifications of IIB supergravity.
-
-We developed a robust pipeline that transitions from numerical exploration to analytical understanding.
-The gradient descent procedure successfully samples the flat direction manifold, while local PCA analysis reveals its intrinsic dimensionality.
-Most notably, our annealed importance sampling approach to symbolic regression automatically discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
-
-Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold, with one direction potentially gauge-fixable.
-The discovered solution preserves $U(1) \times U(1)$ gauged symmetry and exhibits a rich spectrum structure.
-The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold.
-
-The method demonstrates remarkable efficiency and reliability.
-The algorithm discovers eight distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
-Futhermore, upon 1000 the algorithm failed at finding any solution in only 3 cases, demonstrating the robustness of the method.
-
-This approach opens several promising avenues for advancement.
-The scalability to higher-dimensional cases represents the most immediate challenge and opportunity.
-By increasing the number of particles, refining the annealing schedule, and optimizing polynomial search strategies, we anticipate extending this methodology to the full 13-scalar theory and potentially to other supergravity models.
-
-Beyond technical improvements, this work suggests a broader paradigm for exctrating conformal manifolds in string theory and supergravity.
-This analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
-
-The marriage of machine learning techniques with traditional supergravity analysis represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
-As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
-
-While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
-
-\appendix
-\section{Supergravity solutions}
-%\begin{itemize}[label=\textbullet]
-%	\item For each couple of candidate polynomials, we get the same expression for the solution, and it indeed defines a unique vacuum of the 3d SUGRA.
-%	\item Discussion of the vacuum: gauge group, Zham. metric, change of variables, 3d spectrum (and stability), spin 2 spectrum on $S^{3}$, one parameter seems to be a gauge parameter, uplift?
-%\end{itemize}
-
-%For every couples $(p_{i},p_{j})$ of polynomials in eq.~\eqref{eq:pols}, the system
-%\begin{equation}
-%	\begin{cases}
-	%		p_{i} = 0, \\
-	%		p_{j} = 0,
-	%	\end{cases}
-%\end{equation}
-%gives the same solution \ce{That's not true! For example, $x_{1}=x_{2}=0$ solves all polynomials but is not a sugra solution. Mention tests on the sugra?}
-
-In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in Eq.~\ref{eq:pols}.
-We can now solve the system
-\begin{equation}\label{eq:solvepol}
-	p_i = 0, \quad \forall i \in {1,\dots,7}
-\end{equation}
-which leads to the following expressions:
-\begin{equation}
-	\begin{cases}
-		\displaystyle x_{1} = \frac{x_{2}}{\sqrt{2}}\,\frac{e^{x_{8}/2}}{e^{x_{8}}-1}\,\Big(-x_{5}\,e^{x_{8}/2} + \sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}\Big),\\[8pt]
-		\displaystyle x_{4} = \frac{e^{-x_{8}/2}}{\sqrt{2}}\,\sqrt{2-4\,e^{x_{8}}+e^{2x_{8}}\big(2+x_{10}^{2}\big)}.
-	\end{cases}
-\end{equation}
-
-Alternatively, the system can be recast as:
-\begin{equation}\label{eq:rulex8x10}
-	\begin{cases}
-		\displaystyle \tilde{x}_{8} = \frac{x{1}^{2}+x_{2}^{2}}{x_{2}^{2} + \big(x_{1}-x_{2}x_{4}\big)^{2}},\\[10pt]
-		\displaystyle x_{10} = \sqrt{2},x_{4},\frac{x_{2}^{2} - x_{1}^{2}+x_{1}x_{2}x_{4}}{x_{1}^{2}+x_{2}^{2}}.
-	\end{cases}
-\end{equation}
-
-As anticipated, this defines a three-parameter solution corresponding to a three-dimensional slice of the half-maximal supergravity scalar potential.
-
-Let us make a few remarks at this stage.
-First, it is possible to find solutions to Eq.~\ref{eq:solvepol} which, however, are not solutions of $\nabla V = 0$.
-For instance $x_1 = x_2 = 0$; such cases are excluded, as they do not satisfy the stationarity condition and therefore do not correspond to valid physical solutions.
-
-Secondly, one might argue that only two of the seven polynomials are sufficient to fully characterize the solution.
-That is, choosing any pair $(i,j) \in {1, \dots, 7}$ may suffice to extract a complete description.
-In practice, this is not entirely accurate.
-While such a pair can yield partial constraints—for example, recovering Eq.\ref{eq:rulex8x10}—it may also produce alternative (and potentially less general) parameterizations.
-Upon inspection, all such partial rules are found to be consistent with, and included in, the most general expressions given in Eq.\ref{eq:rulex8x10}.
-
-The solution preserves a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.
-
-%\paragraph{Moduli space}
-The $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
-\begin{equation}
-	x_{1} = r\cos(\theta)\cos(\Phi), \quad x_{2} = r\cos(\theta)\sin(\Phi) \quad {\rm and} \quad x_{4} = r\sin(\theta),
-\end{equation}
-for which the Zamolodchikov metric reads
-\begin{equation}
-	\d^{2}s_{\rm Zam.} = -\,\d r^{2} - r^{2}\,\bigg(\d \theta^{2} - r\cos(\theta)\,\d \theta\d\Phi + \sin(\theta)\,\d r\d\Phi + \frac{1}{2}\,\big(3+r^{2}-\cos(2\theta)\big)\,\d\Phi^{2} \bigg).
-\end{equation}
-\ce{Tests other change of variables? Test choices of variables other than $(x_{1},x_{2},x_{4})$?}
-
-\paragraph{Bosonic spectrum}
-Vector fields:
-\begin{equation}
-	\begin{aligned}	
-		m_{\sst{(1)}}\ell_{\rm AdS}:\quad &
-		0\ [2],	\quad
-		-2\ [5],	\quad
-		2\ [1],	\\[5pt]
-		&	-1\pm\sqrt{\left(1+r^2\right)^2-2\,r^2\,\cos(2\theta)}\ [2+2],	\\[5pt]
-		&	1\pm\sqrt{1+4\,r^2+r^{4}}\ [2+2].
-	\end{aligned}
-\end{equation}
-The integers between square brackets indicate the multiplicity of each eigenvalue.
-The spectrum includes two massless vectors corresponding to the unbroken ${\rm U}(1)\times {\rm U}(1)$ gauge symmetry, although in three dimensions they are non-propagating.
-
-Scalars:
-\begin{equation}
-	\begin{aligned}	
-		\left(m_{\sst{(0)}}\ell_{\rm AdS}\right)^2:\quad&
-		0\ [5],	\quad
-		8\ [1],	\quad
-		r^{2}\,\left(4+r^2\right)\ [8],	\\[5pt]
-		&	2r\,\Big(3\,r+r^{3}\pm(2+r^{2})\,\sqrt{2+r^2-2\,\cos(2\theta)}-r\cos(2\theta)\Big)\ [2+2].
-	\end{aligned}
-\end{equation}
-
-Gravitini:
-\begin{equation}
-	m_{{(\nicefrac32)}}\ell_{\rm AdS}:\quad 
-	\quad \dfrac1{2}\bigg[1\pm\sqrt{4+2\,r^{2}+r^{4}-2r^{2}\cos(2\theta)}\bigg]\ [4+4],
-\end{equation}
-no SUSY enhancements other than $r=0$.
-
-No dependence on $\Phi$.
-
 \newpage

### 2025-07-24 Draft_MLFlatDirections.tex
Update of the clustering section and figures, and of the section describing a single run. Polynomials reorder according to the frequencies.

@@
 Consider for example the intersection of two lines: at the intersection point, the local dimension estimated by the previous PCA algorithm would be 2.
-To rule out this possibility, we apply a clustering algorithm, based on local density, on the points with tangent spaces of dimension 3 only.
+To rule out this possibility, we apply a clustering algorithm on the points with tangent spaces of dimension 3 only, as identified by the PCA with $k=20$.
 This, way, we remove the possible intersection points with local dimension 4 or 5.
-For the purpose of the clustering, we used the HDBSCAN algorithm\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation~\cite{10.1007/978-3-642-37456-2_14}.
+For the purpose of the clustering, we use the density-based algorithm HDBSCAN~\cite{10.1007/978-3-642-37456-2_14}.
+%\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation~\cite{10.1007/978-3-642-37456-2_14}.
 Briefly, it is a density-based clustering method that extends DBSCAN by converting it into a hierarchical clustering algorithm and then extracting a flat clustering based on the stability of clusters.}.
-
-	We set the minimum cluster size to 10 points.
-\ce{Redo explanations here, with the new data.
-Explain results with the fact that the algo is density based?
-Try to depopulate a bit the center?
-By randomly removing points?} \ce{Give the choice for $k$: $20$.} Out of the 98,606 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.
-
-	The smallest cluster (10 points) is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
-The last group, comprising 6,849 points, consists of points that the algorithm could not assign to any cluster.
-We interpret these as outliers or edge points rather than representatives of a separate manifold.
-	What the algorithm does indicate, however, is that over 90\% of the data belongs to a single dominant cluster. In Fig.~\ref{3dplots}, we show 3D projections of the data to visualize the clustering. 
-	\begin{figure}[h!]
+	As it can be observed in fig.~\ref{triangular_plot_1_2_4_8_10}, the points obtained after the gradient descent are denser around the origin, leading the algorithm to disregard points with a norm greater than 1.
+To avoid this effect, we de-sample the densest areas by randomly selecting no more than 10 points per 0.25-sided hyper-cube, and apply the HDBSCAN algorithm on the remaining 72,216 points, with minimum cluster size set to 5 points.
+The algorithm identifies one cluster made of 5 points, one other with 71,993 points, and fails to assign any cluster to 218 points.
+We show in fig.~\ref{fig:3dplots} some 3d projections of the data to visualize the clustering.
+In these scatter plots, orange points belong to the main cluster, while blue points are those that the algorithm failed to assign to any cluster.
+The few yellow points correspond to the smallest cluster of 5 points.
+The size of the different points has been adjusted to facilitate the visualisation.
+From visual inspection, it appears that the unassigned (blue) points lie mostly on the boundary of the sampled region.
+We therefore interpret their unassigned status not as evidence of belonging to another manifold, but rather as a result of insufficient local density near the edges of the dataset.
+The smallest yellow cluster is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
+Thus, the algorithm does indicate that over 99\% of the data belongs to a single dominant cluster.
+
+	\begin{figure}
 		\centering
-		\hspace{-2cm}
-		\includegraphics[scale=0.5]{Figures/3d_plot_x4_x8_x10.png}
-		\includegraphics[scale=0.5]{Figures/3d_plot_x2_x4_x8.png}
-		\caption{3D plots of the data in selected coordinates. Left: $(x_4, x_8, x_{10})$. Right: $(x_2, x_4, x_8)$.}
-		\label{3dplots}
+		\centering
+		\subfigure{ \label{fig:3dx4x8x10}
+			\begin{tikzpicture}
+		  		\draw (0,0) node (fig1) {\includegraphics[scale=0.7, trim = 0.75cm 0 0 1cm, clip]{Figures/3d_plot_x4_x8_x10_21_05_2025_desampled.png}};
+		  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+		  		\draw (9,0) node (fig2) {\includegraphics[scale=0.7, trim = 0.75cm 0 0 1cm, clip]{Figures/3d_plot_x1_x4_x8_21_05_2025_desampled.png}};
+		  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+		  		\draw (3.8,-3) node (leg) {\includegraphics[scale=0.85]{Figures/3d_plot_21_05_2025_desampled_legend.pdf}};
+		  	\end{tikzpicture}
+		}
+		\subfigure{\label{fig:3dx1x4x8}}
+		\caption{3d projections of the data set in selected coordinates: (a) $(x_4, x_8, x_{10})$ and (b) $(x_1, x_4, x_8)$.
+The colors are assigned by the clustering algorithm: the orange and yellow points correspond to two different clusters, while the blue points were not assigned to any cluster.
+The size of each class of points has been tuned to favour the visualisation.}
+		\label{fig:3dplots}
 	\end{figure}
-	In these scatter plots, turquoise points belong to the main cluster, while purple points are those that the algorithm failed to assign.
-In one of the plots, a few yellow points can be seen; these correspond to the smallest cluster of 10 points.
-From visual inspection, it appears that the unassigned (purple) points lie mostly on the boundary of the sampled region.
-We therefore interpret their unassigned status not as evidence of belonging to another manifold, but rather as a result of insufficient local density near the edges of the dataset.
 
 	From this analysis, we conclude that the gradient descent procedure has produced a sampling of a single, connected, three-dimensional manifold.
-
-	\vspace{0.5em}
-
-	After performing both PCA and clustering, we thus find that the data obtained after gradient descent samples a three-dimensional manifold.
-
-	\ce{ICI}
 
@@
 		Once the Annealing loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some more fine tuning.
-To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a pertubation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller.
+To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller.
 This allow to fine-tune the coefficients.
@@
 	\subsection{Initialisation of the algorithm}
-	We initialized the algorithm with \ce{Give $\lambda$? Do we have all parameters here?}
+	We initialized the algorithm with \ce{Do we have all parameters here?}
 	\begin{equation}	\label{eq:sample10000adaptativetemp}
@@
 			&\texttt{p\_{multiply} = 0.25},\\
-			&\texttt{p\_{divide} = 0.25}. 
+			&\texttt{p\_{divide} = 0.25},\\
+			&\texttt{lambda = 1000},\\
+			&\texttt{sigma = 0.1}.
 		\end{aligned}
@@
 
-	\subsection{Analysis of a typical run}
-	After a run, the 1000 particles are typically distributed into less than 10 different type of polynomials.
-\ce{Check the exact number.
-Update with a new run.} Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
-We select the representative of each type that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}).
-Here is an example of output for a given run: \ce{Here $\texttt{threshold} = 0.1$ and $\texttt{steps} = 1000$ for the local search.}
+	\subsection{Analysis of a typical run} \label{sec:singlerun}
+	After a run, the 1000 particles are typically distributed into less than 50 different type of polynomials.
+Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
+We analyse them using the following procedure.
+We select the particle that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}), we fine-tune the coefficients by running a quick exploitation phase of 10,000 steps during which we randomly select a coefficient and modify it with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, with $\sigma_1=0.01$, and keep the new particle only if the loss function (without the regularisation) is getting smaller.
+There are two possible outputs after this phase.
+(i) The coefficients stay finite, and the particle is a candidate annihilator polynomial.
+We then filter out all  particles of the same type as this candidate, as they will ultimately give the same polynomial.
+Or (ii), the coefficients are just getting smaller and smaller during the exploration phase, indicating that the only way to minimize the loss with the given monomials is to have very small coefficients.
+The particle is then disregarded.
+We repeat the same steps on the best particles of the remaining set until we explored all the 1000 particles.
+
+	Here is an example for a given run. The best particle after the Annealing loop is
+	 \begin{equation}
+	 	-0.035\,x_{1} + 0.673\,x_{2} + 0.305\,x_{1}x_{4} + 0.396\,x_{1}x_{10} - 0.630\,x_{2}x_{8} - 0.284\,x_{2}x_{8}x_{10}^{2},
+	 \end{equation}
+	 with loss $L^{(\lambda = 0)} \simeq 2 \times 10^{3}$. The coefficients have been rounded to the nearest thousandth. After 10,000 steps of exploitation, this particle becomes
+	  \begin{equation}
+	 	0.396\,x_{2} + 0.396\,x_{1}x_{4} + 0.280\,x_{1}x_{10} - 0.396\,x_{2}x_{8} - 0.198\,x_{2}x_{8}x_{10}^{2},
+	 \end{equation}
+	 with loss $L^{(\lambda = 0)} \simeq 8 \times 10^{-5}$, or equivalently
+	 \begin{equation} \label{eq:expol1}
+	 	2\,x_{2} + 2.000\,x_{1}x_{4} + 1.415\,x_{1}x_{10} - 2.000\,x_{2}x_{8} - 1.000\,x_{2}x_{8}x_{10}^{2}.
+	 \end{equation}
+	 where we normalised the coefficients by setting the one of $x_{2}$ to $2$.
+We are in case (i),the polynomial is a candidate annihilator polynomial.
+After filtering out the 971 particles that are of the same type, the next best particle is
+	 \begin{equation}
+	 	1.039\,x_{2} + 0.383\,x_{1}x_{4} + 0.466\,x_{1}x_{10} - 0.955\,x_{2}x_{8} - 0.233\,x_{2}x_{10}^{2} - 0.006\,x_{1}x_{2}x_{8}x_{10},
+	 \end{equation}
+	 with a loss $L^{(\lambda = 0)} \simeq 2 \times 10^{3}$. After the exploitation phase, it becomes
+	 \begin{equation}
+	 	0.006\,x_{2} + 0.004\,x_{1}x_{4} + 0.002\,x_{1}x_{10} - 0.006\,x_{2}x_{8} - 0.001\,x_{2}x_{10}^{2},
+	 \end{equation}
+	 with a loss $L^{(\lambda = 0)} \simeq 4 \times 10^{-2}$.
+The loss is low only because the coefficients are themselves very low.
+This is an example of case (ii), we disregard this particle.
+Reproducing similar steps for the remaining particles, we get some uninteresting particles and two new candidate polynomials (with normalised coefficients): \ce{I had to replace $x_{4}$ as given in the data to $x_{4}/2$ to have the right polynomials.}
 	 \begin{subequations}
 	    \begin{align}
-			1.999\,x_{2} - 1.999\,x_{2}x_{8} + 1.414\,x_{1}x_{10} + 1.999\,x_{1}x_{4} - x_{10}^{2}x_{2}x_{8},\quad &L^{(\lambda = 0)} \simeq 2 \times 10^{-4},  \label{eq:expol1}\\
-			2\,x_{2} - 1.999\,x_{2}x_{8} + 1.415\,x_{1}x_{8}x_{10} + 2.001\,x_{1}x_{4}x_{8} - 2.002\,x_{2}x_{4}^{2}x_{8},\quad &L^{(\lambda = 0)} \simeq 3 \times 10^{-3}, \label{eq:expol2}\\
-			x_{1}x_{8}x_{10} + 1.416\,x_{1}x_{4}x_{8} - 1.516\,x_{2}x_{4}^{2}x_{8},\quad &L^{(\lambda = 0)} \simeq 3 \times 10^{2}, \label{eq:expol3}\\
-			2\,x_{2} - 1.972\,x_{2}x_{8} + 0.816\,x_{1}x_{10} + 1.369\,x_{1}x_{4} - 0.442\,x_{10}^{2}x_{2},\quad &L^{(\lambda = 0)} \simeq 3 \times 10^{2}, \label{eq:expol4}
+			1.416\,x_{2} + 1.416\,x_{1}x_{4} - 1.417\,x_{2}x_{8} + x_{1}x_{8}x_{10} - 1.001\,x_{2}x_{4}x_{8}x_{10},\quad &L^{(\lambda = 0)} \simeq 1 \times 10^{-3}, \label{eq:expol2}\\
+			-1.414\,x_{1} + 1.414\,x_{1}x_{8} - 1.414\,x_{2}x_{4}x_{8} + x_{2}x_{8}x_{10},\quad &L^{(\lambda = 0)} \simeq 2 \times 10^{-4}. \label{eq:expol3}
 		\end{align}
 	\end{subequations}
-	where we normalised the coefficients by setting one of them to $1$ or $2$.
-Then, we filter out the polynomials with loss higher than $1$, as the polynomials~\eqref{eq:expol3} and~\eqref{eq:expol4}, which do not annihilate the data.
+
 	Given that the coefficients of the gradient $\nabla V$ are only integers and square roots of integers, the coefficients of the polynomials annihilating $\nabla V$ must be combinations of rational numbers or square roots thereof.
-We then deduce from eq.~\eqref{eq:expol1} and~\eqref{eq:expol2} the candidate annihilator polynomials for the above example:
+We then deduce from eq.~\eqref{eq:expol1}, \eqref{eq:expol2} and~\eqref{eq:expol3} the candidate annihilator polynomials for the above example:
 	\begin{equation}
 		\begin{gathered}
-			2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
-	      2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
-	      		- 2\,x_{2} x_{4}^{2}x_8.
+			2\,x_{2} + 2\,x_{1}x_{4} + \sqrt{2}\,x_{1}x_{10} - 2\,x_{2}x_{8} - x_{2}x_{8}x_{10}^{2},\\
+	      \sqrt{2}\,x_{2} + \sqrt{2}\,x_{1}x_{4} - \sqrt{2}\,x_{2}x_{8} + x_{1}x_{8}x_{10} - x_{2}x_{4}x_{8}x_{10}, \\
+	      -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_{8} - \sqrt{2}\,x_{2}x_{4}x_{8} + x_{2}x_{8}x_{10}.
 		\end{gathered}
 	\end{equation}
-
-	\ce{Change of philosophy here: after SR, we select the best particle, and perform local search.
-If loss get very low and coefficient not zero, considered as annihilator polynomial.
-Then filter out the particles containing this polynomial, and repeat on the best particles of the remaining set.
-Keep it concise.
-Maybe plot of the loss for the best particle during local search.}
 
@@
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
-It takes approximately 600\,s to do a single run without local search on a regular computer.
-The code finds the 8 different following polynomials: \ce{Sort polynomials in accordance with their frequency.}
+It takes approximately 10\,min to do a single run on a regular computer.
+\ce{That's with the local search done as described in the previous section.} The code finds the 8 different following polynomials:
 	\begin{subequations} \label{eq:pols}
@@
 	   p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
-	   p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
+	   p_{3} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
 	   		- x_{2}x_{4}x_8x_{10},\\
-	   p_{3} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
+	   p_{4} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
 	   		- 2\,x_{2} x_{4}^{2}x_8,\\
-	   p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
+	   p_{5} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
 	   		- x_{2}^{2}x_{10}, \\
-	   p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
+	   p_{6} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
 	   		+ x_{1}x_8x_{10}^{2},\\
-	   p_{8} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\
-	   p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
+	   p_{7} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\
+	   p_{8} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
 	   		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},
@@
 	\end{subequations}
+	%%% Previous notations
+	% \begin{subequations} \label{eq:pols}
+	%  \begin{align}
+	%    p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\
+	%    p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
+	%    p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
+	%    		- x_{2}x_{4}x_8x_{10},\\
+	%    p_{3} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
+	%    		- 2\,x_{2} x_{4}^{2}x_8,\\
+	%    p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
+	%    		- x_{2}^{2}x_{10}, \\
+	%    p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
+	%    		+ x_{1}x_8x_{10}^{2},\\
+	%    p_{8} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\
+	%    p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
+	%    		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},
+	%  \end{align}
+	% \end{subequations}
 	where $x_{8} = e^{\tilde{x}_{8}}$.
@@
 		\begin{tabular}{c|ccccccccc}
-			& $p_{1}$ & $p_{2}$ & $p_{4}$ & $p_{3}$ & $p_{7}$ & $p_{5}$ & $p_{8}$  & $p_{6}$&  $\varnothing$  \\\hline\hline
+			& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$  & $p_{8}$&  $\varnothing$  \\\hline\hline
 			Frequency & 92.6\% & 75.0\% & 51.9\% & 1.7\% & 0.2\% & 0.7\% & 0.7\% & 0.3\% & 0.1\% \\
@@
 
-	\begin{figure}
+	\begin{figure}[b!]
 		\centering
@@
 It is a matter of balance between exploration and exploitation.
+
+	\begin{figure}
+		\centering
+		\subfigure{ \label{fig:count_pol_all_beta}
+			\begin{tikzpicture}
+		  		\draw (0,0) node (fig1) {\includegraphics[scale=0.7]{Figures/Count_pol_all_beta_1000runs_13.pdf}};
+		  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
+		  		\draw (8.25,0) node (fig2) {\includegraphics[scale=0.7]{Figures/Count_pol_indiv_1000runs_13.pdf}};
+		  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
+		  	\end{tikzpicture}
+		}
+		\subfigure{\label{fig:count_pol_indiv}}
+		\vspace{-1cm}
+		\caption{(a) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp} (left scale) and evolution of the inverse temperature $\beta$ and its $1\sigma$ deviation (right scale).
+(b) Dynamics of the mean number of particles reproducing each polynomial in eq.~\eqref{eq:pols} (the scale of the $y$-axis is logarithmic).}
+		\label{fig:evolutionoftargetreproduction}
+	\end{figure}
 
@@
 	The best loss for each of the 1000 runs is shown in fig.~\ref{fig:lossallASMC} in blue, together with their mean value in yellow, with a logarithmic $y$-axis.
-The losses here do include the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}.
+The losses here do include the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}, and are given without the exploitation phase discussed in sec.~\ref{sec:singlerun}.
 For a given run, we are plotting the best loss at each epoch, the curves thus do not follow single particles.
 On average the loss get bettered by two orders of magnitude during a run, illustrating the convergence of the algorithm.
-\ce{Discuss the fact that it's still high.
-Also linked to the low $\beta$.
-Sufficient to distinguish good polynomials using local search.}
+The best loss is however quite high at the last epoch.
+This is linked to the very low value of $\beta$: the exploration is favoured on exploitation during all the process.
+Although the loss is high, 1000 epochs are sufficient to select candidate annihilator polynomials thanks to the exploitation phase performed on the best particles, as illustrated in sec.~\ref{sec:singlerun}.
 
 	\begin{figure}
-		\centering
-		\subfigure{ \label{fig:count_pol_all_beta}
-			\begin{tikzpicture}
-		  		\draw (0,0) node (fig1) {\includegraphics[scale=0.7]{Figures/Count_pol_all_beta_1000runs_13.pdf}};
-		  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-		  		\draw (8.25,0) node (fig2) {\includegraphics[scale=0.7]{Figures/Count_pol_indiv_1000runs_13.pdf.pdf}};
-		  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-		  	\end{tikzpicture}
-		}
-		\subfigure{\label{fig:count_pol_indiv}}
-		\vspace{-1cm}
-		\caption{(a) Evolution of the mean number of particles reproducing a target polynomial, along with its $1\sigma$ deviation, for the parameters described in~\eqref{eq:sample10000adaptativetemp} (left scale) and evolution of the inverse temperature $\beta$ and its $1\sigma$ deviation (right scale).
-(b) Dynamics of the mean number of particles reproducing each polynomial in eq.~\eqref{eq:pols} (the scale of the $y$-axis is logarithmic).}
-		\label{fig:evolutionoftargetreproduction}
-	\end{figure}
-
-	\begin{figure}[h!]
 		\centering
@@
 We tested analytically that $\nabla V = 0$ for any of these rules.
-The three-parameter manifold then corresponds defines a three-dimensional space of flat directions of the half-maximal supergravity scalar potential.\footnote{One might argue that only two of the eight polynomials are sufficient to fully characterize the solution.
+The three-parameter manifold then defines a three-dimensional space of flat directions of the half-maximal supergravity scalar potential.\footnote{One might argue that only two of the eight polynomials are sufficient to fully characterize the solution.
 That is, choosing any pair $(i,j) \in {1, \dots, 8}$ may suffice to extract a complete description.
@@
 
-In this work, we have presented a novel machine learning approach to systematically identify and characterize flat directions in supergravity scalar potentials.
-Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression, demonstrating its effectiveness on a 5-scalar subsector of 3d (1,1) supergravity derived from
-$AdS_3 \times S^3 \times T^4$ compactifications of IIB supergravity.
+We have presented a novel machine learning approach to systematically identify and characterise flat directions in supergravity scalar potentials.
+Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression on polynomials.
+We demonstrated its efficiency on a 5-scalar subsector of three-dimensional half-maximal supergravity, derived from the $AdS_3 \times S^3 \times T^4$ compactification of IIB supergravity.
 
 We developed a robust pipeline that transitions from numerical exploration to analytical understanding.
-The gradient descent procedure successfully samples the flat direction manifold, while local PCA analysis reveals its intrinsic dimensionality.
-Most notably, our annealed importance sampling approach to symbolic regression automatically discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
+The gradient descent procedure successfully samples the flat directions manifold, while local PCA analysis reveals its intrinsic dimensionality.
+Most notably, our annealed importance sampling approach to symbolic regression automatically and quickly discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
+The algorithm uncovered eight distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
+Furthermore, upon 1000 runs the algorithm failed at finding any solution in only 3 cases, demonstrating the robustness of the method.
 
@@
 The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold.
-
-The method demonstrates remarkable efficiency and reliability.
-The algorithm discovers eight distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
-Futhermore, upon 1000 the algorithm failed at finding any solution in only 3 cases, demonstrating the robustness of the method.
+\ce{This paragraph has to change given the few information we give on the sugra solution.
+Also, conformal manifold not defined.
+Rather open on the fact that having the analytical definition of the family gives access to its study using sugra and ExFT?}
 
@@
 By increasing the number of particles, refining the annealing schedule, and optimizing polynomial search strategies, we anticipate extending this methodology to the full 13-scalar theory and potentially to other supergravity models.
-
-Beyond technical improvements, this work suggests a broader paradigm for exctrating conformal manifolds in string theory and supergravity.
+This will pave the way to an exhaustive characterisation of the flat directions of these models, with prominent applications to the AdS/CFT correspondence: flat directions of supergravity solutions having a CFT dual are in correspondence with the space of CFT deformations preserving the conformal symmetry (called the conformal manifold).
+
+% Beyond technical improvements, this work suggests a broader paradigm for exctrating conformal manifolds in string theory and supergravity.
 This analytical constraints from numerical data could prove invaluable for classifying flat directions across different theories, understanding moduli stabilization mechanisms, and exploring the landscape of consistent supergravity backgrounds.
@@
 As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
+\ce{Not sure if I agree with the last sentence.
+Maybe we could weaken the statement a bit?}
 
 While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
+\ce{Move above when discussing the sugra solution?}
 

### 2025-07-28 Draft_MLFlatDirections.tex
Update of sec. 2 and new appendix on sugra.

@@
 
-The AdS/CFT correspondence \cite{Maldacena:1997re} stands as one of the most profound dualities in theoretical physics, establishing a remarkable equivalence between gravitational theories in Anti-de Sitter (AdS) spacetimes and conformal field theories (CFTs) living on their boundaries.
+The AdS/CFT correspondence stands as one of the most profound dualities in theoretical physics, establishing a remarkable equivalence between string theory solutions on anti-de Sitter (AdS) spacetimes and conformal field theories (CFTs) living on their boundaries~\cite{Maldacena:1997re}.
 This correspondence has revolutionized our understanding of both quantum gravity and strongly coupled field theories, providing unprecedented insights into the holographic nature of gravity.
-
 Within this holographic framework, supergravity theories in AdS backgrounds serve as the low-energy effective descriptions of string theory compactifications, making them natural laboratories for exploring the gravitational side of the duality.
-Studying the CFT side is very interesting : CFT play a crucial role in statistical physics where they are known to describe phase transitions ; they are also fixed point of Renormalisation Group flow and this is this latter point that is our interest in this paper.
-An interesting question is indeed to know wether those CFT are isolated fixed points of RG flows, or belong to a continous family of CFT's.
-If this is the case, the space of deformations that takes from one CFT to another is called the conformal manifold.
-They are parametrized by exactely marginal operator, or in other words operators whose $\beta$ functions exactly vanish.
-
-From this perspective, the AdS/CFT correspondence relates conformal manifolds on the boundary theory to flat directions in the scalar potential of the dual supergravity theory.
-Along these directions, the scalar field configurations vary continuously while the cosmological constant remains fixed.
-In general, supersymmetry is believed to be necessary for the existence of holographic conformal manifolds, as non-supersymmetric AdS solutions are typically expected to be unstable \cite{Ooguri:2016pdq,Palti:2019pca}.
-However, recent investigations \cite{Giambrone:2021wsm} have identified AdS$_4$ configurations that appear to evade this requirement, with no evidence of standard decay channels—neither perturbative nor non-perturbative—being present.
-In the context of AdS$_3$/CFT$_2$, the situation may be even richer.
-A well-known counterexample has existed for some time \cite{Aharony:2001dp,Dong:2014tsa}, which is well understood from both the field theory and gravitational perspectives.
-More generally, within the supergravity approximation, continuous deformations correspond to classically marginal operators.
-These operators become exactly marginal only if their marginality persists at finite values of both the rank $N$ and the CFT coupling.
-Recent work \cite{Eloy:2024lwn} has demonstrated the existence of families of marginal deformations that are perturbatively stable, using the framework of Exceptional Field Theory (ExFT).
-
-In this work, we propose a novel approach, where we study directly the scalar potential of supergravity.
-As already mentionned, the classical marginal deformations of CFT's in the large $N$ limit, are in correspondance with the flat directions in the potential, i.e.
-when there is a continuous set a scalar fields such that $\nabla V = 0$.
-However, the explicit characterization of these flat directions presents formidable technical challenges.
+The CFT side plays a crucial role in statistical physics, as CFT are known to describe phase transitions ; they are also fixed point of Renormalisation Group flow and this is this latter point that is our interest in this paper.
+An interesting question is indeed to know whether those CFT are isolated fixed points of RG flows, or belong to a continuous family of CFT.
+If this is the case, the space of continuous deformations that takes from one CFT to another is called a conformal manifold.
+These deformations are parametrized by exactly marginal operator, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
+
+From the AdS/CFT correspondence perspective, conformal manifolds on the boundary theory are dual to flat directions in the scalar potential of the dual supergravity theory.
+Along these directions, the scalar field configurations vary continuously while the cosmological constant remains unchanged.
+Supersymmetry is believed to be necessary for the existence of holographic conformal manifolds, as non-supersymmetric AdS solutions are expected to be unstable~\cite{Ooguri:2016pdq,Palti:2019pca}.
+However, recent investigations have identified AdS$_4$ configurations that appear to evade this requirement, with no evidence of standard decay channels -- neither perturbative nor non-perturbative -- being present~\cite{Giambrone:2021wsm}.
+The situation is even richer in the context of AdS$_3$/CFT$_2$, as current-current deformations, given by products $J\bar J$ of (anti-)holomorphic conserved currents, are exactly marginal in two dimensions~\cite{Chaudhuri:1988qb}, although they may break supersymmetry.
+The question of the exact form of the gravity dual to $J\bar J$ deformations is however open.
+A well-known example is given in ref.~\cite{Aharony:2001dp,Dong:2014tsa}, and recent works have demonstrated the existence of vast families of classically marginal deformations of the ${\rm AdS}_{3}\times S^{3}\times {\rm T}^{4}$ and ${\rm AdS}_{3}\times S^{3}\times S^{3}\times S^{1}$ solutions of type IIB supergravity that are perturbatively stable though supersymmetry breaking~\cite{Eloy:2023zzh,Eloy:2023acy,Eloy:2024lwn}.
+These deformations were shown in ref.~\cite{Eloy:2024lwn} to be equivalent to current-current deformations of the worldsheet Wess-Zumino-Witten models~\cite{Gepner:1986wi} describing the undeformed solutions~\cite{Eberhardt:2017pty,Eberhardt:2018ouy}, giving strong indications that their CFT duals arise from $J\bar J$ deformations as well.
+
+Although extensive, the families of deformations found in the aforementioned papers have not exhausted all possibilities for marginal deformations of three-dimensional supergravity solutions.
+A complete classification would require a systematic study of the flat directions in the supergravity scalar potential $V$ that defines the AdS configurations, as those directions are in correspondence with classical marginal deformations of the holographic CFT in the large $N$ limit.
+These flat directions are continuous sets in the space of scalar fields along which the value of the potential stay fixed, \textit{i.e.}  along which $\nabla V = 0$.
+However, the explicit characterization of flat directions presents formidable technical challenges.
 Supergravity scalar potentials, even in truncated models, typically involve dozens of scalar fields with intricate non-linear interactions.
-The resulting expressions for critical points—where all first derivatives vanish—quickly become too complex for traditional symbolic manipulation, rendering analytical approaches computationally intractable.
+The resulting expressions for critical points -- where all first-order derivatives vanish -- quickly become too complex for traditional symbolic manipulation, rendering analytical approaches computationally intractable.
 
@@
 
-In this work, we demonstrate the viability of the aformentionned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of six-dimensional non-chiral $\mathcal{N} = (1,1)$ supergravity on $AdS_3 \times S^3$, or to type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
+In this work, we demonstrate the viability of the aforementioned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of six-dimensional non-chiral $\mathcal{N} = (1,1)$ supergravity on $AdS_3 \times S^3$, or to type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
 Our methodology combines gradient descent sampling of the flat direction manifold with some symbolic regression technique.
-There exist a large litterature on symbolic regression, using methods from genetic programming \cite{koza1994genetic} such as \cite{virgolin2021improving,randall2022bingo,burlacu2019parsimony}, to deep machine learning \cite{petersen2019deep,kamienny2022end}, generative modelling \cite{valipour2021symbolicgpt}, diffusion models \cite{bastiani2025diffusion}, and equation learner with the nodes being symbolic operations \cite{2018arXiv180607259S}.
+There exists a large literature on symbolic regression, using methods from genetic programming \cite{koza1994genetic,virgolin2021improving,randall2022bingo,burlacu2019parsimony}, to deep machine learning \cite{petersen2019deep,kamienny2022end}, generative modelling \cite{valipour2021symbolicgpt}, diffusion models \cite{bastiani2025diffusion}, and equation learner with the nodes being symbolic operations \cite{2018arXiv180607259S}.
 Another state-of-the art algorithm is the AIFeynman methods \cite{Udrescu:2019mnk}.
-They use neural network to identify structure in the dataset (such as translational symmetries, multiplicative separability, compositionality, \dots) to recursively define simpler problems on which they can fit the solutions with polynomials.
+They use neural network to identify structure in the dataset (such as translational symmetries, multiplicative separability, compositionality\dots) to recursively define simpler problems on which they can fit the solutions with polynomials.
 However, in the spirit of trying to build a generalisable method, we develop here our own algorithm, which is based on symbolic regression using an Annealing Importance Sampling method (AIS) \cite{neal1998annealedimportancesampling}.
-In this paper, we will study a 5 parameter truncation, which is itself coming from a 13 parameter consistent truncation of $\mathcal{N} = (1,1)$ 6-dimensional supergravity.
-
-The study of this 5 dimensional parameter potentiel is separated into several parts.
+%In this paper, we will study a 5 parameter truncation, which is itself coming from a 13 parameter consistent truncation of $\mathcal{N} = (1,1)$ 6-dimensional supergravity.
+
+The study of the five-parameter potential is separated into several parts.
 We first use the gradient descent to efficiently sample the underlying conformal manifold.
-Combined with numerical analysis, such as principal component analysis and clustering, we can identify the existence of a 3-dimensional continuous family.
+Combined with numerical analysis, such as principal component analysis and clustering, we can identify the existence of a three-dimensional continuous family.
 We then use an AIS technique combined with a sequential Monte Carlo approach (SMC) \cite{del2006sequential} in order to do symbolic regression.
@@
 We manage to identify 8 of those constraints on the data, not all independent, which once solved gives that two of the embedding coordinates can be expressed in terms of the others.
-This provides an explicit 3 dimensional parameters family
-
+This provides an explicit three-dimensional family of solutions.
+
+\paragraph{}
 The paper is organized as follows.
-Section 2 establishes the supergravity setup, presenting the scalar potential in its full complexity and motivating the truncation to five fields.
-Section 3 details our numerical methodology, covering both the gradient descent sampling procedure and the annealed importance sampling approach to symbolic regression.
-Finally, Section 4 concludes with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
+In sec.~\ref{sec:sugra}, we establish the supergravity setup, presenting the scalar potential in its full complexity and motivating the truncation to five fields.
+Sec.~\ref{sec:numanal} details our numerical methodology, covering both the gradient descent sampling procedure and the annealed importance sampling approach to symbolic regression.
+We present in sec.~\ref{sec:results} our main results, both numerical an analytical.
+Finally, sec.~\ref{sec:ccl} concludes with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
 
 \section{Supergravity setup} \label{sec:sugra}
-Three-dimensional $\mathcal{N}=8$ (half-maximal) gauged supergravity is governed by the Lagrangian
+Three-dimensional $\mathcal{N}=8$ (half-maximal) gauged supergravity is governed by the Lagrangian~\cite{Nicolai:2001ac,deWit:2003ja}
 %
 \begin{equation}	\label{eq: lagrangian_rephrased} 
-	e^{-1}\mathcal{L}=R+\frac1{8}g^{\mu\nu}D_\mu M^{\bM\bN}D_\nu M_{\bM\bN}+e^{-1}\mathcal{L}_{\text{CS}}-V\,,
-\end{equation}
-%
-which comprises the Einstein-Hilbert term $R$, the kinetic term for scalar fields parametrized by the matrix $M_{\bM\bN}$, a Chern-Simons contribution $\mathcal{L}_{\text{CS}}$, and a scalar potential $V$.
-
-The gauging structure is encoded in an embedding tensor that takes the general form
-%
-\begin{equation}	\label{eq: embtensor_rephrased}
-	\Theta_{\bK\bL\vert\bM\bN}=\theta_{\bK\bL\bM\bN}+\frac12\Big(\eta_{\bM[\bK}\theta_{\bL]\bN}-\eta_{\bN[\bK}\theta_{\bL]\bM}\Big)+\theta\,\eta_{\bM[\bK}\eta_{\bL]\bN}\,.
-\end{equation}
-%
-where we have a fully antisymmetric component $\theta_{\bK\bL\bM\bN}=\theta_{[\bK\bL\bM\bN]}$, a symmetric traceless part $\theta_{\bL\bK}=\theta_{(\bL\bK)}$, and a constant parameter $\theta$.
-The metric $\eta_{\bK\bL}$ is the SO(8,4)-invariant bilinear form used for index contractions.
-
-The scalar degrees of freedom parametrize the coset space
+	e^{-1}\mathcal{L}=R+\frac1{8}g^{\mu\nu}D_\mu M^{\bM\bN}D_\nu M_{\bM\bN}+e^{-1}\mathcal{L}_{\text{CS}}-V,
+\end{equation}
+%
+which comprises an Einstein-Hilbert term $R$, a kinetic term for scalar fields parametrized by the matrix $M_{\bM\bN}$, a Chern-Simons contribution $\mathcal{L}_{\text{CS}}$, and a scalar potential $V$, see app.~\ref{app:sugra} for details on the definition of the terms.
+The scalar degrees of freedom parametrise the coset space
 %
 \begin{equation}	\label{eq: scalarcoset_rephrased}
-	\frac{\text{SO}(8,4)}{\text{SO}(8)\times\text{SO}(4)}\,,
-\end{equation}
-%
-through the symmetric matrix $M_{\bK\bL}=\mathcal{V}_{\bK}{}^{\bM}\mathcal{V}_{\bL}{}^{\bN}\delta_{\bM\bN}$, where $\mathcal{V}_{\bK}{}^{\bM}$ represents the coset representative.
-
-The gauge covariant derivatives are constructed using the embedding tensor according to
-%
-\begin{equation}
-	D_\mu =\partial_\mu + A_\mu{}^{\bM\bN}\,\Theta_{\bM\bN\vert\bP\bQ}\, T^{\bP\bQ}\,,
-\end{equation}
-%
-where $A_\mu{}^{\bM\bN}$ are the gauge fields and $T^{\bP\bQ}$ are the generators of the SO(8,4) algebra satisfying
-%
-\begin{equation} \label{eq:so84gen_rephrased}
-	\big(T^{\bar M\bar N}\big){}_{\bar P}{}^{\bar Q} = 2\,\delta_{\bar P}{}^{[\bar M}\,\eta^{\bar N]\bar Q}\,.
-\end{equation}
-%
-The covariant derivative acting on the scalar matrix becomes
-%
-\begin{equation}
-	D_\mu M_{\bM\bN}=\partial_\mu M_{\bM\bN}+4\,A_\mu{}^{\bP\bQ}\,\Theta_{\bP\bQ\vert(\bM}{}^{\bK}\, M_{\bN)\bK}\,,
-\end{equation}
-%
-ensuring gauge invariance of the scalar kinetic terms.
-
-The Chern-Simons contribution is given by
-%
-\begin{equation}
-	{\cal L}_{\rm CS}= -\varepsilon^{\,\mu\nu\rho}\,\Theta_{\bar M\bar N|\bar P\bar Q}\,A_{\mu}{}^{\bar M\bar N}\left(\partial_{\nu}\,A_{\rho}{}^{\bar P\bar Q}  + \frac{1}{3}\, \Theta_{\bar R\bar S|\bar U\bar V}\,f^{\bar P\bar Q,\bar R\bar S}{}_{\bar X\bar Y}\, A_{\nu}{}^{\bar U\bar V} A_{\rho}{}^{\bar X\bar Y} \right)\,,
-\end{equation}
-%
-where $f^{\bar M\bar N,\bar P\bar Q}{}_{\bar K\bar L} = 4\,\delta_{[\bar K}{}^{[\bar M}\eta^{\bar N][\bar P}\delta_{\bar L]}{}^{\bar Q]}$ are the structure constants of the SO(8,4) Lie algebra, and $\varepsilon^{\mu\nu\rho}$ is the three-dimensional Levi-Civita symbol.
-
-The scalar potential can be expressed in terms of the embedding tensor components as
-%
-{\setlength\arraycolsep{1.2pt}
-	\begin{equation}	\label{eq: scalarpot_rephrased}
-		\begin{aligned}
-			V	&=	\frac1{12}\,\theta_{\bK\bL\bM\bN}\theta_{\bP\bQ\bR\bS}\Big(M^{\bK\bP}M^{\bL\bQ}M^{\bM\bR}M^{\bN\bS}-6\,M^{\bK\bP}M^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}\\
-			&\qquad\qquad\qquad\qquad\quad+8\,M^{\bK\bP}\eta^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}-3\,\eta^{\bK\bP}\eta^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}\Big)\\
-			&\quad +\frac1{8}\,\theta_{\bK\bL}\theta_{\bP\bQ}\Big(2\,M^{\bK\bP}M^{\bL\bQ}-2\,\eta^{\bK\bP}\eta^{\bL\bQ}-M^{\bK\bL}M^{\bP\bQ}\Big)+4\,\theta\theta_{\bK\bL}M^{\bK\bL}-32\,\theta^2\,.
-		\end{aligned}
-	\end{equation}
-}
-
-Decomposing SO(8,4) according to 
-%
-\begin{equation}	\label{eq: gl3gradingbar}
-	\begin{aligned}
-		\text{SO}(8,4)	&\longrightarrow	\enspace \text{GL}(3,\mathbb{R})\times\text{SO}(1,1)\times\text{SO}(4)_{\rm global}\,,	\\
-		X^{\bM}		&\longrightarrow	\quad \{X^{\bar m},\; X_{\bar m},\; X^\bzero,\; X_\bzero,\; X^\balpha\}\,,
-	\end{aligned}
-\end{equation}
-where $\bar m\in\llbracket1,3\rrbracket$ and $\balpha\in\llbracket9,12\rrbracket$ label the SL(3, $\mathbb{R}$) and SO(4)$_{\rm global}$ vector representations, respectively.
-In this basis, the SO(8,4)-invariant tensor reads
-%
-\begin{equation}	\label{eq: Paulieta}
-	\eta_{\bM\bN}=
+	\frac{\text{SO}(8,4)}{\text{SO}(8)\times\text{SO}(4)},
+\end{equation}
+%
+through the symmetric matrix $M_{\bK\bL}$.\footnote{In full generality, the coset space of half-maximal supergravity in three dimensions is $\text{SO}(8,p)/\big(\text{SO}(8)\times\text{SO}(p)\big)$, we consider here the case $p=4$ only.} With appropriate gauging (see eq.~\eqref{eq:embedtens}), this $\text{SO}(8,4)$ theory is a consistent truncation of six-dimensional ${\cal N}=(1,1)$ supergravity on $S^{3}$~\cite{Cvetic:2000dm,Deger:2014ofa,Hohm:2017wtr}.
+It features an ${\rm AdS}_{3}$ stationary point at the scalar origin ($M_{\bK\bL}=\delta_{\bK\bL}$, the ${\rm SO}(8,4)$ identity matrix), corresponding to an ${\rm AdS}_{3}\times S^{3}$ solution in 6d.
+In the following, we will be interested in exploring flat directions of the potential $V$, \textit{i.e.} other stationary points that are continuously connected to the origin.
+In three dimensions, the flat directions constitute a family of ${\rm AdS}_{3}$ vacua sharing the same cosmological constant.
+The corresponding solutions in six dimensions are of the form ${\rm AdS}_{3}\times M^{3}$, with $M^{3}$ some deformation of the round sphere $S^{3}$, parametrised by the constant scalars defining the 3d vacua.
+
+We parametrise the scalars of the theory following ref.~\cite{Eloy:2021fhc} (see also app.~\ref{app:sugra} for some details): 13 scalars parametrised by a symmetric ${\rm GL}(3,\mathbb{R})$ matrix $m = \nu\nu^{T}$ where
+\begin{equation} \label{eq:13scalars1}
+	\nu = e^{(6\,\tilde{x}_{7}+3\,\tilde{x}_{8}+\sqrt{3}\,\tilde{x}_{9})/6}
 				\begin{pmatrix}
-		0 & \delta_{\bar m}{}^{\bar n} & 0 & 0 &0\\
-		\delta^{\bar m}{}_{\bar n} & 0 & 0 & 0 &0\\
-		0 & 0 & 0 & 1 & 0\\
-		0 & 0 & 1 & 0 & 0\\
-		0 & 0 & 0 & 0 & -\delta_{\balpha\bbeta}
-	\end{pmatrix}\,.
-\end{equation}
-
-Parametrizing the scalar matrix following \cite{Eloy:2021fhc}, we have for the scalar matrix 
-\begin{equation}	\label{eq: scalarmatrix}
-	M_{\bM\bN}
-	=
-	\begin{pmatrix}
-		m+(\xi^2+\phi)m^{-1}(\xi^2-\phi)+2\xi^2	& 	(\xi^2+\phi)m^{-1}		&	0	&  0  &	-\sqrt2\,[1+(\xi^2+\phi)m^{-1}]\xi	\\
-		m^{-1}(\xi^2-\phi)	& 	m^{-1}	&	0  	&  0  &	-\sqrt2\,m^{-1}\xi	\\
-		0		&	0		&	e^{2\tilde\varphi}	&	0				&	0		\\
-		0		&	0		&	0				&	e^{-2\tilde\varphi}	&	0		\\
-		-\sqrt2\,\xi^T[1+m^{-1}(\xi^2-\phi)]	&	-\sqrt2\,\xi^Tm^{-1}	&	0	&	0	&	1+2\,\xi^Tm^{-1}\xi	\\
-	\end{pmatrix}\,,
-\end{equation}
-which encodes 22 scalars of the theory ($22 = 32 - 10$, with 10 scalars gauge fixed using translations in the gauge group), which have been parametrized by 
-$m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$, $\phi$ a $3\times3$ antisymmetric matrix, $\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$, a dilaton $\tilde{\varphi}$.
-With this parametrization, the potential takes the from ref.~\cite{Eloy:2021fhc}:
+					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
+					0 & e^{-\tilde{x}_{8}} & \frac{e^{-\tilde{x}_{8}}\,x_{12}}{\sqrt{2}} \\
+					0 & 0 & e^{-(\tilde{x}_{8}+\sqrt{3}\,\tilde{x}_{9})/2}
+				\end{pmatrix},
+\end{equation}
+the matrices 
+\begin{equation} \label{eq:13scalars2}
+	\phi = 	\begin{pmatrix}
+					0 & x_{4} & x_{5} \\
+					-x_{4} & 0 & x_{6} \\
+					-x_{5} & -x_{6} & 0
+				\end{pmatrix}, \quad
+	\xi = \begin{pmatrix}
+				0 & 0 & 0 & x_{1} \\
+				0 & 0 & 0 & x_{2} \\
+				0 & 0 & 0 & x_{3}
+			\end{pmatrix}, \quad
+	\xi^{2} = \xi \xi^{T},
+\end{equation}
+and a dilaton $\tilde{\varphi} = \tilde{x}_{13}$. With this parametrization, the potential takes the form:
 \begin{equation} \label{eq:scalarpotential}
@@
 \end{equation}
-where ${\rm T}\left(A,B,C\right)=\varepsilon_{mnp}\,\varepsilon_{qrs}\,A^{mq}B^{nr}C^{ps}$. We can further restrict ourselves to a set of 13 scalars which is still a consistent truncation, with 
-\begin{equation}
-	\begin{aligned}
-		\xi &= \begin{pmatrix}
-					0 & 0 & 0 & x_{1} \\
-					0 & 0 & 0 & x_{2} \\
-					0 & 0 & 0 & x_{3}
-				\end{pmatrix}, \\[5pt]
-		\phi &= \begin{pmatrix}
-					0 & x_{4} & x_{5} \\
-					-x_{4} & 0 & x_{6} \\
-					-x_{5} & -x_{6} & 0
-				\end{pmatrix}, \\[5pt]
-		\tilde{\varphi} &= \tilde{x}_{13}, \\[5pt]
-		\nu &= e^{(6\,\tilde{x}_{7}+3\,\tilde{x}_{8}+\sqrt{3}\,\tilde{x}_{9})/6}
-				\begin{pmatrix}
-					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
-					0 & e^{-\tilde{x}_{8}} & \frac{e^{-\tilde{x}_{8}}\,x_{12}}{\sqrt{2}} \\
-					0 & 0 & e^{-(\tilde{x}_{8}+\sqrt{3}\,\tilde{x}_{9})/2}
-				\end{pmatrix}.
-	\end{aligned}
-\end{equation}
+where ${\rm T}\left(A,B,C\right)=\varepsilon_{mnp}\,\varepsilon_{qrs}\,A^{mq}B^{nr}C^{ps}$.
 For later convenience, we define a thirteen-dimensional vector
@@
 	% \vec{X} = (x_1,\dots,x_6,\tilde{x}_7,\tilde{x}_8,\tilde{x}_9,x_{10},\dots,x_{12},\tilde{x}_{13})
-	\vec{X} = (x_1, x_{2}, x_{3}, x_{4}, x_{5}, x_6, \tilde{x}_7, \tilde{x}_8, \tilde{x}_9,x_{10}, x_{11}, x_{12}, \tilde{x}_{13})
+	\vec{X} = (x_1, x_{2}, x_{3}, x_{4}, x_{5}, x_6, \tilde{x}_7, \tilde{x}_8, \tilde{x}_9,x_{10}, x_{11}, x_{12}, \tilde{x}_{13}),
 \end{equation}
@@
 
-A first numerical exploration suggests that attention can be focused on the five scalars $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
+\paragraph{}
+The search for flat directions of the potential~\eqref{eq:scalarpotential} can then start form a study of its gradient $\nabla V$.
+However, carrying out the search for stationary points analytically is by far too complex, even reducing the number of variables or using a symbolic solver such as Mathematica~\cite{Mathematica}: the resulting expressions are too complex to be simplified into a manageable form, and do not yield usable relationships that express some variables in terms of others.
+This complexity does not, however, rule out the possibility that simpler solutions satisfying the condition of vanishing gradient may exist although the solver does not find them.
+In this work, we aim to identify such solutions, which we seek using numerical methods.
+This approach has as additional advantage its broader applicability: it would be effective even in cases where an exact analytic expression for the potential is out of reach, like richer theories as the ${\rm SO}(8,8)$ 3d truncations of type IIB supergravity on ${\rm AdS}_{3}\times S^{3} \times {\rm T}^{4}$ or ${\rm AdS}_{3}\times S^{3}\times S^{3}\times S^{1}$.
+
+A first trial and error numerical exploration suggests that attention can be focused on the five scalars $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
 This subset, selected at random from the original set of thirteen scalar fields, serves to render the problem more tractable at the outset.
-It is important to emphasize, however, that this subset does not constitute a consistent truncation of the full theory.
-Consequently, the truncated theory involving only five scalar fields may not constitute a formally consistent truncation of the full thirteen-scalar theory, as higher-order interactions could, in principle, source the remaining scalar modes.
-As a result, the interpretation of the five-scalar theory as a consistent subsector of the original theory may no longer hold.
+The potential~\eqref{eq:scalarpotential} then reduces to
+\begin{equation} \label{eq:scalarpotential124810}
+	\begin{aligned}
+		V &= \frac{1}{4}\, e^{-2\,\tilde{x}_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,\tilde{x}_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
+		  & \quad\qquad\qquad - 4\,e^{3\,\tilde{x}_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
+     			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
+       & \quad\qquad\qquad - 8\,e^{\tilde{x}_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
+     			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
+       & \quad\qquad\qquad + 4\,e^{2\,\tilde{x}_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
+       			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
+       & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,\tilde{x}_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
+	\end{aligned}
+\end{equation}
+To compute the gradient, we exploit the fact that we possess an analytic expression for the scalar potential~\eqref{eq:scalarpotential124810}.
+Note however that it could have been fully done using a numerical approach as automatic differentiations methods.
+It is important to emphasize, however, that the $\{x_{1}, x_{2}, x_{4}, \tilde{x}_{8}, x_{10}\}$ subset does not constitute a consistent truncation of the full theory, as higher-order interactions could, in principle, source the remaining scalar modes.
 Nonetheless, the five-scalar model remains a self-consistent theory in its own right and can be used independently.
 This distinction does not affect our numerical approach: the solutions we obtain remain valid solutions of the complete theory.
-This is because we identify the critical points of the scalar potential by first computing $\nabla V = 0$ with all scalar fields included, and only then setting the remaining fields
+This is because we identify the critical points of the scalar potential by first computing $\nabla V$ with all scalar fields included, \textit{i.e.} using eq.~\eqref{eq:scalarpotential}, and only then setting the remaining fields,
 \begin{equation} \label{eq:defvecy}
-	\vec{y} = (x_3,x_5,x_6,\tilde{x}_7,\tilde{x}_9,x_{11},x_{12},\tilde{x}_{11})
+	\vec{y} = (x_3,x_5,x_6,\tilde{x}_7,\tilde{x}_9,x_{11},x_{12},\tilde{x}_{11}),
 \end{equation}
@@
 
-To compute the gradient, we exploit the fact that we possess an analytic expression for the scalar potential~\eqref{eq:scalarpotential}, which we implement in Mathematica for numerical analysis.
-Note however that it could have been fully done using a numerical approach, automatic differentiations methods (that we will use later to do the gradient descent for the loss function).
-%Under this truncation, the scalar potential~\eqref{eq:scalarpotential} reduces to:
-%\begin{equation} \label{eq:scalarpotential124810}
-%	\begin{aligned}
-%		V &= \frac{1}{8}\, e^{-2\,\tilde{x}_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,\tilde{x}_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
-%		  & \quad\qquad\qquad - 4\,e^{3\,\tilde{x}_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
-%      			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
-%        & \quad\qquad\qquad - 8\,e^{\tilde{x}_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
-%      			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
-%        & \quad\qquad\qquad + 4\,e^{2\,\tilde{x}_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
-%        			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
-%        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,\tilde{x}_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
-%	\end{aligned}
-%\end{equation}
-
-Let us make a comment at this point.
-Since we have an explicit parametrisation of the potential with \eqref{eq:scalarpotential}, one might argue that the problem of identifying flat directions could be addressed by directly computing the gradient of the expression, setting the appropriate scalar fields to zero and subsequently simplifying the resulting equations.
-However, attempting to carry out this procedure using a symbolic solver such as Mathematica quickly reveals its limitations: the resulting expressions are too complex to be simplified into a manageable form, and do not yield usable relationships that express some variables in terms of others.
-This complexity does not, however, rule out the possibility that simpler solutions satisfying the condition of vanishing gradient may exist.
-In this work, we aim to identify such solutions, which we seek using numerical methods.
-
-An additional advantage of this approach is its broader applicability.
-In scenarios where an explicit analytic expression for the potential and its gradient is inaccessible—yet numerical evaluation remains feasible—our method retains its validity.
-In particular, one could replace the analytic gradient by automatic differentiation methods if one can only evaluate the potential.
-Hence, the numerical strategy adopted here may prove effective even in cases where an exact analytic expression for the potential is out of reach.
-\bd{other motivation?
-Example of this ?
-}
-
-\section{Numerical analysis}
+\section{Numerical analysis} \label{sec:numanal}
 To identify the flat directions in the potential, we will use numerical tools.
@@
 
-\section{Conclusion}
-
+\section{Conclusion} \label{sec:ccl}
 We have presented a novel machine learning approach to systematically identify and characterise flat directions in supergravity scalar potentials.
@@
 
+\ce{Open on the use of ExFT to uplift and compute the full KK spectrum.}
+
 \appendix
+\section{Some details on the supergravity setup} \label{app:sugra}
+We give here some details on the supergravity theory described schematically in sec~\ref{sec:sugra}, following ref.~\cite{Nicolai:2001ac,deWit:2003ja}.\footnote{See also ref.~\cite{Eloy:2021qol} for a review.} The Lagrangian is given in eq.~\eqref{eq: lagrangian_rephrased}.
+The gauging structure is encoded in an embedding tensor~\cite{Nicolai:2000sc,deWit:2002vt} that takes the general form
+%
+\begin{equation}	\label{eq: embtensor_rephrased}
+	\Theta_{\bK\bL\vert\bM\bN}=\theta_{\bK\bL\bM\bN}+\frac12\Big(\eta_{\bM[\bK}\theta_{\bL]\bN}-\eta_{\bN[\bK}\theta_{\bL]\bM}\Big)+\theta\,\eta_{\bM[\bK}\eta_{\bL]\bN},
+\end{equation}
+%
+where $\theta_{\bK\bL\bM\bN}=\theta_{[\bK\bL\bM\bN]}$ is fully antisymmetric, $\theta_{\bL\bK}=\theta_{(\bL\bK)}$ is symmetric and traceless, and $\theta$ is a scalar.
+The metric $\eta_{\bK\bL}$ is the SO(8,4)-invariant bilinear form used for index contractions.
+The gauge covariant derivatives are constructed using the embedding tensor according to
+%
+\begin{equation}
+	D_\mu =\partial_\mu + A_\mu{}^{\bM\bN}\,\Theta_{\bM\bN\vert\bP\bQ}\, T^{\bP\bQ},
+\end{equation}
+%
+where $A_\mu{}^{\bM\bN}$ are the gauge fields and
+%
+\begin{equation} \label{eq:so84gen_rephrased}
+	\big(T^{\bar M\bar N}\big){}_{\bar P}{}^{\bar Q} = 2\,\delta_{\bar P}{}^{[\bar M}\,\eta^{\bar N]\bar Q}
+\end{equation}
+%
+are the generators of the $\mathfrak{so}(8,4)$ algebra. The covariant derivative acting on the scalar matrix is thus
+%
+\begin{equation}
+	D_\mu M_{\bM\bN}=\partial_\mu M_{\bM\bN}+4\,A_\mu{}^{\bP\bQ}\,\Theta_{\bP\bQ\vert(\bM}{}^{\bK}\, M_{\bN)\bK},
+\end{equation}
+%
+ensuring gauge invariance of the scalar kinetic terms. The embedding tensor also defines the scalar potential as following~\cite{Samtleben:2019zrh,Schon:2006kz}:
+%
+{\setlength\arraycolsep{1.2pt}
+	\begin{equation}	\label{eq: scalarpot_rephrased}
+		\begin{aligned}
+			V	&=	\frac1{12}\,\theta_{\bK\bL\bM\bN}\theta_{\bP\bQ\bR\bS}\Big(M^{\bK\bP}M^{\bL\bQ}M^{\bM\bR}M^{\bN\bS}-6\,M^{\bK\bP}M^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}\\
+			&\qquad\qquad\qquad\qquad\quad+8\,M^{\bK\bP}\eta^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}-3\,\eta^{\bK\bP}\eta^{\bL\bQ}\eta^{\bM\bR}\eta^{\bN\bS}\Big)\\
+			&\quad +\frac1{8}\,\theta_{\bK\bL}\theta_{\bP\bQ}\Big(2\,M^{\bK\bP}M^{\bL\bQ}-2\,\eta^{\bK\bP}\eta^{\bL\bQ}-M^{\bK\bL}M^{\bP\bQ}\Big)+4\,\theta\theta_{\bK\bL}M^{\bK\bL}-32\,\theta^2.
+		\end{aligned}
+	\end{equation}
+}
+Finally, the dynamics of the vector fields is governed by the Chern-Simons contribution
+%
+\begin{equation}
+	{\cal L}_{\rm CS}= -\varepsilon^{\,\mu\nu\rho}\,\Theta_{\bar M\bar N|\bar P\bar Q}\,A_{\mu}{}^{\bar M\bar N}\left(\partial_{\nu}\,A_{\rho}{}^{\bar P\bar Q}  + \frac{1}{3}\, \Theta_{\bar R\bar S|\bar U\bar V}\,f^{\bar P\bar Q,\bar R\bar S}{}_{\bar X\bar Y}\, A_{\nu}{}^{\bar U\bar V} A_{\rho}{}^{\bar X\bar Y} \right),
+\end{equation}
+%
+where $f^{\bar M\bar N,\bar P\bar Q}{}_{\bar K\bar L} = 4\,\delta_{[\bar K}{}^{[\bar M}\eta^{\bar N][\bar P}\delta_{\bar L]}{}^{\bar Q]}$ are the structure constants of $\mathfrak{so}(8,4)$, and $\varepsilon^{\mu\nu\rho}$ is the three-dimensional Levi-Civita symbol.
+
+The parametrisation of the gauging to get the truncation of six-dimensional half-maximal supergravity on $S^{3}$ is best described through the decomposition of ${\rm SO}(8,4)$ as~\cite{Eloy:2021fhc} 
+%
+\begin{equation}	\label{eq: gl3gradingbar}
+	\begin{aligned}
+		\text{SO}(8,4)	&\longrightarrow	\enspace \text{GL}(3,\mathbb{R})\times\text{SO}(1,1)\times\text{SO}(4)_{\rm global}\,,	\\
+		X^{\bM}		&\longrightarrow	\quad \{X^{\bar m},\; X_{\bar m},\; X^\bzero,\; X_\bzero,\; X^\balpha\},
+	\end{aligned}
+\end{equation}
+where $\bar m\in\llbracket1,3\rrbracket$ and $\balpha\in\llbracket9,12\rrbracket$ label the ${\rm SL}(3, \mathbb{R})$ and ${\rm SO}(4)_{\rm global}$ vector representations.
+In this basis, the ${\rm SO}(8,4)$-invariant tensor has the expression
+%
+\begin{equation}
+	\eta_{\bM\bN}=
+	\begin{pmatrix}
+		0 & \delta_{\bar m}{}^{\bar n} & 0 & 0 &0\\
+		\delta^{\bar m}{}_{\bar n} & 0 & 0 & 0 &0\\
+		0 & 0 & 0 & 1 & 0\\
+		0 & 0 & 1 & 0 & 0\\
+		0 & 0 & 0 & 0 & -\delta_{\balpha\bbeta}
+	\end{pmatrix},
+\end{equation}
+and the embedding tensor has the following non-vanishing components:
+\begin{equation} \label{eq:embedtens}
+	\theta_{\bM\bN\bP\,\bzero}=-\frac{1}{\sqrt{2}}\,X_{\bM\bN\bP}\,,		\qquad	\theta_{\bzero\bzero}=-4\sqrt{2},	
+\end{equation}
+with 
+%
+\begin{equation}
+	X_{\bar m\bar n \bar p} = \varepsilon_{\bar m \bar n \bar p},		\qquad
+	X_{\bar m}{}^{\bar n \bar p} = \varepsilon_{\bar m \bar n \bar p},	\qquad
+	X^{\bar m}{}_{\bar n}{}^{\bar p} = \varepsilon_{\bar m \bar n \bar p},	\qquad
+	X^{\bar m\bar n}{}_{\bar p} = \varepsilon_{\bar m \bar n \bar p}.
+\end{equation}
+The gauge group is then
+\begin{equation}
+	(T^1)^4\times[\text{SO}(4)\ltimes(T^3\times T^3)],
+\end{equation}
+where $T^{n}$ is a translational group transforming in the representation of dimension $n$ of ${\rm SO}(4)$. A possible parametrisation of the scalar matrix is then
+\begin{equation}	\label{eq: scalarmatrix}
+	M_{\bM\bN}
+	=
+	\begin{pmatrix}
+		m+(\xi^2+\phi)m^{-1}(\xi^2-\phi)+2\xi^2	& 	(\xi^2+\phi)m^{-1}		&	0	&  0  &	-\sqrt2\,[1+(\xi^2+\phi)m^{-1}]\xi	\\
+		m^{-1}(\xi^2-\phi)	& 	m^{-1}	&	0  	&  0  &	-\sqrt2\,m^{-1}\xi	\\
+		0		&	0		&	e^{2\tilde\varphi}	&	0				&	0		\\
+		0		&	0		&	0				&	e^{-2\tilde\varphi}	&	0		\\
+		-\sqrt2\,\xi^T[1+m^{-1}(\xi^2-\phi)]	&	-\sqrt2\,\xi^Tm^{-1}	&	0	&	0	&	1+2\,\xi^Tm^{-1}\xi	\\
+	\end{pmatrix},
+\end{equation}
+in terms of a symmetric ${\rm GL}(3,\mathbb{R})$ matrix $m$, a $3\times3$ antisymmetric matrix $\phi$, a $3\times4$ matrix $\xi$, its $3\times 3$ square $\xi^{2} = \xi \xi^{T}$ and a dilaton $\tilde{\varphi}$.
+This encodes 22 out the 32 scalars of the theory, 10 of the scalars being gauge fixed using the translations in the gauge group.
+With this parametrisation, the potential takes the form~\eqref{eq:scalarpotential}.
+We can further consistently restrict ourselves to a set of 13 scalars by requiring invariance under the diagonal ${\rm SO}(3)$ subgroup of ${\rm SO}(4)_{\rm global}$~\cite{Eloy:2021fhc}, yielding to the parametrisation described in eq.~\eqref{eq:13scalars1} and~\eqref{eq:13scalars2}.
+
 \section{Comparison with AIFeynman} \ce{Appendix?}
-In comparaison with state of the art technique, we have used the AIFeynman algorithm on our data set, with again $x_8 = \exp(\tilde{x}_8)$, such that we again look for polynomial expressions.
+In comparison with state of the art technique, we have used the AIFeynman algorithm on our data set, with again $x_8 = \exp(\tilde{x}_8)$, such that we again look for polynomial expressions.
 We have run it with the following configuration

### 2025-07-28 Draft_MLFlatDirections.tex
Upadte of sec. 5, and small modifications in sec. 4.4.

@@
 
-	The supergravity solution can be shown to preserve a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry.
+	The supergravity solution can be shown to preserve a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry and breaks all supersymmetry, except at the origin where we recover the ${\rm SO}(4)$ isometries and the ${\cal N}=(0,4)$ supercharges.
 Using the parametrisation~\eqref{eq:rulex8x10}, the $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
@@
 	\end{equation}
+
+	\ce{Wouldn't it be interesting to give the scalar masses and speak of the stability of the 3d solution? Would be useful to make contact with ref.~\cite{Eloy:2021fhc}.}
 
@@
 Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression on polynomials.
-We demonstrated its efficiency on a 5-scalar subsector of three-dimensional half-maximal supergravity, derived from the $AdS_3 \times S^3 \times T^4$ compactification of IIB supergravity.
+We demonstrated its efficiency on a 5-scalar subsector of three-dimensional half-maximal supergravity, derived from the ${\rm AdS}_3 \times S^3$ compactification of six-dimensional ${\cal N}=(1,1)$ supergravity, or analogously of the ${\rm AdS}_3 \times S^3 \times T^4$ compactification of IIB supergravity.
 
@@
 
-Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold, with one direction potentially gauge-fixable.
-The discovered solution preserves $U(1) \times U(1)$ gauged symmetry and exhibits a rich spectrum structure.
-The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold.
-\ce{This paragraph has to change given the few information we give on the sugra solution.
-Also, conformal manifold not defined.
-Rather open on the fact that having the analytical definition of the family gives access to its study using sugra and ExFT?}
-
 This approach opens several promising avenues for advancement.
@@
 
+Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold.
+The discovered solutions preserve a ${\rm U}(1) \times {\rm U}(1)$ gauged symmetry and breaks all supersymmetries.
+The Zamolodchikov metric on the moduli space provides a concrete geometric description of the conformal manifold.
+While the specific solutions found may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
+As the solutions live in a 3d consistent truncation of both the ${\rm AdS}_3 \times S^3$ solution of ${\cal N}=(1,1)$ six-dimensional supergravity and of the ${\rm AdS}_3 \times S^3 \times T^4$ vacuum of IIB supergravity, we can uplift the solution to 6d and 10d using the tools of exceptional field theory (ExFT)~\cite{Hohm:2014fxa,Hohm:2014qga,Hohm:2017wtr}.
+The higher-dimensional solutions would be of the form ${\rm AdS}_3 \times M^3$ or ${\rm AdS}_3 \times M^7$, with $M^{3}$, and $M^{7}$ being deformations of the round $S^{3}$ and $S^{3}\times {\rm T}^{4}$, respectively.
+These deformed spaces have as moduli the 3 parameters $\{x_{1},x_{2},x_{4}\}$ that define the solutions.
+ExFT gives further access to the full Kaluza-Klein spectrum for those compactifications~\cite{Malek:2019eaz,Malek:2020yue,Eloy:2020uix}, allowing a test of the perturbative stability of the solutions, and giving valuable information on the spectrum of states of the dual CFT.
+These applications relies entirely on the fact that we have an analytic parametrisation of the solutions thanks to the symbolic regression we performed.
+We live these for future works.
+
 The marriage of machine learning techniques with traditional supergravity analysis represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
@@
 Maybe we could weaken the statement a bit?}
-
-While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit.
-\ce{Move above when discussing the sugra solution?}
-
-\ce{Open on the use of ExFT to uplift and compute the full KK spectrum.}
 

### 2025-09-05 Draft_MLFlatDirections.tex
Updated sec 1-4 of the draft

@@
 Within this holographic framework, supergravity theories in AdS backgrounds serve as the low-energy effective descriptions of string theory compactifications, making them natural laboratories for exploring the gravitational side of the duality.
-The CFT side plays a crucial role in statistical physics, as CFT are known to describe phase transitions ; they are also fixed point of Renormalisation Group flow and this is this latter point that is our interest in this paper.
+The CFT side plays a crucial role in statistical physics, as CFT are known to describe phase transitions ; they are also fixed point of Renormalisation Group flow and this is this latter aspect that is our interest in this paper.
 An interesting question is indeed to know whether those CFT are isolated fixed points of RG flows, or belong to a continuous family of CFT.
 If this is the case, the space of continuous deformations that takes from one CFT to another is called a conformal manifold.
-These deformations are parametrized by exactly marginal operator, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
-
-From the AdS/CFT correspondence perspective, conformal manifolds on the boundary theory are dual to flat directions in the scalar potential of the dual supergravity theory.
+These deformations are parametrised by exactly marginal operators, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
+
+From the AdS/CFT correspondence perspective, conformal manifolds on the boundary theory are dual to continuous families of AdS solutions where the (possibly warped) AdS factor stays undeformed.
+If a consistent truncation on these solutions exists, conformal manifolds can also be identified as flat directions in the scalar potential of the truncation.
 Along these directions, the scalar field configurations vary continuously while the cosmological constant remains unchanged.
@@
 The question of the exact form of the gravity dual to $J\bar J$ deformations is however open.
-A well-known example is given in ref.~\cite{Aharony:2001dp,Dong:2014tsa}, and recent works have demonstrated the existence of vast families of classically marginal deformations of the ${\rm AdS}_{3}\times S^{3}\times {\rm T}^{4}$ and ${\rm AdS}_{3}\times S^{3}\times S^{3}\times S^{1}$ solutions of type IIB supergravity that are perturbatively stable though supersymmetry breaking~\cite{Eloy:2023zzh,Eloy:2023acy,Eloy:2024lwn}.
+A well-known example is given in ref.~\cite{Aharony:2001dp,Dong:2014tsa}, and recent works have demonstrated the existence of vast families of classically marginal deformations of the ${\rm AdS}_{3}\times S^{3}\times {\rm T}^{4}$ and ${\rm AdS}_{3}\times S^{3}\times S^{3}\times S^{1}$ solutions of type IIB supergravity that are perturbatively stable despite supersymmetry breaking~\cite{Eloy:2023zzh,Eloy:2023acy,Eloy:2024lwn}.
 These deformations were shown in ref.~\cite{Eloy:2024lwn} to be equivalent to current-current deformations of the worldsheet Wess-Zumino-Witten models~\cite{Gepner:1986wi} describing the undeformed solutions~\cite{Eberhardt:2017pty,Eberhardt:2018ouy}, giving strong indications that their CFT duals arise from $J\bar J$ deformations as well.
@@
 Although extensive, the families of deformations found in the aforementioned papers have not exhausted all possibilities for marginal deformations of three-dimensional supergravity solutions.
-A complete classification would require a systematic study of the flat directions in the supergravity scalar potential $V$ that defines the AdS configurations, as those directions are in correspondence with classical marginal deformations of the holographic CFT in the large $N$ limit.
+A complete classification would require a systematic study of the flat directions in the supergravity scalar potential $V$ that defines the AdS configurations, as those directions correspond to classical marginal deformations of the holographic CFT in the large $N$ limit.
 These flat directions are continuous sets in the space of scalar fields along which the value of the potential stay fixed, \textit{i.e.}  along which $\nabla V = 0$.
-However, the explicit characterization of flat directions presents formidable technical challenges.
+However, the explicit characterisation of flat directions presents formidable technical challenges.
 Supergravity scalar potentials, even in truncated models, typically involve dozens of scalar fields with intricate non-linear interactions.
@@
 
-The emergence of machine learning techniques in theoretical physics opens new avenues for addressing such complex problems.
+The emergence of machine learning techniques opens new avenues for addressing such complex problems in theoretical physics.
 Instead of solving the full symbolic system analytically from the outset, one can employ numerical methods to sample the solution space and subsequently apply symbolic regression techniques to extract analytical patterns from the data.
-This hybrid approach has the potential to bypass the computational bottlenecks inherent in purely symbolic methods, while still having the potential to uncover exact analytical expressions.
+This hybrid approach has the potential to bypass the computational bottlenecks inherent to purely symbolic methods, while still having the potential to uncover exact analytical expressions.
 
@@
 More broadly, there has been increasing interest in applying machine learning and numerical techniques across various domains of high-energy physics.
-This includes, for instance, the characterization of Calabi–Yau metrics and hypersurfaces \cite{Ashmore:2019wzb,Berman:2021mcw,Larfors:2022nep,Berglund:2022gvm,Jejjala:2020wcc,Douglas:2006rr,Larfors:2021pbb,He:2018jtw}, as well as broader efforts to explore the string theory landscape using machine learning techniques \cite{He:2017aed,Carifio:2017bov,Ruehle:2017mzq}.
+This includes, for instance, the characterisation of Calabi–Yau metrics and hypersurfaces \cite{Ashmore:2019wzb,Berman:2021mcw,Larfors:2022nep,Berglund:2022gvm,Jejjala:2020wcc,Douglas:2006rr,Larfors:2021pbb,He:2018jtw}, as well as broader efforts to explore the string theory landscape \cite{He:2017aed,Carifio:2017bov,Ruehle:2017mzq}.
 Additional applications include studies in CFT \cite{Chen:2020dxg}, investigations of the supergravity landscape \cite{Brady:2025zzi,Krishnan:2020sfg}, and explorations of the AdS/CFT correspondence \cite{Hashimoto:2018ftp}.
@@
 In this work, we demonstrate the viability of the aforementioned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of six-dimensional non-chiral $\mathcal{N} = (1,1)$ supergravity on $AdS_3 \times S^3$, or to type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
-Our methodology combines gradient descent sampling of the flat direction manifold with some symbolic regression technique.
-There exists a large literature on symbolic regression, using methods from genetic programming \cite{koza1994genetic,virgolin2021improving,randall2022bingo,burlacu2019parsimony}, to deep machine learning \cite{petersen2019deep,kamienny2022end}, generative modelling \cite{valipour2021symbolicgpt}, diffusion models \cite{bastiani2025diffusion}, and equation learner with the nodes being symbolic operations \cite{2018arXiv180607259S}.
-Another state-of-the art algorithm is the AIFeynman methods \cite{Udrescu:2019mnk}.
-They use neural network to identify structure in the dataset (such as translational symmetries, multiplicative separability, compositionality\dots) to recursively define simpler problems on which they can fit the solutions with polynomials.
-However, in the spirit of trying to build a generalisable method, we develop here our own algorithm, which is based on symbolic regression using an Annealing Importance Sampling method (AIS) \cite{neal1998annealedimportancesampling}.
-%In this paper, we will study a 5 parameter truncation, which is itself coming from a 13 parameter consistent truncation of $\mathcal{N} = (1,1)$ 6-dimensional supergravity.
+Our methodology combines gradient descent sampling of the conformal manifold with a symbolic regression technique.
+There exists a large body of literature on symbolic regression, using methods from genetic programming \cite{koza1994genetic,virgolin2021improving,randall2022bingo,burlacu2019parsimony}, to deep learning \cite{petersen2019deep,kamienny2022end}, generative models \cite{valipour2021symbolicgpt}, diffusion models \cite{bastiani2025diffusion}, and equation learning with the nodes being symbolic operations \cite{2018arXiv180607259S}.
+An state-of-the-art algorithm is AIFeynman \cite{Udrescu:2019mnk}.
+It uses neural networks to identify structures in the dataset (such as translational symmetries, multiplicative separability, compositionality\dots) to recursively define simpler problems on which they can fit the solutions with polynomials.
+However, this method is slow, usually limited to low-dimensional spaces, and, by construction, can only fit one polynomial at a time.
+Alternatively, we develop here an algorithm based on symbolic regression using Annealing Importance Sampling (AIS) \cite{neal1998annealedimportancesampling}, since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces
 
@@
 We first use the gradient descent to efficiently sample the underlying conformal manifold.
-Combined with numerical analysis, such as principal component analysis and clustering, we can identify the existence of a three-dimensional continuous family.
+Combined with numerical analyses, including a local principal component analysis, we can identify the existence of a three-dimensional continuous family.
 We then use an AIS technique combined with a sequential Monte Carlo approach (SMC) \cite{del2006sequential} in order to do symbolic regression.
-As we will indeed demonstrate in the paper, there exist polynomial constraints on the 5 parameters, viewed as embedding coordinates, that projects them on the 3 dimensional manifolds.
-We manage to identify 8 of those constraints on the data, not all independent, which once solved gives that two of the embedding coordinates can be expressed in terms of the others.
-This provides an explicit three-dimensional family of solutions.
+As we will indeed demonstrate in the paper, there exist polynomial constraints on the 5 parameters, viewed as embedding coordinates, that project them onto the 3 dimensional manifolds.
+We manage to identify 8 of those constraints on the data, not all independent, which once solved  provide an explicit three-dimensional family of solutions.
 
@@
 
-\section{Supergravity setup} \label{sec:sugra}
+%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%
+\section{Supergravity Setup} \label{sec:sugra}
 Three-dimensional $\mathcal{N}=8$ (half-maximal) gauged supergravity is governed by the Lagrangian~\cite{Nicolai:2001ac,deWit:2003ja}
@@
 %
-which comprises an Einstein-Hilbert term $R$, a kinetic term for scalar fields parametrized by the matrix $M_{\bM\bN}$, a Chern-Simons contribution $\mathcal{L}_{\text{CS}}$, and a scalar potential $V$, see app.~\ref{app:sugra} for details on the definition of the terms.
+which comprises an Einstein-Hilbert term $R$, a kinetic term for scalar fields parametrised by the matrix $M_{\bM\bN}$, a Chern-Simons contribution $\mathcal{L}_{\text{CS}}$, and a scalar potential $V$, see app.~\ref{app:sugra} for details on the definition of the terms.
 The scalar degrees of freedom parametrise the coset space
@@
 %
-through the symmetric matrix $M_{\bK\bL}$.\footnote{In full generality, the coset space of half-maximal supergravity in three dimensions is $\text{SO}(8,p)/\big(\text{SO}(8)\times\text{SO}(p)\big)$, we consider here the case $p=4$ only.} With appropriate gauging (see eq.~\eqref{eq:embedtens}), this $\text{SO}(8,4)$ theory is a consistent truncation of six-dimensional ${\cal N}=(1,1)$ supergravity on $S^{3}$~\cite{Cvetic:2000dm,Deger:2014ofa,Hohm:2017wtr}.
+through the symmetric matrix $M_{\bK\bL}$.\footnote{In full generality, the coset space of half-maximal supergravity in three dimensions is $\text{SO}(4+p,4+q)/\big(\text{SO}(4+p)\times\text{SO}(4+q)\big)$ for $p$ vectors and $q$ tensors in 6$d$.
+We consider here the case $p=4$ only.} With appropriate gauging (see eq.~\eqref{eq:embedtens}), this $\text{SO}(8,4)$ theory is a consistent truncation of six-dimensional ${\cal N}=(1,1)$ supergravity on $S^{3}$~\cite{Cvetic:2000dm,Deger:2014ofa,Hohm:2017wtr}.
 It features an ${\rm AdS}_{3}$ stationary point at the scalar origin ($M_{\bK\bL}=\delta_{\bK\bL}$, the ${\rm SO}(8,4)$ identity matrix), corresponding to an ${\rm AdS}_{3}\times S^{3}$ solution in 6d.
-In the following, we will be interested in exploring flat directions of the potential $V$, \textit{i.e.} other stationary points that are continuously connected to the origin.
+In the following, we will be interested in exploring flat directions of the potential $V$ around this point, \textit{i.e.} stationary points that are continuously connected to the origin.
 In three dimensions, the flat directions constitute a family of ${\rm AdS}_{3}$ vacua sharing the same cosmological constant.
-The corresponding solutions in six dimensions are of the form ${\rm AdS}_{3}\times M^{3}$, with $M^{3}$ some deformation of the round sphere $S^{3}$, parametrised by the constant scalars defining the 3d vacua.
+The corresponding solutions in six dimensions are of the form ${\rm AdS}_{3}\times M^{3}$, with $M^{3}$ some deformation of the round sphere $S^{3}$, parametrised by the constant scalar vevs defining the 3d vacua.
 
@@
 Note here that all dilaton fields are denoted with a tilde.
-This convention is adopted in anticipation of a later redefinition of the form \( x_i = e^{\tilde{x}_i} \) for these fields.
+This notation is adopted in anticipation of a later redefinition of the form \( x_i = e^{\tilde{x}_i} \) for these fields.
 %By reserving the notation without tildes for the exponentiated variables, we maintain a clear and consistent distinction for use in subsequent expressions.
@@
 The search for flat directions of the potential~\eqref{eq:scalarpotential} can then start form a study of its gradient $\nabla V$.
-However, carrying out the search for stationary points analytically is by far too complex, even reducing the number of variables or using a symbolic solver such as Mathematica~\cite{Mathematica}: the resulting expressions are too complex to be simplified into a manageable form, and do not yield usable relationships that express some variables in terms of others.
+However, carrying out the search for stationary points analytically is by far too complex, even reducing the number of variables or using a symbolic solver such as Mathematica~\cite{Mathematica}: the resulting expressions are too convoluted to be simplified into a manageable form, and do not yield usable relationships that express some variables in terms of others.
 This complexity does not, however, rule out the possibility that simpler solutions satisfying the condition of vanishing gradient may exist although the solver does not find them.
-In this work, we aim to identify such solutions, which we seek using numerical methods.
-This approach has as additional advantage its broader applicability: it would be effective even in cases where an exact analytic expression for the potential is out of reach, like richer theories as the ${\rm SO}(8,8)$ 3d truncations of type IIB supergravity on ${\rm AdS}_{3}\times S^{3} \times {\rm T}^{4}$ or ${\rm AdS}_{3}\times S^{3}\times S^{3}\times S^{1}$.
-
-A first trial and error numerical exploration suggests that attention can be focused on the five scalars $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$.
-This subset, selected at random from the original set of thirteen scalar fields, serves to render the problem more tractable at the outset.
-The potential~\eqref{eq:scalarpotential} then reduces to
-\begin{equation} \label{eq:scalarpotential124810}
-	\begin{aligned}
-		V &= \frac{1}{4}\, e^{-2\,\tilde{x}_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,\tilde{x}_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
-		  & \quad\qquad\qquad - 4\,e^{3\,\tilde{x}_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
-     			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
-       & \quad\qquad\qquad - 8\,e^{\tilde{x}_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
-     			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
-       & \quad\qquad\qquad + 4\,e^{2\,\tilde{x}_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
-       			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
-       & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,\tilde{x}_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
-	\end{aligned}
-\end{equation}
-To compute the gradient, we exploit the fact that we possess an analytic expression for the scalar potential~\eqref{eq:scalarpotential124810}.
-Note however that it could have been fully done using a numerical approach as automatic differentiations methods.
-It is important to emphasize, however, that the $\{x_{1}, x_{2}, x_{4}, \tilde{x}_{8}, x_{10}\}$ subset does not constitute a consistent truncation of the full theory, as higher-order interactions could, in principle, source the remaining scalar modes.
-Nonetheless, the five-scalar model remains a self-consistent theory in its own right and can be used independently.
-This distinction does not affect our numerical approach: the solutions we obtain remain valid solutions of the complete theory.
-This is because we identify the critical points of the scalar potential by first computing $\nabla V$ with all scalar fields included, \textit{i.e.} using eq.~\eqref{eq:scalarpotential}, and only then setting the remaining fields,
+
+In this work, we aim to identify such solutions. 
+A preliminary numerical exploration suggests that attention can be focused on the five scalars $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$. 
+The solutions we obtain in this truncation remain valid solutions of the complete theory, since we first compute $\nabla V$ with all scalar fields included, \textit{i.e.} using eq.~\eqref{eq:scalarpotential}, and only then setting the remaining fields,
 \begin{equation} \label{eq:defvecy}
-	\vec{y} = (x_3,x_5,x_6,\tilde{x}_7,\tilde{x}_9,x_{11},x_{12},\tilde{x}_{11}),
+	\vec{y} = (x_3,x_5,x_6,\tilde{x}_7,\tilde{x}_9,x_{11},x_{12},\tilde{x}_{13}),
 \end{equation}
@@
 
-\section{Numerical analysis} \label{sec:numanal}
-To identify the flat directions in the potential, we will use numerical tools.
-The procedure is as follows: first, we sample the underlying manifold, and then we use numerical techniques to extract analytical information from the resulting cloud of points.
-The sampling of the manifold is done through a gradient descent.
-We then analyse its dimension and structure using a local Principal Component Analysis~(PCA) and clustering algorithms, and finally extract analytical constraints defining the manifold thanks to Symbolic Regression methods.
-We detail these different procedures in the following.
+To identify the flat directions in the potential, we will combine numerical and symbolic tools.
+The procedure is as follows: first, we sample the underlying manifold by performing a gradient descent on a 5-d hypercube.
+The resulting cloud of points is subsequently analysed using local principal component analysis~(PCA) and clustering algorithms, which allow us to infer the dimension and topological structure of the manifold.
+After these properties are ascertained, we finally extract analytical constraints defining the manifold thanks to symbolic regression methods.
+In the next section, we introduce the symbolic regression algorithm, and defer the details of the numerical methods and results to the following one.
+
+%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%
+\section{Annealed Importance Sampling for Polynomial Symbolic Regression}
+
+	%\item Annealed Importance Sampling: first explain general idea (construct density probability, role of temperature, links with Monte-Carlo), discuss $\beta$ to control exploration and exploitation phases.
+
+The numerical search described above results in clouds of points embedded in a higher-dimensional space. 
+In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe such datasets.
+In the problem discussed in this paper, we are looking for polynomial expressions such that $p(\vec{x}^{\,i}) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
+This task involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods.
+Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and getting trapped in local optima, especially in high-dimensional or multimodal spaces.
+
+To address these challenges, we employ an Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} combined with Sequential Monte Carlo (SMC) methods. 
+AIS aims to estimate ratios of partition functions by constructing a sequence of intermediate distributions that smoothly transition from an initial, tractable distribution (e.g., a prior over symbolic expressions) to the complex target posterior distribution.
+This annealing process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient exploration of the probability landscape.
+
+SMC enhances this procedure by propagating a population of particles—each representing a candidate symbolic expression—through the sequence of distributions.
+At each step, particles are reweighted based on the incremental change in the distribution, resampled to focus computational effort on high-probability regions, and mutated via operations.
+This combination of importance sampling, resampling, and mutation maintains diversity among the particles and prevents premature convergence to suboptimal models.
+These features make AIS-SMC particularly well-suited for symbolic regression tasks, where the search space is not only high-dimensional but also structured and discontinuous.
+
+	\begin{figure}[h!]
+			\centering
+			\begin{minipage}{15cm}
+				\begin{tcolorbox}[
+					colback=white,
+					colframe=myblue,
+					title=\textbf{ASMC Algorithm},
+					fonttitle=\sffamily\large,
+					halign title=flush center,
+					boxrule=2pt,
+					left=6pt,
+					right=6pt,
+					top=8pt,
+					bottom=8pt
+					]
+					\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]
+
+						% Nœuds
+						\node (start) [startstop] {Start};
+
+						\node (init_particles) [process, below of=start] {Initialize particles \& weights};
+
+						\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};
+
+						\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};
+
+						\node (ess_check) [decision, below of=weight_update] {Effective Sample Size $<$ Threshold?};
+
+						\node (resample) [process, right=3.8cm of ess_check] {Resample particles};
+
+						\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with MCMC kernel};
+
+						\node (acceptance) [process, below of=mutation] {Accept/Reject particles};
+
+						\node (end_iter) [decision, below of=acceptance] {Last step?};
+
+						\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};
+
+						\node (output) [process, below of=exploit] {Return particles};
+
+						\node (stop) [startstop, below of=output] {End};
+
+						% Flèches avec étiquettes améliorées
+						\draw [arrow] (start) -- (init_particles);
+						\draw [arrow] (init_particles) -- (compute_beta);
+						\draw [arrow] (compute_beta) -- (weight_update);
+						\draw [arrow] (weight_update) -- (ess_check);
+
+						\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
+						\draw [arrow] (resample) |- (mutation);
+
+						\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
+						\draw [arrow] (mutation) -- (acceptance);
+						\draw [arrow] (acceptance) -- (end_iter);
+
+						% Boucle de retour améliorée
+						\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {No} ++(-4.5,0) |- (compute_beta);
+
+						\draw [arrow] (end_iter) -- node[right, arrow_label] {Yes} (exploit);
+						\draw [arrow] (exploit) -- (output);
+						\draw [arrow] (output) -- (stop);
+
+					\end{tikzpicture}
+				\end{tcolorbox}
+			\end{minipage}
+			\caption{Flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
+			\label{ASMCflowchart}
+		\end{figure}
+
+		%\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
+
+Let us now explain in more detail how does this procedure goes.
+The goal is to reconstruct some distribution function $d(z)$, where here $z$ in going to be some polynomial.
+We will try to reconstruct this density function by series of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{d}z$.
+We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N = 1$.
+The unnormalized density at level $n$ is then given in terms of a prior distribution $p_0(z)$ over the hypothesis space and a loss function $L(z)$:
+		\begin{equation}\label{eq:gamman}
+			\gamma_n(z) := d_0(z) \: \exp \left( -\beta_n L(z) \right).
+		\end{equation}
+
+		At each epoch, we have a set of particles and weights $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
+To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and calculate the new unnormalized importance weight $w_n^k$.
+The latter are updated using the formula
+		\begin{equation}
+			w_n^k = w_{n-1}^k \times \alpha_{n}^k
+		\end{equation}
+		where $\alpha_n^k$ is the incremental importance weight. The standard form for $\alpha_n^k$, which requires introducing an auxiliary backward transition kernel $q(z_{n-1} | z_n)$, is:
+		\begin{equation}
+			\alpha_n^k = \frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) } 
+		\end{equation}
+		The weights are finally normalized and we get $w_n^k \rightarrow \frac{w_n^k}{\sum_j w_n^j}$.
+
+		Let's us now focus on the forward $q(z_n^k | z_{n-1}^k)$ and backward propagation kernel $q(z_{n-1}^k | z_n^k)$ for now.
+The forward propagation kernel defines how we generate the state at time $n$ given the state at time $n-1$.
+It gives the probability to transition from $z_{n-1}$ to $z_n$.
+The backward kernel represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
+The purpose of $q$ is to give a proposition for $z_n$ given $z_{n-1}$.
+For the implementation of the two, we decide to implement an AIS-style MCMC code: we make some move in the space of polynomials, and then accept or reject those new polynomials based on an acceptance rate.
+So we first need to choose what are the available moves in the space of polynomials.
+Here are the choices we have made for our symbolic regression task :
+		\begin{itemize}
+			\item Coefficient pertubation.
+Given a polynomial $z_{n-1}$, we choose randomly one of its coefficient and modify it by a random noise from the guassian distribution $\mathcal{N}(0,\sigma^2)$.
+So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2.1 x_1 + 3 x_2^2$.
+			\item Variable multiplication.
+Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and multiply it by one of the available variable.
+So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$.
+			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x_1 x_2 + 3 x_2^2 \rightarrow  2 x_1 + 3 x_2^2$. 
+		\end{itemize}
+		The polynomials get mutated at each epoch.
+The mutation is chosen randomly, assigning probabilities \texttt{p\_{modify}} , \texttt{p\_{multiply}} and \texttt{p\_{divide}} to each possibility.
+This implementation enables a direct computation of both the forward and backward propagation kernels.
+In particular, for the case of coefficient perturbations, the transition is symmetric.
+That is,
+		\begin{equation}
+			q(z_n^k \mid z_{n-1}^k) = q(z_{n-1}^k \mid z_n^k),
+		\end{equation}
+		which significantly simplifies the computation of the incremental importance weight.
+
+		However, this symmetry does not hold in general.
+For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
+In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
+
+		The acceptance ratio for the MCMC algorithm is given by : 
+		\begin{equation}\label{eq:acceptanceratio}
+			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)
+		\end{equation}
+		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
+
+		We have adapted the classic approach outilned above.
+As can be seen in \eqref{eq:gamman}, what matters the most to determine $\gamma_{n}$ is not the inverse temperature, but rather the product of the inverse temperature and the loss function.
+Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach.
+The number of particles accepted at each run is monitored.
+We aim at following the following schedule as function of the \texttt{epoch}:
+		\begin{equation} \label{eq:acceptanceratioschedule}
+			\texttt{acceptance\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
+		\end{equation}
+		where \texttt{n\_epochs} is the total number of epochs.
+If we accept more particle (in the 5 last epochs), we decrease the temperature by 5\%, if we accept less we increase it by 5\%.
+This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
+\ce{So we don't use eq.~\eqref{eq:acceptanceratio} at all?
+This is not clear to me.}
+
+		Before closing the section, we need to discuss what is the Loss function we choose.
+It is required to compute the unormalized distribution $\gamma_n$.
+Assume that we have $z = \sum_k c_k X_k$, where $c_k$ are the coefficients of the polynomials, and $X_k$ is a short notations for all the possible monomials up to a given degree (so if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_k$ are $1, x, y, x^2, y^2, x y$).
+For the Loss function, we decided to take :
+		\begin{equation} \label{eq:lossreg}
+			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k |c_k|}
+		\end{equation}
+		So the first term is just the sum of the squared of the polynomial evaluated on the data.
+We want to make this 0 so we find polynomial that annihilates our data.
+The second part is a regularisation factor: it prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem.
+We typically take $\lambda \sim \mathcal{O}(1000)$.
+
+		%\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
+
+		Once the Annealing loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some more fine tuning.
+To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller.
+This allow to fine-tune the coefficients.
+\ce{Mention threshold?
+And number of iterations?}
+
+%		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
+Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate.
+Total time needed, without cluster or fancy computers.}
+	%\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Analysis and Results} \label{sec:results}
+
+For the supergravity theory introduced above and to be discussed below, this is a 3$d$ manifold embedded in a 5$d$ space.
+Therefore we can conclude that, in order to characterize the manifold, we need two independent constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
+If we have a look at the form of the potential, we can observe that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to some potential global factor of the dilaton of the form $e^{\tilde{x}_8}$, this potential is actually a polynomial of the embedding coordinates.
+Therefore, the components of $|\nabla V|$ are also polynomials in those variables.
+We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those.
+Note that we are now taking $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
+Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
+The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
 
@@
 When all data points lie within the interval $[-1, 1]$, the SR algorithm tends to favor high-degree polynomials, as these often yield smaller values over this range, thereby artificially lowering the loss.
-Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of overly complex polynomials that exploit this effect.} \ce{Put the footnote later in the SR section?} As the example we're focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points: we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
-As the solutions manifold lie within the five dimensional space, its intrinsic dimension is less than or equal to 5.
+Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of overly complex polynomials that exploit this effect.} \ce{Put the footnote later in the SR section?} As the example we are focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points: we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
+As the solutions lie within the five dimensional space, its intrinsic dimension is less than or equal to 5.
 The value $10^5$ then serves as a conservative upper bound for the number of points needed to adequately sample the manifold.
@@
 	% where $\vec{X}^{(i)} = (x^{(i)}_1,\dots,x^{(i)}_6,\tilde{x}^{(i)}_7,\tilde{x}^{(i)}_8,\tilde{x}^{(i)}_9,x^{(i)}_{10},\dots,x^{(i)}_{12},\tilde{x}^{(i)}_{13})$ and $\vec{y}^{\,(i)} = (x^{(i)}_3,x^{(i)}_5,x^{(i)}_6,\tilde{x}^{(i)}_7,\tilde{x}^{(i)}_9,x^{(i)}_{11},x^{(i)}_{12},\tilde{x}^{(i)}_{11})$
-	see eq.~\eqref{eq:defvecX} and~\eqref{eq:defvecy} for the definitions of the vectors $\vec{X}$ and $\vec{y}$.
+with the vectors $\vec{X}$ and $\vec{y}$ given in~\eqref{eq:defvecX} and~\eqref{eq:defvecy}.
 The exponents $(i)$ denote the data points, with $i\in\llbracket1,n_{\rm points}\rrbracket$.
@@
 	The Adam optimizer was employed throughout the gradient descent procedure~\cite{kingma2017adammethodstochasticoptimization}.
-Through trial and error, we observed that periodically reinitialising the optimizer significantly improved the convergence rate.
+As an accelerator of convergence, we observed that periodically reinitialising the optimizer significantly improved the convergence rate.
 It was reinitialised at iterations {250, 500, 750}, with the learning rate $\alpha$ fixed at $10^{-2}$.
@@
 The evolution of the loss function~\eqref{eq:lossgraddes}, along with the learning rate schedule, is shown in fig.~\ref{fig:loss_grad_des}.
-As can be seen in this figure, the convergence rate improves significantly each time the optimizer is reinitialised.
+As can be seen in this figure, the convergence rate improves significantly each time the optimizer is rebooted.
 We also observe that, following the last few reinitialisations, the loss exhibits a small bump immediately after the restart.
@@
 
-	As a first visualisation, we present a triangular plot of the data in fig.~\ref{triangular_plot_1_2_4_8_10}.
-\ce{Sure of the use of ``triangular''?} This figure shows all possible 2d projections of the data, along with the 1d histograms of each coordinate after gradient descent.
+	As a first visualisation, we present a tomography of the data in fig.~\ref{triangular_plot_1_2_4_8_10}.
+This figure shows all possible 2d projections of the data, along with the 1d histograms of each coordinate after gradient descent.
 Note that all directions appear to be well populated.
@@
 
-	\subsection{Annealed Importance Sampling for polynomial symbolic regression}
-	%\begin{itemize}[label=\textbullet]
-		%\item We can convert the potential to a polynomial by converting the variables that appear in exponentials to logs.
-	%\item As the potential is a polynomial, the solutions satisfy polynomials equations.
-Discuss that fact that we could get polynomials directly by taking the gradient of the potential, but those will be to complicated to express the vacuum in a usable way.
-We search those using Annealed Importance Sampling.
-
-		Now we have sampled the manifold and extracted some basic information about it (namely its dimension and the fact that it is made of one block), we would like to see if we can extract some analytic formula to characterise it.
-What we have at the moment, are points on a 3-dimensional manifold, which are embedded in a 5-dimensional space.
-Therefore we can conclude that, in order to characterise the manifold, we need two independent constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
-If we have a look at the form of the potential, we can observe that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to some potential global factor of the dilaton of the form $e^{\tilde{x}_8}$, this potential is actually a polynomial of the embedding coordinates.
-Therefore, the components of $|\nabla V|$ are also polynomials in those variables.
-We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those.
-Note that we are now taking $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
-Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
-The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
-
-		%\item Annealed Importance Sampling: first explain general idea (construct density probability, role of temperature, links with Monte-Carlo), discuss $\beta$ to control exploration and exploitation phases.
-
-		In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe a given dataset.
-In the problem discussed in this paper, we are looking for polynomial expressions such that $p(\vec{x}^{\,i}) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
-This task involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods.
-Markov Chain Monte Carlo (MCMC) techniques, while widely used, can struggle with poor mixing and getting trapped in local optima, especially in high-dimensional or multimodal spaces.
-
-		\subsubsection{Annealed Sequential Monte Carlo principle}
-
-		\begin{figure}[h!]
-			\centering
-			\begin{minipage}{15cm}
-				\begin{tcolorbox}[
-					colback=white,
-					colframe=myblue,
-					title=\textbf{ASMC Algorithm},
-					fonttitle=\sffamily\large,
-					halign title=flush center,
-					boxrule=2pt,
-					left=6pt,
-					right=6pt,
-					top=8pt,
-					bottom=8pt
-					]
-					\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]
-
-						% Nœuds
-						\node (start) [startstop] {Start};
-
-						\node (init_particles) [process, below of=start] {Initialize particles et weights};
-
-						\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};
-
-						\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};
-
-						\node (ess_check) [decision, below of=weight_update] {Effective Sample Size $<$ Threshold?};
-
-						\node (resample) [process, right=3.8cm of ess_check] {Resampling particles};
-
-						\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with MCMC kernel};
-
-						\node (acceptance) [process, below of=mutation] {Accept/Reject particles};
-
-						\node (end_iter) [decision, below of=acceptance] {Last step?};
-
-						\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};
-
-						\node (output) [process, below of=exploit] {Return particles};
-
-						\node (stop) [startstop, below of=output] {End};
-
-						% Flèches avec étiquettes améliorées
-						\draw [arrow] (start) -- (init_particles);
-						\draw [arrow] (init_particles) -- (compute_beta);
-						\draw [arrow] (compute_beta) -- (weight_update);
-						\draw [arrow] (weight_update) -- (ess_check);
-
-						\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
-						\draw [arrow] (resample) |- (mutation);
-
-						\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
-						\draw [arrow] (mutation) -- (acceptance);
-						\draw [arrow] (acceptance) -- (end_iter);
-
-						% Boucle de retour améliorée
-						\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {No} ++(-4.5,0) |- (compute_beta);
-
-						\draw [arrow] (end_iter) -- node[right, arrow_label] {Yes} (exploit);
-						\draw [arrow] (exploit) -- (output);
-						\draw [arrow] (output) -- (stop);
-
-					\end{tikzpicture}
-				\end{tcolorbox}
-			\end{minipage}
-			\caption{The flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
-			\label{ASMCflowchart}
-		\end{figure}
-
-		To address these challenges, we employ an Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC) methods.
-AIS constructs a sequence of intermediate distributions that smoothly transition from an initial, tractable distribution (e.g., a prior over symbolic expressions) to the complex target posterior distribution.
-This annealing process is guided by a temperature-like parameter that gradually emphasizes the data likelihood, allowing for more efficient exploration of the probability landscape.
-
-		SMC enhances this procedure by propagating a population of particles—each representing a candidate symbolic expression—through the sequence of distributions.
-At each step, particles are reweighted based on the incremental change in the distribution, resampled to focus computational effort on high-probability regions, and mutated via operations.
-This combination of importance sampling, resampling, and mutation maintains diversity among the particles and prevents premature convergence to suboptimal models.
-
-		These features make AIS-SMC particularly well-suited for symbolic regression tasks, where the search space is not only high-dimensional but also structured and discontinuous.
-
-		%\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
-
-		Let us now explain in more details how does this procedure goes.
-The goal is to reconstruct some distribution function $d(z)$, where here $z$ in going to be some polynomial.
-We will try to reconstruct this density function by series of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ is going to be the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{d}z$.
-We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N = 1$.
-We then define the unnormalized density at level $n$ in terms of a prior distribution $p_0(z)$ over the hypothesis space and a loss function $L(z)$:
-		\begin{equation}\label{eq:gamman}
-			\gamma_n(z) := d_0(z) \: \exp \left( -\beta_n L(z) \right).
-		\end{equation}
-
-		At each epoch, we have a set of particles and weights $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
-To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and calculate the new unnormalized importance weight $w_n^k$.
-The latter are updated using the formula
-		\begin{equation}
-			w_n^k = w_{n-1}^k \times \alpha_{n}^k
-		\end{equation}
-		where $\alpha_n^k$ is the incremental importance weight. The standard form for $\alpha_n^k$, which requires introducing an auxiliary backward transition kernel $q(z_{n-1} | z_n)$, is:
-		\begin{equation}
-			\alpha_n^k = \frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) } 
-		\end{equation}
-		The weights are finally normalized and we get $w_n^k \rightarrow \frac{w_n^k}{\sum_j w_n^j}$.
-
-		Let's us now focus on the forward $q(z_n^k | z_{n-1}^k)$ and backward propagation kernel $q(z_{n-1}^k | z_n^k)$ for now.
-The forward propagation kernel defines how we generate the state at time $n$ given the state at time $n-1$.
-It gives the probability to transition from $z_{n-1}$ to $z_n$.
-The backward kernel represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
-The purpose of $q$ is to give a proposition for $z_n$ given $z_{n-1}$.
-For the implementation of the two, we decide to implement an AIS-style MCMC code : we make some move in the space of polynomials, and then accept or reject those new polynomials based on an acceptance rate.
-So we first need to choose what are the available moves in the space of polynomials.
-Here are the choices we have made for our symbolic regression task :
-		\begin{itemize}
-			\item Coefficient pertubation.
-Given a polynomial $z_{n-1}$, we choose randomly one of its coefficient and modify it by a random noise from the guassian distribution $\mathcal{N}(0,\sigma^2)$.
-So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2.1 x_1 + 3 x_2^2$.
-			\item Variable multiplication.
-Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and multiply it by one of the available variable.
-So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$.
-			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x_1 x_2 + 3 x_2^2 \rightarrow  2 x_1 + 3 x_2^2$. 
-		\end{itemize}
-		The polynomials get mutated at each epoch.
-The mutation is chosen randomly, assigning probabilities \texttt{p\_{modify}} , \texttt{p\_{multiply}} and \texttt{p\_{divide}} to each possibility.
-This implementation enables a direct computation of both the forward and backward propagation kernels.
-In particular, for the case of coefficient perturbations, the transition is symmetric.
-That is,
-		\begin{equation}
-			q(z_n^k \mid z_{n-1}^k) = q(z_{n-1}^k \mid z_n^k),
-		\end{equation}
-		which significantly simplifies the computation of the incremental importance weight.
-
-		However, this symmetry does not hold in general.
-For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
-In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
-
-		The acceptance ratio for the MCMC algorithm is given by : 
-		\begin{equation}\label{eq:acceptanceratio}
-			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)
-		\end{equation}
-		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
-
-		We have adapted the classic approach outilned above.
-As can be seen in \eqref{eq:gamman}, what matters the most to determine $\gamma_{n}$ is not the inverse temperature, but rather the product of the inverse temperature and the loss function.
-Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach.
-The number of particles accepted at each run is monitored.
-We aim at following the following schedule as function of the \texttt{epoch}:
-		\begin{equation} \label{eq:acceptanceratioschedule}
-			\texttt{acceptance\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
-		\end{equation}
-		where \texttt{n\_epochs} is the total number of epochs.
-If we accept more particle (in the 5 last epochs), we decrease the temperature by 5\%, if we accept less we increase it by 5\%.
-This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
-\ce{So we don't use eq.~\eqref{eq:acceptanceratio} at all?
-This is not clear to me.}
-
-		Before closing the section, we need to discuss what is the Loss function we choose.
-It is required to compute the unormalized distribution $\gamma_n$.
-Assume that we have $z = \sum_k c_k X_k$, where $c_k$ are the coefficients of the polynomials, and $X_k$ is a short notations for all the possible monomials up to a given degree (so if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_k$ are $1, x, y, x^2, y^2, x y$).
-For the Loss function, we decided to take :
-		\begin{equation} \label{eq:lossreg}
-			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k |c_k|}
-		\end{equation}
-		So the first term is just the sum of the squared of the polynomial evaluated on the data.
-We want to make this 0 so we find polynomial that annihilates our data.
-The second part is a regularisation factor: it prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem.
-We typically take $\lambda \sim \mathcal{O}(1000)$.
-
-		%\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
-
-		Once the Annealing loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some more fine tuning.
-To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller.
-This allow to fine-tune the coefficients.
-\ce{Mention threshold?
-And number of iterations?}
-
-%		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
-Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate.
-Total time needed, without cluster or fancy computers.}
-	%\end{itemize}
-
-\section{Results} \label{sec:results}
 	\subsection{Initialisation of the algorithm}
-	We initialized the algorithm with \ce{Do we have all parameters here?}
+	We initialized the algorithm with
 	\begin{equation}	\label{eq:sample10000adaptativetemp}
 		\begin{aligned}
+			&\texttt{data\_size = 10,000},\\
 			&\texttt{n\_epochs = 1000},\\
@@
 	\end{equation}
+	\gl{link to notations in section 3}
 	This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
@@
 
-	\subsection{Supergravity solution}
+%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%
+\section{Supergravity Solutions}
 In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in eq.~\eqref{eq:pols}.
@@
 \appendix
-\section{Some details on the supergravity setup} \label{app:sugra}
+\section{Some Details on the Supergravity Setup} \label{app:sugra}
 We give here some details on the supergravity theory described schematically in sec~\ref{sec:sugra}, following ref.~\cite{Nicolai:2001ac,deWit:2003ja}.\footnote{See also ref.~\cite{Eloy:2021qol} for a review.} The Lagrangian is given in eq.~\eqref{eq: lagrangian_rephrased}.
@@
 \section{Comparison with AIFeynman} \ce{Appendix?}
-In comparison with state of the art technique, we have used the AIFeynman algorithm on our data set, with again $x_8 = \exp(\tilde{x}_8)$, such that we again look for polynomial expressions.
+We have used the state-of-the-art technique \texttt{AIFeynman} \cite{} on our dataset, with again $x_8 = \exp(\tilde{x}_8)$, so as to identify polynomial expressions fitting the data.
 We have run it with the following configuration
@@
 The first parameter fixes the time limit in seconds for each brute force call, \texttt{polyfit\_deg} gives the maximum degree of the polynomial tried by the polynomial fit routine and \texttt{NN\_epochs} is the number of training epoch for the internal neural network.
-The function used for the brut force tests are
+The function used for the brute force tests are
 \begin{equation}

### 2025-09-05 Draft_MLFlatDirections.tex
Modifications during meeting.

@@
 These deformations are parametrised by exactly marginal operators, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
+\ce{Needs some modifications.}
 
@@
 However, this method is slow, usually limited to low-dimensional spaces, and, by construction, can only fit one polynomial at a time.
-Alternatively, we develop here an algorithm based on symbolic regression using Annealing Importance Sampling (AIS) \cite{neal1998annealedimportancesampling}, since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces
+Alternatively, we develop here a symbolic regression algorithm based on Annealing Importance Sampling (AIS) \cite{neal1998annealedimportancesampling}, since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces
 
@@
 A preliminary numerical exploration suggests that attention can be focused on the five scalars $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$, and $x_{10}$. 
-The solutions we obtain in this truncation remain valid solutions of the complete theory, since we first compute $\nabla V$ with all scalar fields included, \textit{i.e.} using eq.~\eqref{eq:scalarpotential}, and only then setting the remaining fields,
+To ensure that the solutions we obtain in this truncation remain valid solutions of the complete theory, we first compute $\nabla V$ with all scalar fields included, \textit{i.e.} using eq.~\eqref{eq:scalarpotential}, and only then setting the remaining fields,
 \begin{equation} \label{eq:defvecy}
@@
 We will try to reconstruct this density function by series of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{d}z$.
-We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N = 1$.
+We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N$.
 The unnormalized density at level $n$ is then given in terms of a prior distribution $p_0(z)$ over the hypothesis space and a loss function $L(z)$:

### 2025-09-10 Draft_MLFlatDirections.tex
Merge section 4.3-4-5 into setion 4.3 and create new subsubsections. Also add minors changes/comments in the text

@@
 %%%%%%%%%%%%%%%%%%
-\section{Annealed Importance Sampling for Polynomial Symbolic Regression}
+\section{Annealed Importance Sampling for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
 
@@
 We aim at following the following schedule as function of the \texttt{epoch}:
-		\begin{equation} \label{eq:acceptanceratioschedule}
-			\texttt{acceptance\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
+		\begin{equation} \label{eq:eqadaptivetemperatureschedule}
+			\texttt{adaptive\_temperature\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
 		\end{equation}
@@
 This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
-\ce{So we don't use eq.~\eqref{eq:acceptanceratio} at all?
-This is not clear to me.}
+\bd{Move \ref{eq:eqadaptivetemperatureschedule} in seciton 4?}
 
@@
 
-For the supergravity theory introduced above and to be discussed below, this is a 3$d$ manifold embedded in a 5$d$ space.
+For the theory introduced above and to be discussed below, this is a 3$d$ manifold embedded in a 5$d$ space.
 Therefore we can conclude that, in order to characterize the manifold, we need two independent constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
@@
 Note that we are now taking $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
+
 Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
@@
 This choice is important to ensure that points are not restricted to the inner range~$[-1,1]$, which will be crucial for the Symbolic Regression.\footnote{The rationale is that symbolic regression (SR) evaluates the data points $\vec{x}^{(i)}$ using a candidate polynomial function $p$.
-The loss function—used later to assess the quality of a given polynomial—is defined as $\sum_i p(\vec{x}^{(i)}$.
+The loss function—used later to assess the quality of a given polynomial—is defined as $\sum_i p(\vec{x}^{(i)})$.
 When all data points lie within the interval $[-1, 1]$, the SR algorithm tends to favor high-degree polynomials, as these often yield smaller values over this range, thereby artificially lowering the loss.
-Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of overly complex polynomials that exploit this effect.} \ce{Put the footnote later in the SR section?} As the example we are focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points: we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
+Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of polynomials that exploit this effect.} \ce{Put the footnote later in the SR section?} \bd{I believe here is great to justify the volume of the hypercube.
+Otherwise it remains a bit misterious}.
+As the example we are focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points: we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
 As the solutions lie within the five dimensional space, its intrinsic dimension is less than or equal to 5.
@@
 The learning rate then gets suddenly increased, and some points that previously had low loss values may momentarily worsen before benefiting from faster convergence.
-This effect is likely due to points initially located in regions with weak attractive basins being pushed toward areas where the potential gradient is steeper, thus accelerating their convergence.
+This effect of faster convergence after the reinitialization is likely due to points initially located in regions with weak attractive basins being pushed toward areas where the potential gradient is steeper, thus accelerating their convergence.
 This strategy introduces the risk of desampling certain regions in favour of others, introducing the risk to hide some flat directions in the potential.
@@
 Specifically, nearly all points attained $V(0)$ within an absolute error of at least $10^{-4}$, with the exception of four points whose deviations were of the order of $10^{-3}$ (not visible on the graph).
-As the origin $\vec{X}=0$ of the parameter space corresponds to the three-dimensional truncation of the round ${\rm AdS}_{3}\times S^{3}$ solution of half-maximal supergravity in six dimensions, this confirms that the data points lie within flat directions of the potential.
+As the origin $\vec{X}=0$ of the parameter space corresponds to the three-dimensional truncation of the round ${\rm AdS}_{3}\times S^{3}$ solution of half-maximal supergravity in six dimensions with $V(0)=-4$, this confirms that the data points lie within flat directions of the potential.
 
@@
 Specifically, we aim at determining the dimension of the manifold and whether it consists of a single connected component or multiple disjoint components (\textit{e.g.} two intersecting hyperplanes).
-To this end, we apply a local Principal Component Analysis (PCA, see for example ref.~\cite{scikit-learn}).
+To this end, we apply a local Principal Component Analysis (PCA\footnote{Principal Component Analysis is a dimensionality reduction technique that transforms high-dimensional data into a lower-dimensional space while preserving the maximum amount of variance.
+The method identifies orthogonal linear combinations of the original variables, called principal components, which are ordered by the proportion of total variance they explain.
+PCA operates by computing the eigenvalues and eigenvectors of the data covariance matrix, where the eigenvectors define the direction of maximum variance and the eigenvalues quantify the amount of variance captured along each direction.
+From a physicist point of view, as we are doing it locally, this gives access to information about the local tangent plane.}, see for example ref.~\cite{scikit-learn}).
 For each point, we identify its $k$ nearest neighbours and perform a PCA on that local neighbourhood.
@@
 For $k = 5$, a noticeable fraction of points are assigned dimension 2.
-This can be attributed to the fact that if the true dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality for a fraction of the points.
+This can be attributed to the fact that if the genuine dimension is 3, then selecting only 5 neighbours may not sufficiently populate all three directions, leading the algorithm to underestimate the dimensionality for a fraction of the points.
 Additionally, for $k \geq 20$, we observe an increasing number of points being assigned dimensions 4 or 5.
@@
 
-	\subsection{Initialisation of the algorithm}
+	\subsection{AIS-SMC algorithm}  \label{sec:AIS-SMC_application}
+	Based on the preceding analysis, we have established that our objective is to identify a single, connected three-dimensional manifold.
+Having characterized those geometric structures, we proceed to present the symbolic regression problem, utilizing the points obtained through gradient descent as our training dataset.
+In the following section, we detail the implementation of the AIS-SMC framework previously outlined in Section \ref{Sec:AIS-SMC}.
+
+	\subsubsection{Initialization of the algorithm}
+
 	We initialized the algorithm with
@@
 			&\texttt{lambda = 1000},\\
-			&\texttt{sigma = 0.1}.
+			&\texttt{sigma = 0.1},\\
+			&\texttt{n\_particles = 1000}.
 		\end{aligned}
@@
 
-	\subsection{Analysis of a typical run} \label{sec:singlerun}
+	\subsubsection{Analysis of a typical run}
 	After a run, the 1000 particles are typically distributed into less than 50 different type of polynomials.
@@
 We then filter out all  particles of the same type as this candidate, as they will ultimately give the same polynomial.
-Or (ii), the coefficients are just getting smaller and smaller during the exploration phase, indicating that the only way to minimize the loss with the given monomials is to have very small coefficients.
+Or (ii), the coefficients are just getting smaller and smaller during the exploitation phase, indicating that the only way to minimize the loss with the given monomials is to have very small coefficients.
 The particle is then disregarded.
@@
 	 \end{equation}
-	 with loss $L^{(\lambda = 0)} \simeq 2 \times 10^{3}$. The coefficients have been rounded to the nearest thousandth. After 10,000 steps of exploitation, this particle becomes
+	 with loss $L^{(\lambda = 0)} \simeq 2 \times 10^{3}$ \bd{10e2 maybe?}. The coefficients have been rounded to the nearest thousandth. After 10,000 steps of exploitation, this particle becomes
 	  \begin{equation}
@@
 	 where we normalised the coefficients by setting the one of $x_{2}$ to $2$.
-We are in case (i),the polynomial is a candidate annihilator polynomial.
+We removed $x_1$ monomial, because its coefficient was smaller that $10^{-3}$.
+We are in case (i), the polynomial is a candidate annihilator polynomial.
 After filtering out the 971 particles that are of the same type, the next best particle is
@@
 
-	\subsection{Statistics}
+	\paragraph{Statistics}
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
-It takes approximately 10\,min to do a single run on a regular computer.
+It takes approximately 10\,min to do a single run on a regular computer, including annealing loop and local search described in the previous section.
 \ce{That's with the local search done as described in the previous section.} The code finds the 8 different following polynomials:
@@
 
-	The evolution of the inverse temperature is dictated by eq.~\eqref{eq:acceptanceratioschedule}.
-Note that $\beta$ is equal to $0.02$ in average at the end of the runs.
+	The evolution of the inverse temperature is dictated by eq.~\eqref{eq:eqadaptivetemperatureschedule}.
+Note that $\beta$ is equal to $0.02$ on average at the end of the runs.
 The temperature is thus still quite high, which favours diversity.
 This is a key ingredient to get more than one candidate polynomials per run.
-The end value of $\beta$ is intimately linked to the choice of target acceptance ratio in eq.~\eqref{eq:acceptanceratioschedule}: the lower the acceptance ratio, the higher the inverse temperature $\beta$.
+The end value of $\beta$ is intimately linked to the choice of target adaptative temperature ratio in eq.~\eqref{eq:eqadaptivetemperatureschedule}: the lower the acceptance ratio, the higher the inverse temperature $\beta$.
 On the one hand, if the ratio is too low, very few particles get mutated and it's difficult to explore the space of polynomials and to have diverse outputs.
@@
 	The best loss for each of the 1000 runs is shown in fig.~\ref{fig:lossallASMC} in blue, together with their mean value in yellow, with a logarithmic $y$-axis.
-The losses here do include the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}, and are given without the exploitation phase discussed in sec.~\ref{sec:singlerun}.
+The losses here do include the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}, and are given without the exploitation phase discussed in sec.~\ref{sec:AIS-SMC_application}.
 For a given run, we are plotting the best loss at each epoch, the curves thus do not follow single particles.
@@
 This is linked to the very low value of $\beta$: the exploration is favoured on exploitation during all the process.
-Although the loss is high, 1000 epochs are sufficient to select candidate annihilator polynomials thanks to the exploitation phase performed on the best particles, as illustrated in sec.~\ref{sec:singlerun}.
+Although the loss is high, 1000 epochs are sufficient to select candidate annihilator polynomials thanks to the exploitation phase performed on the best particles, as illustrated in sec.~\ref{sec:AIS-SMC_application}.
 
@@
 In contrast, our method treats all polynomials as equally probable, regardless of their degree, enabling it to uncover more intricate structures more efficiently \footnote{Note that we do not claim that we have used the AIFeynman in the most optimal way.}.
-\newpage
-\section{Details on the algorithm}
-
-\begin{algorithm}
-	\caption{Local Dimension Estimation using PCA}
-	\label{alg:local-dim}
-	\begin{algorithmic}[1]
-
-		\State \textbf{Function} \textsc{LocalDim1Point}($\texttt{x}$, $\texttt{var\_thres}$)
-		\State \hspace{0.5cm} Apply PCA to data matrix $\texttt{x}$
-		\State \hspace{0.5cm} Compute explained variance ratios: $\texttt{lambda\_1, lambda\_2,} \ldots, \texttt{lambda\_d}$
-		\State \hspace{0.5cm} Compute cumulative variance: $\texttt{cumvar\_k} = \sum_{\texttt{i=1}}^\texttt{k} \texttt{lambda\_i}$ for $\texttt{k = 1, }\ldots\texttt{, d}$
-		\State \hspace{0.5cm} Find $\texttt{dim = min\{k : cumvar\_k} \geq \texttt{var\_thres\}}$
-		\State \hspace{0.5cm} \textbf{return} $\texttt{dim}$
-		\State
-
-%		\State \textbf{Function} \textsc{ComputeLocalDim}(\texttt{i, data, neighbors\_idx, var\_thres})
-%		\State \hspace{0.5cm} Extract local neighbors : \texttt{local\_neighbors} $\leftarrow$ \texttt{data[neighbors\_idx[i]]}
-%		\State \hspace{0.5cm} \texttt{dim} $\leftarrow$ \textsc{LocalDim1Point}(\texttt{local\_neighbors, var\_thres})
-%		\State \hspace{0.5cm} \textbf{return} \texttt{[dim, i]}
+%\newpage
+%\section{Details on the algorithm}
+%
+%\begin{algorithm}
+%	\caption{Local Dimension Estimation using PCA}
+%	\label{alg:local-dim}
+%	\begin{algorithmic}[1]
+%		
+%		\State \textbf{Function} \textsc{LocalDim1Point}($\texttt{x}$, $\texttt{var\_thres}$)
+%		\State \hspace{0.5cm} Apply PCA to data matrix $\texttt{x}$
+%		\State \hspace{0.5cm} Compute explained variance ratios: $\texttt{lambda\_1, lambda\_2,} \ldots, \texttt{lambda\_d}$
+%		\State \hspace{0.5cm} Compute cumulative variance: $\texttt{cumvar\_k} = \sum_{\texttt{i=1}}^\texttt{k} \texttt{lambda\_i}$ for $\texttt{k = 1, }\ldots\texttt{, d}$
+%		\State \hspace{0.5cm} Find $\texttt{dim = min\{k : cumvar\_k} \geq \texttt{var\_thres\}}$
+%		\State \hspace{0.5cm} \textbf{return} $\texttt{dim}$
 %		\State
-
-%		\Require \texttt{data} (input data matrix of size \texttt{n $\times$ d}), \texttt{n\_neig} (number of neighbors), \texttt{var\_thres} (variance threshold)
-%		\Ensure Local dimensions for all points
-
-		\State \textbf{Function} \textsc{LocalDimNPoints}(\texttt{data, n\_neig, var\_thres})
-		\State \hspace{0.5cm} \texttt{n\_points} $\leftarrow$ number of rows in \texttt{data}
-		\State \hspace{0.5cm} Initialize \texttt{results} $\leftarrow \emptyset$
-%		\State \hspace{0.5cm} Fit KD-Tree on \texttt{data} with \texttt{n\_neig} neighbors \Comment{Find k-nearest neighbors using KD-Tree}
-		\State \hspace{0.5cm} Compute \texttt{neighbors\_idx} for all points in \texttt{data}
-		\For{\texttt{i = 1} to \texttt{n\_points}} \Comment{Compute local dimensions for all points}
-		\State \texttt{result\_i} $\leftarrow$ \textsc{ComputeLocalDim}(\texttt{i, data, neighbors\_idx, var\_thres})
-		\State Append \texttt{result\_i} to \texttt{results}
-		\EndFor
-
-		\Return \texttt{results}
-	\end{algorithmic}
-\end{algorithm}
-
-In this appendix, we detail the different algorithm that we used. We first here provide a pseudo-code for the AIS-SMC algorithm :
+%		
+%%		\State \textbf{Function} \textsc{ComputeLocalDim}(\texttt{i, data, neighbors\_idx, var\_thres})
+%%		\State \hspace{0.5cm} Extract local neighbors : \texttt{local\_neighbors} $\leftarrow$ \texttt{data[neighbors\_idx[i]]}
+%%		\State \hspace{0.5cm} \texttt{dim} $\leftarrow$ \textsc{LocalDim1Point}(\texttt{local\_neighbors, var\_thres})
+%%		\State \hspace{0.5cm} \textbf{return} \texttt{[dim, i]}
+%%		\State
+%
+%%		\Require \texttt{data} (input data matrix of size \texttt{n $\times$ d}), \texttt{n\_neig} (number of neighbors), \texttt{var\_thres} (variance threshold)
+%%		\Ensure Local dimensions for all points
+%
+%		\State \textbf{Function} \textsc{LocalDimNPoints}(\texttt{data, n\_neig, var\_thres})
+%		\State \hspace{0.5cm} \texttt{n\_points} $\leftarrow$ number of rows in \texttt{data}
+%		\State \hspace{0.5cm} Initialize \texttt{results} $\leftarrow \emptyset$
+%%		\State \hspace{0.5cm} Fit KD-Tree on \texttt{data} with \texttt{n\_neig} neighbors \Comment{Find k-nearest neighbors using KD-Tree}
+%		\State \hspace{0.5cm} Compute \texttt{neighbors\_idx} for all points in \texttt{data}
+%		\For{\texttt{i = 1} to \texttt{n\_points}} \Comment{Compute local dimensions for all points}
+%		\State \texttt{result\_i} $\leftarrow$ \textsc{ComputeLocalDim}(\texttt{i, data, neighbors\_idx, var\_thres})
+%		\State Append \texttt{result\_i} to \texttt{results}
+%		\EndFor
+%
+%		
+%		\Return \texttt{results}
+%	\end{algorithmic}
+%\end{algorithm}
+%
+%
+%In this appendix, we detail the different algorithm that we used. We first here provide a pseudo-code for the AIS-SMC algorithm :
 
@@
 %\end{algorithm}
-
-\begin{algorithm}
-	\caption{Annealing Importance Sampling for Polynomial Discovery}
-	\label{alg:annealing-is}
-	\begin{algorithmic}[1]
-		\Require \texttt{n\_iter} (number of iterations), \texttt{n\_particles} (number of particles), \texttt{target\_acc\_rate}$(\cdot,\cdot)$ (target acceptance rate), \texttt{adaptation\_strength} (temperature adaptation parameter)
-
-		\State Initialize particles $\{\texttt{z\_0}^{(k)}\}_{k=1}^{\texttt{n\_particles}}$ with sparse polynomials
-		\State Set $\texttt{w\_0}^{\texttt{(k)}} = 1/\texttt{n\_particles}$ and $\texttt{w\_unorm\_0}^{\texttt{(k)}} = 1$ for all $\texttt k$ \Comment{normalized and unnormalized weights}
-		\State $\texttt{z\_prev} \leftarrow \texttt{z\_0}$, $\texttt{best\_loss} \leftarrow \infty$, $\texttt{acceptance\_history} \leftarrow \emptyset$, $\texttt{q\_ratio}^{\texttt{(k)}}=1$ for all $k$, $\texttt{beta\_0} \leftarrow \texttt{init\_beta}$ \Comment{q is the proposal ratio}
-
-		\For{$\texttt{i = 1}$ to \texttt{n\_iter}} \Comment{Temperature adaptation}
-		\State $\texttt{beta\_{prev}} \leftarrow \texttt{beta\_current}$
-		\State $\texttt{avg\_acc} \leftarrow$ mean$(\texttt{acceptance\_history})$ \Comment{only of the last 5 epochs}
-		\If{$\texttt{avg\_acc < target\_acc\_rate(i, n\_iter) - 0.05}$}
-		\State $\texttt{beta\_current} \leftarrow \texttt{beta\_current} \times \texttt{(1 - adaptation\_strength)}$
-		\ElsIf{$\texttt{avg\_acc > target\_acc\_rate(i, n\_iter) + 0.05}$}
-		\State $\texttt{beta\_current} \leftarrow \texttt{beta\_current} \times \texttt{(1 + adaptation\_strength)}$
-		\EndIf
-
-		\For{$\texttt{k = 1}$ to \texttt{n\_particles}} \Comment{Reweighting step}
-		\State Compute $\texttt{log(gamma\_i(z\_i}^{\texttt{(k)}} \texttt{)) = - beta\_current} \times \texttt{loss}(\texttt{z\_i}^{\texttt{(k)}}) $
-		\State Compute $\texttt{log(gamma\_(i-1)}(\texttt{z\_(i-1)}^{\texttt{(k)}}\texttt{)) = - beta\_prev} \times \texttt{loss}(\texttt{z\_prev}^{\texttt{(k)}})$
-		\State $\Delta \log \texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{log(gamma\_i(\texttt{z\_i}}^{\texttt{(k)}}  \texttt{) - log(gamma\_(i-1)(z\_(i-1)}^{\texttt{(k)}} \texttt{) + log(q\_ratio}^{\texttt{(k)}}\texttt)$
-		\EndFor
-
-		\State Update unnormalized weights: $\texttt{w\_unorm\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_(i-1)}^{\texttt{(k)}} \times \texttt{exp(}\Delta \texttt{log w\_i}^{\texttt{(k)}}\texttt)$
-		\State Normalize weights: $\texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt/ \sum_{\texttt{j=1}}^{\texttt{n\_particles}} \texttt{w\_unorm\_i}^{\texttt{(j)}}$
-		\State Compute ESS: $\texttt{ESS = 1 /} \sum_{\texttt{k=1}}^{\texttt{n\_particles}} \texttt{(w\_i}^{\texttt{(k)}})^\texttt2$
-
-		\If{$\texttt{ESS < n\_particles / 2}$} \Comment{Resampling}
-		\State Resample particles: $\{\texttt{z\_i}^{\texttt{(k)}}\}_{\texttt{k=1}}^{\texttt{n\_particles}} \sim \texttt{Multinomial}(\texttt{n\_particles}, \{\texttt{w\_i}^{\texttt{(k)}}\}_{\texttt{k=1}}^{\texttt{n\_particles}})$
-		\State Reset weights: $\texttt{w\_i}^{\texttt{(k)}} = \texttt{1/n\_particles}$, $\texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt{= 1}$ for all $\texttt k$
-		\State Update $\texttt{z\_prev}$ accordingly
-		\EndIf
-
-		\State $\texttt{z\_before\_mutation} \leftarrow \texttt{z\_i}$ (save current particles)
-		\For{$\texttt{k = 1}$ to \texttt{n\_particles}} \Comment{Mutating with Metropolis-Hasting}
-		\State Propose $\texttt{z}'^{\texttt{(k)}} \sim \texttt{q}(\texttt{z}'^{\texttt{(k)}} | \texttt{z\_i}^{\texttt{(k)}})$ using specialized MH proposal
-		\State Compute $ \texttt{log(p\_current}^{\texttt{(k)}} \texttt{) = - beta\_current} \times \texttt{loss}(\texttt{z\_i}^{\texttt{(k)}}) + \texttt{sparsity\_prior}(\texttt{z\_i}^{\texttt{(k)}})$
-		\State Compute $\texttt{log(p\_proposed}^{\texttt{(k)}} \texttt{) = - beta\_current} \times \texttt{loss}(\texttt{z}'^{\texttt{(k)}}) + \texttt{sparsity\_prior}(\texttt{z}'^{\texttt{(k)}})$
-		\State $\texttt{log(alpha}^{\texttt{(k)}} \texttt) \leftarrow  \texttt{log(p\_proposed}^{\texttt{(k)}}  \texttt{) -  log(p\_current}^{\texttt{(k)}}  \texttt{) + log(q\_ratio}^{\texttt{(k)}}\texttt)$
-		\State Generate $\texttt{u}^{\texttt{(k)}} \sim \mathcal{U}\texttt{(0,1)}$
-		\If{$\texttt{u}^{\texttt{(k)}} \texttt{ < alpha}^{\texttt{(k)}}$}
-		\State $\texttt{z\_i}^{\texttt{(k)}} \leftarrow \texttt{z}'^{\texttt{(k)}}$ (accept proposal)
-		\EndIf
-		\EndFor
-
-		\State $\texttt{acceptance\_rate} \leftarrow$ fraction of accepted proposals
-		\State Add $\texttt{acceptance\_rate}$ to $\texttt{acceptance\_history}$
-		\State $\texttt{z\_prev} \leftarrow \texttt{z\_before\_mutation}$ (update for next iteration)
-
-		\EndFor
-
-		\Return \texttt{final particles, final losses, final weights}
-	\end{algorithmic}
-\end{algorithm}
-
-This pseudo code sketch how does our annealing loops work.
+%
+%\begin{algorithm}
+%	\caption{Annealing Importance Sampling for Polynomial Discovery}
+%	\label{alg:annealing-is}
+%	\begin{algorithmic}[1]
+%		\Require \texttt{n\_iter} (number of iterations), \texttt{n\_particles} (number of particles), \texttt{target\_acc\_rate}$(\cdot,\cdot)$ (target acceptance rate), \texttt{adaptation\_strength} (temperature adaptation parameter)
+%		
+%		\State Initialize particles $\{\texttt{z\_0}^{(k)}\}_{k=1}^{\texttt{n\_particles}}$ with sparse polynomials
+%		\State Set $\texttt{w\_0}^{\texttt{(k)}} = 1/\texttt{n\_particles}$ and $\texttt{w\_unorm\_0}^{\texttt{(k)}} = 1$ for all $\texttt k$ \Comment{normalized and unnormalized weights}
+%		\State $\texttt{z\_prev} \leftarrow \texttt{z\_0}$, $\texttt{best\_loss} \leftarrow \infty$, $\texttt{acceptance\_history} \leftarrow \emptyset$, $\texttt{q\_ratio}^{\texttt{(k)}}=1$ for all $k$, $\texttt{beta\_0} \leftarrow \texttt{init\_beta}$ \Comment{q is the proposal ratio}
+%		
+%		\For{$\texttt{i = 1}$ to \texttt{n\_iter}} \Comment{Temperature adaptation}
+%		\State $\texttt{beta\_{prev}} \leftarrow \texttt{beta\_current}$
+%		\State $\texttt{avg\_acc} \leftarrow$ mean$(\texttt{acceptance\_history})$ \Comment{only of the last 5 epochs}
+%		\If{$\texttt{avg\_acc < target\_acc\_rate(i, n\_iter) - 0.05}$}
+%		\State $\texttt{beta\_current} \leftarrow \texttt{beta\_current} \times \texttt{(1 - adaptation\_strength)}$
+%		\ElsIf{$\texttt{avg\_acc > target\_acc\_rate(i, n\_iter) + 0.05}$}
+%		\State $\texttt{beta\_current} \leftarrow \texttt{beta\_current} \times \texttt{(1 + adaptation\_strength)}$
+%		\EndIf
+%		
+%		\For{$\texttt{k = 1}$ to \texttt{n\_particles}} \Comment{Reweighting step}
+%		\State Compute $\texttt{log(gamma\_i(z\_i}^{\texttt{(k)}} \texttt{)) = - beta\_current} \times \texttt{loss}(\texttt{z\_i}^{\texttt{(k)}}) $
+%		\State Compute $\texttt{log(gamma\_(i-1)}(\texttt{z\_(i-1)}^{\texttt{(k)}}\texttt{)) = - beta\_prev} \times \texttt{loss}(\texttt{z\_prev}^{\texttt{(k)}})$
+%		\State $\Delta \log \texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{log(gamma\_i(\texttt{z\_i}}^{\texttt{(k)}}  \texttt{) - log(gamma\_(i-1)(z\_(i-1)}^{\texttt{(k)}} \texttt{) + log(q\_ratio}^{\texttt{(k)}}\texttt)$
+%		\EndFor
+%		
+%		\State Update unnormalized weights: $\texttt{w\_unorm\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_(i-1)}^{\texttt{(k)}} \times \texttt{exp(}\Delta \texttt{log w\_i}^{\texttt{(k)}}\texttt)$
+%		\State Normalize weights: $\texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt/ \sum_{\texttt{j=1}}^{\texttt{n\_particles}} \texttt{w\_unorm\_i}^{\texttt{(j)}}$
+%		\State Compute ESS: $\texttt{ESS = 1 /} \sum_{\texttt{k=1}}^{\texttt{n\_particles}} \texttt{(w\_i}^{\texttt{(k)}})^\texttt2$
+%		
+%		\If{$\texttt{ESS < n\_particles / 2}$} \Comment{Resampling}
+%		\State Resample particles: $\{\texttt{z\_i}^{\texttt{(k)}}\}_{\texttt{k=1}}^{\texttt{n\_particles}} \sim \texttt{Multinomial}(\texttt{n\_particles}, \{\texttt{w\_i}^{\texttt{(k)}}\}_{\texttt{k=1}}^{\texttt{n\_particles}})$
+%		\State Reset weights: $\texttt{w\_i}^{\texttt{(k)}} = \texttt{1/n\_particles}$, $\texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt{= 1}$ for all $\texttt k$
+%		\State Update $\texttt{z\_prev}$ accordingly
+%		\EndIf
+%		
+%		\State $\texttt{z\_before\_mutation} \leftarrow \texttt{z\_i}$ (save current particles)
+%		\For{$\texttt{k = 1}$ to \texttt{n\_particles}} \Comment{Mutating with Metropolis-Hasting}
+%		\State Propose $\texttt{z}'^{\texttt{(k)}} \sim \texttt{q}(\texttt{z}'^{\texttt{(k)}} | \texttt{z\_i}^{\texttt{(k)}})$ using specialized MH proposal
+%		\State Compute $ \texttt{log(p\_current}^{\texttt{(k)}} \texttt{) = - beta\_current} \times \texttt{loss}(\texttt{z\_i}^{\texttt{(k)}}) + \texttt{sparsity\_prior}(\texttt{z\_i}^{\texttt{(k)}})$
+%		\State Compute $\texttt{log(p\_proposed}^{\texttt{(k)}} \texttt{) = - beta\_current} \times \texttt{loss}(\texttt{z}'^{\texttt{(k)}}) + \texttt{sparsity\_prior}(\texttt{z}'^{\texttt{(k)}})$
+%		\State $\texttt{log(alpha}^{\texttt{(k)}} \texttt) \leftarrow  \texttt{log(p\_proposed}^{\texttt{(k)}}  \texttt{) -  log(p\_current}^{\texttt{(k)}}  \texttt{) + log(q\_ratio}^{\texttt{(k)}}\texttt)$
+%		\State Generate $\texttt{u}^{\texttt{(k)}} \sim \mathcal{U}\texttt{(0,1)}$
+%		\If{$\texttt{u}^{\texttt{(k)}} \texttt{ < alpha}^{\texttt{(k)}}$}
+%		\State $\texttt{z\_i}^{\texttt{(k)}} \leftarrow \texttt{z}'^{\texttt{(k)}}$ (accept proposal)
+%		\EndIf
+%		\EndFor
+%		
+%		\State $\texttt{acceptance\_rate} \leftarrow$ fraction of accepted proposals
+%		\State Add $\texttt{acceptance\_rate}$ to $\texttt{acceptance\_history}$
+%		\State $\texttt{z\_prev} \leftarrow \texttt{z\_before\_mutation}$ (update for next iteration)
+%		
+%		\EndFor
+%		
+%		\Return \texttt{final particles, final losses, final weights}
+%	\end{algorithmic}
+%\end{algorithm}
+%
+%This pseudo code sketch how does our annealing loops work.
 Here is the pseudo-code for the initialization of each individual polynomial.
@@
 However, in the spirit of making "small" steps in the search space, we decided not to for now.
-
-\begin{algorithm}
-	\caption{Initialize Sparse Polynomials}
-	\label{alg:initialize-sparse}
-	\begin{algorithmic}[1]
-		\Require $\texttt{n\_particles}$ (number of particles), $\texttt{max\_degree}$ (maximum polynomial degree), $\texttt{num\_vars}$ (number of variables), $\texttt{max\_num\_monomials}$ (maximum number of monomials per polynomial), $\texttt{num\_terms}$ (total number of possible terms)
-
-		\State $\texttt{particles} \leftarrow \mathbf{0}_{\texttt{n\_particles} \times \texttt{num\_terms}}$
-		\State $\texttt{max\_monomials} \leftarrow \texttt{max\_num\_monomials}$
-
-		\State $\texttt{n\_mon\_to\_max\_order} \leftarrow \binom{\texttt{max\_degree + num\_vars}}{\texttt{max\_degree}}$ \Comment{Compute total number of possible monomials up to max degree}
-
-		\State $\texttt{n\_mon\_all\_coeff} \leftarrow \emptyset$
-		\State $\texttt{n\_tot\_pol} \leftarrow \texttt{0}$ 
-		\For{$\texttt{i = 1}$ to $\texttt{max\_num\_monomials}$} \Comment{Compute probability distribution over number of monomials}
-		\State $\texttt{n\_mon\_i\_coeff} \leftarrow \binom{\texttt{n\_mon\_to\_max\_order}}{i}$ \Comment{Number of polynomials with exactly $i$ monomials}
-		\State $\texttt{n\_tot\_pol} \leftarrow \texttt{n\_tot\_pol + n\_mon\_i\_coeff}$
-		\State Append $\texttt{n\_mon\_i\_coeff}$ to $\texttt{n\_mon\_all\_coeff}$
-		\EndFor
-
-		\State $\texttt{proba} \leftarrow \texttt{n\_mon\_all\_coeff / n\_tot\_pol}$ \Comment{Normalize to get probabilities}
-
-		\For{$\texttt{i = 1}$ to $\texttt{n\_particles}$} \Comment{Generate particles}
-
-		\State $\texttt{num\_monomials} \sim \texttt{Categorical(\{1, 2, \ldots, max\_monomials\}, proba)}$ \Comment{Sample number of monomials according to computed distribution}
-
-		\State $\texttt{nonzero\_indices}\leftarrow$ sample $\texttt{num\_monomials}$ indices from $\{\texttt{1, 2, }\ldots, \texttt{num\_terms}\}$ without replacement \Comment{Randomly select which monomials will be non-zero}
-
-		\For{\texttt{j} $ \in \texttt{nonzero\_indices}$} \Comment{Generate random coefficients}
-		\State $\texttt{particles[i, j] }\leftarrow \mathcal{U}(-2,2)$ 
-		\Comment{Uniform in $[-2, 2]$}
-		\EndFor
-		\EndFor
-
-		\Return $\texttt{particles}$
-	\end{algorithmic}
-\end{algorithm}
+%
+%\begin{algorithm}
+%	\caption{Initialize Sparse Polynomials}
+%	\label{alg:initialize-sparse}
+%	\begin{algorithmic}[1]
+%		\Require $\texttt{n\_particles}$ (number of particles), $\texttt{max\_degree}$ (maximum polynomial degree), $\texttt{num\_vars}$ (number of variables), $\texttt{max\_num\_monomials}$ (maximum number of monomials per polynomial), $\texttt{num\_terms}$ (total number of possible terms)
+%		
+%		\State $\texttt{particles} \leftarrow \mathbf{0}_{\texttt{n\_particles} \times \texttt{num\_terms}}$
+%		\State $\texttt{max\_monomials} \leftarrow \texttt{max\_num\_monomials}$
+%		
+%		\State $\texttt{n\_mon\_to\_max\_order} \leftarrow \binom{\texttt{max\_degree + num\_vars}}{\texttt{max\_degree}}$ \Comment{Compute total number of possible monomials up to max degree}
+%		
+%		\State $\texttt{n\_mon\_all\_coeff} \leftarrow \emptyset$
+%		\State $\texttt{n\_tot\_pol} \leftarrow \texttt{0}$ 
+%		\For{$\texttt{i = 1}$ to $\texttt{max\_num\_monomials}$} \Comment{Compute probability distribution over number of monomials}
+%		\State $\texttt{n\_mon\_i\_coeff} \leftarrow \binom{\texttt{n\_mon\_to\_max\_order}}{i}$ \Comment{Number of polynomials with exactly $i$ monomials}
+%		\State $\texttt{n\_tot\_pol} \leftarrow \texttt{n\_tot\_pol + n\_mon\_i\_coeff}$
+%		\State Append $\texttt{n\_mon\_i\_coeff}$ to $\texttt{n\_mon\_all\_coeff}$
+%		\EndFor
+%		
+%		\State $\texttt{proba} \leftarrow \texttt{n\_mon\_all\_coeff / n\_tot\_pol}$ \Comment{Normalize to get probabilities}
+%
+%		\For{$\texttt{i = 1}$ to $\texttt{n\_particles}$} \Comment{Generate particles}
+%
+%		\State $\texttt{num\_monomials} \sim \texttt{Categorical(\{1, 2, \ldots, max\_monomials\}, proba)}$ \Comment{Sample number of monomials according to computed distribution}
+%		
+%		\State $\texttt{nonzero\_indices}\leftarrow$ sample $\texttt{num\_monomials}$ indices from $\{\texttt{1, 2, }\ldots, \texttt{num\_terms}\}$ without replacement \Comment{Randomly select which monomials will be non-zero}
+%		
+%		\For{\texttt{j} $ \in \texttt{nonzero\_indices}$} \Comment{Generate random coefficients}
+%		\State $\texttt{particles[i, j] }\leftarrow \mathcal{U}(-2,2)$ 
+%		\Comment{Uniform in $[-2, 2]$}
+%		\EndFor
+%		\EndFor
+%		
+%		\Return $\texttt{particles}$
+%	\end{algorithmic}
+%\end{algorithm}
 

### 2025-09-10 Draft_MLFlatDirections.tex
Add changes on the AIFeynman appendix (time and comments)

@@
 
-	\subsubsection{Analysis of a typical run}
+	\subsubsection{Analysis of a typical run}\label{sec:1runanalysis}
 	After a run, the 1000 particles are typically distributed into less than 50 different type of polynomials.
@@
 	\begin{aligned}
-		&\texttt{BF\_try\_time} = 300, \\
-		&\texttt{polyfit\_deg} = 6, \\
-		&\texttt{NN\_epochs} = 5000.\\
+		&\texttt{BF\_try\_time} = 60, \\
+		&\texttt{polyfit\_deg} = 5, \\
+		&\texttt{NN\_epochs} = 1000.\\
 	\end{aligned}
@@
 While the AIFeynman code is able to recover one of the constraints, it exhibits several drawbacks compared to our method.
-First, it is significantly slower: it required TIME (to be specified) compared to approximately 600 seconds for a single run of our ASMC algorithm.
+First, it is significantly slower: it required 5685 seconds (1 hour 34 minutes and 45 seconds) compared to approximately 600 seconds for a single run of our ASMC algorithm \footnote{This time only accounts for the annealing loop, without the local search algorithm described in section \ref{sec:1runanalysis}.
+Furthermore, this computational time reflects the overhead incurred by verifying at each iteration whether the particles reproduce one of the polynomials specified in Eq.
+\eqref{eq:pols}, which substantially increases the overall execution time.
+In the absence of this verification step, the annealing loop would require approximately 350 seconds on standard computational hardware.}.
 Moreover, the AIFeynman framework is based on expressing one variable as a function of the others, which assumes the invertibility of the underlying relation.

### 2025-09-10 Draft_MLFlatDirections.tex
typo
Changes during meeting

@@
 
-{\Large Machine learning the Conformal Manifold of Holographic CFT2’s}
+{\Large Machine Learning the Conformal Manifold of Holographic CFT2’s}
 
@@
 
-In this work, we demonstrate the viability of the aforementioned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of six-dimensional non-chiral $\mathcal{N} = (1,1)$ supergravity on $AdS_3 \times S^3$, or to type IIB supergravity on $AdS_3 \times S^3 \times T^4$.
+In this work, we demonstrate the viability of the aforementioned machine learning approach by applying it to a five-scalar subsector of a 13 scalar consistent truncation of six-dimensional non-chiral $\mathcal{N} = (1,1)$ supergravity on ${\rm AdS}_3 \times S^3$, or to type IIB supergravity on ${\rm AdS}_3 \times S^3 \times T^4$.
 Our methodology combines gradient descent sampling of the conformal manifold with a symbolic regression technique.
 There exists a large body of literature on symbolic regression, using methods from genetic programming \cite{koza1994genetic,virgolin2021improving,randall2022bingo,burlacu2019parsimony}, to deep learning \cite{petersen2019deep,kamienny2022end}, generative models \cite{valipour2021symbolicgpt}, diffusion models \cite{bastiani2025diffusion}, and equation learning with the nodes being symbolic operations \cite{2018arXiv180607259S}.
-An state-of-the-art algorithm is AIFeynman \cite{Udrescu:2019mnk}.
-It uses neural networks to identify structures in the dataset (such as translational symmetries, multiplicative separability, compositionality\dots) to recursively define simpler problems on which they can fit the solutions with polynomials.
-However, this method is slow, usually limited to low-dimensional spaces, and, by construction, can only fit one polynomial at a time.
+A state-of-the-art algorithm is AIFeynman \cite{Udrescu:2019mnk}.
+It uses neural networks to identify structures in the dataset (such as translational symmetries, multiplicative separability, compositionality\dots) to recursively define simpler problems on which they can fit the solutions with polynomials and basic functions.
+However, this method is slow, usually limited to low-dimensional spaces, and, by construction, can only fit one expression at a time.
 Alternatively, we develop here a symbolic regression algorithm based on Annealing Importance Sampling (AIS) \cite{neal1998annealedimportancesampling}, since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces
@@
 The study of the five-parameter potential is separated into several parts.
-We first use the gradient descent to efficiently sample the underlying conformal manifold.
+We first use a gradient descent to efficiently sample the underlying conformal manifold.
 Combined with numerical analyses, including a local principal component analysis, we can identify the existence of a three-dimensional continuous family.
-We then use an AIS technique combined with a sequential Monte Carlo approach (SMC) \cite{del2006sequential} in order to do symbolic regression.
+We then use an AIS technique combined with a sequential Monte Carlo approach~(SMC)~\cite{del2006sequential} in order to do symbolic regression.
 As we will indeed demonstrate in the paper, there exist polynomial constraints on the 5 parameters, viewed as embedding coordinates, that project them onto the 3 dimensional manifolds.
@@
 The paper is organized as follows.
-In sec.~\ref{sec:sugra}, we establish the supergravity setup, presenting the scalar potential in its full complexity and motivating the truncation to five fields.
-Sec.~\ref{sec:numanal} details our numerical methodology, covering both the gradient descent sampling procedure and the annealed importance sampling approach to symbolic regression.
+In sec.~\ref{sec:sugra}, we establish the supergravity setup, presenting the scalar potential in its full complexity and motivating the restriction to five fields.
+Sec.~\ref{Sec:AIS-SMC} details our annealed importance sampling approach to symbolic regression.
 We present in sec.~\ref{sec:results} our main results, both numerical an analytical.
+Sec.~\ref{sec:sugrasol} gives some details on the new supergravity solutions discovered by the numerical analysis.
 Finally, sec.~\ref{sec:ccl} concludes with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
@@
 
-For the theory introduced above and to be discussed below, this is a 3$d$ manifold embedded in a 5$d$ space.
-Therefore we can conclude that, in order to characterize the manifold, we need two independent constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
-If we have a look at the form of the potential, we can observe that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to some potential global factor of the dilaton of the form $e^{\tilde{x}_8}$, this potential is actually a polynomial of the embedding coordinates.
-Therefore, the components of $|\nabla V|$ are also polynomials in those variables.
-We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those.
-Note that we are now taking $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$.
-
-Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
-The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
+\ce{Add small intro here.}
 
@@
 When all data points lie within the interval $[-1, 1]$, the SR algorithm tends to favor high-degree polynomials, as these often yield smaller values over this range, thereby artificially lowering the loss.
-Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of polynomials that exploit this effect.} \ce{Put the footnote later in the SR section?} \bd{I believe here is great to justify the volume of the hypercube.
-Otherwise it remains a bit misterious}.
+Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of polynomials that exploit this effect.}.
 As the example we are focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points: we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
@@
 In these scatter plots, orange points belong to the main cluster, while blue points are those that the algorithm failed to assign to any cluster.
-The few yellow points correspond to the smallest cluster of 5 points.
+The smallest cluster, made of 5 points, is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
 The size of the different points has been adjusted to facilitate the visualisation.
@@
 We therefore interpret their unassigned status not as evidence of belonging to another manifold, but rather as a result of insufficient local density near the edges of the dataset.
-The smallest yellow cluster is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
 Thus, the algorithm does indicate that over 99\% of the data belongs to a single dominant cluster.
@@
 		\caption{3d projections of the data set in selected coordinates: (a) $(x_4, x_8, x_{10})$ and (b) $(x_1, x_4, x_8)$.
-The colors are assigned by the clustering algorithm: the orange and yellow points correspond to two different clusters, while the blue points were not assigned to any cluster.
+The colors are assigned by the clustering algorithm: the orange points correspond to the cluster, while the blue points were not assigned to any cluster.
 The size of each class of points has been tuned to favour the visualisation.}
@@
 
-	From this analysis, we conclude that the gradient descent procedure has produced a sampling of a single, connected, three-dimensional manifold.
-
-	\subsection{AIS-SMC algorithm}  \label{sec:AIS-SMC_application}
-	Based on the preceding analysis, we have established that our objective is to identify a single, connected three-dimensional manifold.
-Having characterized those geometric structures, we proceed to present the symbolic regression problem, utilizing the points obtained through gradient descent as our training dataset.
-In the following section, we detail the implementation of the AIS-SMC framework previously outlined in Section \ref{Sec:AIS-SMC}.
+	\subsection{AIS-SMC algorithm and results}  \label{sec:AIS-SMC_application}
+	From the preceding analysis, we conclude that the gradient descent procedure has produced a sampling of a single, connected, three-dimensional manifold.
+Therefore to characterize the manifold, we need two independent constraints on the coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
+If we have a look at the form of the potential, we can observe that if we use $x_{i} = e^{\tilde{x}_i}$, that, up to some potential global factor and field redefinitions, this potential is actually a polynomial on the $\vec{X}$ coordinates.
+Therefore, the components of $\left.\nabla V\right|_{\vec{y}=0}$ are also polynomials on the $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$ coordinates.
+We conclude that the constraints on $\vec{x}$ we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those.
+Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
+The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
+We now proceed to present the symbolic regression problem, utilizing the points obtained through gradient descent as our training dataset.
+In the following section, we detail the implementation of the AIS-SMC framework previously outlined in sec.~\ref{Sec:AIS-SMC}.
 
@@
 There are two possible outputs after this phase.
-(i) The coefficients stay finite, and the particle is a candidate annihilator polynomial.
+(i)~The coefficients stay finite, and the particle is a candidate annihilator polynomial.
 We then filter out all  particles of the same type as this candidate, as they will ultimately give the same polynomial.
@@
 	 \end{equation}
-	 with loss $L^{(\lambda = 0)} \simeq 2 \times 10^{3}$ \bd{10e2 maybe?}. The coefficients have been rounded to the nearest thousandth. After 10,000 steps of exploitation, this particle becomes
+	 with loss $L^{(\lambda = 0)} \simeq 2.1 \times 10^{3}$. The coefficients have been rounded to the nearest thousandth. After 10,000 steps of exploitation, this particle becomes
 	  \begin{equation}
@@
 	 \begin{equation} \label{eq:expol1}
-	 	2\,x_{2} + 2.000\,x_{1}x_{4} + 1.415\,x_{1}x_{10} - 2.000\,x_{2}x_{8} - 1.000\,x_{2}x_{8}x_{10}^{2}.
+	 	2\,x_{2} + 2.000\,x_{1}x_{4} + 1.415\,x_{1}x_{10} - 2.000\,x_{2}x_{8} - 1.000\,x_{2}x_{8}x_{10}^{2},
 	 \end{equation}
 	 where we normalised the coefficients by setting the one of $x_{2}$ to $2$.
-We removed $x_1$ monomial, because its coefficient was smaller that $10^{-3}$.
+We removed the $x_1$ monomial, because its coefficient was smaller that $10^{-3}$.
 We are in case (i), the polynomial is a candidate annihilator polynomial.
@@
 	 \end{equation}
-	 with a loss $L^{(\lambda = 0)} \simeq 2 \times 10^{3}$. After the exploitation phase, it becomes
+	 with a loss $L^{(\lambda = 0)} \simeq 2.4 \times 10^{3}$. After the exploitation phase, it becomes
 	 \begin{equation}
@@
 This is an example of case (ii), we disregard this particle.
-Reproducing similar steps for the remaining particles, we get some uninteresting particles and two new candidate polynomials (with normalised coefficients): \ce{I had to replace $x_{4}$ as given in the data to $x_{4}/2$ to have the right polynomials.}
+Reproducing similar steps for the remaining particles, we get some uninteresting particles and two new candidate polynomials (with normalised coefficients):
 	 \begin{subequations}
@@
 
-	\paragraph{Statistics}
+	\subsubsection{Statistics}
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
 It takes approximately 10\,min to do a single run on a regular computer, including annealing loop and local search described in the previous section.
-\ce{That's with the local search done as described in the previous section.} The code finds the 8 different following polynomials:
+The code finds the 8 different following polynomials:
 	\begin{subequations} \label{eq:pols}
@@
 %%%%%%%%%%%%%%%%%%%
-\section{Supergravity Solutions}
+\section{Supergravity Solutions} \label{sec:sugrasol}
 In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in eq.~\eqref{eq:pols}.
-We know from sec.~\ref{sec:gadientlocalanalysis} that the manifold we are aiming at parametrising is three-dimensional.
+We know from sec.~\ref{sec:results} that the manifold we are aiming at parametrising is three-dimensional.
 As the parameter space is of dimension $5$, we only need two constraints to define the solutions, and the eight polynomials of eq.~\eqref{eq:pols} are not independent.
@@
 
-\section{Comparison with AIFeynman} \ce{Appendix?}
-We have used the state-of-the-art technique \texttt{AIFeynman} \cite{} on our dataset, with again $x_8 = \exp(\tilde{x}_8)$, so as to identify polynomial expressions fitting the data.
+\section{Comparison with AIFeynman}
+We have used the state-of-the-art technique \texttt{AIFeynman} \cite{Udrescu:2019mnk} on our dataset, with again $x_8 = \exp(\tilde{x}_8)$, so as to identify polynomial expressions fitting the data.
 We have run it with the following configuration
@@
 
-In this algorithm, one tries to fit one of the variables in term of the others. Here, we used it to fit $x_{10}$ in terms of the others. The AIFeynman algorithm finds a solution in TIME : 
+In this algorithm, one tries to fit one of the variables in term of the others. Here, we used it to fit $x_{10}$ in terms of the others. The AIFeynman algorithm finds a solution: 
 \begin{equation}
@@
 In addition, AIFeynman is limited to recovering one constraint per run, whereas our ASMC method can discover multiple constraints simultaneously.
-This is reflected in our results, where each run identified an average of 2.15 polynomials, with up to 4 found in the best case.
+This is reflected in our results, where each run identified an average of 2.2 polynomials, with up to 4 found in the best case.
 Finally, the brute-force regression strategy used by AIFeynman makes it less effective for identifying higher-degree polynomials, whose complexity increases the search difficulty.

### 2025-09-12 Draft_MLFlatDirections.tex
Dealing with the intro of sec. 4 and the scalar masses.

@@
 These deformations are parametrised by exactly marginal operators, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
-\ce{Needs some modifications.}
+%%ICI \ce{Needs some modifications.}
 
@@
 
-		We have adapted the classic approach outilned above.
+		We have adapted the classic approach outlined above.
 As can be seen in \eqref{eq:gamman}, what matters the most to determine $\gamma_{n}$ is not the inverse temperature, but rather the product of the inverse temperature and the loss function.
@@
 This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
-\bd{Move \ref{eq:eqadaptivetemperatureschedule} in seciton 4?}
+%ICI \bd{Move \eqref{eq:eqadaptivetemperatureschedule} in section 4?}
 
@@
 This allow to fine-tune the coefficients.
-\ce{Mention threshold?
+%%ICI \ce{Mention threshold?
 And number of iterations?}
@@
 \section{Numerical Analysis and Results} \label{sec:results}
-
-\ce{Add small intro here.}
+We now detail the numerical analysis and present our main results.
+We start by describing how we sampled the solutions manifold using a gradient descent.
+Once the manifold correctly sampled, we determine its dimension using a local principal component analysis and a clustering procedure.
+We finally exploit the annealed importance sampling algorithm described in sec.~\ref{Sec:AIS-SMC} to find an analytical characterisation of the manifold.
 
@@
 		\centering
-		\centering
 		\subfigure{ \label{fig:3dx4x8x10}
@@
 	\end{equation}
-	\gl{link to notations in section 3}
+	%ICI \gl{link to notations in section 3}
 	This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
@@
 
-	\ce{Wouldn't it be interesting to give the scalar masses and speak of the stability of the 3d solution? Would be useful to make contact with ref.~\cite{Eloy:2021fhc}.}
+	The spectrum of scalar fields around the flat directions is the following:
+	\begin{equation}
+		\begin{aligned}
+			\big(m_{(0)}\ell_{\rm AdS}\big)^{2}: & \qquad 0 \ [5], \quad 8 \ [1], \quad r^{2}\big(4+r^{2}\big)\ [8],\\
+			& \quad 2\,r\left(3\,r + r^{3} - r\cos(2\theta) \pm \big(2+r^{2}\big) \sqrt{2+r^{2}-2\cos(2\theta)} \right)\ [2+2].
+		\end{aligned}
+	\end{equation}
+	The masses are normalised with respect to the AdS length $\ell_{\rm AdS}^{2} = -2/V(0) = 1/2$.
+The numbers between brackets indicate the multiplicity of each mode.
+The three-dimensional spectrum is thus stable (\textit{i.e.} satisfies the Breitenlohner-Freedman bound $\big(m_{(0)}\ell_{\rm AdS}\big)^{2}\geq -1$~\cite{Breitenlohner:1982jf}) if
+	\begin{equation}
+		\theta = \pm\frac{1}{2}\,\arccos\left(-1 + \sqrt{3} + \frac{- 7 + 4\sqrt{3})}{2\,r^2}\right) \quad {\rm and} \quad r \geq \sqrt{-2+\frac{7}{2\sqrt{3}}}.
+	\end{equation}
 
@@
 As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
-\ce{Not sure if I agree with the last sentence.
+%ICI \ce{Not sure if I agree with the last sentence.
 Maybe we could weaken the statement a bit?}

### 2025-09-15 Draft_MLFlatDirections.tex
Abstract propostion

@@
 
-\begin{center}
-\textbf{Abstract}
-\end{center}
+\begin{abstract}
+	We investigate the structure of conformal manifolds arising in the context of the AdS$_3$/CFT$_2$ correspondence, with a focus on continuous flat directions in the scalar potential of gauged supergravity.
+Starting from a consistent truncation of six-dimensional $N=(1,1)$ supergravity compactified on AdS$_3 \times S^3$, we restrict to a five-scalar subsector and search for flat directions around the AdS$_3 \times S^3$ vacuum.
+	Our approach combines numerical exploration and symbolic inference.
+We first employ gradient descent methods to efficiently sample the solution space and identify the dimensionality of the underlying manifold.
+The analysis reveals a connected three-dimensional family of solutions preserving the AdS$_3$ background.
+To obtain analytic relations, we develop a symbolic regression algorithm based on Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
+	The algorithm reconstructs a set of polynomial relations projecting a five embedding set of coordinates onto the three-dimensional manifold, thereby providing an explicit analytic parametrization of the solutions.
+	This work demonstrates the potential of machine learning techniques to bypass the complexity of direct symbolic manipulation in supergravity and opens the way for systematic classifications of conformal manifolds in holographic theories.
+\end{abstract}
 

### 2025-09-22 Draft_MLFlatDirections.tex
Updated section 3 and added a few minor edits on sec 4

--- 2025-09-12 Draft_MLFlatDirections.tex
@@
 
-MI-HET-??? \\
 \today
@@
 
-\begin{center}
-\textbf{Abstract}
-\end{center}
-
-\begin{quote}
-
-...
-
-\end{quote}
+\begin{abstract}
+	We investigate the structure of conformal manifolds around AdS$_3 \times S^3$ which lift from continuous flat directions in the scalar potential of gauged supergravity resulting from six-dimensional $\mathcal{N}=(1,1)$.
+	Our approach combines numerical exploration and symbolic inference.
+For the latter, we develop a symbolic regression algorithm based on Sequential Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
+	The algorithm reconstructs a set of polynomial relations that provides an explicit analytic parametrization of a new family of solutions. 
+\end{abstract}
 
@@
 Sec.~\ref{Sec:AIS-SMC} details our annealed importance sampling approach to symbolic regression.
-We present in sec.~\ref{sec:results} our main results, both numerical an analytical.
-Sec.~\ref{sec:sugrasol} gives some details on the new supergravity solutions discovered by the numerical analysis.
-Finally, sec.~\ref{sec:ccl} concludes with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
+Our main results, both numerical an analytical, are presented in sec.~\ref{sec:results}, and sec.~\ref{sec:sugrasol} gives some details on the new supergravity solutions discovered by the numerical analysis.
+We conclude with prospects for extending this approach to higher-dimensional cases and its broader implications for systematic studies of conformal manifolds in holographic theories.
 
@@
 
-The numerical search described above results in clouds of points embedded in a higher-dimensional space. 
-In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe such datasets.
-In the problem discussed in this paper, we are looking for polynomial expressions such that $p(\vec{x}^{\,i}) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
-This task involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods.
-Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and getting trapped in local optima, especially in high-dimensional or multimodal spaces.
-
-To address these challenges, we employ an Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} combined with Sequential Monte Carlo (SMC) methods. 
-AIS aims to estimate ratios of partition functions by constructing a sequence of intermediate distributions that smoothly transition from an initial, tractable distribution (e.g., a prior over symbolic expressions) to the complex target posterior distribution.
+The numerical sampling of the space of vacua described above results in clouds of points embedded in a higher-dimensional space. 
+In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe the embedding of these loci of solutions. 
+In the present context, the form of the supergravity potential \eqref{eq:scalarpotential} determining the solutions implies that the loci can be defined through polynomial expressions such that $p(\vec{x}^{\,i}) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
+Finding such polynomials involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods. 
+Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and often get trapped in local optima, especially in high-dimensional or multimodal spaces \cite{??}.
+
+To address these challenges, we employ an Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} combined with Sequential Monte Carlo (SMC) methods \cite{naesseth2024elementssequentialmontecarlo}.
+AIS aims to estimate ratios of partition functions by constructing a sequence of intermediate distributions that smoothly transition from an initial, tractable distribution (e.g.
+a prior over symbolic expressions) to the complex target posterior distribution.
 This annealing process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient exploration of the probability landscape.
 
-SMC enhances this procedure by propagating a population of particles—each representing a candidate symbolic expression—through the sequence of distributions.
-At each step, particles are reweighted based on the incremental change in the distribution, resampled to focus computational effort on high-probability regions, and mutated via operations.
+SMC realises this procedure by encoding the probability distributions into a set of particles—each representing a candidate symbolic expression— and weights, and making them evolve so as to focus computational effort on high-probability regions.
 This combination of importance sampling, resampling, and mutation maintains diversity among the particles and prevents premature convergence to suboptimal models.
@@
 
-Let us now explain in more detail how does this procedure goes.
-The goal is to reconstruct some distribution function $d(z)$, where here $z$ in going to be some polynomial.
-We will try to reconstruct this density function by series of density function $\pi_n(z_n) = \gamma_n(z_n)/Z_n$ with $n = 1,\dots,N$ the number of annealing steps, $\pi_n$ is defined in terms of an unnormalized density $\gamma_n$ and we have the normalizing constant $Z_n = \int \gamma_n(z) \mathrm{d}z$.
-We also assume we have a sequence of inverse temperature constants $\beta_n$, where $0 = \beta_1 < \beta_2 <\dots< \beta_N$.
-The unnormalized density at level $n$ is then given in terms of a prior distribution $p_0(z)$ over the hypothesis space and a loss function $L(z)$:
+Let us now explain in more detail the procedure. 
+The goal is to obtain a probability distribution $d(z)$, where $z$ runs over a space of polynomials. 
+This function assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify such symbolic expressions.
+We reconstruct this density function by series of density functions $\pi_n(z)$ such that $\pi_n\to d(z)$ as $n\to\infty$. 
+On every annealing step, $\pi_n$ is defined in terms of an unnormalised density $\gamma_n$ and a normalisation constant as $\pi_n(z) = \gamma_n(z)/Z_n$.
+The unnormalised density at level $n$ is given in terms of a prior distribution $d_0(z)$ over the hypothesis space and a loss function $L(z)$:
 		\begin{equation}\label{eq:gamman}
-			\gamma_n(z) := d_0(z) \: \exp \left( -\beta_n L(z) \right).
-		\end{equation}
-
-		At each epoch, we have a set of particles and weights $\{z_{n-1}^k, w_{n-1}^k\}$ approximating $\pi_{n-1}$ (meaning $\mathbb{E}_{\pi_{n-1}}[f] \approx \frac{\sum_k w_{n-1}^k f(z_{n-1}^k)}{\sum_k w_{n-1}^k}$), and we want to obtain a new set $\{z_n^k, w_n^k\}$ approximating $\pi_n$.
-To do so, for each particle $z^k_{n-1}$, we propose a new particle $z_n^k \sim q(z_n | z_{n-1}^k)$ and calculate the new unnormalized importance weight $w_n^k$.
-The latter are updated using the formula
-		\begin{equation}
-			w_n^k = w_{n-1}^k \times \alpha_{n}^k
-		\end{equation}
-		where $\alpha_n^k$ is the incremental importance weight. The standard form for $\alpha_n^k$, which requires introducing an auxiliary backward transition kernel $q(z_{n-1} | z_n)$, is:
-		\begin{equation}
-			\alpha_n^k = \frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) } 
-		\end{equation}
-		The weights are finally normalized and we get $w_n^k \rightarrow \frac{w_n^k}{\sum_j w_n^j}$.
-
-		Let's us now focus on the forward $q(z_n^k | z_{n-1}^k)$ and backward propagation kernel $q(z_{n-1}^k | z_n^k)$ for now.
-The forward propagation kernel defines how we generate the state at time $n$ given the state at time $n-1$.
-It gives the probability to transition from $z_{n-1}$ to $z_n$.
-The backward kernel represents a hypothetical probability of transitioning back from state $z_n$ to state $z_{n-1}$.
-The purpose of $q$ is to give a proposition for $z_n$ given $z_{n-1}$.
-For the implementation of the two, we decide to implement an AIS-style MCMC code: we make some move in the space of polynomials, and then accept or reject those new polynomials based on an acceptance rate.
-So we first need to choose what are the available moves in the space of polynomials.
-Here are the choices we have made for our symbolic regression task :
+			\gamma_n(z) = d_0(z) \: \exp \left( -\beta_n L(z) \right),
+		\end{equation} 
+where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_1 < \beta_2 <\dots< \beta_N$.
+
+		Sequential importance sampling \cite{...} further assumes that the density functions $\pi_n(z)$ can be given in terms of importance densities $q^k_n(z)$ and weights $w^k_n$ as $\pi_n(z) = \sum w^k_n q^k_n(z)/Z_n$, and these importance densities can be sequentially given as
+		 \begin{equation}
+		 	q_n(z_n) = q_{n-1}(z_{n-1}) q_{n\vert n-1}(z_n\vert z_{n-1})\,.
+		 \end{equation}
+At each epoch, we $\pi_{n}$ can be approximated via a set of particles and weights $\{z_{n}^k,\ w_{n}^k\}$  so that\footnote{In the following, we always normalise the weights so that $\sum_k w_{n}^k=1$.}
+		 \begin{equation}
+		 	\pi_n(z) \approx \sum_k w_{n}^k\ \delta(z-z_{n}^k)\,,
+		 \end{equation}
+To obtain a new set $\{z_{n+1}^k,\ w_{n+1}^k\}$ approximating $\pi_{n+1}$, we sample from the forward propagation kernel $q_{n+1}(z_{n+1}\vert z_n)$ that defines how we generate the state at time $n+1$ given the state at time $n$.
+Similarly, the evolution of the weights is given by
+\[
+	w_{n+1} = \frac{\gamma_{n+1}}{q_{n+1}} = \frac{\gamma_{n+1}}{q_{n}\ q_{n+1 \vert n}} = w_{n}\ \alpha_{n+1}\,,
+\]
+where the incremental importance weights $\alpha_{n}^k$ are given by
+		\begin{equation}	\label{eq: incremental_importance}
+			\begin{aligned}
+				\alpha^k_{n+1} &= \frac{\gamma_{n+1}(z_{n+1})}{\gamma_{n}(z_n)}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}	\\
+				&=e^{-\beta_nL(z_n)+\beta_{n+1}L(z_{n+1})}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}\,.
+			\end{aligned}
+		\end{equation}
+
+		For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm. 
+On every step, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
+The moves that have been allowed in our implementation are:
 		\begin{itemize}
-			\item Coefficient pertubation.
-Given a polynomial $z_{n-1}$, we choose randomly one of its coefficient and modify it by a random noise from the guassian distribution $\mathcal{N}(0,\sigma^2)$.
-So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2.1 x_1 + 3 x_2^2$.
-			\item Variable multiplication.
-Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and multiply it by one of the available variable.
-So for eg : $2 x_1 + 3 x_2^2 \rightarrow  2 x_1 x_2 + 3 x_2^2$.
-			\item Variable division. Given a polynomial $z_{n-1}$, we choose randomly one of his monomial, and divide it by one of its variable. So for eg : $2 x_1 x_2 + 3 x_2^2 \rightarrow  2 x_1 + 3 x_2^2$. 
+			\item \textbf{Coefficient pertubation}. Given a polynomial $z_{n}$, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$. E.g.
+			\[
+				2 x_1 + 3 x_2^2 \mapsto  2.1 x_1 + 3 x_2^2\,.
+			\]
+			\item \textbf{Variable multiplication}. Given a polynomial $z_{n}$, we pick randomly one of its monomials, and multiply it by one of the available variables. E.g.
+			\[
+				2 x_1 + 3 x_2^2 \mapsto  2 x_1 x_2 + 3 x_2^2\,.
+			\]
+			\item \textbf{Variable division}. Given a polynomial $z_{n}$, we choose randomly one of its monomials, and divide it by one of its variables. E.g.
+			\[
+				2 x_1 x_2 + 3 x_2^2 \mapsto  2 x_1 + 3 x_2^2\,.
+			\]
 		\end{itemize}
-		The polynomials get mutated at each epoch.
-The mutation is chosen randomly, assigning probabilities \texttt{p\_{modify}} , \texttt{p\_{multiply}} and \texttt{p\_{divide}} to each possibility.
-This implementation enables a direct computation of both the forward and backward propagation kernels.
-In particular, for the case of coefficient perturbations, the transition is symmetric.
-That is,
-		\begin{equation}
-			q(z_n^k \mid z_{n-1}^k) = q(z_{n-1}^k \mid z_n^k),
-		\end{equation}
-		which significantly simplifies the computation of the incremental importance weight.
-
-		However, this symmetry does not hold in general.
+		Each of these operations is chosen randomly, with probabilities $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$.
+%		For the case of coefficient perturbations, the transition is symmetric. 
+%		However, this symmetry does not hold in general.
 For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
 In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
-
-		The acceptance ratio for the MCMC algorithm is given by : 
+After performing these updates, the change is accepted based on the temperature-dependent rate
 		\begin{equation}\label{eq:acceptanceratio}
-			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)
+			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)\,.
 		\end{equation}
 		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
-
-		We have adapted the classic approach outlined above.
-As can be seen in \eqref{eq:gamman}, what matters the most to determine $\gamma_{n}$ is not the inverse temperature, but rather the product of the inverse temperature and the loss function.
-Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach.
-The number of particles accepted at each run is monitored.
-We aim at following the following schedule as function of the \texttt{epoch}:
-		\begin{equation} \label{eq:eqadaptivetemperatureschedule}
-			\texttt{adaptive\_temperature\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right),
-		\end{equation}
-		where \texttt{n\_epochs} is the total number of epochs.
-If we accept more particle (in the 5 last epochs), we decrease the temperature by 5\%, if we accept less we increase it by 5\%.
-This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
-%ICI \bd{Move \eqref{eq:eqadaptivetemperatureschedule} in section 4?}
-
-		Before closing the section, we need to discuss what is the Loss function we choose.
-It is required to compute the unormalized distribution $\gamma_n$.
-Assume that we have $z = \sum_k c_k X_k$, where $c_k$ are the coefficients of the polynomials, and $X_k$ is a short notations for all the possible monomials up to a given degree (so if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_k$ are $1, x, y, x^2, y^2, x y$).
-For the Loss function, we decided to take :
+		The kernels $q$ and $\tilde{q}$ thus encapsulate the effects of performing these operations on the polynomials at step $n$.
+
+		To compute the weights and kernels via \eqref{eq: incremental_importance} and \eqref{eq:acceptanceratio} we need to consider the loss function in \eqref{eq:gamman}.
+In the present context, we use the following loss, where the polynomials have been parameterised as $z = \sum_k c_k X_k$ with $X_k$ denoting the possible monomials up to a given degree,%
+\footnote{So, if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_k$ are $1, x, y, x^2, y^2, x y$.}
 		\begin{equation} \label{eq:lossreg}
-			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k |c_k|}
-		\end{equation}
-		So the first term is just the sum of the squared of the polynomial evaluated on the data.
-We want to make this 0 so we find polynomial that annihilates our data.
-The second part is a regularisation factor: it prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem.
-We typically take $\lambda \sim \mathcal{O}(1000)$.
-
-		%\item Analysis after AIS: select the best polynomials and do exploitation on the coefficients (without MC: we keep only the proposal of it betters the polynomial).
-
-		Once the Annealing loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some more fine tuning.
-To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller.
-This allow to fine-tune the coefficients.
-%%ICI \ce{Mention threshold?
-And number of iterations?}
+			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k |c_k|}\,.
+		\end{equation}
+Here, the first term is just the sum of the square of the polynomial evaluated on the data, and is therefore minimal when the polynomial annihilates the data. 
+The second term is a regularisation factor that prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem. 
+We typically take $\lambda \sim \mathcal{O}(10^3)$. 
+Together with the loss function, we also need to specify a cooling schedule for $\beta$. We will discuss different approaches in the next section.
+
+		Once the Annealing loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
+To deal with it, for each polynomial we now only modify its coefficients with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma')$ and keep the particles when the loss function decreases.
 
@@
 \section{Numerical Analysis and Results} \label{sec:results}
-We now detail the numerical analysis and present our main results.
-We start by describing how we sampled the solutions manifold using a gradient descent.
+After describing the theory we want to address in sec.~\ref{sec:sugra}, and the symbolic regression method to be employed in sec.~\ref{Sec:AIS-SMC}, we now proceed to detail the numerical analysis and present our main results.
+We start by describing how we sampled the space of solutions using gradient descent.
 Once the manifold correctly sampled, we determine its dimension using a local principal component analysis and a clustering procedure.
-We finally exploit the annealed importance sampling algorithm described in sec.~\ref{Sec:AIS-SMC} to find an analytical characterisation of the manifold.
+We finally exploit the ASMC algorithm described in sec.~\ref{Sec:AIS-SMC} to find an analytical characterisation of the manifold.
 
@@
 	To perform the gradient descent, we initialise randomly and uniformly points within a hypercube of range $[-2,2]$.
-This choice is important to ensure that points are not restricted to the inner range~$[-1,1]$, which will be crucial for the Symbolic Regression.\footnote{The rationale is that symbolic regression (SR) evaluates the data points $\vec{x}^{(i)}$ using a candidate polynomial function $p$.
-The loss function—used later to assess the quality of a given polynomial—is defined as $\sum_i p(\vec{x}^{(i)})$.
-When all data points lie within the interval $[-1, 1]$, the SR algorithm tends to favor high-degree polynomials, as these often yield smaller values over this range, thereby artificially lowering the loss.
-Introducing data points with absolute values greater than 1 mitigates this bias by discouraging the selection of polynomials that exploit this effect.}.
-As the example we are focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points: we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
+This choice is important to ensure that points are not restricted to the inner range~$[-1,1]$, which will be crucial for the symbolic regression.\footnote{The rationale is that our symbolic regression evaluates the data points $\vec{x}^{(i)}$ using a candidate polynomial function $z$.
+When all data points lie within the interval $[-1, 1]$, the algorithm tends to favor high-degree polynomials artificially lowering the loss.
+Introducing data points with absolute values greater than 1 mitigates this bias.} As the example we are focussing on has a five-dimensional parameter space, we choose to generate $n_{\rm points}=10^5$ points, since we aim at populating all five directions and want approximately $\mathcal{O}(10)$ points per direction.
 As the solutions lie within the five dimensional space, its intrinsic dimension is less than or equal to 5.
@@
 		\includegraphics[scale = 0.75]{Figures/Loss_grad_des_21_05_2025.pdf}
-		\caption{Evolution of the loss function~\eqref{eq:lossgraddes} during gradient descent (right $y$-axis, in blue) and corresponding learning rate schedule $\alpha$ (left $y$-axis in orange), both plotted on a logarithmic scale.
+		\caption{Evolution of the loss function $\mathcal{L}$ in~\eqref{eq:lossgraddes} during gradient descent (right axis, in blue) and corresponding learning rate schedule $\alpha$ (left axis in orange), both plotted in logarithmic scale.
 Dashed lines indicate epochs at which the optimizer was reinitialized.}
@@
 This strategy introduces the risk of desampling certain regions in favour of others, introducing the risk to hide some flat directions in the potential.
-However, we believe that with enough points, it is very unlikely for a flat direction to be completely hidden from us and desampled.
+However, we believe that with enough points, it is very unlikely for a flat direction to be completely desampled.
 This method bears similarity to the concept of warm restarts introduced in ref.~\cite{loshchilov2017sgdrstochasticgradientdescent}, where the authors reset the learning rate to some value at each reset, without reinitialising the whole optimizer.
@@
 (b)~Histogram of the distance of the value of the potential to $V(0)$ for each point ($x$-axis is in $\log$ scale).
-Note that four points have deviations of the order of $10^{-3}$ and are not visible on the figure.}
+		%Note that four points have deviations of the order of $10^{-3}$ and are not visible on the figure.
+		}
 		\label{fig:Analyze_V_points}
@@
 
-	Upon completion, the loss function converges around $0.002$.
+	Upon completion, the loss function converges around $0.002$ \gl{$10^{-3}$?}.
 The distribution of the values of the gradient at each of the data points is plotted in fig.~\ref{fig:log_grad_V}.
@@
 Note that all directions appear to be well populated.
-There also seems to be non-trivial correlations in the data, see for example the $x_1/x_2$, $x_4/\tilde{x}_8$ or $x_4/x_{10}$ graphs.
+There also seem to be non-trivial correlations in the data, see for example the $x_1/x_2$, $x_4/\tilde{x}_8$ or $x_4/x_{10}$ graphs.
 They could be genuine correlations, or may result from larger basins of attraction.
-Thanks to the analysis of sec.~\ref{sec:results}, we will conclude that the structures in the $x_1/x_2$ plot are artefacts of the gradient descent, whereas the ones seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots reflect genuine features of the manifold.
+Thanks to the subsequent analysis, we find that the structures in the $x_1/x_2$ plot are artefacts of the gradient descent, whereas the ones seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots reflect genuine features of the manifold.
 
@@
 Specifically, we aim at determining the dimension of the manifold and whether it consists of a single connected component or multiple disjoint components (\textit{e.g.} two intersecting hyperplanes).
-To this end, we apply a local Principal Component Analysis (PCA\footnote{Principal Component Analysis is a dimensionality reduction technique that transforms high-dimensional data into a lower-dimensional space while preserving the maximum amount of variance.
+To this end, we apply a local Principal Component Analysis (PCA,%\footnote{Principal Component Analysis is a dimensionality reduction technique that transforms high-dimensional data into a lower-dimensional space while preserving the maximum amount of variance.
 The method identifies orthogonal linear combinations of the original variables, called principal components, which are ordered by the proportion of total variance they explain.
 PCA operates by computing the eigenvalues and eigenvectors of the data covariance matrix, where the eigenvectors define the direction of maximum variance and the eigenvalues quantify the amount of variance captured along each direction.
-From a physicist point of view, as we are doing it locally, this gives access to information about the local tangent plane.}, see for example ref.~\cite{scikit-learn}).
+From a physicist point of view, as we are doing it locally, this gives access to information about the local tangent plane.}
+see for example ref.~\cite{scikit-learn}).
 For each point, we identify its $k$ nearest neighbours and perform a PCA on that local neighbourhood.
@@
 This artificial enlargement of the neighbourhood can cause the estimated local dimensionality to rise.
-We thus conclude that the manifold under investigation has an intrinsic dimension of 3.
+We thus infer that the manifold under investigation has an intrinsic dimension of 3.
 
@@
 
-	One possible scenario is that our data actually consists of several distinct three-dimensional manifolds, intersecting at least at the origin $\vec{X}=0$, and the points previously identified with dimension $4$ may lie at the intersections of these manifolds.
+	After determining the local dimension of the space of solutions, we need to ascertain its topology. 
+One possible scenario is that our data consists of several three-dimensional manifolds, intersecting at least at the origin $\vec{X}=0$, and the points previously identified with dimension $4$ may lie at the intersections of these manifolds.
 Consider for example the intersection of two lines: at the intersection point, the local dimension estimated by the previous PCA algorithm would be 2. 
@@
 For the purpose of the clustering, we use the density-based algorithm HDBSCAN~\cite{10.1007/978-3-642-37456-2_14}. 
-%\footnote{Details of the algorithm can be found in the original HDBSCAN paper or documentation~\cite{10.1007/978-3-642-37456-2_14}.
-Briefly, it is a density-based clustering method that extends DBSCAN by converting it into a hierarchical clustering algorithm and then extracting a flat clustering based on the stability of clusters.}.
 As it can be observed in fig.~\ref{triangular_plot_1_2_4_8_10}, the points obtained after the gradient descent are denser around the origin, leading the algorithm to disregard points with a norm greater than 1.
-To avoid this effect, we de-sample the densest areas by randomly selecting no more than 10 points per 0.25-sided hyper-cube, and apply the HDBSCAN algorithm on the remaining 72,216 points, with minimum cluster size set to 5 points.
-The algorithm identifies one cluster made of 5 points, one other with 71,993 points, and fails to assign any cluster to 218 points.
+To avoid this effect, we de-sample the densest areas by randomly selecting no more than 10 points per 0.25-sided hyper-cube, and apply the HDBSCAN algorithm on the remaining points, with minimum cluster size set to 5 points.
+For our initial $10^5$ points, the algorithm identifies one cluster made of 5 points, one other with 71,993 points, and fails to assign any cluster to 218 points.
 We show in fig.~\ref{fig:3dplots} some 3d projections of the data to visualize the clustering.
@@
 	From the preceding analysis, we conclude that the gradient descent procedure has produced a sampling of a single, connected, three-dimensional manifold.
-Therefore to characterize the manifold, we need two independent constraints on the coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
-If we have a look at the form of the potential, we can observe that if we use $x_{i} = e^{\tilde{x}_i}$, that, up to some potential global factor and field redefinitions, this potential is actually a polynomial on the $\vec{X}$ coordinates.
+Therefore to characterise the manifold, we need two independent constraints on the coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
+If we have a look at the form of the potential, we can observe that if we use $x_{i} = e^{\tilde{x}_i}$, then, up to some potential global factor and field redefinitions, this potential is actually a polynomial on the $\vec{X}$ coordinates.
 Therefore, the components of $\left.\nabla V\right|_{\vec{y}=0}$ are also polynomials on the $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$ coordinates.
@@
 Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
-The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points.
+The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions that vanish once evaluated on our data points.
 We now proceed to present the symbolic regression problem, utilizing the points obtained through gradient descent as our training dataset.
@@
 	%ICI \gl{link to notations in section 3}
-	This strategy was determined empirically through trial and error; a systematic analysis of its optimization is left for future work.
+	The convenience of these parameters was determined empirically --a systematic analysis of its optimization is left for future work.
 For the representation of polynomials, we adopt a vectorial approach: each polynomial is represented as an array of its coefficients $\{c_k\}$, where $k \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of available monomials, determined by the chosen maximum degree \texttt{max\_degree} and the number of variables.
 We also impose a constraint on the maximum number of terms within a single polynomial \texttt{max\_num\_monomials} to promote sparsity.
-An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.
-For the simulations we have done, we chose :
+\footnote{An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.} For our simulations, we chose:
 	\begin{equation} \label{eq:parampol}
@@
 
+	Regarding the temperature schedule, as can be seen in \eqref{eq:gamman}, what matters to determine $\gamma_{n}$ is not the inverse temperature, but rather the product of the inverse temperature and the loss function.
+Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach that sets the number of particles to be updated at each run as
+		\begin{equation} \label{eq:eqadaptivetemperatureschedule}
+			\texttt{adaptive\_temperature\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right).
+		\end{equation}
+This encourages exploration during the early stages of training and gradually transitions to a more selective regime. %ICI \bd{Move \eqref{eq:eqadaptivetemperatureschedule} in section 4?}
+
 	\subsubsection{Analysis of a typical run}\label{sec:1runanalysis}
-	After a run, the 1000 particles are typically distributed into less than 50 different type of polynomials.
+	After a run, the 1000 particles are typically distributed into less than 50 different types of polynomials.
 Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
 We analyse them using the following procedure.
-We select the particle that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}), we fine-tune the coefficients by running a quick exploitation phase of 10,000 steps during which we randomly select a coefficient and modify it with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, with $\sigma_1=0.01$, and keep the new particle only if the loss function (without the regularisation) is getting smaller.
+We select the particle that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}), we fine-tune the coefficients by running a quick exploitation phase of 10,000 steps during which we randomly select a coefficient and modify it with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma')$, with $\sigma'=0.01$, and keep the new particle only if the loss function (without the regularisation) is getting smaller.
 There are two possible outputs after this phase.
@@
 The particle is then disregarded.
-We repeat the same steps on the best particles of the remaining set until we explored all the 1000 particles.
+We repeat the same steps on the best particles of the remaining set until we have explored all particles.
 
@@
 		\begin{gathered}
-			2\,x_{2} + 2\,x_{1}x_{4} + \sqrt{2}\,x_{1}x_{10} - 2\,x_{2}x_{8} - x_{2}x_{8}x_{10}^{2},\\
-	      \sqrt{2}\,x_{2} + \sqrt{2}\,x_{1}x_{4} - \sqrt{2}\,x_{2}x_{8} + x_{1}x_{8}x_{10} - x_{2}x_{4}x_{8}x_{10}, \\
+			2\,x_{2} + 2\,x_{1}x_{4} + \sqrt{2}\,x_{1}x_{10} - 2\,x_{2}x_{8} - x_{2}x_{8}x_{10}^{2},\\[5pt]
+	      \sqrt{2}\,x_{2} + \sqrt{2}\,x_{1}x_{4} - \sqrt{2}\,x_{2}x_{8} + x_{1}x_{8}x_{10} - x_{2}x_{4}x_{8}x_{10}, \\[5pt]
 	      -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_{8} - \sqrt{2}\,x_{2}x_{4}x_{8} + x_{2}x_{8}x_{10}.
@@
 It takes approximately 10\,min to do a single run on a regular computer, including annealing loop and local search described in the previous section.
-The code finds the 8 different following polynomials:
+The code finds the following 8 different polynomials:
 	\begin{subequations} \label{eq:pols}
 	 \begin{align}
-	   p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\
-	   p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\
+	   p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\[4pt]
+	   p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\[4pt]
 	   p_{3} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
-	   		- x_{2}x_{4}x_8x_{10},\\
+	   		- x_{2}x_{4}x_8x_{10},\\[4pt]
 	   p_{4} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
-	   		- 2\,x_{2} x_{4}^{2}x_8,\\
+	   		- 2\,x_{2} x_{4}^{2}x_8,\\[4pt]
 	   p_{5} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
-	   		- x_{2}^{2}x_{10}, \\
+	   		- x_{2}^{2}x_{10}, \\[4pt]
 	   p_{6} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
-	   		+ x_{1}x_8x_{10}^{2},\\
-	   p_{7} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\
+	   		+ x_{1}x_8x_{10}^{2},\\[4pt]
+	   p_{7} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\[4pt]
 	   p_{8} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
@@
 The frequencies represent the percentage of runs featuring a given polynomial in its outputs, and the maximum number of representatives gives the maximum number of particles representing the polynomial in a given run.
-The column $\varnothing$ counts the runs that failed to produce an annihilator polynomial.}
+The column $\varnothing$ counts the runs that failed to produce any annihilator polynomial.}
 		\label{table:results}
@@
 This is a key ingredient to get more than one candidate polynomials per run.
-The end value of $\beta$ is intimately linked to the choice of target adaptative temperature ratio in eq.~\eqref{eq:eqadaptivetemperatureschedule}: the lower the acceptance ratio, the higher the inverse temperature $\beta$.
-On the one hand, if the ratio is too low, very few particles get mutated and it's difficult to explore the space of polynomials and to have diverse outputs.
+The end value of $\beta$ is intimately linked to the choice of target adaptative temperature ratio in eq.~\eqref{eq:eqadaptivetemperatureschedule}: the lower this acceptance ratio, the higher the inverse temperature $\beta$.
+On the one hand, if the ratio is too low, very few particles get mutated and it is difficult to explore the space of polynomials and to have diverse outputs.
 On the other hand, if the ratio is too high, there are too many mutations: the output features a large number of polynomials, but lots of them do not converge to an annihilator polynomials because the algorithm is not selective enough.
@@
 The best loss is however quite high at the last epoch.
-This is linked to the very low value of $\beta$: the exploration is favoured on exploitation during all the process.
+This is linked to the very low value of $\beta$: the exploration is favoured with respect to exploitation during all the process.
 Although the loss is high, 1000 epochs are sufficient to select candidate annihilator polynomials thanks to the exploitation phase performed on the best particles, as illustrated in sec.~\ref{sec:AIS-SMC_application}.
@@
 We tested analytically that $\nabla V = 0$ for any of these rules.
-The three-parameter manifold then defines a three-dimensional space of flat directions of the half-maximal supergravity scalar potential.\footnote{One might argue that only two of the eight polynomials are sufficient to fully characterize the solution.
+The three-parameter manifold then defines a three-dimensional space of flat directions of the half-maximal supergravity scalar potential.\footnote{One might argue that only two of the eight polynomials are sufficient to fully characterise the solution.
 That is, choosing any pair $(i,j) \in {1, \dots, 8}$ may suffice to extract a complete description.
@@
 The gradient descent procedure successfully samples the flat directions manifold, while local PCA analysis reveals its intrinsic dimensionality.
-Most notably, our annealed importance sampling approach to symbolic regression automatically and quickly discovers polynomial constraints characterizing the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
+Most notably, our annealed importance sampling approach to symbolic regression automatically and quickly discovers polynomial constraints characterising the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
 The algorithm uncovered eight distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
@@
 %		\State Initialize particles $\{z_0^{(k)}\}_{k=1}^{n\_particles}$ with sparse polynomials
-%		\State Set $w_0^{(k)} = 1/n\_particles$ and $\tilde{w}_0^{(k)} = 1$ for all $k$ \Comment{normalized and unnormalized weights}
+%		\State Set $w_0^{(k)} = 1/n\_particles$ and $\tilde{w}_0^{(k)} = 1$ for all $k$ \Comment{normalised and unnormalised weights}
 %
@@
 %		
-%		\State Update unnormalized weights: $\tilde{w}_i^{(k)} \leftarrow \tilde{w}_{i-1}^{(k)} \times \exp(\Delta \log w_i^{(k)})$
-%		\State Normalize weights: $w_i^{(k)} \leftarrow \tilde{w}_i^{(k)} / \sum_{j=1}^{n\_particles} \tilde{w}_i^{(j)}$
+%		\State Update unnormalised weights: $\tilde{w}_i^{(k)} \leftarrow \tilde{w}_{i-1}^{(k)} \times \exp(\Delta \log w_i^{(k)})$
+%		\State normalise weights: $w_i^{(k)} \leftarrow \tilde{w}_i^{(k)} / \sum_{j=1}^{n\_particles} \tilde{w}_i^{(j)}$
 %		\State Compute ESS: $ESS = 1 / \sum_{k=1}^{n\_particles} (w_i^{(k)})^2$
@@
 %		\State Initialize particles $\{\texttt{z\_0}^{(k)}\}_{k=1}^{\texttt{n\_particles}}$ with sparse polynomials
-%		\State Set $\texttt{w\_0}^{\texttt{(k)}} = 1/\texttt{n\_particles}$ and $\texttt{w\_unorm\_0}^{\texttt{(k)}} = 1$ for all $\texttt k$ \Comment{normalized and unnormalized weights}
+%		\State Set $\texttt{w\_0}^{\texttt{(k)}} = 1/\texttt{n\_particles}$ and $\texttt{w\_unorm\_0}^{\texttt{(k)}} = 1$ for all $\texttt k$ \Comment{normalised and unnormalised weights}
 %		\State $\texttt{z\_prev} \leftarrow \texttt{z\_0}$, $\texttt{best\_loss} \leftarrow \infty$, $\texttt{acceptance\_history} \leftarrow \emptyset$, $\texttt{q\_ratio}^{\texttt{(k)}}=1$ for all $k$, $\texttt{beta\_0} \leftarrow \texttt{init\_beta}$ \Comment{q is the proposal ratio}
@@
 %		
-%		\State Update unnormalized weights: $\texttt{w\_unorm\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_(i-1)}^{\texttt{(k)}} \times \texttt{exp(}\Delta \texttt{log w\_i}^{\texttt{(k)}}\texttt)$
-%		\State Normalize weights: $\texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt/ \sum_{\texttt{j=1}}^{\texttt{n\_particles}} \texttt{w\_unorm\_i}^{\texttt{(j)}}$
+%		\State Update unnormalised weights: $\texttt{w\_unorm\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_(i-1)}^{\texttt{(k)}} \times \texttt{exp(}\Delta \texttt{log w\_i}^{\texttt{(k)}}\texttt)$
+%		\State normalise weights: $\texttt{w\_i}^{\texttt{(k)}} \leftarrow \texttt{w\_unorm\_i}^{\texttt{(k)}} \texttt/ \sum_{\texttt{j=1}}^{\texttt{n\_particles}} \texttt{w\_unorm\_i}^{\texttt{(j)}}$
 %		\State Compute ESS: $\texttt{ESS = 1 /} \sum_{\texttt{k=1}}^{\texttt{n\_particles}} \texttt{(w\_i}^{\texttt{(k)}})^\texttt2$
@@
 %		
-%		\State $\texttt{proba} \leftarrow \texttt{n\_mon\_all\_coeff / n\_tot\_pol}$ \Comment{Normalize to get probabilities}
+%		\State $\texttt{proba} \leftarrow \texttt{n\_mon\_all\_coeff / n\_tot\_pol}$ \Comment{normalise to get probabilities}
 %

### 2025-09-22 Draft_MLFlatDirections.tex
Fixed a couple of typos

@@
 	Our approach combines numerical exploration and symbolic inference.
-For the latter, we develop a symbolic regression algorithm based on Sequential Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
+For the latter, we develop a symbolic regression algorithm based on Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
 	The algorithm reconstructs a set of polynomial relations that provides an explicit analytic parametrization of a new family of solutions. 
@@
 To obtain a new set $\{z_{n+1}^k,\ w_{n+1}^k\}$ approximating $\pi_{n+1}$, we sample from the forward propagation kernel $q_{n+1}(z_{n+1}\vert z_n)$ that defines how we generate the state at time $n+1$ given the state at time $n$.
-Similarly, the evolution of the weights is given by
+Similarly, the evolution of the weights is given by \gl{for $k>1$, this is a bit schematic...}
 \[
@@
 In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
-After performing these updates, the change is accepted based on the temperature-dependent rate
+After performing these updates, the change is accepted based on the temperature-dependent rate \gl{need to double check this}
 		\begin{equation}\label{eq:acceptanceratio}
@@
 		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
-		The kernels $q$ and $\tilde{q}$ thus encapsulate the effects of performing these operations on the polynomials at step $n$.
+		The kernel $q(z_{n-1}^k | z_n^k)$ thus encapsulates the effects of performing these operations on the polynomials at step $n$.
 

### 2025-09-23 Draft_MLFlatDirections.tex
Updates of AIS-SMC section with Bastien.

@@
-%!TEX output_directory = aux
-
 \documentclass[11pt,a4paper]{article}
@@
 
+%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%
+\section{Annealed Importance Sampling for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
+
+	\subsection{General idea}
+	The numerical sampling of the space of vacua described above results in clouds of points embedded in a higher-dimensional space. 
+	The aim of symbolic regression is to uncover interpretable mathematical expressions that best describe the embedding of these loci of solutions. 
+	In the present context, the form of the supergravity potential \eqref{eq:scalarpotential} determining the solutions implies that the loci can be defined through polynomials $p_{m}$ such that $p_{m}(\vec{x}^{(i)}) = 0$, with $i \in \{1, \dots, n_{\rm points}\}$.
+Such polynomials will be called ``annihilating polynomials'' in the following.
+	Finding annihilating polynomials involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods. 
+	Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and often get trapped in local optima, especially in high-dimensional or multimodal spaces \cite{??}.
+\ce{Citation.}
+
+	To address these challenges, we formulate the search for annihilating polynomials as a determination of a density probability on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimises $\displaystyle \sum_{i=1}^{n_{\rm points}}p(\vec{x}^{(i)})^{2}$.
+Such a density probability is \textit{a priori} hard to find, but can be approximated using variations of Important Sampling methods~\cite{910e8e7d-2e70-317c-adf6-e21cd50755a1}.
+Importance sampling is a method to approximate expectation values with respect to a target distribution $d$ from a weighted average from another distribution $\pi$.
+It is based on the observation that the expectation
+	\begin{equation}
+		\mathbb{E}_{d}[f] = \int f(z)d(z)\ \d z
+	\end{equation}
+	of a function $f$ with respect to $d$ can be computed from the expectation $\mathbb{E}_{\pi}[w f]$, now computed with respect to the distribution $\pi$, with unnormalised $w(z) = d(z)/\pi(z)$.
+Therefore, if it is easier to draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\pi$ than from $d$, one can estimate $\mathbb{E}_{d}[f]$ from the weighted average
+	\begin{equation}
+		\mathbb{E}_{d}[f] \simeq \frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w(z^{(k)})\,f(z^{(k)})}{\displaystyle \sum_{i=1}^{n_{\rm particles}} w(z^{(k)})}.
+	\end{equation}
+	The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the distribution $\pi$.
+
+	To have an accurate estimation of $d$, we employ an Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} combined with Sequential Monte Carlo (SMC) methods \cite{del2006sequential,naesseth2024elementssequentialmontecarlo}.
+AIS aims at estimating $d$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $d_{0}$ (chosen to be easy to sample from) to the complex target distribution $d$.
+	These distributions are approximated by weighted samples $\{z^{(k)}_{n},w^{(k)}_{n}\}$ of particles, each representing a candidate symbolic expression, such that the resulting weighted average estimates $\pi_{n}$: \ce{Normalise the weights?}
+	\begin{equation}
+		\frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}\,f(z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}} \underset{n_{\rm particles}\rightarrow+\infty}{\longrightarrow} \mathbb{E}_{\pi_{n}}[f],
+	\end{equation}
+	or equivalently
+	\begin{equation} \label{eq:pifromweights}
+		\pi_{n}(z) \simeq \frac{\displaystyle \sum_{k=1}^{N} w^{(k)}_{n}\,\delta(z-z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{N} w^{(k)}_{n}}.
+	\end{equation}
+	The $\pi_{n}$ are incrementally deformed using a Markov kernel to gradually reproduce the target $d$ and the particles get reweighed.
+This annealing process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
+
+	This procedure has the disadvantage that the weights variance tends to increase, leading to weight degeneracy.
+We use SMC methods to incorporate a resampling procedure to AIS, thus focussing computational effort on high-probability regions.
+This combination of importance sampling, mutation and resampling maintains diversity among the particles and prevents premature convergence to suboptimal models.
+These features make AIS-SMC particularly well-suited for symbolic regression tasks, where the search space is not only high-dimensional but also structured and discontinuous.
+
+	\subsection{Detailed procedure}
+
+	\begin{figure}[h!]
+			\centering
+			\begin{minipage}{15cm}
+				\begin{tcolorbox}[
+					colback=white,
+					colframe=myblue,
+					title=\textbf{ASMC Algorithm},
+					fonttitle=\sffamily\large,
+					halign title=flush center,
+					boxrule=2pt,
+					left=6pt,
+					right=6pt,
+					top=8pt,
+					bottom=8pt
+					]
+					\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]
+
+						% Nœuds
+						\node (start) [startstop] {Start};
+
+						\node (init_particles) [process, below of=start] {Initialize particles \& weights};
+
+						\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};
+
+						\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};
+
+						\node (ess_check) [decision, below of=weight_update] {Effective Sample Size $<$ Threshold?};
+
+						\node (resample) [process, right=3.8cm of ess_check] {Resample particles};
+
+						\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with MCMC kernel};
+
+						\node (acceptance) [process, below of=mutation] {Accept/Reject particles};
+
+						\node (end_iter) [decision, below of=acceptance] {Last step?};
+
+						\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};
+
+						\node (output) [process, below of=exploit] {Return particles};
+
+						\node (stop) [startstop, below of=output] {End};
+
+						% Flèches avec étiquettes améliorées
+						\draw [arrow] (start) -- (init_particles);
+						\draw [arrow] (init_particles) -- (compute_beta);
+						\draw [arrow] (compute_beta) -- (weight_update);
+						\draw [arrow] (weight_update) -- (ess_check);
+
+						\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
+						\draw [arrow] (resample) |- (mutation);
+
+						\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
+						\draw [arrow] (mutation) -- (acceptance);
+						\draw [arrow] (acceptance) -- (end_iter);
+
+						% Boucle de retour améliorée
+						\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {No} ++(-4.5,0) |- (compute_beta);
+
+						\draw [arrow] (end_iter) -- node[right, arrow_label] {Yes} (exploit);
+						\draw [arrow] (exploit) -- (output);
+						\draw [arrow] (output) -- (stop);
+
+					\end{tikzpicture}
+				\end{tcolorbox}
+			\end{minipage}
+			\caption{Flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
+			\label{ASMCflowchart}
+		\end{figure}
+
+		%\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
+
+	Let us now explain in more detail the procedure. 
+	The goal is to obtain a probability distribution $d(z)$, where $z$ runs over a space of polynomials, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
+	We reconstruct this density function $d$ by series of density functions $\pi_n(z)$, $n\in\llbracket1,n_{\rm epochs}\rrbracket$, such that $\pi_n\to d$ as $n\to n_{\rm epochs}$. 
+	On every annealing step, $\pi_n$ is defined in terms of an unnormalised density $\gamma_n$ and a normalisation constant as $\pi_n(z) = \gamma_n(z)/Z_n$.
+	The unnormalised density at level $n$ is given in terms of a prior distribution $d_0(z)$ over the space of polynomials and a loss function $L(z)$, as \ce{Citation.}
+			\begin{equation}\label{eq:gamman}
+				\gamma_n(z) = d_0(z) \: \exp \Big( -\beta_n L(z)\Big),
+			\end{equation} 
+	where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_1 < \beta_2 <\dots< \beta_{n_{\rm epochs}}$.
+The importance given to each polynomial $z$ is thus updated at each steps, with polynomials $z$ with high loss being disfavoured.
+This update is controlled by the inverse temperature constants, enabling deeper exploration during the early stages and protecting the procedure from being trapped in local minima.
+The loss function is chosen to be minimal on annihilating polynomials, its design will be discussed at the end of the section.
+We chose the prior distribution $d_{0}$ to be flat on the space of polynomials, giving equal importance to all of them, which makes easy the initial sampling of the particles $\{z^{(k)}_{0}\}$.
+
+	At each epoch $n$, $\pi_{n}$ is approximated \textit{via} a set of particles and weights $\{z_{n}^{(k)},\ w_{n}^{(k)}\}$ in the sense of eq.~\eqref{eq:pifromweights}.
+The sample of particles $z^{(k)}_{n}$ get mutated using a forward propagation Markov kernel $q(z^{(k)}_{n+1}\vert z^{(k)}_{n})$, defining the probability to get $z^{(k)}_{n+1}$ when the current state is $z^{(k)}_{n}$.
+For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm.
+	On every epoch, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
+	The moves that have been allowed in our implementation are the following.
+	\begin{itemize}
+		\item \textbf{Coefficient pertubation}\quad Given a polynomial, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$, \textit{e.g.}
+		\begin{equation}
+			2 x_1x_{2} + 3 x_2^2 \longmapsto  2.1 x_1x_{2} + 3 x_2^2\,.
+		\end{equation}
+		\item \textbf{Variable multiplication}\quad Given a polynomial, we pick randomly one of its monomials, and multiply it by one of the available variables, \textit{e.g.}
+		\begin{equation}
+			2 x_1x_{2} + 3 x_2^2 \longmapsto  2 x_1 x_2^{2} + 3 x_2^2\,.
+		\end{equation}
+		\item \textbf{Variable division}\quad Given a polynomial, we choose randomly one of its monomials, and divide it by one of its variables, \textit{e.g.}
+		\begin{equation}
+			2 x_1 x_2 + 3 x_2^2 \longmapsto  2 x_1 + 3 x_2^2\,.
+		\end{equation}
+	\end{itemize}
+	Each of these operations is chosen randomly, with probabilities $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$.
+	%		For the case of coefficient perturbations, the transition is symmetric. 
+	%		However, this symmetry does not hold in general.
+For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
+In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
+	After performing these updates, the change is accepted based on the temperature-dependent rate
+	\begin{equation}\label{eq:acceptanceratio}
+		A(z_{n+1}^{(k)},z_{n}^{(k)}) = \mathrm{min} \left(1,\frac{ \gamma_{n+1}(z_{n+1}^{(k)}) q(z_{n}^{(k)} | z_{n+1}^{(k)}) }{ \gamma_{n}(z_{n}^{(k)}) q(z_{n+1}^{(k)} | z_{n}^{(k)}) }  \right)\,.
+	\end{equation}
+	We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_{n+1}^{(k)},z_{n}^{(k)})$ and reject it otherwise.
+	The kernel $q(z_{n-1}^k | z_n^k)$ thus encapsulates the effects of performing these operations on the polynomials at step $n$. \ce{Why this comment?}
+
+	Once the particles have been mutated, the evolution of the weights is given by
+	\begin{equation}
+		w_{n+1}^{(k)} = w_{n}^{(k)}\ \alpha_{n+1}^{(k)},
+	\end{equation}
+	where the incremental importance weights $\alpha_{n+1}^{(k)}$ are given by\footnote{The incremental weight is in general defined as $\alpha^{(k)}_{n+1} = \frac{\gamma_{n+1}(z_{n+1}^{(k)})}{\gamma_{n}(z_n^{(k)})}\,\frac{K(z^{(k)}_{n}\vert z^{(k)}_{n+1})}{q(z^{(k)}_{n+1}\vert z^{(k)}_{n})}$, where $K(z^{(k)}_{n}\vert z^{(k)}_{n+1})$ is the backward propagation kernel~\cite{del2006sequential}.
+For simplicity, we chose to identify $K$ to the forward propagation kernel $q$.}~\cite{del2006sequential}
+	\begin{equation}	\label{eq: incremental_importance}
+			\alpha^{(k)}_{n+1} = \frac{\gamma_{n+1}(z_{n+1}^{(k)})}{\gamma_{n}(z_n^{(k)})}\,\frac{q(z^{(k)}_{n}\vert z^{(k)}_{n+1})}{q(z^{(k)}_{n+1}\vert z^{(k)}_{n})}=\frac{\exp\big(-\beta_{n+1}L(z_{n+1}^{(k)})\big)}{\exp\big(-\beta_{n}L(z_{n}^{(k)})\big)}\,\frac{q(z^{(k)}_{n}\vert z^{(k)}_{n+1})}{q(z^{(k)}_{n+1}\vert z^{(k)}_{n})}.
+	\end{equation}
+
+	To ensure an efficient exploration of the landscape, we would like to avoid having to many particles with low weights: as the algorithm progresses, particles with negligible weights contribute minimally to the approximation of the target distribution (see eq.~\eqref{eq:pifromweights}), leading to a concentration of the effective sample on a subset of particles with substantial weights.
+This can be estimated using the effective sample size~\cite{Liu01091998}
+	\begin{equation}
+		{\rm ESS}_{n+1} = \Bigg(\sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}_{n+1}{}^{2}\Bigg)^{-1},
+	\end{equation}
+	where the $\tilde{w}^{(k)}_{n+1}$ are normalised weights deduced from the $w^{(k)}_{n+1}$.
+${\rm ESS}_{n+1}$ takes values between $1$ (complete degeneracy, there is only one meaningful particle) and $n_{\rm particles}$ (no degeneracy, all particles contribute equally).
+We resample the particles when the ESS falls below a predetermined threshold, typically $n_{\rm particles}/2$.
+During resampling, new particles are drawn from the empirical distribution defined by the current particle weights $\tilde{w}^{(k)}_{n+1}$.	This procedure results in a new particle set where high-weight particles may appear multiple times, while low-weight particles may be eliminated entirely.
+Following resampling, all particle weights are reset to uniform values $w_{n+1}^{(k)} = 1/n_{\rm particles}$, as the information previously encoded in the weight distribution has been incorporated into the spatial distribution of the resampled particles.
+This resampling mechanism ensures that computational resources are concentrated on exploring the most promising regions of the state space.
+
+	A flow chart of the full AIS-SMC procedure is given in fig.~\ref{ASMCflowchart}.
+Note that in practice the reweighing and resampling of particles $z_{n-1}^{(k)}$ are done at the beginning of the epoch $n$.
+
+	\paragraph{}
+	To compute the acceptance ratio and weights \textit{via} eq.~\eqref{eq:acceptanceratio} and \eqref{eq: incremental_importance} and we need to consider the loss function in~\eqref{eq:gamman}.
+	In the present context, we use the following loss, where the polynomials have been parameterised as $z = \sum_m c_m X_m$ with $X_m$ denoting the possible monomials up to a given degree,%
+	\footnote{So, if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_m$ are $1, x, y, x^2, y^2, x y$.}
+	\begin{equation} \label{eq:lossreg}
+		L(z) = \sum_{i=1}^{n_{\rm points}} z(x^{(i)})^2 + \frac{\lambda}{\sum_m |c_m|}\,.
+	\end{equation}
+	Here, the first term is just the sum of the square of the polynomial evaluated on the data, and is therefore minimal when the polynomial annihilates the data. 
+	The second term is a regularisation factor that prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem. 
+	We typically take $\lambda \sim \mathcal{O}(10^3)$. 
+	Together with the loss function, we also need to specify a cooling schedule for $\beta$. We will discuss different approaches in the next section.
+
+	\paragraph{}
+	Once the Annealing loop is over, we end up with a total of $n_{\rm particles}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
+To deal with it, for each polynomial we run a fine tuning loop as described in sec.~\ref{sec:1runanalysis}.
+
 %%%%%%%%%%%%%%%%%%%%
@@
 		\begin{aligned}
-			&\texttt{data\_size = 10,000},\\
+			&\texttt{n\_points = 10,000},\\
 			&\texttt{n\_epochs = 1000},\\
@@
 	The convenience of these parameters was determined empirically --a systematic analysis of its optimization is left for future work.
-For the representation of polynomials, we adopt a vectorial approach: each polynomial is represented as an array of its coefficients $\{c_k\}$, where $k \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of available monomials, determined by the chosen maximum degree \texttt{max\_degree} and the number of variables.
+For the representation of polynomials, we adopt a vectorial approach: each polynomial is represented as an array of its coefficients $\{c_m\}$, where $m \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of available monomials, determined by the chosen maximum degree \texttt{max\_degree} and the number of variables.
 We also impose a constraint on the maximum number of terms within a single polynomial \texttt{max\_num\_monomials} to promote sparsity.
@@
 Regarding the temperature schedule, as can be seen in \eqref{eq:gamman}, what matters to determine $\gamma_{n}$ is not the inverse temperature, but rather the product of the inverse temperature and the loss function.
-Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach that sets the number of particles to be updated at each run as
+Therefore, instead of implementing an arbitrary schedule for $\beta$, we employed an adaptive temperature approach, whose aim is to ensure that the number of particles to be updated at each run is close to
 \begin{equation} \label{eq:eqadaptivetemperatureschedule}
-			\texttt{adaptive\_temperature\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{epoch}}{\texttt{n\_epochs}}\right).
-		\end{equation}
-This encourages exploration during the early stages of training and gradually transitions to a more selective regime. %ICI \bd{Move \eqref{eq:eqadaptivetemperatureschedule} in section 4?}
+	\texttt{adaptive\_temperature\_ratio} = 0.8 - 0.5 \times \left(\frac{\texttt{n}}{\texttt{n\_epochs}}\right).
+\end{equation}
+In other words, if the number of accepted particles after the MCMC step at a given \texttt{n} is higher than the target~\eqref{eq:eqadaptivetemperatureschedule}, we decrease the temperature and hence increase $\beta_{n}$, and \textit{vice versa} if this number is lower than \texttt{adaptive\_temperature\_ratio}.
+
+This encourages exploration during the early stages of training and gradually transitions to a more selective regime.
 

### 2025-09-23 Draft_MLFlatDirections.tex
Update during meeting.

@@
 These deformations are parametrised by exactly marginal operators, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
-%%ICI \ce{Needs some modifications.}
+ICI \ce{Needs some modifications.}
 
@@
 	To address these challenges, we formulate the search for annihilating polynomials as a determination of a density probability on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimises $\displaystyle \sum_{i=1}^{n_{\rm points}}p(\vec{x}^{(i)})^{2}$.
-Such a density probability is \textit{a priori} hard to find, but can be approximated using variations of Important Sampling methods~\cite{910e8e7d-2e70-317c-adf6-e21cd50755a1}.
-Importance sampling is a method to approximate expectation values with respect to a target distribution $d$ from a weighted average from another distribution $\pi$.
+Such a probability density is \textit{a priori} hard to find, but can be approximated using variations of Important Sampling methods~\cite{910e8e7d-2e70-317c-adf6-e21cd50755a1}.
+Importance sampling is a method to parametrise expectation values with respect to a target distribution $d$, from a weighted average using another distribution $\pi$.
 It is based on the observation that the expectation
@@
 	The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the distribution $\pi$.
+\ce{Add conclusion saying that you can parametrise $d$ using a sample and weights, and eq.
+as (4.4).}
 
@@
 	\begin{equation} \label{eq:pifromweights}
-		\pi_{n}(z) \simeq \frac{\displaystyle \sum_{k=1}^{N} w^{(k)}_{n}\,\delta(z-z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{N} w^{(k)}_{n}}.
+		\pi_{n}(z) \simeq \frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}\,\delta(z-z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}}.
 	\end{equation}
@@
 	\begin{itemize}
-		\item \textbf{Coefficient pertubation}\quad Given a polynomial, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$, \textit{e.g.}
+		\item \textbf{Coefficient perturbation}\quad Given a polynomial, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$, \textit{e.g.}
 		\begin{equation}
@@
 	We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_{n+1}^{(k)},z_{n}^{(k)})$ and reject it otherwise.
-	The kernel $q(z_{n-1}^k | z_n^k)$ thus encapsulates the effects of performing these operations on the polynomials at step $n$. \ce{Why this comment?}
 
@@
 Specifically, we aim at determining the dimension of the manifold and whether it consists of a single connected component or multiple disjoint components (\textit{e.g.} two intersecting hyperplanes).
-To this end, we apply a local Principal Component Analysis (PCA,%\footnote{Principal Component Analysis is a dimensionality reduction technique that transforms high-dimensional data into a lower-dimensional space while preserving the maximum amount of variance.
-The method identifies orthogonal linear combinations of the original variables, called principal components, which are ordered by the proportion of total variance they explain.
+To this end, we apply a local Principal Component Analysis (PCA).\footnote{Principal Component Analysis is a dimensionality reduction technique that transforms high-dimensional data into a lower-dimensional space while preserving the maximum amount of variance, see for example ref.~\cite{scikit-learn}.} % The method identifies orthogonal linear combinations of the original variables, called principal components, which are ordered by the proportion of total variance they explain.
 PCA operates by computing the eigenvalues and eigenvectors of the data covariance matrix, where the eigenvectors define the direction of maximum variance and the eigenvalues quantify the amount of variance captured along each direction.
 From a physicist point of view, as we are doing it locally, this gives access to information about the local tangent plane.}
-see for example ref.~\cite{scikit-learn}).
 	For each point, we identify its $k$ nearest neighbours and perform a PCA on that local neighbourhood.
@@
 As it can be observed in fig.~\ref{triangular_plot_1_2_4_8_10}, the points obtained after the gradient descent are denser around the origin, leading the algorithm to disregard points with a norm greater than 1.
-To avoid this effect, we de-sample the densest areas by randomly selecting no more than 10 points per 0.25-sided hyper-cube, and apply the HDBSCAN algorithm on the remaining points, with minimum cluster size set to 5 points.
-For our initial $10^5$ points, the algorithm identifies one cluster made of 5 points, one other with 71,993 points, and fails to assign any cluster to 218 points.
+To avoid this effect, we de-sample the densest areas by randomly selecting no more than 10 points per 0.25-sided hyper-cube, and apply the HDBSCAN algorithm on the remaining 72,216 points, with minimum cluster size set to 5 points.
+The algorithm identifies one cluster made of 5 points, one other with 71,993 points, and fails to assign any cluster to 218 points.
 We show in fig.~\ref{fig:3dplots} some 3d projections of the data to visualize the clustering.
@@
 In other words, if the number of accepted particles after the MCMC step at a given \texttt{n} is higher than the target~\eqref{eq:eqadaptivetemperatureschedule}, we decrease the temperature and hence increase $\beta_{n}$, and \textit{vice versa} if this number is lower than \texttt{adaptive\_temperature\_ratio}.
-
 This encourages exploration during the early stages of training and gradually transitions to a more selective regime.

### 2025-09-25 Draft_MLFlatDirections.tex
Modify the draft, beginning of section 4 on discussion of IS/AIS/Sequential MC AND add the modifications for the figures generation

@@
 Such a probability density is \textit{a priori} hard to find, but can be approximated using variations of Important Sampling methods~\cite{910e8e7d-2e70-317c-adf6-e21cd50755a1}.
-Importance sampling is a method to parametrise expectation values with respect to a target distribution $d$, from a weighted average using another distribution $\pi$.
-It is based on the observation that the expectation
+Importance sampling is a method to parametrise expectation values with respect to a target distribution $d$, for which you can compute $d(z)$ for some sample $z$, but for which you do not know how to draw from.
+IS uses another distribution $\pi$ whose density probabilty is proportional to $d$, but from which you know how to draw from.
+IS then parametrizes the density $d$ with a sequence of weights $w^{(k)}$ and is based on the observation that the expectation
 	\begin{equation}
@@
 	\end{equation}
-	of a function $f$ with respect to $d$ can be computed from the expectation $\mathbb{E}_{\pi}[w f]$, now computed with respect to the distribution $\pi$, with unnormalised $w(z) = d(z)/\pi(z)$.
+	for some function $f$ with respect to $d$ can be computed from the expectation $\mathbb{E}_{\pi}[w f]$, now computed with respect to the distribution $\pi$, with unnormalised $w^{(k)} = d(z^{k})/\pi(z^{(k)})$.
 Therefore, if it is easier to draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\pi$ than from $d$, one can estimate $\mathbb{E}_{d}[f]$ from the weighted average
 	\begin{equation}
-		\mathbb{E}_{d}[f] \simeq \frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w(z^{(k)})\,f(z^{(k)})}{\displaystyle \sum_{i=1}^{n_{\rm particles}} w(z^{(k)})}.
+		\mathbb{E}_{d}[f] \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w(z^{(k)})\,f(z^{(k)})/\displaystyle \sum_{i=1}^{n_{\rm particles}} w(z^{(k)}).
+	\end{equation}
+	or stated differently 
+	\begin{equation} \label{eq:}
+		d(z) \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}\,\delta(z-z^{(k)})/\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}.
 	\end{equation}	
 	The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the distribution $\pi$.
-\ce{Add conclusion saying that you can parametrise $d$ using a sample and weights, and eq.
-as (4.4).}
-
-	To have an accurate estimation of $d$, we employ an Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} combined with Sequential Monte Carlo (SMC) methods \cite{del2006sequential,naesseth2024elementssequentialmontecarlo}.
-AIS aims at estimating $d$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $d_{0}$ (chosen to be easy to sample from) to the complex target distribution $d$.
-	These distributions are approximated by weighted samples $\{z^{(k)}_{n},w^{(k)}_{n}\}$ of particles, each representing a candidate symbolic expression, such that the resulting weighted average estimates $\pi_{n}$: \ce{Normalise the weights?}
-	\begin{equation}
-		\frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}\,f(z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}} \underset{n_{\rm particles}\rightarrow+\infty}{\longrightarrow} \mathbb{E}_{\pi_{n}}[f],
+
+	However, providing a good $\pi$ distribution may still remains an hard problem.
+In order to fix this point, we employ a so called Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling}.
+AIS aims at estimating $\pi$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $\pi_{0}$ (chosen to be easy to sample from) to the complex target distribution $\pi$.
+	These distributions are approximated by weighted samples $\{z^{(k)}_{n},w^{(k)}_{n}\}$ of particles, such that the resulting weighted average estimates $\pi_{n}$
+	\begin{equation}
+		\mathbb{E}_{\pi_{n}}[f] \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}_{n}\,f(z^{(k)}_{n})
 	\end{equation}
@@
 	\begin{equation} \label{eq:pifromweights}
-		\pi_{n}(z) \simeq \frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}\,\delta(z-z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}}.
-	\end{equation}
+		\pi_{n}(z) \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}_{n}\,\delta(z-z^{(k)}_{n}).
+	\end{equation}
+	with  $\tilde{w}^{(k)}_n  = w^{(k)}_n/\sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}$ the normalised weights.
 The $\pi_{n}$ are incrementally deformed using a Markov kernel to gradually reproduce the target $d$ and the particles get reweighed.
 This annealing process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
+The approximation procedure can be sum up as follow
+	\begin{equation}
+	\pi_0(z) \underset{\rm Annealing}{\longrightarrow}\pi_n(z) \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}_{n}\,\delta(z-z^{(k)}_{n}) \underset{\rm{n} \rightarrow +\infty}{\longrightarrow} \pi(z) \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}\,\delta(z-z^{(k)}) \underset{\rm{n_{particles}} \rightarrow +\infty}{\longrightarrow} d(z)
+	\nonumber
+	\end{equation}
+	Therefore, we start from an intial, easy to sample distribution $\pi_0$, that is parametrised by a set of particles and weights $\{z_0^{(k)},w_0^{(k)}\}$.
+We gradually mutate them with an annealing procedure to get a set of $\{z_n^{(k)},w_n^{(k)}\}$, which are used to parametrise $\pi_n$.
+As $n$ increases, the procedure converges to the distribution $\pi$, which itself is used to parametrise the target distribution $d$.
 
 	This procedure has the disadvantage that the weights variance tends to increase, leading to weight degeneracy.
-We use SMC methods to incorporate a resampling procedure to AIS, thus focussing computational effort on high-probability regions.
+We combine the previously mentionne AIS technique with SMC methods  \cite{del2006sequential,naesseth2024elementssequentialmontecarlo} to incorporate a resampling procedure, thus focussing computational effort on high-probability regions.
 This combination of importance sampling, mutation and resampling maintains diversity among the particles and prevents premature convergence to suboptimal models.

### 2025-09-29 Draft_MLFlatDirections.tex
Update the draft and add the 3d figures

@@
 	However, providing a good $\pi$ distribution may still remains an hard problem.
-In order to fix this point, we employ a so called Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling}.
+In order to fix this point, we employ a so called Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} which is a class of Sequetial Monte Carlo algorithm (SMC) \cite{del2006sequential,naesseth2024elementssequentialmontecarlo}.
 AIS aims at estimating $\pi$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $\pi_{0}$ (chosen to be easy to sample from) to the complex target distribution $\pi$.
@@
 The $\pi_{n}$ are incrementally deformed using a Markov kernel to gradually reproduce the target $d$ and the particles get reweighed.
-This annealing process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
+This process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
 The approximation procedure can be sum up as follow
@@
 	This procedure has the disadvantage that the weights variance tends to increase, leading to weight degeneracy.
-We combine the previously mentionne AIS technique with SMC methods  \cite{del2006sequential,naesseth2024elementssequentialmontecarlo} to incorporate a resampling procedure, thus focussing computational effort on high-probability regions.
+We combine the previously mentionned AIS-SMC with a resampling procedure, thus focussing computational effort on high-probability regions.
 This combination of importance sampling, mutation and resampling maintains diversity among the particles and prevents premature convergence to suboptimal models.

### 2025-10-01 Draft_MLFlatDirections.tex
Substantial update of the description of AIS-SMC section (here sec. 4).

--- 2025-09-23 Draft_MLFlatDirections.tex
@@
 %%%%%%%%%%%%%%%%%%
-\section{Annealed Importance Sampling for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
+\section{Sequential Monte Carlo sampler for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
 
@@
 	The aim of symbolic regression is to uncover interpretable mathematical expressions that best describe the embedding of these loci of solutions. 
-	In the present context, the form of the supergravity potential \eqref{eq:scalarpotential} determining the solutions implies that the loci can be defined through polynomials $p_{m}$ such that $p_{m}(\vec{x}^{(i)}) = 0$, with $i \in \{1, \dots, n_{\rm points}\}$.
+	In the present context, the form of the supergravity potential \eqref{eq:scalarpotential} determining the solutions implies that the loci can be defined through polynomials $p_{m}$ such that $p_{m}\big(\vec{x}^{(i)}\big) = 0$, with $i \in \{1, \dots, n_{\rm points}\}$.
 Such polynomials will be called ``annihilating polynomials'' in the following.
 	Finding annihilating polynomials involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods. 
-	Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and often get trapped in local optima, especially in high-dimensional or multimodal spaces \cite{??}.
-\ce{Citation.}
-
-	To address these challenges, we formulate the search for annihilating polynomials as a determination of a density probability on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimises $\displaystyle \sum_{i=1}^{n_{\rm points}}p(\vec{x}^{(i)})^{2}$.
-Such a probability density is \textit{a priori} hard to find, but can be approximated using variations of Important Sampling methods~\cite{910e8e7d-2e70-317c-adf6-e21cd50755a1}.
-Importance sampling is a method to parametrise expectation values with respect to a target distribution $d$, from a weighted average using another distribution $\pi$.
-It is based on the observation that the expectation
+	Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and often get trapped in local optima, especially in high-dimensional or multimodal spaces.
+
+	To address these challenges, we formulate the search for annihilating polynomials as a determination of a probability density on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimises $\displaystyle \sum_{i=1}^{n_{\rm points}}p\big(\vec{x}^{(i)}\big)^{2}$.
+Polynomials sampled from this density would thus be annihilating polynomials.
+Such a probability density is \textit{a priori} hard to find, but can be approximated using algorithms based on Sequential Important Sampling~\cite{Doucet2001,Liu2004} such as Sequential Monte Carlo samplers~\cite{del2006sequential}.
+They are inspired from Important Sampling (IS)~\cite{osti_4441935,RobertCasella2004}, a method to parametrise expectation values with respect to a target distribution $d$, that can be evaluated pointwise, but from which one does not know how to draw samples.
+IS uses another, usually simpler, distribution $\pi$ (called importance distribution) from which you know how to draw from.
+It is based on the observation that the expectation value
 	\begin{equation}
@@
 	\end{equation}
-	of a function $f$ with respect to $d$ can be computed from the expectation $\mathbb{E}_{\pi}[w f]$, now computed with respect to the distribution $\pi$, with unnormalised $w(z) = d(z)/\pi(z)$.
-Therefore, if it is easier to draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\pi$ than from $d$, one can estimate $\mathbb{E}_{d}[f]$ from the weighted average
-	\begin{equation}
-		\mathbb{E}_{d}[f] \simeq \frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w(z^{(k)})\,f(z^{(k)})}{\displaystyle \sum_{i=1}^{n_{\rm particles}} w(z^{(k)})}.
-	\end{equation}
-	The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the distribution $\pi$.
-\ce{Add conclusion saying that you can parametrise $d$ using a sample and weights, and eq.
-as (4.4).}
-
-	To have an accurate estimation of $d$, we employ an Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} combined with Sequential Monte Carlo (SMC) methods \cite{del2006sequential,naesseth2024elementssequentialmontecarlo}.
-AIS aims at estimating $d$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $d_{0}$ (chosen to be easy to sample from) to the complex target distribution $d$.
-	These distributions are approximated by weighted samples $\{z^{(k)}_{n},w^{(k)}_{n}\}$ of particles, each representing a candidate symbolic expression, such that the resulting weighted average estimates $\pi_{n}$: \ce{Normalise the weights?}
-	\begin{equation}
-		\frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}\,f(z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}} \underset{n_{\rm particles}\rightarrow+\infty}{\longrightarrow} \mathbb{E}_{\pi_{n}}[f],
-	\end{equation}
-	or equivalently
+	for some function $f$ with respect to $d$ can be computed from the expectation $\mathbb{E}_{\pi}[w f]$, now computed with respect to the distribution $\pi$, with unnormalised weights $w = d/\pi$.
+Therefore, one can estimate $\mathbb{E}_{d}[f]$ from a Monte Carlo method: we draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\pi$ and use the weighted average
+	\begin{equation}
+		\mathbb{E}_{d}[f] \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w\big(z^{(k)}\big)\,f\big(z^{(k)}\big)/\displaystyle \sum_{i=1}^{n_{\rm particles}} w\big(z^{(k)}\big).
+	\end{equation}
+	Stated differently, the target distribution $d$ can be approximated from a weighted collection of particles $\{z^{(k)},w^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ drawn from the importance distribution $\pi$ :
+	\begin{equation}
+		d(z) \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}\,\delta\big(z-z^{(k)}\big)/\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)},
+	\end{equation}
+	where $w^{(k)} = w\big(z^{(k)}\big)$.
+The sample admits $d$ as marginal distribution asymptotically when $n_{\rm particles}\rightarrow+\infty$.
+The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the distribution $\pi$, that needs to be close enough to $d$.
+
+	However, providing a good importance distribution $\pi$ remains a hard problem.
+In order to fix this point, we employ a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo} mixed with inspirations from Annealed Importance Sampling (AIS)~\cite{neal1998annealedimportancesampling}.
+SMC aims at estimating $\pi$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $\pi_{0}$ (chosen to be easy to sample from) to the complex distribution $\pi$.
+These distributions are approximated by weighted samples of particles $\big\{z^{(k)}_{n},w^{(k)}_{n}\big\}$ approximating $\pi_{n}$:
 	\begin{equation} \label{eq:pifromweights}
-		\pi_{n}(z) \simeq \frac{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}\,\delta(z-z^{(k)}_{n})}{\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}}.
-	\end{equation}
-	The $\pi_{n}$ are incrementally deformed using a Markov kernel to gradually reproduce the target $d$ and the particles get reweighed.
-This annealing process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
+		\pi_{n}(z) \simeq \sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}_{n}\,\delta(z-z^{(k)}_{n}),
+	\end{equation}
+	with  $\displaystyle \tilde{w}^{(k)}_n  = w^{(k)}_n/\sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}$ the normalised weights.
+The particles are incrementally deformed and reweighed using a Markov kernel to gradually sample the target distribution $d$.
+This process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
+The approximation procedure can be summed up as follows.
+We define the schedule of intermediate distributions $\pi_{n}$ using a temperature-like parameter, starting from an initial, easy to sample distribution $\pi_0$ which is parametrised by a set of particles and weights $\big\{z_0^{(k)},w_0^{(k)}\big\}$.
+We gradually mutate them with an annealing procedure to get a set of $\{z_n^{(k)},w_n^{(k)}\}$, which are used to parametrise $\pi_n$.
+As $n$ increases, the procedure converges such that the particles sample the distribution $\pi$, which itself is used to parametrise the target distribution $d$.
 
 	This procedure has the disadvantage that the weights variance tends to increase, leading to weight degeneracy.
-We use SMC methods to incorporate a resampling procedure to AIS, thus focussing computational effort on high-probability regions.
+AIS-SMC includes a resampling procedure, thus focussing computational effort on high-probability regions.
 This combination of importance sampling, mutation and resampling maintains diversity among the particles and prevents premature convergence to suboptimal models.
@@
 	\subsection{Detailed procedure}	
+	Let us now explain in more detail the procedure, based on ref.~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo}. 
+	The goal is to obtain particles sampled from a probability distribution $d(z)$, where $z$ runs over a space of polynomials, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
+We reconstruct this density function $d$ by series of density functions $\pi_n(z)$, $n\in\llbracket0,n_{\rm epochs}\rrbracket$, such that $\pi_n\to d$ as $n\to n_{\rm epochs}$.
+On every annealing step, $\pi_n$ is defined in terms of an unnormalised density $\gamma_n$ and a normalisation constant as $\pi_n(z) = \gamma_n(z)/Z_n$.
+The unnormalised density at level $n$ is given in terms of a prior distribution $d_0(z)$ over the space of polynomials and a loss function $L(z)$, as
+		\begin{equation}\label{eq:gamman}
+			\gamma_n(z) = d_0(z) \: \exp \Big( -\beta_n L(z)\Big),
+		\end{equation}
+	where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_0 < \beta_1 <\dots< \beta_{n_{\rm epochs}}$.
+The importance given to each polynomial $z$ is thus updated at each steps, with polynomials $z$ with high loss being disfavoured.
+This update is controlled by the inverse temperature constants, enabling deeper exploration during the early stages and protecting the procedure from being trapped in local minima.
+The loss function is chosen to be minimal on annihilating polynomials, its design will be discussed at the end of the section.
+We choose the prior distribution $d_{0}$ to be flat on the space of polynomials, giving equal importance to all of them, which makes easy the initial sampling of the weighted particles $\big\{z^{(k)}_{0},w^{(k)}_{0} = 1/n_{\rm particles}\big\}$.
+
+	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}^{(k)}\big) = \tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)/\tilde{Z}_{n}$, with $z_{0:n}^{(k)} = \big(z_{0}^{(k)},\ldots,z_{n}^{(k)}\big)$, that knows about the whole path of the particles until step $n$.
+$\tilde{\gamma}_{n}$ is defined thanks to a backward propagation kernel $K\big(z^{(k)}_{i-1}\vert z^{(k)}_{i}\big)$:
+	\begin{equation}
+		\tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big) = \gamma_{n}\big(z_{n}^{(k)}\big)\,\prod_{i=1}^{n} K\big(z^{(k)}_{i-1}\vert z^{(k)}_{i}\big).
+	\end{equation}
+	This way, the distribution $\tilde{\pi}_{n}$ describes $\pi_{n}$ as well as the trajectory that followed the particles from epochs $0$ to $n$.
+This allows for more accuracy, correcting potential bias introduced by the mutations, and results in a setup that is more tunable.
+
+	At the beginning of epoch $n\geq1$, $\tilde{\pi}_{n-1}$ is approximated \textit{via} Importance Sampling from an importance distribution $\eta_{n-1}$, \textit{i.e.} from a set of particles and weights $\big\{z_{n-1}^{(k)},\ w_{n-1}^{(k)}\big\}$ using eq.~\eqref{eq:pifromweights}, with $\big\{z_{n-1}^{(k)}\big\}$ drawn from $\eta_{n-1}$ and $w_{n-1}^{(k)} = \tilde{\gamma}_{n-1}\big(z_{0:n-1}^{(k)}\big)/\eta_{n-1}\big(z_{0:n-1}^{(k)}\big)$.\footnote{We define $\eta_{0} = \pi_{0} = \tilde{\pi}_{0} = d_{0}$.} The importance density $\eta_{n-1}$ get mutated using a forward propagation Markov kernel $q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)$, defining the probability to get $z^{(k)}_{n}$ when the current state is $z^{(k)}_{n-1}$:
+	\begin{equation}
+		\eta_{n}\big(z_{0:n}^{(k)}\big) = \eta_{n-1}\big(z_{0:n-1}^{(k)}\big)\,q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big).
+	\end{equation}
+	We then use Importance Sampling to approximate $\tilde{\pi}_{n}$: we draw particles $\big\{z^{(k)}_{n}\big\}$ from $\eta_{n}$, and compute the weights
+	% \begin{equation}
+	% 	w_{n}^{(k)} = \frac{\tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)}{\eta_{n}\big(z_{0:n}^{(k)}\big)} = \frac{\tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)}{\eta_{n-1}\big(z_{0:n-1}^{(k)}\big)\,q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)} = w_{n-1}^{(k)}\,\frac{\tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)}{\tilde{\gamma}_{n-1}\big(z_{0:n-1}^{(k)}\big)\,q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)}= w_{n-1}^{(k)}\,\frac{\gamma_{n}\big(z_{n}^{(k)}\big)\,L\big(z^{(k)}_{n-1}\vert z^{(k)}_{n}\big)}{\gamma_{n-1}\big(z_{n-1}^{(k)}\big)\,q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)}.
+	% \end{equation}
+	\begin{equation} \label{eq:weightsupdate}
+		w_{n}^{(k)} = \frac{\tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)}{\eta_{n}\big(z_{0:n}^{(k)}\big)} = w_{n-1}^{(k)}\,\alpha_{n}^{(k)},
+	\end{equation}
+	with the incremental importance weights $\alpha_{n}^{(k)}$ defined as
+	\begin{equation}	\label{eq: incremental_importance}
+			\alpha^{(k)}_{n} =  \frac{\gamma_{n}\big(z_{n}^{(k)}\big)\,K\big(z^{(k)}_{n-1}\vert z^{(k)}_{n}\big)}{\gamma_{n-1}\big(z_{n-1}^{(k)}\big)\,q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)} = \frac{\exp\Big(-\beta_{n+1}L\big(z_{n+1}^{(k)}\big)\Big)}{\exp\Big(-\beta_{n}L\big(z_{n}^{(k)}\big)\Big)}\,\frac{K\big(z^{(k)}_{n}\vert z^{(k)}_{n+1}\big)}{q\big(z^{(k)}_{n+1}\vert z^{(k)}_{n}\big)}.
+	\end{equation}
+
+	For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm.
+On every epoch, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
+The moves that have been allowed in our implementation are the following.
+	\begin{itemize}
+		\item \textbf{Coefficient perturbation}\quad Given a polynomial, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$, \textit{e.g.}
+		\begin{equation}
+			2\, x_1x_{2} + 3\, x_2^2 \longmapsto  2.1\, x_1x_{2} + 3\, x_2^2.
+		\end{equation}
+		\item \textbf{Variable multiplication}\quad Given a polynomial, we pick randomly one of its monomials, and multiply it by one of the available variables, \textit{e.g.}
+		\begin{equation}
+			2\, x_1x_{2} + 3\, x_2^2 \longmapsto  2\, x_1 x_2^{2} + 3\, x_2^2.
+		\end{equation}
+		\item \textbf{Variable division}\quad Given a polynomial, we choose randomly one of its monomials, and divide it by one of its variables, \textit{e.g.}
+		\begin{equation}
+			2\,x_1 x_2 + 3\, x_2^2 \longmapsto  2\, x_1 + 3\, x_2^2.
+		\end{equation}
+	\end{itemize}
+	Each of these operations is chosen randomly, with probabilities $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$.
+	%		For the case of coefficient perturbations, the transition is symmetric. 
+	%		However, this symmetry does not hold in general.
+For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
+In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
+	A common choice of backward kernel in such context is the reversed forward kernel $K\big(z^{(k)}_{n-1}\vert z^{(k)}_{n}\big) = q\big(z^{(k)}_{n-1}\vert z^{(k)}_{n}\big)$.
+	After performing these updates, the change is accepted based on the temperature-dependent rate
+	\begin{equation}\label{eq:acceptanceratio}
+		A\big(z_{n}^{(k)},z_{n-1}^{(k)}\big) = \mathrm{min} \left(1,\alpha_{n}^{(k)}\right) = \mathrm{min} \left(1,\frac{\gamma_{n}\big(z_{n}^{(k)}\big)\,q\big(z^{(k)}_{n-1}\vert z^{(k)}_{n}\big)}{\gamma_{n-1}\big(z_{n-1}^{(k)}\big)\,q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)}  \right).
+	\end{equation}
+	We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A\big(z_{n+1}^{(k)},z_{n}^{(k)}\big)$ and reject it otherwise.
+This way we accept systematically all moves that increase the weights, and some of those that lower the weights, allowing for some exploration of the space of polynomials.	Once the particles have been mutated, the evolution of the weights is computed using eq.~\eqref{eq:weightsupdate}.
+
+	To ensure an efficient exploration of the landscape, we would like to avoid having too many particles with low weights: as the algorithm progresses, particles with negligible weights contribute minimally to the approximation of the target distribution (see eq.~\eqref{eq:pifromweights}), leading to a concentration of the effective sample on a subset of particles with substantial weights.
+This can be estimated using the effective sample size~\cite{ca54d442-d5bd-32ea-a920-38aa7d8a4043}
+	\begin{equation}
+		{\rm ESS}_{n} = \Bigg(\sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}_{n}{}^{2}\Bigg)^{-1},
+	\end{equation}
+	where the $\tilde{w}^{(k)}_{n}$ are normalised weights deduced from the $w^{(k)}_{n}$.
+${\rm ESS}_{n}$ takes values between $1$ (complete degeneracy, there is only one meaningful particle) and $n_{\rm particles}$ (no degeneracy, all particles contribute equally).
+We resample the particles when the ESS falls below a predetermined threshold, typically $n_{\rm particles}/2$.
+During resampling, new particles are drawn from the empirical distribution defined by the current particle weights $\tilde{w}^{(k)}_{n}$.	This procedure results in a new particle set where high-weight particles may appear multiple times, while low-weight particles may be eliminated entirely.
+Following resampling, all particle weights are reset to uniform values $w_{n}^{(k)} = 1/n_{\rm particles}$, as the information previously encoded in the weight distribution has been incorporated into the spatial distribution of the resampled particles.
+This resampling mechanism ensures that computational resources are concentrated on exploring the most promising regions of the state space.
 
@@
 
-		%\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
-
-	Let us now explain in more detail the procedure. 
-	The goal is to obtain a probability distribution $d(z)$, where $z$ runs over a space of polynomials, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
-	We reconstruct this density function $d$ by series of density functions $\pi_n(z)$, $n\in\llbracket1,n_{\rm epochs}\rrbracket$, such that $\pi_n\to d$ as $n\to n_{\rm epochs}$. 
-	On every annealing step, $\pi_n$ is defined in terms of an unnormalised density $\gamma_n$ and a normalisation constant as $\pi_n(z) = \gamma_n(z)/Z_n$.
-	The unnormalised density at level $n$ is given in terms of a prior distribution $d_0(z)$ over the space of polynomials and a loss function $L(z)$, as \ce{Citation.}
-			\begin{equation}\label{eq:gamman}
-				\gamma_n(z) = d_0(z) \: \exp \Big( -\beta_n L(z)\Big),
-			\end{equation} 
-	where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_1 < \beta_2 <\dots< \beta_{n_{\rm epochs}}$.
-The importance given to each polynomial $z$ is thus updated at each steps, with polynomials $z$ with high loss being disfavoured.
-This update is controlled by the inverse temperature constants, enabling deeper exploration during the early stages and protecting the procedure from being trapped in local minima.
-The loss function is chosen to be minimal on annihilating polynomials, its design will be discussed at the end of the section.
-We chose the prior distribution $d_{0}$ to be flat on the space of polynomials, giving equal importance to all of them, which makes easy the initial sampling of the particles $\{z^{(k)}_{0}\}$.
-
-	At each epoch $n$, $\pi_{n}$ is approximated \textit{via} a set of particles and weights $\{z_{n}^{(k)},\ w_{n}^{(k)}\}$ in the sense of eq.~\eqref{eq:pifromweights}.
-The sample of particles $z^{(k)}_{n}$ get mutated using a forward propagation Markov kernel $q(z^{(k)}_{n+1}\vert z^{(k)}_{n})$, defining the probability to get $z^{(k)}_{n+1}$ when the current state is $z^{(k)}_{n}$.
-For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm.
-	On every epoch, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
-	The moves that have been allowed in our implementation are the following.
-	\begin{itemize}
-		\item \textbf{Coefficient perturbation}\quad Given a polynomial, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$, \textit{e.g.}
-		\begin{equation}
-			2 x_1x_{2} + 3 x_2^2 \longmapsto  2.1 x_1x_{2} + 3 x_2^2\,.
-		\end{equation}
-		\item \textbf{Variable multiplication}\quad Given a polynomial, we pick randomly one of its monomials, and multiply it by one of the available variables, \textit{e.g.}
-		\begin{equation}
-			2 x_1x_{2} + 3 x_2^2 \longmapsto  2 x_1 x_2^{2} + 3 x_2^2\,.
-		\end{equation}
-		\item \textbf{Variable division}\quad Given a polynomial, we choose randomly one of its monomials, and divide it by one of its variables, \textit{e.g.}
-		\begin{equation}
-			2 x_1 x_2 + 3 x_2^2 \longmapsto  2 x_1 + 3 x_2^2\,.
-		\end{equation}
-	\end{itemize}
-	Each of these operations is chosen randomly, with probabilities $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$.
-	%		For the case of coefficient perturbations, the transition is symmetric. 
-	%		However, this symmetry does not hold in general.
-For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
-In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
-	After performing these updates, the change is accepted based on the temperature-dependent rate
-	\begin{equation}\label{eq:acceptanceratio}
-		A(z_{n+1}^{(k)},z_{n}^{(k)}) = \mathrm{min} \left(1,\frac{ \gamma_{n+1}(z_{n+1}^{(k)}) q(z_{n}^{(k)} | z_{n+1}^{(k)}) }{ \gamma_{n}(z_{n}^{(k)}) q(z_{n+1}^{(k)} | z_{n}^{(k)}) }  \right)\,.
-	\end{equation}
-	We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_{n+1}^{(k)},z_{n}^{(k)})$ and reject it otherwise.
-
-	Once the particles have been mutated, the evolution of the weights is given by
-	\begin{equation}
-		w_{n+1}^{(k)} = w_{n}^{(k)}\ \alpha_{n+1}^{(k)},
-	\end{equation}
-	where the incremental importance weights $\alpha_{n+1}^{(k)}$ are given by\footnote{The incremental weight is in general defined as $\alpha^{(k)}_{n+1} = \frac{\gamma_{n+1}(z_{n+1}^{(k)})}{\gamma_{n}(z_n^{(k)})}\,\frac{K(z^{(k)}_{n}\vert z^{(k)}_{n+1})}{q(z^{(k)}_{n+1}\vert z^{(k)}_{n})}$, where $K(z^{(k)}_{n}\vert z^{(k)}_{n+1})$ is the backward propagation kernel~\cite{del2006sequential}.
-For simplicity, we chose to identify $K$ to the forward propagation kernel $q$.}~\cite{del2006sequential}
-	\begin{equation}	\label{eq: incremental_importance}
-			\alpha^{(k)}_{n+1} = \frac{\gamma_{n+1}(z_{n+1}^{(k)})}{\gamma_{n}(z_n^{(k)})}\,\frac{q(z^{(k)}_{n}\vert z^{(k)}_{n+1})}{q(z^{(k)}_{n+1}\vert z^{(k)}_{n})}=\frac{\exp\big(-\beta_{n+1}L(z_{n+1}^{(k)})\big)}{\exp\big(-\beta_{n}L(z_{n}^{(k)})\big)}\,\frac{q(z^{(k)}_{n}\vert z^{(k)}_{n+1})}{q(z^{(k)}_{n+1}\vert z^{(k)}_{n})}.
-	\end{equation}
-
-	To ensure an efficient exploration of the landscape, we would like to avoid having to many particles with low weights: as the algorithm progresses, particles with negligible weights contribute minimally to the approximation of the target distribution (see eq.~\eqref{eq:pifromweights}), leading to a concentration of the effective sample on a subset of particles with substantial weights.
-This can be estimated using the effective sample size~\cite{Liu01091998}
-	\begin{equation}
-		{\rm ESS}_{n+1} = \Bigg(\sum_{k=1}^{n_{\rm particles}} \tilde{w}^{(k)}_{n+1}{}^{2}\Bigg)^{-1},
-	\end{equation}
-	where the $\tilde{w}^{(k)}_{n+1}$ are normalised weights deduced from the $w^{(k)}_{n+1}$.
-${\rm ESS}_{n+1}$ takes values between $1$ (complete degeneracy, there is only one meaningful particle) and $n_{\rm particles}$ (no degeneracy, all particles contribute equally).
-We resample the particles when the ESS falls below a predetermined threshold, typically $n_{\rm particles}/2$.
-During resampling, new particles are drawn from the empirical distribution defined by the current particle weights $\tilde{w}^{(k)}_{n+1}$.	This procedure results in a new particle set where high-weight particles may appear multiple times, while low-weight particles may be eliminated entirely.
-Following resampling, all particle weights are reset to uniform values $w_{n+1}^{(k)} = 1/n_{\rm particles}$, as the information previously encoded in the weight distribution has been incorporated into the spatial distribution of the resampled particles.
-This resampling mechanism ensures that computational resources are concentrated on exploring the most promising regions of the state space.
-
 	A flow chart of the full AIS-SMC procedure is given in fig.~\ref{ASMCflowchart}.
@@
 	\paragraph{}
-	To compute the acceptance ratio and weights \textit{via} eq.~\eqref{eq:acceptanceratio} and \eqref{eq: incremental_importance} and we need to consider the loss function in~\eqref{eq:gamman}.
+	To compute the acceptance ratio and weights \textit{via} eq.~\eqref{eq:acceptanceratio} and \eqref{eq: incremental_importance} and we need to consider the loss function in eq~\eqref{eq:gamman}.
 	In the present context, we use the following loss, where the polynomials have been parameterised as $z = \sum_m c_m X_m$ with $X_m$ denoting the possible monomials up to a given degree,%

### 2025-10-02 Draft_MLFlatDirections.tex
Update of the clustering figures, small changes in sec? 4 and 5, acknowledgements.

@@
 \definecolor{myred}{rgb}{0.5, 0.0, 0.13}
+\definecolor{clusteringred1}{RGB}{139, 0, 0}
+\definecolor{clusteringred2}{RGB}{231, 76, 60}
+\definecolor{clusteringyellow1}{RGB}{192, 200, 44}
 
@@
 
-{\large  Bastien Duboeuf$^{1}$, Camille Eloy$^{1}$ \,and\, Gabriel Larios$^{2}$}
+{\large  Bastien Duboeuf$^{1}$, Camille Eloy$^{2}$ \,and\, Gabriel Larios$^{3}$}
 
@@
 
-	{\it $^{1}$ ENS de Lyon, CNRS, LPENSL, UMR5672,\\ 69342, Lyon cedex 07, France}  \\
+	{\it $^{1}$ Max-Planck-Institut f\"ur Gravitationsphysik (Albert-Einstein-Institut)\\ Am M\"uhlenberg 1, DE-14476 Potsdam, Germany}  \\
 
@@
 
-	{\it $^{2}$ Mitchell Institute for Fundamental Physics and Astronomy, \\
+	{\it $^{2}$ ENS de Lyon, CNRS, LPENSL, UMR5672,\\ 69342, Lyon cedex 07, France}  \\
+
+	\vspace{10pt}
+
+	{\it $^{3}$ Mitchell Institute for Fundamental Physics and Astronomy, \\
 	Texas A\&M University, College Station, TX, 77843, USA}     \\
@@
 	Our approach combines numerical exploration and symbolic inference.
-For the latter, we develop a symbolic regression algorithm based on Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
+For the latter, we develop a symbolic regression algorithm based on Annealed Importance Sampling combined with Sequential Monte Carlo, well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
 	The algorithm reconstructs a set of polynomial relations that provides an explicit analytic parametrization of a new family of solutions. 
@@
 These deformations are parametrised by exactly marginal operators, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
-ICI \ce{Needs some modifications.}
+\ce{Needs some modifications.}
 
@@
 
-		Once the Annealing loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
+Once the AIS-SMC loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
 To deal with it, for each polynomial we now only modify its coefficients with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma')$ and keep the particles when the loss function decreases.
-
-%		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold).
-Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate.
-Total time needed, without cluster or fancy computers.}
-	%\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%
-\section{Sequential Monte Carlo sampler for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
+\section{Annealed Sequential Monte Carlo sampler for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
 
 	\subsection{General idea}
-	The numerical sampling of the space of vacua described above results in clouds of points embedded in a higher-dimensional space. 
+	The numerical sampling of the space of vacua (described in sec.~\ref{sec:graddes}) results in clouds of points embedded in a higher-dimensional space. 
 	The aim of symbolic regression is to uncover interpretable mathematical expressions that best describe the embedding of these loci of solutions. 
@@
 	However, providing a good importance distribution $\pi$ remains a hard problem.
-In order to fix this point, we employ a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo} mixed with inspirations from Annealed Importance Sampling (AIS)~\cite{neal1998annealedimportancesampling}.
+In order to fix this point, we employ a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo} enhanced by Annealed Importance Sampling (AIS)~\cite{neal1998annealedimportancesampling}.
 SMC aims at estimating $\pi$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $\pi_{0}$ (chosen to be easy to sample from) to the complex distribution $\pi$.
@@
 
-	\subsection{Detailed procedure}	
+	\subsection{Detailed procedure}	\label{sec:detailedAISSMC}
 	Let us now explain in more detail the procedure, based on ref.~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo}. 
@@
 
-	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}^{(k)}\big) = \tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)/\tilde{Z}_{n}$, with $z_{0:n}^{(k)} = \big(z_{0}^{(k)},\ldots,z_{n}^{(k)}\big)$, that knows about the whole path of the particles until step $n$.
+	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}^{(k)}\big) = \tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)/\tilde{Z}_{n}$, with $z_{0:n}^{(k)} = \big(z_{0}^{(k)},\ldots,z_{n}^{(k)}\big)$, that describes the global trajectory of the particles until step~$n$.
 $\tilde{\gamma}_{n}$ is defined thanks to a backward propagation kernel $K\big(z^{(k)}_{i-1}\vert z^{(k)}_{i}\big)$:
@@
 	\end{equation}
-	This way, the distribution $\tilde{\pi}_{n}$ describes $\pi_{n}$ as well as the trajectory that followed the particles from epochs $0$ to $n$.
+	This way, the distribution $\tilde{\pi}_{n}$ describes $\pi_{n}$ as well as the path that followed the particles from epochs $0$ to $n$.
 This allows for more accuracy, correcting potential bias introduced by the mutations, and results in a setup that is more tunable.
@@
 		\item \textbf{Coefficient perturbation}\quad Given a polynomial, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$, \textit{e.g.}
-		\begin{equation}
+		\begin{equation} \label{eq:coeffperturb}
 			2\, x_1x_{2} + 3\, x_2^2 \longmapsto  2.1\, x_1x_{2} + 3\, x_2^2.
@@
 
-	Upon completion, the loss function converges around $0.002$ \gl{$10^{-3}$?}.
+	Upon completion, the loss function converges around $10^{-3}$.
 The distribution of the values of the gradient at each of the data points is plotted in fig.~\ref{fig:log_grad_V}.
@@
 We show in fig.~\ref{fig:3dplots} some 3d projections of the data to visualize the clustering.
-In these scatter plots, orange points belong to the main cluster, while blue points are those that the algorithm failed to assign to any cluster.
+In these scatter plots, red points belong to the main cluster, while yellow points are those that the algorithm failed to assign to any cluster.
 The smallest cluster, made of 5 points, is likely an artefact of local fluctuations in the data density and is not interpreted as physically meaningful.
@@
 		\centering
+		\centerline{
 			\subfigure{ \label{fig:3dx4x8x10}
 				\begin{tikzpicture}
-		  		\draw (0,0) node (fig1) {\includegraphics[scale=0.7, trim = 0.75cm 0 0 1cm, clip]{Figures/3d_plot_x4_x8_x10_21_05_2025_desampled.png}};
-		  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
-		  		\draw (9,0) node (fig2) {\includegraphics[scale=0.7, trim = 0.75cm 0 0 1cm, clip]{Figures/3d_plot_x1_x4_x8_21_05_2025_desampled.png}};
-		  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
-		  		\draw (3.8,-3) node (leg) {\includegraphics[scale=0.85]{Figures/3d_plot_21_05_2025_desampled_legend.pdf}};
+					\draw (0,0) node (fig11) {\includegraphics[scale=0.7, trim = 0.25cm 0.2cm 0.25cm 1.2cm, clip]{Figures/3d_plot_x4_x8_x10_21_05_2025_desampled_1.png}};
+			  		\draw ($(fig11.north west) + (0,0)$) node {\small (a)};
+			  		\draw (5.75,-0.25) node (fig12) {\includegraphics[scale=0.7, trim = 0.5cm 0.1cm 1.3cm 1.4cm, clip]{Figures/3d_plot_x4_x8_x10_21_05_2025_desampled_2.png}};
+			  		% \draw ($(fig12.north west) + (0,0)$) node {\small (b)};
+			  		\draw (11.5,0) node (fig13) {\includegraphics[scale=0.7, trim = 0.25cm 0.2cm 0.2cm 1.2cm, clip]{Figures/3d_plot_x4_x8_x10_21_05_2025_desampled_3.png}};
+			  		% \draw ($(fig13.north west) + (0,0)$) node {\small (c)};
+
+			  		\begin{scope}[shift={(0,-5.75)}]
+			  			\draw (-0.25,0) node (fig21) {\includegraphics[scale=0.7, trim = 0.25cm 0.2cm 0.25cm 1.2cm, clip]{Figures/3d_plot_x1_x4_x8_21_05_2025_desampled_1.png}};
+				  		\draw ($(fig11.north west) + (0,-5.5)$) node {\small (b)};
+				  		\draw (5.75,-0.25) node (fig22) {\includegraphics[scale=0.7, trim = 0.2cm 0.1cm 0.35cm 1.4cm, clip]{Figures/3d_plot_x1_x4_x8_21_05_2025_desampled_2.png}};
+				  		\draw (11.75,0) node (fig33) {\includegraphics[scale=0.7, trim = 0.6cm 0.2cm 0.2cm 1.2cm, clip]{Figures/3d_plot_x1_x4_x8_21_05_2025_desampled_3.png}};
+			  		\end{scope}
+
+			  		\draw [thick, clusteringred1, fill=clusteringred2,opacity=0.9] (12,-2.6) circle [radius=2.5pt] node [right=0.3cm, black, opacity=1] {\small Cluster};
+			  		\draw [gray, fill=clusteringyellow1, opacity=0.6] (12,-3.1) circle [radius=3pt] node [right=0.3cm, black, opacity=1] {\small Not assigned};
+			  		\draw [rounded corners=2pt] (11.75,-2.35) rectangle +(2.75,-1.05);
 			  	\end{tikzpicture}
 			}
+		}
 		\subfigure{\label{fig:3dx1x4x8}}
+		\vspace{-0.5cm}
 		\caption{3d projections of the data set in selected coordinates: (a) $(x_4, x_8, x_{10})$ and (b) $(x_1, x_4, x_8)$.
-The colors are assigned by the clustering algorithm: the orange points correspond to the cluster, while the blue points were not assigned to any cluster.
+The colors are assigned by the clustering algorithm: the red points correspond to the cluster, while the yellow points were not assigned to any cluster.
 The size of each class of points has been tuned to favour the visualisation.}
@@
 
-	We initialized the algorithm with
+	We initialized the algorithm with\footnote{$n_{\rm points}$ is the number of points used in the gradient descent, see sec.~\ref{sec:graddes} ; $n_{\rm epochs}$, $n_{\rm particles}$, $\beta_{0}$, $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$ are, respectively, the number of steps, the number of particles, the initial inverse temperature and the probabilities of each MCMC moves used in the AIS-SMC procedure, see sec.~\ref{sec:detailedAISSMC} ; $\lambda$ is the regularisation parameter used in the loss function, see eq.~\eqref{eq:lossreg} ; $\sigma$ is the parameter defining the Gaussian noise for the coefficient perturbation move of the AIS-SMC procedure, see eq.~\eqref{eq:coeffperturb}.}
 	\begin{equation}	\label{eq:sample10000adaptativetemp}
@@
 			&\texttt{n\_epochs = 1000},\\
-			&\texttt{beta  = 1e-6}, \\
-			&\texttt{p\_{modify} = 0.5},\\
+			&\texttt{n\_particles = 1000},\\
+			&\texttt{beta0  = 1e-6}, \\
+			&\texttt{p\_{shift} = 0.5},\\
 			&\texttt{p\_{multiply} = 0.25},\\
@@
 			&\texttt{lambda = 1000},\\
-			&\texttt{sigma = 0.1},\\
-			&\texttt{n\_particles = 1000}.
+			&\texttt{sigma = 0.1}.
 		\end{aligned}
 	\end{equation}
-	%ICI \gl{link to notations in section 3}
+	\gl{link to notations in section 3}
 	The convenience of these parameters was determined empirically --a systematic analysis of its optimization is left for future work.
@@
 As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
-%ICI \ce{Not sure if I agree with the last sentence.
+\ce{Not sure if I agree with the last sentence.
 Maybe we could weaken the statement a bit?}
+
+\section*{Acknowledgements}
+We would like to thank Magdalena Larfors, whose talk on Machine Learning at the kick-off meeting of the COST action ``Fundamental challenges in theoretical physics'' in Padova in May 2024 triggered this project.
+We are thankful to \ce{Jan?
+for ...}, and to Nelly Pustelnik, Jason Reneuve and Henning Samtleben for inspiring discussions.
+\ce{Funding Bastien?} \ce{Others?}
 

### 2025-10-02 Draft_MLFlatDirections.tex
Changes during meeting.

@@
 Within this holographic framework, supergravity theories in AdS backgrounds serve as the low-energy effective descriptions of string theory compactifications, making them natural laboratories for exploring the gravitational side of the duality.
-The CFT side plays a crucial role in statistical physics, as CFT are known to describe phase transitions ; they are also fixed point of Renormalisation Group flow and this is this latter aspect that is our interest in this paper.
-An interesting question is indeed to know whether those CFT are isolated fixed points of RG flows, or belong to a continuous family of CFT.
-If this is the case, the space of continuous deformations that takes from one CFT to another is called a conformal manifold.
-These deformations are parametrised by exactly marginal operators, or in other words operators that preserves the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
-\ce{Needs some modifications.}
+On the other side, CFT’s appear in multiple scenarios, providing nice descriptions of phase transitions in statistical physics, and from a fundamental perspective, they are of utmost importance in quantum field theories (QFTs), where they describe fixed points of Renormalisation Group flow.
+From the latter perspective, an interesting question is  whether CFTs are isolated fixed points or instead belong to a continuous families. 
+In that case, the space of continuous deformations that takes from one CFT to another is called a conformal manifold. 
+These deformations are parametrised by exactly marginal operators, or in other words, operators that preserve the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
+\ce{Bastien: changed here.}
 
@@
 %%%%%%%%%%%%%%%%%%
-\section{Annealed Importance Sampling for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
-
-	%\item Annealed Importance Sampling: first explain general idea (construct density probability, role of temperature, links with Monte-Carlo), discuss $\beta$ to control exploration and exploitation phases.
-
-The numerical sampling of the space of vacua described above results in clouds of points embedded in a higher-dimensional space. 
-In the realm of symbolic regression, the aim is to uncover interpretable mathematical expressions that best describe the embedding of these loci of solutions. 
-In the present context, the form of the supergravity potential \eqref{eq:scalarpotential} determining the solutions implies that the loci can be defined through polynomial expressions such that $p(\vec{x}^{\,i}) = 0$, with $i \in \{1, \dots, \texttt{n\_{sample}}\}$.
-Finding such polynomials involves navigating a vast, discrete, and often rugged search space of possible symbolic models, which poses significant challenges for traditional sampling methods. 
-Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and often get trapped in local optima, especially in high-dimensional or multimodal spaces \cite{??}.
-
-To address these challenges, we employ an Annealed Importance Sampling (AIS) \cite{neal1998annealedimportancesampling} combined with Sequential Monte Carlo (SMC) methods \cite{naesseth2024elementssequentialmontecarlo}.
-AIS aims to estimate ratios of partition functions by constructing a sequence of intermediate distributions that smoothly transition from an initial, tractable distribution (e.g.
-a prior over symbolic expressions) to the complex target posterior distribution.
-This annealing process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient exploration of the probability landscape.
-
-SMC realises this procedure by encoding the probability distributions into a set of particles—each representing a candidate symbolic expression— and weights, and making them evolve so as to focus computational effort on high-probability regions.
-This combination of importance sampling, resampling, and mutation maintains diversity among the particles and prevents premature convergence to suboptimal models.
-These features make AIS-SMC particularly well-suited for symbolic regression tasks, where the search space is not only high-dimensional but also structured and discontinuous.
-
-	\begin{figure}[h!]
-			\centering
-			\begin{minipage}{15cm}
-				\begin{tcolorbox}[
-					colback=white,
-					colframe=myblue,
-					title=\textbf{ASMC Algorithm},
-					fonttitle=\sffamily\large,
-					halign title=flush center,
-					boxrule=2pt,
-					left=6pt,
-					right=6pt,
-					top=8pt,
-					bottom=8pt
-					]
-					\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]
-
-						% Nœuds
-						\node (start) [startstop] {Start};
-
-						\node (init_particles) [process, below of=start] {Initialize particles \& weights};
-
-						\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};
-
-						\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};
-
-						\node (ess_check) [decision, below of=weight_update] {Effective Sample Size $<$ Threshold?};
-
-						\node (resample) [process, right=3.8cm of ess_check] {Resample particles};
-
-						\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with MCMC kernel};
-
-						\node (acceptance) [process, below of=mutation] {Accept/Reject particles};
-
-						\node (end_iter) [decision, below of=acceptance] {Last step?};
-
-						\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};
-
-						\node (output) [process, below of=exploit] {Return particles};
-
-						\node (stop) [startstop, below of=output] {End};
-
-						% Flèches avec étiquettes améliorées
-						\draw [arrow] (start) -- (init_particles);
-						\draw [arrow] (init_particles) -- (compute_beta);
-						\draw [arrow] (compute_beta) -- (weight_update);
-						\draw [arrow] (weight_update) -- (ess_check);
-
-						\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
-						\draw [arrow] (resample) |- (mutation);
-
-						\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
-						\draw [arrow] (mutation) -- (acceptance);
-						\draw [arrow] (acceptance) -- (end_iter);
-
-						% Boucle de retour améliorée
-						\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {No} ++(-4.5,0) |- (compute_beta);
-
-						\draw [arrow] (end_iter) -- node[right, arrow_label] {Yes} (exploit);
-						\draw [arrow] (exploit) -- (output);
-						\draw [arrow] (output) -- (stop);
-
-					\end{tikzpicture}
-				\end{tcolorbox}
-			\end{minipage}
-			\caption{Flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
-			\label{ASMCflowchart}
-		\end{figure}
-
-		%\item Then more details: discuss hypotheses to compute the weights, choice of transformations, choice of $\beta$, choice of loss, prior, initial sampling, choice of representation for the polynomials.
-
-Let us now explain in more detail the procedure. 
-The goal is to obtain a probability distribution $d(z)$, where $z$ runs over a space of polynomials. 
-This function assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify such symbolic expressions.
-We reconstruct this density function by series of density functions $\pi_n(z)$ such that $\pi_n\to d(z)$ as $n\to\infty$. 
-On every annealing step, $\pi_n$ is defined in terms of an unnormalised density $\gamma_n$ and a normalisation constant as $\pi_n(z) = \gamma_n(z)/Z_n$.
-The unnormalised density at level $n$ is given in terms of a prior distribution $d_0(z)$ over the hypothesis space and a loss function $L(z)$:
-		\begin{equation}\label{eq:gamman}
-			\gamma_n(z) = d_0(z) \: \exp \left( -\beta_n L(z) \right),
-		\end{equation} 
-where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_1 < \beta_2 <\dots< \beta_N$.
-
-		Sequential importance sampling \cite{...} further assumes that the density functions $\pi_n(z)$ can be given in terms of importance densities $q^k_n(z)$ and weights $w^k_n$ as $\pi_n(z) = \sum w^k_n q^k_n(z)/Z_n$, and these importance densities can be sequentially given as
-		 \begin{equation}
-		 	q_n(z_n) = q_{n-1}(z_{n-1}) q_{n\vert n-1}(z_n\vert z_{n-1})\,.
-		 \end{equation}
-At each epoch, we $\pi_{n}$ can be approximated via a set of particles and weights $\{z_{n}^k,\ w_{n}^k\}$  so that\footnote{In the following, we always normalise the weights so that $\sum_k w_{n}^k=1$.}
-		 \begin{equation}
-		 	\pi_n(z) \approx \sum_k w_{n}^k\ \delta(z-z_{n}^k)\,,
-		 \end{equation}
-To obtain a new set $\{z_{n+1}^k,\ w_{n+1}^k\}$ approximating $\pi_{n+1}$, we sample from the forward propagation kernel $q_{n+1}(z_{n+1}\vert z_n)$ that defines how we generate the state at time $n+1$ given the state at time $n$.
-Similarly, the evolution of the weights is given by \gl{for $k>1$, this is a bit schematic...}
-\[
-	w_{n+1} = \frac{\gamma_{n+1}}{q_{n+1}} = \frac{\gamma_{n+1}}{q_{n}\ q_{n+1 \vert n}} = w_{n}\ \alpha_{n+1}\,,
-\]
-where the incremental importance weights $\alpha_{n}^k$ are given by
-		\begin{equation}	\label{eq: incremental_importance}
-			\begin{aligned}
-				\alpha^k_{n+1} &= \frac{\gamma_{n+1}(z_{n+1})}{\gamma_{n}(z_n)}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}	\\
-				&=e^{-\beta_nL(z_n)+\beta_{n+1}L(z_{n+1})}\frac1{q^k_{n+1 \vert n}(z_{n+1}\vert z_{n})}\,.
-			\end{aligned}
-		\end{equation}
-
-		For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm. 
-On every step, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
-The moves that have been allowed in our implementation are:
-		\begin{itemize}
-			\item \textbf{Coefficient pertubation}. Given a polynomial $z_{n}$, we choose one of its coefficients at random and modify it by a Gaussian noise distributed as $\mathcal{N}(0,\sigma^2)$. E.g.
-			\[
-				2 x_1 + 3 x_2^2 \mapsto  2.1 x_1 + 3 x_2^2\,.
-			\]
-			\item \textbf{Variable multiplication}. Given a polynomial $z_{n}$, we pick randomly one of its monomials, and multiply it by one of the available variables. E.g.
-			\[
-				2 x_1 + 3 x_2^2 \mapsto  2 x_1 x_2 + 3 x_2^2\,.
-			\]
-			\item \textbf{Variable division}. Given a polynomial $z_{n}$, we choose randomly one of its monomials, and divide it by one of its variables. E.g.
-			\[
-				2 x_1 x_2 + 3 x_2^2 \mapsto  2 x_1 + 3 x_2^2\,.
-			\]
-		\end{itemize}
-		Each of these operations is chosen randomly, with probabilities $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$.
-%		For the case of coefficient perturbations, the transition is symmetric. 
-%		However, this symmetry does not hold in general.
-For other types of operations—such as multiplication or division by a variable—the transition from \( z_{n-1}^k \) to \( z_n^k \) is generally not equivalent to the reverse transition from \( z_n^k \) to \( z_{n-1}^k \).
-In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
-After performing these updates, the change is accepted based on the temperature-dependent rate \gl{need to double check this}
-		\begin{equation}\label{eq:acceptanceratio}
-			A(z_n,z_{n-1}) = \mathrm{min} \left(1,\frac{ \gamma_n(z_n^k) q(z_{n-1}^k | z_n^k) }{ \gamma_{n-1}(z_{n-1}^k) q(z_n^k | z_{n-1}^k) }  \right)\,.
-		\end{equation}
-		We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A(z_n,z_{n-1})$ and reject it otherwise.
-		The kernel $q(z_{n-1}^k | z_n^k)$ thus encapsulates the effects of performing these operations on the polynomials at step $n$.
-
-		To compute the weights and kernels via \eqref{eq: incremental_importance} and \eqref{eq:acceptanceratio} we need to consider the loss function in \eqref{eq:gamman}.
-In the present context, we use the following loss, where the polynomials have been parameterised as $z = \sum_k c_k X_k$ with $X_k$ denoting the possible monomials up to a given degree,%
-\footnote{So, if we have $x$ and $y$ as variables, and the maximum degree is 2, then $X_k$ are $1, x, y, x^2, y^2, x y$.}
-		\begin{equation} \label{eq:lossreg}
-			L(z) = \sum_{i} z(x_i)^2 + \frac{\lambda}{\sum_k |c_k|}\,.
-		\end{equation}
-Here, the first term is just the sum of the square of the polynomial evaluated on the data, and is therefore minimal when the polynomial annihilates the data. 
-The second term is a regularisation factor that prevents the algorithm to send all the coefficient to 0, which would give a trivial solution to the problem. 
-We typically take $\lambda \sim \mathcal{O}(10^3)$. 
-Together with the loss function, we also need to specify a cooling schedule for $\beta$. We will discuss different approaches in the next section.
-
-Once the AIS-SMC loop is over, we end up with a total of $n_{\rm sample}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
-To deal with it, for each polynomial we now only modify its coefficients with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma')$ and keep the particles when the loss function decreases.
-
-%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%
-\section{Annealed Sequential Monte Carlo sampler for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
+\section{Annealed Sequential Monte Carlo Sampler for Polynomial Symbolic Regression} \label{Sec:AIS-SMC}
 
@@
 	Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and often get trapped in local optima, especially in high-dimensional or multimodal spaces.
-
-	To address these challenges, we formulate the search for annihilating polynomials as a determination of a probability density on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimises $\displaystyle \sum_{i=1}^{n_{\rm points}}p\big(\vec{x}^{(i)}\big)^{2}$.
-Polynomials sampled from this density would thus be annihilating polynomials.
+\ce{Try to find a ref.}
+
+	To address these challenges, we formulate the search for annihilating polynomials as a determination of a probability density on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimise the error \ce{Bastien: changed here.}
+	\begin{equation}
+		\sum_{i=1}^{n_{\rm points}}p\big(\vec{x}^{(i)}\big)^{2}.
+	\end{equation}
+	Polynomials sampled from this density would thus be good approximations to annihilating polynomials.
 Such a probability density is \textit{a priori} hard to find, but can be approximated using algorithms based on Sequential Important Sampling~\cite{Doucet2001,Liu2004} such as Sequential Monte Carlo samplers~\cite{del2006sequential}.
 They are inspired from Important Sampling (IS)~\cite{osti_4441935,RobertCasella2004}, a method to parametrise expectation values with respect to a target distribution $d$, that can be evaluated pointwise, but from which one does not know how to draw samples.
-IS uses another, usually simpler, distribution $\pi$ (called importance distribution) from which you know how to draw from.
-It is based on the observation that the expectation value
+IS uses another, usually simpler, distribution $\pi$ (called importance distribution) that one knows how to draw from.
+It is based on the observation that the expectation value \ce{Change $\pi$ to $\eta$, $d$ to $\pi$.}
 	\begin{equation}
@@
 	This procedure has the disadvantage that the weights variance tends to increase, leading to weight degeneracy.
-AIS-SMC includes a resampling procedure, thus focussing computational effort on high-probability regions.
+AIS-SMC includes a resampling procedure, that focusses computational effort on high-probability regions.
 This combination of importance sampling, mutation and resampling maintains diversity among the particles and prevents premature convergence to suboptimal models.
@@
 	Let us now explain in more detail the procedure, based on ref.~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo}. 
-	The goal is to obtain particles sampled from a probability distribution $d(z)$, where $z$ runs over a space of polynomials, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
+	The goal is to obtain particles sampled from a probability distribution $d(z)$, where $z$ runs over a space of polynomials \ce{Here we should say what this space is, and stress that this space is finite dimensional.}, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
 We reconstruct this density function $d$ by series of density functions $\pi_n(z)$, $n\in\llbracket0,n_{\rm epochs}\rrbracket$, such that $\pi_n\to d$ as $n\to n_{\rm epochs}$.
@@
 	where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_0 < \beta_1 <\dots< \beta_{n_{\rm epochs}}$.
-The importance given to each polynomial $z$ is thus updated at each steps, with polynomials $z$ with high loss being disfavoured.
+The importance given to each polynomial $z$ is thus updated at each step, with polynomials $z$ with high loss being disfavoured.
 This update is controlled by the inverse temperature constants, enabling deeper exploration during the early stages and protecting the procedure from being trapped in local minima.
-The loss function is chosen to be minimal on annihilating polynomials, its design will be discussed at the end of the section.
+The loss function is chosen to be minimal on annihilating polynomials and its design will be discussed at the end of the section.
 We choose the prior distribution $d_{0}$ to be flat on the space of polynomials, giving equal importance to all of them, which makes easy the initial sampling of the weighted particles $\big\{z^{(k)}_{0},w^{(k)}_{0} = 1/n_{\rm particles}\big\}$.
-
-	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}^{(k)}\big) = \tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big)/\tilde{Z}_{n}$, with $z_{0:n}^{(k)} = \big(z_{0}^{(k)},\ldots,z_{n}^{(k)}\big)$, that describes the global trajectory of the particles until step~$n$.
-$\tilde{\gamma}_{n}$ is defined thanks to a backward propagation kernel $K\big(z^{(k)}_{i-1}\vert z^{(k)}_{i}\big)$:
-	\begin{equation}
-		\tilde{\gamma}_{n}\big(z_{0:n}^{(k)}\big) = \gamma_{n}\big(z_{n}^{(k)}\big)\,\prod_{i=1}^{n} K\big(z^{(k)}_{i-1}\vert z^{(k)}_{i}\big).
+\ce{Change sentence.}
+
+	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}\big) = \tilde{\gamma}_{n}\big(z_{0:n}\big)/\tilde{Z}_{n}$, with $z_{0:n} = \big(z_{0},\ldots,z_{n}\big)$, that describes the global trajectory of the particles until step~$n$.
+$\tilde{\gamma}_{n}$ is defined thanks to a backward propagation kernel $K\big(z_{i-1}\vert z_{i}\big)$:\footnote{Note that $\pi_{n}$ is a function on the cartesian product blabla.} \ce{Footnote.}
+	\begin{equation}
+		\tilde{\gamma}_{n}\big(z_{0:n}\big) = \gamma_{n}\big(z_{n}\big)\,\prod_{i=1}^{n} K\big(z_{i-1}\vert z_{i}\big).
 	\end{equation}
@@
 
-	At the beginning of epoch $n\geq1$, $\tilde{\pi}_{n-1}$ is approximated \textit{via} Importance Sampling from an importance distribution $\eta_{n-1}$, \textit{i.e.} from a set of particles and weights $\big\{z_{n-1}^{(k)},\ w_{n-1}^{(k)}\big\}$ using eq.~\eqref{eq:pifromweights}, with $\big\{z_{n-1}^{(k)}\big\}$ drawn from $\eta_{n-1}$ and $w_{n-1}^{(k)} = \tilde{\gamma}_{n-1}\big(z_{0:n-1}^{(k)}\big)/\eta_{n-1}\big(z_{0:n-1}^{(k)}\big)$.\footnote{We define $\eta_{0} = \pi_{0} = \tilde{\pi}_{0} = d_{0}$.} The importance density $\eta_{n-1}$ get mutated using a forward propagation Markov kernel $q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)$, defining the probability to get $z^{(k)}_{n}$ when the current state is $z^{(k)}_{n-1}$:
-	\begin{equation}
-		\eta_{n}\big(z_{0:n}^{(k)}\big) = \eta_{n-1}\big(z_{0:n-1}^{(k)}\big)\,q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big).
+	At the beginning of epoch $n\geq1$, $\tilde{\pi}_{n-1}$ is approximated \textit{via} Importance Sampling from an importance distribution $\eta_{n-1}$, \textit{i.e.} from a set of particles and weights $\big\{z_{n-1}^{(k)},\ w_{n-1}^{(k)}\big\}$ using eq.~\eqref{eq:pifromweights}, with $\big\{z_{n-1}^{(k)}\big\}$ drawn from $\eta_{n-1}$ and $w_{n-1}^{(k)} = \tilde{\gamma}_{n-1}\big(z_{0:n-1}^{(k)}\big)/\eta_{n-1}\big(z_{0:n-1}^{(k)}\big)$.\footnote{We define $\eta_{0} = \pi_{0} = \tilde{\pi}_{0} = d_{0}$.} \ce{Footnote.} The importance density $\eta_{n-1}$ gets mutated using a forward propagation Markov kernel $q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)$, defining the probability to get $z^{(k)}_{n}$ when the current state is $z^{(k)}_{n-1}$:
+	\begin{equation}
+		\eta_{n}\big(z_{0:n}\big) = \eta_{n-1}\big(z_{0:n-1}\big)\,q\big(z_{n}\vert z_{n-1}\big).
 	\end{equation}
@@
 	\end{equation}
-	\gl{link to notations in section 3}
 	The convenience of these parameters was determined empirically --a systematic analysis of its optimization is left for future work.
@@
 
-The marriage of machine learning techniques with traditional supergravity analysis represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
-As computational power increases and algorithms improve, we envision this methodology becoming a standard tool for exploring the intricate relationships between geometry, symmetry, and dynamics in supergravity theories.
-\ce{Not sure if I agree with the last sentence.
-Maybe we could weaken the statement a bit?}
+The marriage of machine learning techniques with the study of geometry, symmetry, and dynamics in supergravity theories represents a step toward more systematic approaches to understanding the rich geometric structures underlying these theories.
+As computational power increases and algorithms improve, this marriage might become an important player for exploring the landscape of supergravity theories.
+\ce{Bastien: change here.}
 
@@
 for ...}, and to Nelly Pustelnik, Jason Reneuve and Henning Samtleben for inspiring discussions.
-\ce{Funding Bastien?} \ce{Others?}
+\ce{Funding Bastien?} \ce{Others?} \ce{Mitchell foundations and Cook branch.}
 

### 2025-10-03 Draft_MLFlatDirections.tex
Updates of the ref in intro, some paragraphs in sec 3, placement of the figures.

@@
 	Our approach combines numerical exploration and symbolic inference.
-For the latter, we develop a symbolic regression algorithm based on Annealed Importance Sampling combined with Sequential Monte Carlo, well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
+For the latter, we develop a symbolic regression algorithm based on Annealed Sequential Monte Carlo samples, a combination of Annealed Importance Sampling and Sequential Monte Carlo samplers, well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
 	The algorithm reconstructs a set of polynomial relations that provides an explicit analytic parametrization of a new family of solutions. 
@@
 These deformations are parametrised by exactly marginal operators, or in other words, operators that preserve the conformal symmetry, \textit{i.e.} whose $\beta$ functions exactly vanish.
-\ce{Bastien: changed here.}
 
@@
 However, this method is slow, usually limited to low-dimensional spaces, and, by construction, can only fit one expression at a time.
-Alternatively, we develop here a symbolic regression algorithm based on Annealing Importance Sampling (AIS) \cite{neal1998annealedimportancesampling}, since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces
+Alternatively, we develop here a symbolic regression algorithm based on Annealed Sequential Monte Carlo sampler~\cite{zimmermann2021nested,syed2024optimisedannealedsequentialmonte} (combining the Annealed Importance Sampling~\cite{neal1998annealedimportancesampling} approach with a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential}), since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces.
 
@@
 Combined with numerical analyses, including a local principal component analysis, we can identify the existence of a three-dimensional continuous family.
-We then use an AIS technique combined with a sequential Monte Carlo approach~(SMC)~\cite{del2006sequential} in order to do symbolic regression.
+We then use an ASMC technique in order to do symbolic regression.
 As we will indeed demonstrate in the paper, there exist polynomial constraints on the 5 parameters, viewed as embedding coordinates, that project them onto the 3 dimensional manifolds.
@@
 In sec.~\ref{sec:sugra}, we establish the supergravity setup, presenting the scalar potential in its full complexity and motivating the restriction to five fields.
-Sec.~\ref{Sec:AIS-SMC} details our annealed importance sampling approach to symbolic regression.
+Sec.~\ref{Sec:AIS-SMC} details our Annealed Sequential Monte Carlo sampler approach to symbolic regression.
 Our main results, both numerical an analytical, are presented in sec.~\ref{sec:results}, and sec.~\ref{sec:sugrasol} gives some details on the new supergravity solutions discovered by the numerical analysis.
@@
 	Markov Chain Monte Carlo (MCMC) techniques such as Metropolis-Hastings or Gibbs sampling, while widely used, can struggle with poor mixing and often get trapped in local optima, especially in high-dimensional or multimodal spaces.
-\ce{Try to find a ref.}
-
-	To address these challenges, we formulate the search for annihilating polynomials as a determination of a probability density on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimise the error \ce{Bastien: changed here.}
+
+	To address these challenges, we formulate the search for annihilating polynomials as a determination of a probability density on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimise the error
 	\begin{equation}
@@
 Such a probability density is \textit{a priori} hard to find, but can be approximated using algorithms based on Sequential Important Sampling~\cite{Doucet2001,Liu2004} such as Sequential Monte Carlo samplers~\cite{del2006sequential}.
-They are inspired from Important Sampling (IS)~\cite{osti_4441935,RobertCasella2004}, a method to parametrise expectation values with respect to a target distribution $d$, that can be evaluated pointwise, but from which one does not know how to draw samples.
-IS uses another, usually simpler, distribution $\pi$ (called importance distribution) that one knows how to draw from.
-It is based on the observation that the expectation value \ce{Change $\pi$ to $\eta$, $d$ to $\pi$.}
-	\begin{equation}
-		\mathbb{E}_{d}[f] = \int f(z)d(z)\ \d z
-	\end{equation}
-	for some function $f$ with respect to $d$ can be computed from the expectation $\mathbb{E}_{\pi}[w f]$, now computed with respect to the distribution $\pi$, with unnormalised weights $w = d/\pi$.
-Therefore, one can estimate $\mathbb{E}_{d}[f]$ from a Monte Carlo method: we draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\pi$ and use the weighted average
-	\begin{equation}
-		\mathbb{E}_{d}[f] \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w\big(z^{(k)}\big)\,f\big(z^{(k)}\big)/\displaystyle \sum_{i=1}^{n_{\rm particles}} w\big(z^{(k)}\big).
-	\end{equation}
-	Stated differently, the target distribution $d$ can be approximated from a weighted collection of particles $\{z^{(k)},w^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ drawn from the importance distribution $\pi$ :
-	\begin{equation}
-		d(z) \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}\,\delta\big(z-z^{(k)}\big)/\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)},
+They are inspired from Important Sampling (IS)~\cite{osti_4441935,RobertCasella2004}, a method to parametrise expectation values with respect to a target distribution $\pi$, that can be evaluated pointwise, but from which one does not know how to draw samples.
+IS uses another, typically simpler, distribution $\eta$ (called importance distribution) that one knows how to draw from.
+It is based on the observation that the expectation value
+	\begin{equation}
+		\mathbb{E}_{\pi}[f] = \int f(z)\pi(z)\ \d z
+	\end{equation}
+	for some function $f$ with respect to $\pi$ can be computed from the expectation $\mathbb{E}_{\eta}[w f]$, now computed with respect to the distribution $\eta$, with unnormalised weights $w = \pi/\eta$.
+Therefore, one can estimate $\mathbb{E}_{\pi}[f]$ from a Monte Carlo method: we draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\eta$ and use the weighted average
+	\begin{equation}
+		\mathbb{E}_{\pi}[f] \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w\big(z^{(k)}\big)\,f\big(z^{(k)}\big)\Bigg/\displaystyle \sum_{i=1}^{n_{\rm particles}} w\big(z^{(k)}\big).
+	\end{equation}
+	Stated differently, the target distribution $\pi$ can be approximated from a weighted collection of particles $\{z^{(k)},w^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ drawn from the importance distribution $\eta$ :
+	\begin{equation}
+		\pi(z) \simeq \displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)}\,\delta\big(z-z^{(k)}\big)\Bigg/\displaystyle \sum_{k=1}^{n_{\rm particles}} w^{(k)},
 	\end{equation}
 	where $w^{(k)} = w\big(z^{(k)}\big)$.
-The sample admits $d$ as marginal distribution asymptotically when $n_{\rm particles}\rightarrow+\infty$.
-The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the distribution $\pi$, that needs to be close enough to $d$.
-
-	However, providing a good importance distribution $\pi$ remains a hard problem.
-In order to fix this point, we employ a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo} enhanced by Annealed Importance Sampling (AIS)~\cite{neal1998annealedimportancesampling}.
+The sample admits $\pi$ as marginal distribution asymptotically when $n_{\rm particles}\rightarrow+\infty$.
+The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the importance distribution $\eta$, that needs to be close enough to $\pi$.
+
+	However, providing a good importance distribution $\eta$ remains a hard problem.
+In order to fix this point, we employ an Annealed Sequential Monte Carlo sampler (ASMC)~\cite{zimmermann2021nested,syed2024optimisedannealedsequentialmonte}, \textit{i.e.} a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo} enhanced by Annealed Importance Sampling (AIS)~\cite{neal1998annealedimportancesampling}.
 SMC aims at estimating $\pi$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $\pi_{0}$ (chosen to be easy to sample from) to the complex distribution $\pi$.
@@
 	with  $\displaystyle \tilde{w}^{(k)}_n  = w^{(k)}_n/\sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}$ the normalised weights.
-The particles are incrementally deformed and reweighed using a Markov kernel to gradually sample the target distribution $d$.
+The particles are incrementally deformed and reweighed using a Markov kernel to gradually sample the target distribution $\pi$.
 This process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
@@
 We gradually mutate them with an annealing procedure to get a set of $\{z_n^{(k)},w_n^{(k)}\}$, which are used to parametrise $\pi_n$.
-As $n$ increases, the procedure converges such that the particles sample the distribution $\pi$, which itself is used to parametrise the target distribution $d$.
+As $n$ increases, the procedure converges such that the particles sample the target distribution $\pi$.
 
 	This procedure has the disadvantage that the weights variance tends to increase, leading to weight degeneracy.
-AIS-SMC includes a resampling procedure, that focusses computational effort on high-probability regions.
+ASMC includes a resampling procedure, that focusses computational effort on high-probability regions.
 This combination of importance sampling, mutation and resampling maintains diversity among the particles and prevents premature convergence to suboptimal models.
-These features make AIS-SMC particularly well-suited for symbolic regression tasks, where the search space is not only high-dimensional but also structured and discontinuous.
+These features make ASMC particularly well-suited for symbolic regression tasks, where the search space is not only high-dimensional but also structured and discontinuous.
 
 	\subsection{Detailed procedure}	\label{sec:detailedAISSMC}
-	Let us now explain in more detail the procedure, based on ref.~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo}. 
-	The goal is to obtain particles sampled from a probability distribution $d(z)$, where $z$ runs over a space of polynomials \ce{Here we should say what this space is, and stress that this space is finite dimensional.}, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
-We reconstruct this density function $d$ by series of density functions $\pi_n(z)$, $n\in\llbracket0,n_{\rm epochs}\rrbracket$, such that $\pi_n\to d$ as $n\to n_{\rm epochs}$.
+	Let us now explain in more detail the procedure, based on ref.~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo,Dai03072022}. 
+	The goal is to obtain particles sampled from a probability distribution $\pi(z)$, where $z$ runs over a space of polynomials $E$, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
+We restrict ourselves to polynomials of maximum degree ${\rm max}_{\rm degree}$.
+Given the number of variables $n_{\rm var}$, this fixes the number of different possible monomials to $\binom{{\rm max}_{\rm degree}+n_{\rm var}}{{\rm max}_{\rm degree}}$.
+We further restrict $E$ to include only polynomials with a maximum number of ${\rm max}_{\rm mon}$ monomials.
+The space $E$ is then finite dimensional.
+
+	We reconstruct the density function $\pi$ by series of density functions $\pi_n(z)$, $n\in\llbracket0,n_{\rm epochs}\rrbracket$, such that $\pi_n\to \pi$ as $n\to n_{\rm epochs}$.
 On every annealing step, $\pi_n$ is defined in terms of an unnormalised density $\gamma_n$ and a normalisation constant as $\pi_n(z) = \gamma_n(z)/Z_n$.
-The unnormalised density at level $n$ is given in terms of a prior distribution $d_0(z)$ over the space of polynomials and a loss function $L(z)$, as
+The unnormalised density at level $n$ is given in terms of a prior distribution $\pi_0(z)$ over the space $E$ of polynomials and a loss function $L(z)$, as
 		\begin{equation}\label{eq:gamman}
-			\gamma_n(z) = d_0(z) \: \exp \Big( -\beta_n L(z)\Big),
-		\end{equation}
-	where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_0 < \beta_1 <\dots< \beta_{n_{\rm epochs}}$.
+			\gamma_n(z) = \pi_0(z) \: \exp \Big( -\beta_n L(z)\Big),
+		\end{equation}
+	where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_0 = 0 < \beta_1 <\dots< \beta_{n_{\rm epochs}}$.
 The importance given to each polynomial $z$ is thus updated at each step, with polynomials $z$ with high loss being disfavoured.
@@
 The loss function is chosen to be minimal on annihilating polynomials and its design will be discussed at the end of the section.
-We choose the prior distribution $d_{0}$ to be flat on the space of polynomials, giving equal importance to all of them, which makes easy the initial sampling of the weighted particles $\big\{z^{(k)}_{0},w^{(k)}_{0} = 1/n_{\rm particles}\big\}$.
-\ce{Change sentence.}
-
-	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}\big) = \tilde{\gamma}_{n}\big(z_{0:n}\big)/\tilde{Z}_{n}$, with $z_{0:n} = \big(z_{0},\ldots,z_{n}\big)$, that describes the global trajectory of the particles until step~$n$.
-$\tilde{\gamma}_{n}$ is defined thanks to a backward propagation kernel $K\big(z_{i-1}\vert z_{i}\big)$:\footnote{Note that $\pi_{n}$ is a function on the cartesian product blabla.} \ce{Footnote.}
+We choose the prior distribution $\pi_{0}$ to be flat on the space of polynomials $E$, giving equal importance to all of them, which makes easy the initial sampling of the weighted particles $\big\{z^{(k)}_{0},w^{(k)}_{0} = 1/n_{\rm particles}\big\}$.\footnote{Note that with this choice there is a higher probability to draw polynomials with multiple monomials.} The random draw is done on the monomials of each polynomials, and the coefficients are chosen randomly in the range $[-2,2]$.
+
+	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}\big) = \tilde{\gamma}_{n}\big(z_{0:n}\big)/\tilde{Z}_{n}$ defined on $E^{n+1}$, with $z_{0:n} = \big(z_{0},\ldots,z_{n}\big)$, that describes the global trajectory of the particles until step $n$.
+$\tilde{\gamma}_{n}$ is defined thanks to a backward propagation kernel $K\big(z_{i-1}\vert z_{i}\big)$:
 	\begin{equation}
@@
 	This way, the distribution $\tilde{\pi}_{n}$ describes $\pi_{n}$ as well as the path that followed the particles from epochs $0$ to $n$.
+$\tilde{\pi}_{n}$ evaluates not only the probability that the particle is in a given state $z_{n}$, but also the probability that the particle has followed the path from $z_{0}$ to $z_{n}$.
 This allows for more accuracy, correcting potential bias introduced by the mutations, and results in a setup that is more tunable.
 
-	At the beginning of epoch $n\geq1$, $\tilde{\pi}_{n-1}$ is approximated \textit{via} Importance Sampling from an importance distribution $\eta_{n-1}$, \textit{i.e.} from a set of particles and weights $\big\{z_{n-1}^{(k)},\ w_{n-1}^{(k)}\big\}$ using eq.~\eqref{eq:pifromweights}, with $\big\{z_{n-1}^{(k)}\big\}$ drawn from $\eta_{n-1}$ and $w_{n-1}^{(k)} = \tilde{\gamma}_{n-1}\big(z_{0:n-1}^{(k)}\big)/\eta_{n-1}\big(z_{0:n-1}^{(k)}\big)$.\footnote{We define $\eta_{0} = \pi_{0} = \tilde{\pi}_{0} = d_{0}$.} \ce{Footnote.} The importance density $\eta_{n-1}$ gets mutated using a forward propagation Markov kernel $q\big(z^{(k)}_{n}\vert z^{(k)}_{n-1}\big)$, defining the probability to get $z^{(k)}_{n}$ when the current state is $z^{(k)}_{n-1}$:
+	At the beginning of epoch $n\geq1$, $\tilde{\pi}_{n-1}$ is approximated \textit{via} Importance Sampling from an importance distribution $\eta_{n-1}$, \textit{i.e.} from a set of particles and weights $\big\{z_{n-1}^{(k)},\ w_{n-1}^{(k)}\big\}$ using eq.~\eqref{eq:pifromweights}, with $\big\{z_{n-1}^{(k)}\big\}$ drawn from $\eta_{n-1}$ and $w_{n-1}^{(k)} = \tilde{\gamma}_{n-1}\big(z_{0:n-1}^{(k)}\big)/\eta_{n-1}\big(z_{0:n-1}^{(k)}\big)$.\footnote{We define $\eta_{0} = \pi_{0} = \tilde{\pi}_{0}$.} The importance density $\eta_{n-1}$ gets mutated using a forward propagation Markov kernel $q\big(z_{n}\vert z_{n-1}\big)$, defining the probability to get $z_{n}$ when the current state is $z_{n-1}$:
 	\begin{equation}
@@
 In such cases $q(z_n^k \mid z_{n-1}^k) \ne q(z_{n-1}^k \mid z_n^k)$ and particular care must be taken in the computation of the backward propagation kernel.
-	A common choice of backward kernel in such context is the reversed forward kernel $K\big(z^{(k)}_{n-1}\vert z^{(k)}_{n}\big) = q\big(z^{(k)}_{n-1}\vert z^{(k)}_{n}\big)$.
+	A common choice of backward kernel in such context is the reversed forward kernel $K\big(z_{n-1}\vert z_{n}\big) = q\big(z_{n-1}\vert z_{n}\big)$.
 	After performing these updates, the change is accepted based on the temperature-dependent rate
@@
 
-	A flow chart of the full AIS-SMC procedure is given in fig.~\ref{ASMCflowchart}.
+	To sum up, the algorithm starts initially with $n_{\rm particles}$ particles $\big\{z^{(k)}_{0}\big\}$ sampled from the prior distribution $\eta_{0}=\pi_{0}$, with equal weights $\big\{w^{(k)}_{0} = 1/n_{\rm particles}\big\}$.
+At each epoch $n\geq1$, the intermediate target distribution $\tilde{\pi}_{n}$ is estimated from the sample of weighted particles $\big\{z^{(k)}_{n}, w^{(k)}_{n}\big\}$, obtained from propagation using MCMC moves, reweighing~\eqref{eq:weightsupdate} and, if needed, resampling.
+At the final epoch $n_{\rm epochs}$, the particles $\big\{z^{(k)}_{n_{\rm epochs}}, w^{(k)}_{n_{\rm epochs}}\big\}$ approximate a sampling of the target distribution $\pi$.
+A flow chart of the full ASMC procedure is given in fig.~\ref{ASMCflowchart}.
 Note that in practice the reweighing and resampling of particles $z_{n-1}^{(k)}$ are done at the beginning of the epoch $n$.
@@
 	\begin{equation} \label{eq:lossreg}
-		L(z) = \sum_{i=1}^{n_{\rm points}} z(x^{(i)})^2 + \frac{\lambda}{\sum_m |c_m|}\,.
+		L(z) = \sum_{i=1}^{n_{\rm points}} z(x^{(i)})^2 + \frac{\lambda}{\displaystyle \sum_m |c_m|}\,.
 	\end{equation}
@@
 	\paragraph{}
-	Once the Annealing loop is over, we end up with a total of $n_{\rm particles}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
+	Once the ASMC loop is over, we end up with a total of $n_{\rm particles}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
 To deal with it, for each polynomial we run a fine tuning loop as described in sec.~\ref{sec:1runanalysis}.
@@
 
-	\begin{figure}
+	\begin{figure}[!b]
 		\centering
@@
 
-	\subsection{AIS-SMC algorithm and results}  \label{sec:AIS-SMC_application}
+	\subsection{ASMC algorithm and results}  \label{sec:AIS-SMC_application}
 	From the preceding analysis, we conclude that the gradient descent procedure has produced a sampling of a single, connected, three-dimensional manifold.
@@
 We now proceed to present the symbolic regression problem, utilizing the points obtained through gradient descent as our training dataset.
-In the following section, we detail the implementation of the AIS-SMC framework previously outlined in sec.~\ref{Sec:AIS-SMC}.
+In the following section, we detail the implementation of the ASMC framework previously outlined in sec.~\ref{Sec:AIS-SMC}.
 
@@
 
-	We initialized the algorithm with\footnote{$n_{\rm points}$ is the number of points used in the gradient descent, see sec.~\ref{sec:graddes} ; $n_{\rm epochs}$, $n_{\rm particles}$, $\beta_{0}$, $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$ are, respectively, the number of steps, the number of particles, the initial inverse temperature and the probabilities of each MCMC moves used in the AIS-SMC procedure, see sec.~\ref{sec:detailedAISSMC} ; $\lambda$ is the regularisation parameter used in the loss function, see eq.~\eqref{eq:lossreg} ; $\sigma$ is the parameter defining the Gaussian noise for the coefficient perturbation move of the AIS-SMC procedure, see eq.~\eqref{eq:coeffperturb}.}
+	We initialized the algorithm with\footnote{$n_{\rm points}$ is the number of points used in the gradient descent, see sec.~\ref{sec:graddes} ; $n_{\rm epochs}$, $n_{\rm particles}$, $\beta_{0}$, $p_{\rm shift}$, $p_{\rm multiply}$, and $p_{\rm divide}$ are, respectively, the number of steps, the number of particles, the initial inverse temperature and the probabilities of each MCMC moves used in the ASMC procedure, see sec.~\ref{sec:detailedAISSMC} ; $\lambda$ is the regularisation parameter used in the loss function, see eq.~\eqref{eq:lossreg} ; $\sigma$ is the parameter defining the Gaussian noise for the coefficient perturbation move of the ASMC procedure, see eq.~\eqref{eq:coeffperturb}.}
 	\begin{equation}	\label{eq:sample10000adaptativetemp}
@@
 For the representation of polynomials, we adopt a vectorial approach: each polynomial is represented as an array of its coefficients $\{c_m\}$, where $m \in \{1,\dots,n_{\text{mon}}\}$ and $n_{\text{mon}}$ denotes the number of available monomials, determined by the chosen maximum degree \texttt{max\_degree} and the number of variables.
-We also impose a constraint on the maximum number of terms within a single polynomial \texttt{max\_num\_monomials} to promote sparsity.
-\footnote{An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.} For our simulations, we chose:
+We also impose a constraint on the maximum number of terms within a single polynomial \texttt{max\_num\_monomials} to promote sparsity.\footnote{An alternative approach would be to encourage sparsity through the prior distribution or within the loss function formulation.} For our simulations, we chose:
 	\begin{equation} \label{eq:parampol}
@@
 	\subsubsection{Statistics}
+
+	\begin{table}[b!]
+		\centering
+		\renewcommand{\arraystretch}{1.3}
+		\begin{tabular}{c|ccccccccc}
+			& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$  & $p_{8}$&  $\varnothing$  \\\hline\hline
+			Frequency & 92.6\% & 75.0\% & 51.9\% & 1.7\% & 0.2\% & 0.7\% & 0.7\% & 0.3\% & 0.1\% \\
+			Maximum \# of representatives & 1000 & 1000 & 991 & 869 & 879 & 710 & 207 & 18 & --
+		\end{tabular}
+		\caption{Statistics of the ability of the ASMC algorithm to produce the polynomials~\eqref{eq:pols} on 1000 runs with parameters~\eqref{eq:sample10000adaptativetemp} and~\eqref{eq:parampol}.
+The frequencies represent the percentage of runs featuring a given polynomial in its outputs, and the maximum number of representatives gives the maximum number of particles representing the polynomial in a given run.
+The column $\varnothing$ counts the runs that failed to produce any annihilator polynomial.}
+		\label{table:results}
+	\end{table}
+
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
@@
 
-	\begin{table}
-		\centering
-		\renewcommand{\arraystretch}{1.3}
-		\begin{tabular}{c|ccccccccc}
-			& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$  & $p_{8}$&  $\varnothing$  \\\hline\hline
-			Frequency & 92.6\% & 75.0\% & 51.9\% & 1.7\% & 0.2\% & 0.7\% & 0.7\% & 0.3\% & 0.1\% \\
-			Maximum \# of representatives & 1000 & 1000 & 991 & 869 & 879 & 710 & 207 & 18 & --
-		\end{tabular}
-		\caption{Statistics of the ability of the ASMC algorithm to produce the polynomials~\eqref{eq:pols} on 1000 runs with parameters~\eqref{eq:sample10000adaptativetemp} and~\eqref{eq:parampol}.
-The frequencies represent the percentage of runs featuring a given polynomial in its outputs, and the maximum number of representatives gives the maximum number of particles representing the polynomial in a given run.
-The column $\varnothing$ counts the runs that failed to produce any annihilator polynomial.}
-		\label{table:results}
-	\end{table}
-
-	\begin{figure}[b!]
+	\begin{figure}
 		\centering
@@
 
-	We have tracked the appearance of the polynomials~\eqref{eq:pols} during each of the 1000 runs.
-To do so, we have counted at each epoch the number of particles including the same monomials as the annihilator polynomials.\footnote{Thus, a particle featuring the same monomials as one of the polynomials~\eqref{eq:pols} will be counted, even if the coefficients do not match, and if there are additional monomials.} The total number of particles reproducing at least one of the annihilator polynomials listed in eq.~\eqref{eq:pols} is plotted in fig.~\ref{fig:count_pol_all_beta}, together with the evolution of the inverse temperature $\beta$, both averaged on the 1000 runs.
-The proportion of annihilator polynomials among the particles start to be significant after approximately 700 epochs.
-It then increases quickly and, towards the end of each run, an average of $88\%$ of the particles do reproduce one of the annihilator polynomials, with a standard deviation of $20\%$.
-The evolution of this proportion is explained by the structure of the method: the code favours the particles with highest weights, and thus those that cause a significant improvement to the loss function, at each resampling.
-Once an annihilator polynomials is reached, it colonises larger and larger proportions of the particles at each resampling.
-
-	The evolution of the inverse temperature is dictated by eq.~\eqref{eq:eqadaptivetemperatureschedule}.
-Note that $\beta$ is equal to $0.02$ on average at the end of the runs.
-The temperature is thus still quite high, which favours diversity.
-This is a key ingredient to get more than one candidate polynomials per run.
-The end value of $\beta$ is intimately linked to the choice of target adaptative temperature ratio in eq.~\eqref{eq:eqadaptivetemperatureschedule}: the lower this acceptance ratio, the higher the inverse temperature $\beta$.
-On the one hand, if the ratio is too low, very few particles get mutated and it is difficult to explore the space of polynomials and to have diverse outputs.
-On the other hand, if the ratio is too high, there are too many mutations: the output features a large number of polynomials, but lots of them do not converge to an annihilator polynomials because the algorithm is not selective enough.
-It is a matter of balance between exploration and exploitation.
-
-	\begin{figure}
+	\begin{figure}[b!]
 		\centering
@@
 
+	We have tracked the appearance of the polynomials~\eqref{eq:pols} during each of the 1000 runs.
+To do so, we have counted at each epoch the number of particles including the same monomials as the annihilator polynomials.\footnote{Thus, a particle featuring the same monomials as one of the polynomials~\eqref{eq:pols} will be counted, even if the coefficients do not match, and if there are additional monomials.} The total number of particles reproducing at least one of the annihilator polynomials listed in eq.~\eqref{eq:pols} is plotted in fig.~\ref{fig:count_pol_all_beta}, together with the evolution of the inverse temperature $\beta$, both averaged on the 1000 runs.
+The proportion of annihilator polynomials among the particles start to be significant after approximately 700 epochs.
+It then increases quickly and, towards the end of each run, an average of $88\%$ of the particles do reproduce one of the annihilator polynomials, with a standard deviation of $20\%$.
+The evolution of this proportion is explained by the structure of the method: the code favours the particles with highest weights, and thus those that cause a significant improvement to the loss function, at each resampling.
+Once an annihilator polynomials is reached, it colonises larger and larger proportions of the particles at each resampling.
+
+	The evolution of the inverse temperature is dictated by eq.~\eqref{eq:eqadaptivetemperatureschedule}.
+Note that $\beta$ is equal to $0.02$ on average at the end of the runs.
+The temperature is thus still quite high, which favours diversity.
+This is a key ingredient to get more than one candidate polynomials per run.
+The end value of $\beta$ is intimately linked to the choice of target adaptative temperature ratio in eq.~\eqref{eq:eqadaptivetemperatureschedule}: the lower this acceptance ratio, the higher the inverse temperature $\beta$.
+On the one hand, if the ratio is too low, very few particles get mutated and it is difficult to explore the space of polynomials and to have diverse outputs.
+On the other hand, if the ratio is too high, there are too many mutations: the output features a large number of polynomials, but lots of them do not converge to an annihilator polynomials because the algorithm is not selective enough.
+It is a matter of balance between exploration and exploitation.
+
 	The dynamics of appearance of each annihilator polynomial is plotted in fig.~\ref{fig:count_pol_indiv}, averaged on the 1000 runs.
@@
 
+	\begin{figure}[b!]
+		\centering
+		\includegraphics[scale=0.75]{Figures/Loss_all_ASMC_1000runs_13.pdf}
+		\caption{Evolution of the lowest loss during each of the 1000 runs (in blue) and their average (in yellow).
+The losses are computed with the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}.}
+		\label{fig:lossallASMC}
+	\end{figure}
+
 	The best loss for each of the 1000 runs is shown in fig.~\ref{fig:lossallASMC} in blue, together with their mean value in yellow, with a logarithmic $y$-axis.
@@
 Although the loss is high, 1000 epochs are sufficient to select candidate annihilator polynomials thanks to the exploitation phase performed on the best particles, as illustrated in sec.~\ref{sec:AIS-SMC_application}.
-
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.75]{Figures/Loss_all_ASMC_1000runs_13.pdf}
-		\caption{Evolution of the lowest loss during each of the 1000 runs (in blue) and their average (in yellow).
-The losses are computed with the regularisation factor $\lambda$, see eq.~\eqref{eq:lossreg}.}
-		\label{fig:lossallASMC}
-	\end{figure}
 
@@
 The gradient descent procedure successfully samples the flat directions manifold, while local PCA analysis reveals its intrinsic dimensionality.
-Most notably, our annealed importance sampling approach to symbolic regression automatically and quickly discovers polynomial constraints characterising the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
+Most notably, our Annealed Sequential Monte Carlo sampler approach to symbolic regression automatically and quickly discovers polynomial constraints characterising the manifold, bypassing the computational complexity that renders direct symbolic manipulation intractable.
 The algorithm uncovered eight distinct polynomial relations with varying frequencies, suggesting a hierarchical structure in constraint discovery.
@@
 As computational power increases and algorithms improve, this marriage might become an important player for exploring the landscape of supergravity theories.
-\ce{Bastien: change here.}
 
@@
 We would like to thank Magdalena Larfors, whose talk on Machine Learning at the kick-off meeting of the COST action ``Fundamental challenges in theoretical physics'' in Padova in May 2024 triggered this project.
-We are thankful to \ce{Jan?
-for ...}, and to Nelly Pustelnik, Jason Reneuve and Henning Samtleben for inspiring discussions.
-\ce{Funding Bastien?} \ce{Others?} \ce{Mitchell foundations and Cook branch.}
+We are thankful to Nelly Pustelnik, Jason Reneuve, Henning Samtleben and Jan-Willem van de Meent for inspiring discussions.
+We thank especially Jan-Willem van de Meent for guiding us to the relevant numerical methods.
+\ce{Funding Bastien?} \ce{Gabriel: Mitchell foundations and Cook branch.}
 

### 2025-10-21 Draft_MLFlatDirections.tex
Small updates in the text, tildas in the figures.

@@
 
-{\Large Machine Learning the Conformal Manifold of Holographic CFT2’s}
+{\Large Machine Learning the Conformal Manifold of Holographic CFT$_{2}$’s}
 
@@
 \begin{abstract}
-	We investigate the structure of conformal manifolds around AdS$_3 \times S^3$ which lift from continuous flat directions in the scalar potential of gauged supergravity resulting from six-dimensional $\mathcal{N}=(1,1)$.
+	We investigate the structure of conformal manifolds around AdS$_3 \times S^3$ which lift from continuous flat directions in the scalar potential of gauged supergravity resulting from six-dimensional $\mathcal{N}=(1,1)$ supergravity.
 	Our approach combines numerical exploration and symbolic inference.
-For the latter, we develop a symbolic regression algorithm based on Annealed Sequential Monte Carlo samples, a combination of Annealed Importance Sampling and Sequential Monte Carlo samplers, well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
+For the latter, we develop a symbolic regression algorithm based on Annealed Sequential Monte Carlo samplers, a combination of Annealed Importance Sampling and Sequential Monte Carlo samplers, well-suited to uncovering polynomial constraints in high-dimensional parameter spaces.
 	The algorithm reconstructs a set of polynomial relations that provides an explicit analytic parametrization of a new family of solutions. 
@@
 More broadly, there has been increasing interest in applying machine learning and numerical techniques across various domains of high-energy physics.
-This includes, for instance, the characterisation of Calabi–Yau metrics and hypersurfaces \cite{Ashmore:2019wzb,Berman:2021mcw,Larfors:2022nep,Berglund:2022gvm,Jejjala:2020wcc,Douglas:2006rr,Larfors:2021pbb,He:2018jtw}, as well as broader efforts to explore the string theory landscape \cite{He:2017aed,Carifio:2017bov,Ruehle:2017mzq}.
+This includes, for instance, the characterisation of Calabi–Yau metrics and hypersurfaces \cite{Ashmore:2019wzb,Berman:2021mcw,Larfors:2022nep,Berglund:2022gvm,Jejjala:2020wcc,Douglas:2006rr,Larfors:2021pbb,He:2018jtw}, as well as broader efforts to explore the string theory landscape \cite{He:2017aed,Carifio:2017bov,Ruehle:2017mzq,Walden:2025cpf}.
 Additional applications include studies in CFT \cite{Chen:2020dxg}, investigations of the supergravity landscape \cite{Brady:2025zzi,Krishnan:2020sfg}, and explorations of the AdS/CFT correspondence \cite{Hashimoto:2018ftp}.
@@
 However, this method is slow, usually limited to low-dimensional spaces, and, by construction, can only fit one expression at a time.
-Alternatively, we develop here a symbolic regression algorithm based on Annealed Sequential Monte Carlo sampler~\cite{zimmermann2021nested,syed2024optimisedannealedsequentialmonte} (combining the Annealed Importance Sampling~\cite{neal1998annealedimportancesampling} approach with a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential}), since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces.
+Alternatively, we develop here a symbolic regression algorithm based on an Annealed Sequential Monte Carlo sampler (ASMC)~\cite{zimmermann2021nested,syed2024optimisedannealedsequentialmonte} (combining the Annealed Importance Sampling~\cite{neal1998annealedimportancesampling} approach with a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential}), since this approach is much better suited to the study of geometric loci defined by intersecting polynomials in high-dimensional spaces.
 
@@
 %
-through the symmetric matrix $M_{\bK\bL}$.\footnote{In full generality, the coset space of half-maximal supergravity in three dimensions is $\text{SO}(4+p,4+q)/\big(\text{SO}(4+p)\times\text{SO}(4+q)\big)$ for $p$ vectors and $q$ tensors in 6$d$.
+through the symmetric matrix $M_{\bK\bL}$.\footnote{In full generality, the coset space of half-maximal supergravity in three dimensions is $\text{SO}(8,p)/\big(\text{SO}(8)\times\text{SO}(p)\big)$.
 We consider here the case $p=4$ only.} With appropriate gauging (see eq.~\eqref{eq:embedtens}), this $\text{SO}(8,4)$ theory is a consistent truncation of six-dimensional ${\cal N}=(1,1)$ supergravity on $S^{3}$~\cite{Cvetic:2000dm,Deger:2014ofa,Hohm:2017wtr}.
@@
 	\begin{equation}
-		\mathbb{E}_{\pi}[f] = \int f(z)\pi(z)\ \d z
-	\end{equation}
-	for some function $f$ with respect to $\pi$ can be computed from the expectation $\mathbb{E}_{\eta}[w f]$, now computed with respect to the distribution $\eta$, with unnormalised weights $w = \pi/\eta$.
+		\mathbb{E}_{\pi}[f] = \int f(z)\pi(z)\ \d z,
+	\end{equation}
+	for some function $f$ with respect to $\pi$, can be computed from the expectation $\mathbb{E}_{\eta}[w f]$, now computed with respect to the distribution $\eta$, with unnormalised weights $w = \pi/\eta$.
 Therefore, one can estimate $\mathbb{E}_{\pi}[f]$ from a Monte Carlo method: we draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\eta$ and use the weighted average
@@
 			\end{minipage}
-			\caption{Flow chart of the Annealed Importance Sampling - Sequential Monte Carlo algorithm}
+			\caption{Flow chart of the Annealed Sequential Monte Carlo sampler algorithm.}
 			\label{ASMCflowchart}
@@
 	\paragraph{}
-	Once the ASMC loop is over, we end up with a total of $n_{\rm particles}$ particles, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
+	Once the ASMC loop is over, we end up with a total of $n_{\rm particles}$ polynomials, which in principle should be close to annihilate our data, but whose coefficients may need some refinement.
 To deal with it, for each polynomial we run a fine tuning loop as described in sec.~\ref{sec:1runanalysis}.
@@
 	To perform the gradient descent, we initialise randomly and uniformly points within a hypercube of range $[-2,2]$.
-This choice is important to ensure that points are not restricted to the inner range~$[-1,1]$, which will be crucial for the symbolic regression.\footnote{The rationale is that our symbolic regression evaluates the data points $\vec{x}^{(i)}$ using a candidate polynomial function $z$.
+This choice is important to ensure that points are not restricted to the inner range~$[-1,1]$, which will be crucial for the symbolic regression.\footnote{The rationale is that our symbolic regression evaluates the data points $\vec{x}^{(i)}$ using a candidate polynomial function~$z$.
 When all data points lie within the interval $[-1, 1]$, the algorithm tends to favor high-degree polynomials artificially lowering the loss.
@@
 The exponents $(i)$ denote the data points, with $i\in\llbracket1,n_{\rm points}\rrbracket$.
-This way we only keep $(x^{(i)}_1,x^{(i)}_2,x^{(i)}_4,\tilde{x}^{(i)}_8,x^{(i)}_{10})$ alive after we have taken the derivative.
+This way we only keep $\vec{x}^{(i)} = (x^{(i)}_1,x^{(i)}_2,x^{(i)}_4,\tilde{x}^{(i)}_8,x^{(i)}_{10})$ alive after we have taken the derivative.
 As already mentioned above, we use the analytic formula for $\nabla V$, but we could have performed the gradient descent by fully using automatic differentiation.
@@
 It was reinitialised at iterations {250, 500, 750}, with the learning rate $\alpha$ fixed at $10^{-2}$.
-At iteration 1000, the optimizer was reinitialised once more, this time with a reduced learning rate of $10^{-3}$.
+At iteration 1000, the optimizer was reinitialised once more, this time with a reduced learning rate of~$10^{-3}$.
 A final reinitialisation was performed at iteration 1500, setting the learning rate to $10^{-4}$, and the optimization was continued for an additional 500 epochs.
@@
 The distribution of the values of the gradient at each of the data points is plotted in fig.~\ref{fig:log_grad_V}.
-More than $93\%$ of the points converged to values of $\vert\nabla V\vert$ lower than $10^{-4}$, and more than $99\%$ of them exhibited gradient norms smaller than $10^{-3}$, yielding a satisfying sampling of the flat directions.
+More than $93\%$ of the points converged to values of $\vert\nabla V\vert$ lower than $10^{-4}$, and more than $99\%$ of them exhibited gradient norms smaller than~$10^{-3}$, yielding a satisfying sampling of the flat directions.
 As can be observed in fig.~\ref{fig:log_Vp4}, all data points converged to values close to $V(0)=-4$.
@@
 They could be genuine correlations, or may result from larger basins of attraction.
-Thanks to the subsequent analysis, we find that the structures in the $x_1/x_2$ plot are artefacts of the gradient descent, whereas the ones seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots reflect genuine features of the manifold.
-
-	\subsection{Local analysis: extracting the dimension}
+Thanks to the analysis of sec.~\ref{sec:localanalysis} and~\ref{sec:AIS-SMC_application}, we find that the structures in the $x_1/x_2$ plot are artefacts of the gradient descent, whereas the ones seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots reflect genuine features of the manifold.
+
+	\subsection{Local analysis: extracting the dimension} \label{sec:localanalysis}
 	Once the gradient descent has been completed and the flat directions sampled, the next step is to identify the structure of the underlying manifold.
@@
 	From the preceding analysis, we conclude that the gradient descent procedure has produced a sampling of a single, connected, three-dimensional manifold.
-Therefore to characterise the manifold, we need two independent constraints on the coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
+Therefore to characterise the manifold, we need two independent constraints on the coordinates $(x_1,x_2,x_4,\tilde{x}_8,x_{10})$.
 If we have a look at the form of the potential, we can observe that if we use $x_{i} = e^{\tilde{x}_i}$, then, up to some potential global factor and field redefinitions, this potential is actually a polynomial on the $\vec{X}$ coordinates.
@@
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
-It takes approximately 10\,min to do a single run on a regular computer, including annealing loop and local search described in the previous section.
+It takes approximately 10\,min to do a single run on a regular computer, including the annealing loop and the local search described in the previous section.
 The code finds the following 8 different polynomials:
@@
 The dynamics depend strongly on the polynomial and we observe three different classes.
-In the first case, for $p_{1}, p_{2}$ and $p_{4}$, the first occurrences appear typically after only few dozen of epochs; and in the the second one, constituted of $p_{3}, p_{5}, p_{7}$ and $p_{8}$, after few hundreds of epochs.
-The last class has $p_{6}$ as its only representative.
+In the first case, for $p_{1}, p_{2}$ and $p_{3}$, the first occurrences appear typically after only few dozen of epochs; and in the the second one, constituted of $p_{4}, p_{5}, p_{6}$ and $p_{7}$, after few hundreds of epochs.
+The last class has $p_{8}$ as its only representative.
 This polynomial is very difficult to produce, and when it appears it is only towards the end of the runs.
@@
 In the previous section, we introduced a numerical method that enabled symbolic regression, yielding a set of polynomials that vanish on our dataset, as presented in eq.~\eqref{eq:pols}.
-We know from sec.~\ref{sec:results} that the manifold we are aiming at parametrising is three-dimensional.
-As the parameter space is of dimension $5$, we only need two constraints to define the solutions, and the eight polynomials of eq.~\eqref{eq:pols} are not independent.
+We know from sec.~\ref{sec:localanalysis} that the manifold we are aiming at parametrising is three-dimensional.
+As the parameter space is of dimension~$5$, we only need two constraints to define the solutions, and the eight polynomials of eq.~\eqref{eq:pols} are not independent.
 We are however only interested in finding an analytic parametrisation of the solutions manifold, and the easiest to find it is to solve the system
@@
 	As anticipated, this defines a three-parameter manifold.
-We tested analytically that $\nabla V = 0$ for any of these rules.
+We tested analytically that $\nabla V = 0$ for any of these rules, with additionnaly $\vec{y}=0$ (see eq.~\eqref{eq:defvecy}).
 The three-parameter manifold then defines a three-dimensional space of flat directions of the half-maximal supergravity scalar potential.\footnote{One might argue that only two of the eight polynomials are sufficient to fully characterise the solution.
@@
 We have presented a novel machine learning approach to systematically identify and characterise flat directions in supergravity scalar potentials.
-Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression on polynomials.
+Our methodology combines gradient descent sampling with an Annealed Sequential Monte Carlo sampler for symbolic regression on polynomials.
 We demonstrated its efficiency on a 5-scalar subsector of three-dimensional half-maximal supergravity, derived from the ${\rm AdS}_3 \times S^3$ compactification of six-dimensional ${\cal N}=(1,1)$ supergravity, or analogously of the ${\rm AdS}_3 \times S^3 \times T^4$ compactification of IIB supergravity.
@@
 Furthermore, upon 1000 runs the algorithm failed at finding any solution in only 3 cases, demonstrating the robustness of the method.
+We compared our method to the AIFeynman algorithm~\cite{Udrescu:2019mnk} in app.~\ref{app:AIFeynman}.
 
@@
 %
-where $\theta_{\bK\bL\bM\bN}=\theta_{[\bK\bL\bM\bN]}$ is fully antisymmetric, $\theta_{\bL\bK}=\theta_{(\bL\bK)}$ is symmetric and traceless, and $\theta$ is a scalar.
+where $\theta_{\bK\bL\bM\bN}=\theta_{[\bK\bL\bM\bN]}$ is fully antisymmetric, $\theta_{\bK\bL}=\theta_{(\bK\bL)}$ is symmetric and traceless, and $\theta$ is a scalar.
 The metric $\eta_{\bK\bL}$ is the SO(8,4)-invariant bilinear form used for index contractions.
@@
 %
-ensuring gauge invariance of the scalar kinetic terms. The embedding tensor also defines the scalar potential as following~\cite{Samtleben:2019zrh,Schon:2006kz}:
+ensuring gauge invariance of the scalar kinetic terms. The embedding tensor also defines the scalar potential as follows~\cite{Samtleben:2019zrh,Schon:2006kz}:
 %
@@
 
-\section{Comparison with AIFeynman}
+\section{Comparison with AIFeynman} \label{app:AIFeynman}
 We have used the state-of-the-art technique \texttt{AIFeynman} \cite{Udrescu:2019mnk} on our dataset, with again $x_8 = \exp(\tilde{x}_8)$, so as to identify polynomial expressions fitting the data.
@@
 \begin{equation}
-\texttt{+*-/><} \sim \texttt{\textbackslash R1}
+\texttt{+*-/><} \sim \texttt{\textbackslash R1}.
 \end{equation}
@@
 \begin{equation}
-	\texttt{x\_10 = 1.414213551821*(x\_4-((x\_1/x\_2)-((x\_1/x\_2)/x\_8))}
+	\texttt{x\_10 = 1.414213551821*(x\_4-((x\_1/x\_2)-((x\_1/x\_2)/x\_8))},
 \end{equation}
@@
 \begin{equation}
-	- \sqrt 2 x_1 + \sqrt 2 x_1 x_8 + x_2 x_8  x_{10} -\sqrt 2 x_2 x_4 x_8 = 0
-\end{equation}
-which corresponds to $p_1$ of Eq.
-\eqref{eq:pols}.
+	- \sqrt 2\, x_1 + \sqrt 2\, x_1 x_8 + x_2 x_8  x_{10} -\sqrt 2\, x_2 x_4 x_8 = 0,
+\end{equation}
+which corresponds to $p_1$ of eq.~\eqref{eq:pols}.
 While the AIFeynman code is able to recover one of the constraints, it exhibits several drawbacks compared to our method.
-First, it is significantly slower: it required 5685 seconds (1 hour 34 minutes and 45 seconds) compared to approximately 600 seconds for a single run of our ASMC algorithm \footnote{This time only accounts for the annealing loop, without the local search algorithm described in section \ref{sec:1runanalysis}.
-Furthermore, this computational time reflects the overhead incurred by verifying at each iteration whether the particles reproduce one of the polynomials specified in Eq.
-\eqref{eq:pols}, which substantially increases the overall execution time.
-In the absence of this verification step, the annealing loop would require approximately 350 seconds on standard computational hardware.}.
-Moreover, the AIFeynman framework is based on expressing one variable as a function of the others, which assumes the invertibility of the underlying relation.
-In general, this is not guaranteed for the class of polynomials in Eq.
-\eqref{eq:pols}, and obtaining a closed-form inverse can be nontrivial or even impossible for higher-degree expressions.
+First, it is significantly slower: it required 5685 seconds (1 hour 34 minutes and 45 seconds) compared to approximately 600 seconds for a single run of our ASMC algorithm.\footnote{This time only accounts for the annealing loop, without the local search algorithm described in sec.~\ref{sec:1runanalysis}.
+Furthermore, this computational time reflects the overhead incurred by verifying at each iteration whether the particles reproduce one of the polynomials specified in eq.~\eqref{eq:pols}, which substantially increases the overall execution time.
+In the absence of this verification step, the annealing loop would require approximately 350 seconds on standard computational hardware.} Moreover, the AIFeynman framework is based on expressing one variable as a function of the others, which assumes the invertibility of the underlying relation.
+In general, this is not guaranteed for the class of polynomials in eq.~\eqref{eq:pols}, and obtaining a closed-form inverse can be nontrivial or even impossible for higher-degree expressions.
 In our case, each polynomial involves at most quadratic terms in any single variable, ensuring invertibility, but this property would not hold for more complex models.
 In addition, AIFeynman is limited to recovering one constraint per run, whereas our ASMC method can discover multiple constraints simultaneously.
-This is reflected in our results, where each run identified an average of 2.2 polynomials, with up to 4 found in the best case.
+This is reflected in our results, where each run identified an average of 2.2 polynomials, with up to 4 found in the best cases.
 Finally, the brute-force regression strategy used by AIFeynman makes it less effective for identifying higher-degree polynomials, whose complexity increases the search difficulty.
-In contrast, our method treats all polynomials as equally probable, regardless of their degree, enabling it to uncover more intricate structures more efficiently \footnote{Note that we do not claim that we have used the AIFeynman in the most optimal way.}.
+In contrast, our method treats all polynomials as equally probable, regardless of their degree, enabling it to uncover more intricate structures more efficiently.\footnote{Note that we do not claim that we have used the AIFeynman in the most optimal way.}
 %\newpage

### 2025-10-31 Draft_MLFlatDirections.tex
Substantial modifications of sec. 3.1, and 3.2 and 4 marginally following comments by Jason and Henning.

@@
 	The aim of symbolic regression is to uncover interpretable mathematical expressions that best describe the embedding of these loci of solutions. 
-	In the present context, the form of the supergravity potential \eqref{eq:scalarpotential} determining the solutions implies that the loci can be defined through polynomials $p_{m}$ such that $p_{m}\big(\vec{x}^{(i)}\big) = 0$, with $i \in \{1, \dots, n_{\rm points}\}$.
+	In the present context, the form of the supergravity potential \eqref{eq:scalarpotential} determining the solutions implies that the loci can be defined through polynomials $z_{m}$ such that $z_{m}\big(\vec{x}^{(i)}\big) = 0$, with $i \in \{1, \dots, n_{\rm points}\}$.
 Such polynomials will be called ``annihilating polynomials'' in the following.
@@
 
-	To address these challenges, we formulate the search for annihilating polynomials as a determination of a probability density on the space of polynomials that stresses higher probabilities on polynomials $p$ that minimise the error
-	\begin{equation}
-		\sum_{i=1}^{n_{\rm points}}p\big(\vec{x}^{(i)}\big)^{2}.
-	\end{equation}
-	Polynomials sampled from this density would thus be good approximations to annihilating polynomials.
-Such a probability density is \textit{a priori} hard to find, but can be approximated using algorithms based on Sequential Important Sampling~\cite{Doucet2001,Liu2004} such as Sequential Monte Carlo samplers~\cite{del2006sequential}.
+	To address these challenges, we formulate the search for annihilating polynomials as a determination of a probability density on the space of polynomials $E_{\rm pol}$ that stresses higher probabilities on polynomials~$z$ that minimise the error
+	\begin{equation}
+		\sum_{i=1}^{n_{\rm points}}z\big(\vec{x}^{(i)}\big)^{2}.
+	\end{equation}
+	Polynomials sampled from this density would thus be good approximations to annihilating polynomials. Such a probability density can take the form
+	\begin{equation}
+		\pi(z) = \frac{e^{-L(z)}}{Z},
+	\end{equation}
+	with $L(z)$ a loss function chosen to be minimal on annihilating polynomials (its design will be discussed at the end of the sec.~\ref{sec:detailedAISSMC}) and $Z$ a normalisation constant.
+However, although one could in principle evaluate $\pi$ on a given polynomials, it is highly non trivial to draw a sample from it.
+Such a sample can be approximated using algorithms based on Sequential Important Sampling~\cite{Doucet2001,Liu2004} such as Sequential Monte Carlo samplers~\cite{del2006sequential}.
 They are inspired from Important Sampling (IS)~\cite{osti_4441935,RobertCasella2004}, a method to parametrise expectation values with respect to a target distribution $\pi$, that can be evaluated pointwise, but from which one does not know how to draw samples.
-IS uses another, typically simpler, distribution $\eta$ (called importance distribution) that one knows how to draw from.
+IS uses another, typically simpler, distribution $\eta$ (called importance distribution) that one knows how to draw from (the easiest would be the distribution that assigns equal probability to all polynomials).
 It is based on the observation that the expectation value
 	\begin{equation}
-		\mathbb{E}_{\pi}[f] = \int f(z)\pi(z)\ \d z,
+		\mathbb{E}_{\pi}[f] = \int_{E_{\rm pol}} f(z)\pi(z)\ \d z,
 	\end{equation}
 	for some function $f$ with respect to $\pi$, can be computed from the expectation $\mathbb{E}_{\eta}[w f]$, now computed with respect to the distribution $\eta$, with unnormalised weights $w = \pi/\eta$.
-Therefore, one can estimate $\mathbb{E}_{\pi}[f]$ from a Monte Carlo method: we draw a sample $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\eta$ and use the weighted average
+Therefore, one can estimate $\mathbb{E}_{\pi}[f]$ from a Monte Carlo method: we draw a sample of polynomials $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\eta$ and use the weighted average
 	\begin{equation}
@@
 	\end{equation}
-	Stated differently, the target distribution $\pi$ can be approximated from a weighted collection of particles $\{z^{(k)},w^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ drawn from the importance distribution $\eta$ :
+	Stated differently, the target distribution $\pi$ can be approximated from a weighted collection of polynomials $\{z^{(k)},w^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ drawn from the importance distribution $\eta$ :
 	\begin{equation}
@@
 The accuracy of this estimation depends on the size of the sample and, crucially, on the choice of the importance distribution $\eta$, that needs to be close enough to $\pi$.
+In the following we will often use ``particles'' to denote the polynomials in the sample, as done in the IS literature.
 
@@
 In order to fix this point, we employ an Annealed Sequential Monte Carlo sampler (ASMC)~\cite{zimmermann2021nested,syed2024optimisedannealedsequentialmonte}, \textit{i.e.} a Sequential Monte Carlo sampler (SMC)~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo} enhanced by Annealed Importance Sampling (AIS)~\cite{neal1998annealedimportancesampling}.
+We give here a general overview of the method and defer the details to sec.~\ref{sec:detailedAISSMC}.
 SMC aims at estimating $\pi$ sequentially from multiple intermediate distributions $\pi_{n}$ that smoothly transition from an initial, tractable distribution $\pi_{0}$ (chosen to be easy to sample from) to the complex distribution $\pi$.
+Here we consider the sequence
+	\begin{equation}
+		\pi_{n}(z) = \pi_{0}(z)\,\frac{e^{-\beta_{n}\,L(z)}}{Z_{n}},
+	\end{equation}
+	with $\beta_{0}=0$, $(\beta_{n})$ tending towards $1$ and normalising constants $Z_{n}$.
 These distributions are approximated by weighted samples of particles $\big\{z^{(k)}_{n},w^{(k)}_{n}\big\}$ approximating $\pi_{n}$:
@@
 	with  $\displaystyle \tilde{w}^{(k)}_n  = w^{(k)}_n/\sum_{k=1}^{n_{\rm particles}} w^{(k)}_{n}$ the normalised weights.
-The particles are incrementally deformed and reweighed using a Markov kernel to gradually sample the target distribution $\pi$.
-This process is guided by a temperature-like parameter that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
+The particles are incrementally deformed and reweighed to gradually sample the target distribution $\pi$.
+These deformations, for example a perturbation of the coefficients or a modification of a given monomial, are performed using a Markov kernel $q\big(z_{n}\vert z_{n-1}\big)$ that defines the probability to get $z_{n}$ when the current particle is $z_{n-1}$ (its definition will be discussed in sec.~\ref{sec:detailedAISSMC}).
+The weights are then updated:
+	\begin{equation}
+		w_{n}^{(k)} = w_{n-1}^{(k)}\,\alpha_{n}^{(k)},
+	\end{equation}
+	with the incremental importance weights $\alpha_{n}^{(k)}$ defined as
+	\begin{equation}
+			\alpha^{(k)}_{n} = \frac{\exp\Big(-\beta_{n+1}L\big(z_{n+1}^{(k)}\big)\Big)}{\exp\Big(-\beta_{n}L\big(z_{n}^{(k)}\big)\Big)}\,\frac{q\big(z^{(k)}_{n}\vert z^{(k)}_{n+1}\big)}{q\big(z^{(k)}_{n+1}\vert z^{(k)}_{n}\big)}.
+	\end{equation}
+	This process is guided by the temperature-like parameter $1/\beta_{n}$ that gradually emphasises the data likelihood, allowing for more efficient and tunable exploration of the polynomials landscape.
 The approximation procedure can be summed up as follows.
@@
 We gradually mutate them with an annealing procedure to get a set of $\{z_n^{(k)},w_n^{(k)}\}$, which are used to parametrise $\pi_n$.
-As $n$ increases, the procedure converges such that the particles sample the target distribution $\pi$.
+As $n$ increases, the procedure converges such that the particles sample the target distribution $\pi$, \textit{i.e.} the polynomials $z_n^{(k)}$ tends to annihilating polynomials.
 
@@
 	Let us now explain in more detail the procedure, based on ref.~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo,Dai03072022}. 
-	The goal is to obtain particles sampled from a probability distribution $\pi(z)$, where $z$ runs over a space of polynomials $E$, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
+	The goal is to obtain particles sampled from a probability distribution $\pi(z)$, where $z$ runs over a space of polynomials $E_{\rm pol}$, that assigns high probabilities to those polynomials that annihilate the data, and therefore will be used to identify their symbolic expressions.
 We restrict ourselves to polynomials of maximum degree ${\rm max}_{\rm degree}$.
 Given the number of variables $n_{\rm var}$, this fixes the number of different possible monomials to $\binom{{\rm max}_{\rm degree}+n_{\rm var}}{{\rm max}_{\rm degree}}$.
-We further restrict $E$ to include only polynomials with a maximum number of ${\rm max}_{\rm mon}$ monomials.
-The space $E$ is then finite dimensional.
+We further restrict $E_{\rm pol}$ to include only polynomials with a maximum number of ${\rm max}_{\rm mon}$ monomials.
+The space $E_{\rm pol}$ is then finite dimensional.
 
@@
 On every annealing step, $\pi_n$ is defined in terms of an unnormalised density $\gamma_n$ and a normalisation constant as $\pi_n(z) = \gamma_n(z)/Z_n$.
-The unnormalised density at level $n$ is given in terms of a prior distribution $\pi_0(z)$ over the space $E$ of polynomials and a loss function $L(z)$, as
+The unnormalised density at level $n$ is given in terms of a prior distribution $\pi_0(z)$ over the space $E_{\rm pol}$ of polynomials and a loss function $L(z)$, as
 		\begin{equation}\label{eq:gamman}
@@
 	where the inverse temperature constants $\beta_n$ are taken to evolve monotonically as $\beta_0 = 0 < \beta_1 <\dots< \beta_{n_{\rm epochs}}$.
-The importance given to each polynomial $z$ is thus updated at each step, with polynomials $z$ with high loss being disfavoured.
+The importance given to each polynomial $z$ is thus updated at each step, with polynomials~$z$ with high loss being disfavoured.
 This update is controlled by the inverse temperature constants, enabling deeper exploration during the early stages and protecting the procedure from being trapped in local minima.
-The loss function is chosen to be minimal on annihilating polynomials and its design will be discussed at the end of the section.
-We choose the prior distribution $\pi_{0}$ to be flat on the space of polynomials $E$, giving equal importance to all of them, which makes easy the initial sampling of the weighted particles $\big\{z^{(k)}_{0},w^{(k)}_{0} = 1/n_{\rm particles}\big\}$.\footnote{Note that with this choice there is a higher probability to draw polynomials with multiple monomials.} The random draw is done on the monomials of each polynomials, and the coefficients are chosen randomly in the range $[-2,2]$.
-
-	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}\big) = \tilde{\gamma}_{n}\big(z_{0:n}\big)/\tilde{Z}_{n}$ defined on $E^{n+1}$, with $z_{0:n} = \big(z_{0},\ldots,z_{n}\big)$, that describes the global trajectory of the particles until step $n$.
+We refer to eq.~\eqref{eq:lossreg} for the definition of the loss function $L(z)$.
+We choose the prior distribution $\pi_{0}$ to be flat on the space of polynomials $E_{\rm pol}$, giving equal importance to all of them, which makes easy the initial sampling of the weighted particles $\big\{z^{(k)}_{0},w^{(k)}_{0} = 1/n_{\rm particles}\big\}$.\footnote{Note that with this choice there is a higher probability to draw polynomials with multiple monomials.} The random draw is done on the monomials of each polynomials, and the coefficients are chosen randomly in the range $[-2,2]$.
+
+	At each epoch $n\geq1$, we do not directly approximate $\pi_{n}$, but rather a distribution $\tilde{\pi}_{n}\big(z_{0:n}\big) = \tilde{\gamma}_{n}\big(z_{0:n}\big)/\tilde{Z}_{n}$ defined on $E_{\rm pol}^{n+1}$, with $z_{0:n} = \big(z_{0},\ldots,z_{n}\big)$, that describes the global trajectory of the particles until step $n$.
 $\tilde{\gamma}_{n}$ is defined thanks to a backward propagation kernel $K\big(z_{i-1}\vert z_{i}\big)$:
@@
 	\end{equation}
-	This way, the distribution $\tilde{\pi}_{n}$ describes $\pi_{n}$ as well as the path that followed the particles from epochs $0$ to $n$.
+	This way, the distribution $\tilde{\pi}_{n}$ describes $\pi_{n}$ as well as the path that followed the particles from epochs $0$ to~$n$.
 $\tilde{\pi}_{n}$ evaluates not only the probability that the particle is in a given state $z_{n}$, but also the probability that the particle has followed the path from $z_{0}$ to $z_{n}$.
@@
 	\end{equation}
-	with the incremental importance weights $\alpha_{n}^{(k)}$ defined as
+	with the incremental importance weights
 	\begin{equation}	\label{eq: incremental_importance}
@@
 
-	For the implementation of the forward propagation kernel, we perform an AIS-style MCMC algorithm.
+	For the implementation of the forward propagation kernel $q\big(z_{n}\vert z_{n-1}\big)$, we perform an AIS-style MCMC algorithm.
 On every epoch, we make some move in the space of polynomials, and then accept or reject those new polynomials based on a fixed rate.
@@
 	\end{equation}
-	We then draw $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A\big(z_{n+1}^{(k)},z_{n}^{(k)}\big)$ and reject it otherwise.
+	We then draw a number $u\sim \mathrm{Uniform}(0,1)$, accept the new particle if $u<A\big(z_{n+1}^{(k)},z_{n}^{(k)}\big)$ and reject it otherwise.
 This way we accept systematically all moves that increase the weights, and some of those that lower the weights, allowing for some exploration of the space of polynomials.	Once the particles have been mutated, the evolution of the weights is computed using eq.~\eqref{eq:weightsupdate}.
@@
 
-	\begin{figure}[!b]
+	\begin{figure}
 		\centering
@@
 
-	\begin{figure}[!b]
+	\begin{figure}[t!]
 		\centering
@@
 		\caption{Triangular plot showing all $2d$ projections and $1d$ histograms of the data after the gradient descent.}
+		\vspace{-0.5cm}
 		\label{triangular_plot_1_2_4_8_10}
@@
 The size of the different points has been adjusted to facilitate the visualisation.
-From visual inspection, it appears that the unassigned (blue) points lie mostly on the boundary of the sampled region.
+From visual inspection, it appears that the unassigned (yellow) points lie mostly on the boundary of the sampled region.
 We therefore interpret their unassigned status not as evidence of belonging to another manifold, but rather as a result of insufficient local density near the edges of the dataset.
@@
 
-	\begin{figure}
+	\begin{figure}[t!]
 		\centering
@@
 		\subfigure{\label{fig:3dx1x4x8}}
-		\vspace{-0.5cm}
-		\caption{3d projections of the data set in selected coordinates: (a) $(x_4, x_8, x_{10})$ and (b) $(x_1, x_4, x_8)$.
+		\vspace{-1cm}
+		\caption{3d projections of the data set in selected coordinates: (a) $(x_4, \tilde{x}_8, x_{10})$ and (b) $(x_1, x_4, \tilde{x}_8)$.
 The colors are assigned by the clustering algorithm: the red points correspond to the cluster, while the yellow points were not assigned to any cluster.
@@
 Therefore, the components of $\left.\nabla V\right|_{\vec{y}=0}$ are also polynomials on the $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$ coordinates.
-We conclude that the constraints on $\vec{x}$ we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those.
+We conclude that the constraints on $\vec{x}$ we are looking for are polynomial constraints of the form $z(\vec{x}) = 0$, and that there should be at least two of those.
 Of course if one takes directly the gradient of \eqref{eq:scalarpotential}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others.
@@
 	\begin{equation}	\label{eq:sample10000adaptativetemp}
-		\begin{aligned}
-			&\texttt{n\_points = 10,000},\\
-			&\texttt{n\_epochs = 1000},\\
-			&\texttt{n\_particles = 1000},\\
-			&\texttt{beta0  = 1e-6}, \\
-			&\texttt{p\_{shift} = 0.5},\\
-			&\texttt{p\_{multiply} = 0.25},\\
-			&\texttt{p\_{divide} = 0.25},\\
-			&\texttt{lambda = 1000},\\
-			&\texttt{sigma = 0.1}.
-		\end{aligned}
+		% \begin{aligned}
+		% 	&\texttt{n\_points = 10,000},\\
+		% 	&\texttt{n\_epochs = 1000},\\
+		% 	&\texttt{n\_particles = 1000},\\
+		% 	&\texttt{beta0  = 1e-6}, \\
+		% 	&\texttt{p\_{shift} = 0.5},\\
+		% 	&\texttt{p\_{multiply} = 0.25},\\
+		% 	&\texttt{p\_{divide} = 0.25},\\
+		% 	&\texttt{lambda = 1000},\\
+		% 	&\texttt{sigma = 0.1}.
+		% \end{aligned}
+		\begin{array}{lllll}
+			\texttt{n\_points = 10,000}, & \qquad \qquad &  \texttt{p\_{shift} = 0.5}, & \qquad \qquad & \texttt{beta0  = 1e-6}, \\
+			\texttt{n\_epochs = 1000}, & &\texttt{p\_{multiply} = 0.25}, & & \texttt{lambda = 1000}, \\
+			\texttt{n\_particles = 1000}, & & \texttt{p\_{divide} = 0.25},- & & \texttt{sigma = 0.1}.\\
+		\end{array}
 	\end{equation}
@@
 	\subsubsection{Analysis of a typical run}\label{sec:1runanalysis}
-	After a run, the 1000 particles are typically distributed into less than 50 different types of polynomials.
+	After a run, the 1000 polynomials are typically distributed into less than 50 different types of polynomials.
 Each particles of a given type share the same monomials, but their coefficients fluctuate a bit.
 We analyse them using the following procedure.
-We select the particle that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}), we fine-tune the coefficients by running a quick exploitation phase of 10,000 steps during which we randomly select a coefficient and modify it with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma')$, with $\sigma'=0.01$, and keep the new particle only if the loss function (without the regularisation) is getting smaller.
+We select the polynomial that features the minimal loss (without the regularisation, $\lambda=0$, see eq.~\eqref{eq:lossreg}), we fine-tune the coefficients by running a quick exploitation phase of 10,000 steps during which we randomly select a coefficient and modify it with a perturbation $\epsilon \sim \mathcal{N}(0, \sigma')$, with $\sigma'=0.01$, and keep the new polynomial only if the loss function (without the regularisation) is getting smaller.
 There are two possible outputs after this phase.
-(i)~The coefficients stay finite, and the particle is a candidate annihilator polynomial.
-We then filter out all  particles of the same type as this candidate, as they will ultimately give the same polynomial.
+(i)~The coefficients stay finite, and the polynomial is a candidate annihilator polynomial.
+We then filter out all  polynomials of the same type as this candidate, as they will ultimately give the same polynomial.
 Or (ii), the coefficients are just getting smaller and smaller during the exploitation phase, indicating that the only way to minimize the loss with the given monomials is to have very small coefficients.
-The particle is then disregarded.
-We repeat the same steps on the best particles of the remaining set until we have explored all particles.
-
-	Here is an example for a given run. The best particle after the Annealing loop is
+The polynomial is then disregarded.
+We repeat the same steps on the best polynomials of the remaining set until we have explored all polynomials.
+
+	Here is an example for a given run. The best polynomial after the Annealing loop is
 	 \begin{equation}
@@
 	 \end{equation}
-	 with loss $L^{(\lambda = 0)} \simeq 2.1 \times 10^{3}$. The coefficients have been rounded to the nearest thousandth. After 10,000 steps of exploitation, this particle becomes
+	 with loss $L^{(\lambda = 0)} \simeq 2.1 \times 10^{3}$. The coefficients have been rounded to the nearest thousandth. After 10,000 steps of exploitation, this polynomial becomes
 	  \begin{equation}
@@
 We are in case (i), the polynomial is a candidate annihilator polynomial.
-After filtering out the 971 particles that are of the same type, the next best particle is
+After filtering out the 971 polynomials that are of the same type, the next best polynomial is
 	 \begin{equation}
@@
 The loss is low only because the coefficients are themselves very low.
-This is an example of case (ii), we disregard this particle.
-Reproducing similar steps for the remaining particles, we get some uninteresting particles and two new candidate polynomials (with normalised coefficients):
+This is an example of case (ii), we disregard this polynomial.
+Reproducing similar steps for the remaining polynomials, we get some uninteresting polynomials and two new candidate polynomials (with normalised coefficients):
 	 \begin{subequations}
@@
 	\subsubsection{Statistics}
-
-	\begin{table}[b!]
-		\centering
-		\renewcommand{\arraystretch}{1.3}
-		\begin{tabular}{c|ccccccccc}
-			& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$  & $p_{8}$&  $\varnothing$  \\\hline\hline
-			Frequency & 92.6\% & 75.0\% & 51.9\% & 1.7\% & 0.2\% & 0.7\% & 0.7\% & 0.3\% & 0.1\% \\
-			Maximum \# of representatives & 1000 & 1000 & 991 & 869 & 879 & 710 & 207 & 18 & --
-		\end{tabular}
-		\caption{Statistics of the ability of the ASMC algorithm to produce the polynomials~\eqref{eq:pols} on 1000 runs with parameters~\eqref{eq:sample10000adaptativetemp} and~\eqref{eq:parampol}.
-The frequencies represent the percentage of runs featuring a given polynomial in its outputs, and the maximum number of representatives gives the maximum number of particles representing the polynomial in a given run.
-The column $\varnothing$ counts the runs that failed to produce any annihilator polynomial.}
-		\label{table:results}
-	\end{table}
-
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
-It takes approximately 10\,min to do a single run on a regular computer, including the annealing loop and the local search described in the previous section.
+It takes approximately 10\,min to do a single run on a regular computer using CPU and about 20\,s using GPU, including the annealing loop and the local search described in the previous section.
 The code finds the following 8 different polynomials:
@@
 	 \begin{align}
-	   p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\[4pt]
-	   p_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\[4pt]
-	   p_{3} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
+	   z_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}x_8 + x_{2}x_8x_{10} - \sqrt{2}\,x_{2}x_{4}x_8,\\[4pt]
+	   z_{2} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}x_8x_{10}^{2},\\[4pt]
+	   z_{3} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}x_8 + \sqrt{2}\,x_{1}\,x_{4} + x_{1}x_8x_{10}
 	   		- x_{2}x_{4}x_8x_{10},\\[4pt]
-	   p_{4} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
+	   z_{4} &= 2\,x_{2} - 2\,x_{2}x_8 + \sqrt{2}\,x_{1}x_8x_{10} + 2\,x_{1}x_{4}x_8
 	   		- 2\,x_{2} x_{4}^{2}x_8,\\[4pt]
-	   p_{5} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
+	   z_{5} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
 	   		- x_{2}^{2}x_{10}, \\[4pt]
-	   p_{6} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
+	   z_{6} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}x_8 + \sqrt{2}\,x_{2}x_{10}
 	   		+ x_{1}x_8x_{10}^{2},\\[4pt]
-	   p_{7} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\[4pt]
-	   p_{8} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
+	   z_{7} &= -2 + 4\,x_{8} - 2\,x_8^2 + 2\,x_{4}^2 x_8 - x_8^2 x_{10}^2,\\[4pt]
+	   z_{8} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}x_8 + \sqrt{2}\,x_{2}x_{10} 
 	   		- \sqrt{2}\,x_{2}x_8x_{10} +  x_{1}x_8x_{10}^{2},
@@
 
-	\begin{figure}
+	\begin{table}
+		\centering
+		\renewcommand{\arraystretch}{1.3}
+		\begin{tabular}{c|ccccccccc}
+			& $z_{1}$ & $z_{2}$ & $z_{3}$ & $z_{4}$ & $z_{5}$ & $z_{6}$ & $z_{7}$  & $z_{8}$&  $\varnothing$  \\\hline\hline
+			Frequency & 92.6\% & 75.0\% & 51.9\% & 1.7\% & 0.2\% & 0.7\% & 0.7\% & 0.3\% & 0.1\% \\
+			Maximum \# of representatives & 1000 & 1000 & 991 & 869 & 879 & 710 & 207 & 18 & --
+		\end{tabular}
+		\caption{Statistics of the ability of the ASMC algorithm to produce the polynomials~\eqref{eq:pols} on 1000 runs with parameters~\eqref{eq:sample10000adaptativetemp} and~\eqref{eq:parampol}.
+The frequencies represent the percentage of runs featuring a given polynomial in its outputs, and the maximum number of representatives gives the maximum number of particles representing the polynomial in a given run.
+The column $\varnothing$ counts the runs that failed to produce any annihilator polynomial.}
+		\label{table:results}
+	\end{table}
+
+	\begin{figure}[b!]
 		\centering
@@
 
-	\begin{figure}[b!]
+	We have tracked the appearance of the polynomials~\eqref{eq:pols} during each of the 1000 runs.
+To do so, we have counted at each epoch the number of particles including the same monomials as the annihilator polynomials.\footnote{Thus, a particle featuring the same monomials as one of the polynomials~\eqref{eq:pols} will be counted, even if the coefficients do not match, and if there are additional monomials.} The total number of particles reproducing at least one of the annihilator polynomials listed in eq.~\eqref{eq:pols} is plotted in fig.~\ref{fig:count_pol_all_beta}, together with the evolution of the inverse temperature $\beta$, both averaged on the 1000 runs.
+The proportion of annihilator polynomials among the particles start to be significant after approximately 700 epochs.
+It then increases quickly and, towards the end of each run, an average of $88\%$ of the particles do reproduce one of the annihilator polynomials, with a standard deviation of $20\%$.
+The evolution of this proportion is explained by the structure of the method: the code favours the particles with highest weights, and thus those that cause a significant improvement to the loss function, at each resampling.
+Once an annihilator polynomials is reached, it colonises larger and larger proportions of the particles at each resampling.
+
+	\begin{figure}
 		\centering
@@
 
-	We have tracked the appearance of the polynomials~\eqref{eq:pols} during each of the 1000 runs.
-To do so, we have counted at each epoch the number of particles including the same monomials as the annihilator polynomials.\footnote{Thus, a particle featuring the same monomials as one of the polynomials~\eqref{eq:pols} will be counted, even if the coefficients do not match, and if there are additional monomials.} The total number of particles reproducing at least one of the annihilator polynomials listed in eq.~\eqref{eq:pols} is plotted in fig.~\ref{fig:count_pol_all_beta}, together with the evolution of the inverse temperature $\beta$, both averaged on the 1000 runs.
-The proportion of annihilator polynomials among the particles start to be significant after approximately 700 epochs.
-It then increases quickly and, towards the end of each run, an average of $88\%$ of the particles do reproduce one of the annihilator polynomials, with a standard deviation of $20\%$.
-The evolution of this proportion is explained by the structure of the method: the code favours the particles with highest weights, and thus those that cause a significant improvement to the loss function, at each resampling.
-Once an annihilator polynomials is reached, it colonises larger and larger proportions of the particles at each resampling.
-
 	The evolution of the inverse temperature is dictated by eq.~\eqref{eq:eqadaptivetemperatureschedule}.
@@
 The dynamics depend strongly on the polynomial and we observe three different classes.
-In the first case, for $p_{1}, p_{2}$ and $p_{3}$, the first occurrences appear typically after only few dozen of epochs; and in the the second one, constituted of $p_{4}, p_{5}, p_{6}$ and $p_{7}$, after few hundreds of epochs.
-The last class has $p_{8}$ as its only representative.
+In the first case, for $z_{1}, z_{2}$ and $z_{3}$, the first occurrences appear typically after only few dozen of epochs; and in the the second one, constituted of $z_{4}, z_{5}, z_{6}$ and $z_{7}$, after few hundreds of epochs.
+The last class has $z_{8}$ as its only representative.
 This polynomial is very difficult to produce, and when it appears it is only towards the end of the runs.
@@
 
-	\begin{figure}[b!]
+	\begin{figure}
 		\centering
@@
 	\begin{equation}\label{eq:solvepol}
-		p_i = 0, \quad \forall i \in {1,\dots,8}.
+		z_i = 0, \quad \forall i \in {1,\dots,8}.
 	\end{equation}
@@
 	\begin{equation}
-		\theta = \pm\frac{1}{2}\,\arccos\left(-1 + \sqrt{3} + \frac{- 7 + 4\sqrt{3})}{2\,r^2}\right) \quad {\rm and} \quad r \geq \sqrt{-2+\frac{7}{2\sqrt{3}}}.
+		\theta = \pm\frac{1}{2}\,\arccos\left(-1 + \sqrt{3} + \frac{- 7 + 4\sqrt{3}}{2\,r^2}\right) \quad {\rm and} \quad r \geq \sqrt{-2+\frac{7}{2\sqrt{3}}}.
 	\end{equation}

### 2025-11-04 Draft_MLFlatDirections.tex
Updates before submitting to arxiv.

@@
 	\begin{equation}
-		\pi(z) = \frac{e^{-L(z)}}{Z},
-	\end{equation}
-	with $L(z)$ a loss function chosen to be minimal on annihilating polynomials (its design will be discussed at the end of the sec.~\ref{sec:detailedAISSMC}) and $Z$ a normalisation constant.
+		\pi(z) \propto e^{-L(z)},
+	\end{equation}
+	with $L(z)$ a loss function chosen to be minimal on annihilating polynomials (its design will be discussed at the end of the sec.~\ref{sec:detailedAISSMC}).
 However, although one could in principle evaluate $\pi$ on a given polynomials, it is highly non trivial to draw a sample from it.
@@
 	for some function $f$ with respect to $\pi$, can be computed from the expectation $\mathbb{E}_{\eta}[w f]$, now computed with respect to the distribution $\eta$, with unnormalised weights $w = \pi/\eta$.
-Therefore, one can estimate $\mathbb{E}_{\pi}[f]$ from a Monte Carlo method: we draw a sample of polynomials $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\eta$ and use the weighted average
+Therefore, one can estimate $\mathbb{E}_{\pi}[f]$ from a Monte Carlo method: we draw a sample of polynomials $\{z^{(k)}\}_{k\in\llbracket 1, n_{\rm particles}\rrbracket}$ from $\eta$ and use the weighted average\footnote{Elements of this sample are often referred to as particles in the specialised literature~\cite{del2006sequential,DoucetTutorial,naesseth2024elementssequentialmontecarlo,Dai03072022}.}
 	\begin{equation}
@@
 		\vspace{-1cm}
-		\caption{(a) Histogram of the the norm of the gradient for each point ($x$-axis is in $\log$ scale).
+		\caption{(a) Histogram of the norm of the gradient for each point ($x$-axis is in $\log$ scale).
 (b)~Histogram of the distance of the value of the potential to $V(0)$ for each point ($x$-axis is in $\log$ scale).
@@
 			\texttt{n\_epochs = 1000}, & &\texttt{p\_{multiply} = 0.25}, & & \texttt{lambda = 1000}, \\
-			\texttt{n\_particles = 1000}, & & \texttt{p\_{divide} = 0.25},- & & \texttt{sigma = 0.1}.\\
+			\texttt{n\_particles = 1000}, & & \texttt{p\_{divide} = 0.25}, & & \texttt{sigma = 0.1}.\\
 		\end{array}
@@
 	We performed 1000 independent runs with the same parameters as above, each involving 1000 particles.
-It takes approximately 10\,min to do a single run on a regular computer using CPU and about 20\,s using GPU, including the annealing loop and the local search described in the previous section.
-The code finds the following 8 different polynomials:
+It takes approximately 10\,min to do a single run on a regular computer using CPU, including the annealing loop and the local search described in the previous section.\footnote{While writing the paper, we adapted the code to run with GPU.
+With a single NVIDIA Tesla P100 12 GB, it now takes 20\,s to do a single run.} The code finds the following 8 different polynomials:
 	\begin{subequations} \label{eq:pols}
@@
 The dynamics depend strongly on the polynomial and we observe three different classes.
-In the first case, for $z_{1}, z_{2}$ and $z_{3}$, the first occurrences appear typically after only few dozen of epochs; and in the the second one, constituted of $z_{4}, z_{5}, z_{6}$ and $z_{7}$, after few hundreds of epochs.
+In the first case, for $z_{1}, z_{2}$ and $z_{3}$, the first occurrences appear typically after only few dozen of epochs; and in the second one, constituted of $z_{4}, z_{5}, z_{6}$ and $z_{7}$, after few hundreds of epochs.
 The last class has $z_{8}$ as its only representative.
@@
 This also induces a competition between the annihilator polynomials, the ones that get bettered the more easily (typically those with fewest terms) are favoured.
-This mechanism explains the decrease in the averaged population of the polynomial $p_{8}$ observed after 800 epochs in fig.~\ref{fig:count_pol_indiv}.
+This mechanism explains the decrease in the averaged population of the polynomial $z_{8}$ observed after 800 epochs in fig.~\ref{fig:count_pol_indiv}.
 
@@
 We would like to thank Magdalena Larfors, whose talk on Machine Learning at the kick-off meeting of the COST action ``Fundamental challenges in theoretical physics'' in Padova in May 2024 triggered this project.
-We are thankful to Nelly Pustelnik, Jason Reneuve, Henning Samtleben and Jan-Willem van de Meent for inspiring discussions.
+We are thankful to Nelly Pustelnik, Jason Reneuve, Henning Samtleben, Dave Tennyson and Jan-Willem van de Meent for inspiring discussions.
 We thank especially Jan-Willem van de Meent for guiding us to the relevant numerical methods.
-\ce{Funding Bastien?} \ce{Gabriel: Mitchell foundations and Cook branch.}
+GL was supported by endowment funds from the Mitchell Family Foundation during the initial stages of this project.
+The work of BD is supported by the Alexander von Humboldt foundation.
 
@@
 \end{equation}
-which corresponds to $p_1$ of eq.~\eqref{eq:pols}.
+which corresponds to $z_1$ of eq.~\eqref{eq:pols}.
 While the AIFeynman code is able to recover one of the constraints, it exhibits several drawbacks compared to our method.
